### 2013-08-28 paper/paper.tex
add inital paper tex file. modified git ignore

%% PNAStwoS.tex
%% Sample file to use for PNAS articles prepared in LaTeX
%% For two column PNAS articles
%% Version: Apr 15, 2008

%% BASIC CLASS FILE
\documentclass{pnastwo}

%% ADDITIONAL OPTIONAL STYLE FILES
%\usepackage[dvips]{graphicx}
%\usepackage{pnastwof}
\usepackage{amssymb,amsfonts,amsmath}

%% OPTIONAL MACRO DEFINITIONS
\def\s{\sigma}

%%%%%%%%%%%%
%% For PNAS Only:
\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
\copyrightyear{2008}
\issuedate{Issue Date}
\volume{Volume}
\issuenumber{Issue Number}
%\setcounter{page}{2687} %Set page number here if desired
%%%%%%%%%%%%

\begin{document}

\title{Almost sharp fronts for the surface geostrophic equation}

\author{Roberta Graff\affil{1}{University of Cambridge, Cambridge,
United Kingdom},
Javier de Ruiz Garcia\affil{2}{Universidad de Murcia, Bioquimica y Biologia
Molecular, Murcia, Spain},
\and
Franklin Sonnery\affil{2}{}}

\contributor{Submitted to Proceedings of the National Academy of Sciences
of the United States of America}

\maketitle

\begin{article}
\begin{abstract}
We use heat kernels or eigenfunctions of the Laplacian to construct
local coordinates on large classes of Euclidean domains and Riemannian
manifolds (not necessarily smooth, e.g. with $\mathcal{C}^\alpha$
metric). These coordinates are bi-Lipschitz on large neighborhoods of
the domain or manifold, with  constants controlling the distortion and
the size of the neighborhoods that depend only on natural geometric
properties of the domain or manifold. The proof of these results relies
on novel estimates, from above and below, for the heat kernel and its
gradient, as well as for the eigenfunctions of the Laplacian and their
gradient, that hold in the non-smooth category, and are stable with
respect to perturbations within this category. Finally, these coordinate
systems are intrinsic and efficiently computable, and are of value in
applications. 
\end{abstract}

\keywords{monolayer | structure | x-ray reflectivity | molecular electronics}

\abbreviations{SAM, self-assembled monolayer; OTS,
octadecyltrichlorosilane}

\dropcap{I}n this article we study the evolution of ``almost-sharp'' fronts
for the surface quasi-geostrophic equation. This 2-D active scalar
equation reads for the surface quasi-geostrophic equation. 
\begin{equation}
\mfrac{D \theta}{Dt}=\mfrac{\pr \theta}{\pr t} + u\cdot \nabla
\theta=0 \label{qg1}
\end{equation}
where,
\begin{equation}
 u=(u_1,u_2)=(-\mfrac{\pr \psi}{\pr y},\mfrac{\pr \psi}{\pr
x})\label{qg2} \end{equation}
and,
\begin{equation} (-\triangle)^{\f12}\psi=\theta \, ,\label{qg3} \end{equation}
For simplicity we are considering fronts on the cylinder, i.e. we
take $(x,y)$ in $\mathbb{R}/_{\displaystyle{\mathbb{Z}}}\times
\mathbb{R}$. In this setting we define $-\triangle^{-\f12}$ that
comes from inverting the third equation by convolution with the
kernel. To avoid irrelevant considerations at $\infty$ we
will take $\eta$ to be compactly supported
\[
\mfrac{\chi(u,v)}{(u^2+v^2)^{\f12}}+\eta(u,v)
\]
where $\chi (x,y)\ \epsilon\ C^{\infty}_{0},\,\,
\chi(x,y)=1 \hspace{8pt} \mbox{in} \hspace{5pt} |x-y|\leq r \,\,
\mbox{and}\,\, supp \chi$ is contained in $  \{|x-y|\leq R\} $
with $0<r<R<\frac{1}{2}$. Also $ \eta\ \epsilon\ C^{\infty}_0$,
$\eta(0,0)=0 $.

The main mathematical interest in the quasi-geostrophic equation
lies in its strong similarities with the 3-Euler equations. These
results were first proved by Constantin, Majda and Tabak, see
\cite{1}, \cite{2} and \cite{3} for more details. There
are several other research lines for this equation, both
theoretical and numerical. See  \cite{4}, \cite{5}, and
\cite{6}.
The question
about the regularity of the solutions for QG  remains as an open
problem.

Recently one of the authors has obtained the equation for the
evolution of sharp fronts (in the periodic setting), proving its
local well-posedness for that equation. (see \cite{ZhaZha} and
\cite{TSL} for more details). This is a problem in contour
dynamics. Contour dynamics for other fluid equations has been
studied extensively.

\section{Analysis of almost sharp fronts}
We begin our analysis on almost sharp fronts for the
quasi-geostrophic equation recalling the notion of weak solution.

For these solutions we have the following

\begin{definition}
A bounded function $\theta$ is a weak solution of QG if for any
$\phi\,\epsilon\,
C_0^{\infty}(\fdb\times\mathbb{R}\times[0,\vep])$ we have
\begin{eqnarray}
&&  \int_{\mathbb{R}^+\times\fd\times\mathbb{R}} \hspace{-25pt}
 \theta(x,y,t)\, \pr_t \phi
\,(x,y,t) dy dx dt+\nonumber\\
  & +&\int_{\mathbb{R}^+\times\fd\times\mathbb{R}}
\hspace{-26pt} \theta\,(x,y,t) u(x,y,t)\cdot\nabla\phi\,(x,y,t)
dydxdt = 0 \label{weaksol} \end{eqnarray}
where $u$ is determined by equations \eqref{qg2} and \eqref{qg3}.
\end{definition}

\subsection{Data Sources}
We are interested in studying the evolution of almost sharp fronts
for the QG equation. These are weak solutions of the equation with
large gradient ($\sim \displaystyle{ \inlinefrac{1}{\delta}}$, where $2
\delta$ is the thickness of the transition layer for $\theta$).

\section{Discussion}
\subsection{Cylindrical Case}
We are going to consider the cylindrical case here. We consider a
transition layer of thickness smaller than $2\delta$ in which
 $\theta$ changes from 0 to 1. (see Figure ).That means we are considering $\theta$  of the form
\[
\theta  = 1   \mbox{ if }\quad  y\geq \varphi(x,t)+\delta
\]
\[
\theta \mbox{ bounded} \mbox{ if }\quad |\varphi(x,t)-y|\leq\delta
\]
\be \theta = 0  \mbox{ if }\quad  y\leq \varphi(x,t)-\delta
\label{theta} \ee
where $\varphi$ is a smooth periodic function and
$0<\delta<\frac{1}{2}$.

%For these solutions we have the following

\begin{theorem}
If the active scalar $\theta$ is as in \eqref{theta} and satisfies
the equation \eqref{weaksol}, then $\varphi$ satisfies the
equation
\begin{eqnarray}
\mfrac{\pr \varphi}{\pr t}(x,t)&=&\hspace{-2pt}\dst
\int_{\fd}\mfrac{\mfrac{\pr \varphi}{\pr x}(x,t)-\mfrac{\pr
\varphi}{\pr
u}(u,t)}{[(x-u)^{2}+(\varphi(x,t)-\varphi(u,t))^{2}]^{\f12}}\nonumber\\
&&
\chi(x-u,\varphi(x,t)-\varphi(u,t)) du \hspace{3pt} +
\nonumber\\
&+&\dst \int_{\fd} \Big{[}\mfrac{\pr \varphi} {\pr
x}(x,t)-\mfrac{\pr \varphi}{\pr u} (u,t)\Big{]}
\nonumber\\&&
\eta(x-u,\varphi(x,t)-\varphi(u,t)) du + Error
\end{eqnarray}
with $|Error|\leq C\, \delta | log\delta| $ where $C$ depends only
on $\|\theta\|_{L^{\infty}}$ and $\|
\nabla\varphi\|_{L^{\infty}}$.
\end{theorem}

\begin{remark}
Note that equation \eqref{theta} specifies  the function $\varphi$
up to an error of order $\delta$. Theorem 1 provides an evolution
equation for the function $\varphi$ up to an error of order
$\delta |log \delta|$.
\end{remark}

In order to analyze the evolution of the ``almost-sharp'' front we
substitute the above expression for $\theta$ in the definition of
a weak solution (see \eqref{weaksol}). We use the notation $X =O(
Y)$ to indicate that $|X|\leq C |Y|$ where the constant $C$
depends only on $\|\theta\|_{L^{\infty}}$, $\|
\nabla\varphi\|_{L^{\infty}}$ and $\|\phi\|_{C^1}$, where $\phi$
is a test function appearing in Definition 1.

We consider the 3 different regions defined by the form on
$\theta$. Since $\theta=0$ in the region I the contribution from
that region is 0, i.e.
\[
  \int_{I\times \mathbb{R}}
 \theta(x,y,t)\, \pr_t \phi
\,(x,y,t) dy dx dt+  \]
\[
   +\int_{I\times \mathbb{R}}
 \theta\,(x,y,t) u(x,y,t)\cdot\nabla\phi\,(x,y,t) dydxdt = 0
\]

As for the region II
\[
\int_{II\times \mathbb{R}} \theta (x,y,t) \pr_t\phi (x,y,t)dx dy
dt = O(\delta)
\]
since $\theta$ is bounded and hence $O(1)$, and the area of the
region II is $O(\delta)$. As for the second term
\[
\int_{II\times \mathbb{R}} u \theta \nabla \phi dx dy dt =
O(\delta log(\delta))
\]

To see this, we fix $t$. We must estimate
\[
\int_{\mathbb{R}^2} u\cdot(\mathbb{1}_{II}\theta\nabla\phi) dx dy
\]
We are left to estimate the terms
\[
\int_{III\times \mathbb{R}} \theta \pr_t\phi dx dy
dt+\int_{III\times \mathbb{R}} \theta u_f\cdot \nabla \phi dx dy
dt=:A+B
\]

\subsection{Observations}
The following observations can be made form the numerical experiments
described in this section, and are consistent with the results
of more extensive experimentation performed by the authors:
\begin{itemize}
\item The CPU times in Tables 1--3 are compatible with the estimates in
formulae {\bf 14}, {\bf 16}, and {\bf 23}.
\item
The precision produced by each of Algorithms {\bf I} and {\bf II}
is similar to that provided by formula {\bf 3}, even when
$\omega_{k+1}$ is close to the machine precision.
\end{itemize}

\begin{materials}
\section{Digital RNA SNP Analysis} A real-time PCR assay was designed
to amplify {\it PLAC4} mRNA, with the two SNP alleles being discriminated
by TaqMan probes. {\it PLAC4} mRNA concentrations were quantified in
extracted RNA samples followed by dilutions to approximately one target
template molecule of either type (i.e., either allele) per well.
Details are given in the {\it SI Materials and Methods}.

\section{Digital RCD Analysis} Extracted DNA was quantified by
spectrophotometry (NanoDrop Technologies, Wilmington, DE) and diluted to a
concentration of 
approximately one target template from either chr21 or ch1 per well.
\end{materials}

\appendix[Estimating the Spectral Norm of a Matrix]
In this appendix we describe a method for the estimation of the spectral norm
of matrix $A$. The method does not require access to the individual
entries of $A$; it requires only applications of $A$ and $A$* to vectors.
It is a version of the classical power method. Its probabilistic
analysis summarized below was introduced fairly recently in refs. 13
and 14. This appendix is included here for completeness.

\appendix
This is an example of an appendix without a title.

\begin{acknowledgments}
This work was partially supported by 
Spanish Ministry of Science and Technology Grant BFM2002-02042 (to D.C. and
J.L.R.) and by National Science Foundation Grand DMS-0245242 (to C.F.).
\end{acknowledgments}

\begin{thebibliography}{10}
\bibitem{BN}
M.~Belkin and P.~Niyogi, {\em Using manifold structure for partially
  labelled classification}, Advances in NIPS, 15 (2003).

\bibitem{BBG:EmbeddingRiemannianManifoldHeatKernel}
P.~B\'erard, G.~Besson, and S.~Gallot, {\em Embedding {R}iemannian
  manifolds by their heat kernel}, Geom. and Fun. Anal., 4 (1994),
  pp.~374--398.

\bibitem{CLAcha1}
R.R.~Coifman and S.~Lafon, {\em Diffusion maps}, Appl. Comp. Harm. Anal.,
  21 (2006), pp.~5--30.

\bibitem{DiffusionPNAS}
R.R.~Coifman, S.~Lafon, A.~Lee, M.~Maggioni, B.~Nadler, F.~Warner, and
  S.~Zucker, {\em Geometric diffusions as a tool for harmonic analysis and
  structure definition of data. {P}art {I}: Diffusion maps}, Proc. of Nat.
  Acad. Sci.,  (2005), pp.~7426--7431.

\bibitem{Clementi:LowDimensionaFreeEnergyLandscapesProteinFolding}
P.~Das, M.~Moll, H.~Stamati, L.~Kavraki, and C.~Clementi, {\em
  Low-dimensional, free-energy landscapes of protein-folding reactions by
  nonlinear dimensionality reduction}, P.N.A.S., 103 (2006), pp.~9885--9890.

\bibitem{DoGri}
D.~Donoho and C.~Grimes, {\em Hessian eigenmaps: new locally linear
  embedding techniques for high-dimensional data}, Proceedings of the National
  Academy of Sciences, 100 (2003), pp.~5591--5596.

\bibitem{DoGri:WhenDoesIsoMap}
D.~L. Donoho and C.~Grimes, {\em When does isomap recover natural
  parameterization of families of articulated images?}, Tech. Report Tech. Rep.
  2002-27, Department of Statistics, Stanford University, August 2002.

\bibitem{GruterWidman:GreenFunction}
M.~Gr\"uter and K.-O. Widman, {\em The {G}reen function for uniformly
  elliptic equations}, Man. Math., 37 (1982), pp.~303--342.

\bibitem{Simon:NeumannEssentialSpectrum}
R.~Hempel, L.~Seco, and B.~Simon, {\em The essential spectrum of neumann
  laplacians on some bounded singular domains}, 1991.

\bibitem{1}
Kadison, R.\ V.\ and Singer, I.\ M.\ (1959)
Extensions of pure states, {\it Amer.\ J.\ Math.\ \bf
81}, 383-400.

\bibitem{2}
Anderson, J.\ (1981) A conjecture concerning the pure states of
$B(H)$ and a related theorem. in {\it Topics in Modern Operator
Theory}, Birkha\"user, pp.\ 27-43.

\bibitem{3}
Anderson, J.\ (1979) Extreme points in sets of
positive linear maps on $B(H)$. {\it J.\ Funct.\
Anal.\
\bf 31}, 195-217.

\bibitem{4}
Anderson, J.\ (1979) Pathology in the Calkin algebra. {\it J.\
Operator Theory \bf 2}, 159-167.

\bibitem{5}
Johnson, B.\ E.\ and Parrott, S.\ K.\ (1972) Operators commuting
with a von Neumann algebra modulo the set of compact operators.
{\it J.\ Funct.\ Anal.\ \bf 11}, 39-61.

\bibitem{6}
Akemann, C.\ and Weaver, N.\ (2004) Consistency of a
counterexample to Naimark's problem. {\it Proc.\ Nat.\ Acad.\
Sci.\ USA \bf 101}, 7522-7525.

\bibitem{TSL}
J.~Tenenbaum, V.~de~Silva, and J.~Langford, {\em A global geometric
  framework for nonlinear dimensionality reduction}, Science, 290 (2000),
  pp.~2319--2323.

\bibitem{ZhaZha}
Z.~Zhang and H.~Zha, {\em Principal manifolds and nonlinear dimension
  reduction via local tangent space alignement}, Tech. Report CSE-02-019,
  Department of computer science and engineering, Pennsylvania State
  University, 2002.
\end{thebibliography}
\end{article}

\begin{table}[h]
\caption{Repeat length of longer allele by age of onset class.
This is what happens when the text continues.}
\begin{tabular}{@{\vrule height 10.5pt depth4pt  width0pt}lrcccc}
&\multicolumn5c{Repeat length}\\
\noalign{\vskip-11pt}
Age of onset,\\
\cline{2-6}
\vrule depth 6pt width 0pt years&\multicolumn1c{\it n}&Mean&SD&Range&Median\\
\hline
Juvenile, 2$-$20&40&60.15& 9.32&43$-$86&60\\
Typical, 21$-$50&377&45.72&2.97&40$-$58&45\\
Late, $>$50&26&41.85&1.56&40$-$45&42\tablenote{The no. of wells for all samples was 384. Genotypes were
determined by mass spectrometric assay. The $m_t$ value indicates the
average number of wells positive for the over represented allele.}
\\
\hline
\end{tabular}
\end{table}

\begin{table*}[ht]
\caption{Summary of the experimental results}
\begin{tabular*}{\hsize}
{@{\extracolsep{\fill}}rrrrrrrrrrrrr}
\multicolumn{3}{l}{Parameters}&
\multicolumn{5}{c}{Averaged Results}&
\multicolumn{5}{c}{Comparisons}\cr
\hline
\multicolumn1c{$n$}&\multicolumn1c{$S^*_{MAX}$}&
\multicolumn1c{$t_1$}&\multicolumn1c{\ $r_1$}&
\multicolumn1c{\ $m_1$}&\multicolumn1c{$t_2$}&
\multicolumn1c{$r_2$}&\multicolumn1c{$m_2$}
&\multicolumn1c{$t_{lb}$}&\multicolumn1c{\ \ $t_1/t_2$}&
$r_1/r_2$&$m_1/m_2$&
$t_1/t_{lb}$\cr
\hline
10\tablenote{Stanford Synchrotron Radiation Laboratory (Stanford University,
Stanford, CA)}&1\quad &4&.0007&4&4&.0020&4&4&1.000&.333&1.000&1.000\cr
10\tablenote{$R_{\rm FREE}=R$ factor for the $\sim 5$\% of the randomly
chosen unique ref\/lections not used in the ref\/inement.}&5\quad &50&.0008&8&50&.0020&12&49&.999&.417&.698&1.020\cr
100\tablenote{Calculated for all observed data}&20\quad &2840975&.0423&95&2871117&.1083&521&---&
.990&.390&.182&---\ \ \cr
\hline
\end{tabular*}
\end{table*}

\end{document}

### 2013-08-28 cccp.py
Added drop iv results command

@@ -17,6 +17,12 @@ def scrap_all_works():
     print "Scrapy has returned %s" % ret
 
 
+def drop_iv():
+    from pymongo import MongoClient
+    client = MongoClient()
+    print "Dropping IV results"
+    db = client.lenin
+    db.drop_collection('information_value_result')
 
 def main():
     parser = argparse.ArgumentParser(description='Central de Control de Comandos y Procesos para el TP de Analisis de Lenin.')
@@ -25,6 +31,7 @@ def main():
     parser.add_argument('--scrap', action='store_true', default=False, help='Scraps all the Lenin Works')
     parser.add_argument('--populate-database', action='store_true', default=False, help="From the scrapped works creates database called \"lenin\" (it assumes you're running MongoDB at localhost)")
     parser.add_argument('--plot', action='store_true', default=False, help="Add this flag for plotting")
+    parser.add_argument('--drop-iv', action='store_true', default=False, help="Drop Information Value Results")
     parser.add_argument('--analysis', action='store_true', default=False, help="Add this flag for results calculation")
     parser.add_argument('--analysis-store-only-best', action='store_true', default=False, help="Add this flag for results calculation storing only the best result")
     parser.add_argument('--plot-iv-analysis', action='store_true', default=False, help="Shows some plot about Information Value Analysis")
@@ -54,6 +61,8 @@ def main():
     if args.documents:
         from information_value.models import DocumentList
         doc_list = DocumentList(args.documents[0])
+    if args.drop_iv:
+        drop_iv()
     if args.analysis:
         from commands.database import calculate_results
         documents = None

### 2013-08-29 get_dump.sh
Delete get_dump.sh

@@ -1,7 +1,0 @@
-#/bin/sh
-#asume que borraste las colecciones de lenin, por ejemplo, ejecutando un test
-#mkdir dump
-#mkdir dump/lenin
-#wget ftp://lu000482:sakiraMI58@jmperez.com.ar/dump/lenin-with-iv/* -P dump/lenin
-cd dump
-mongorestore lenin

### 2013-10-04 interpreter.py
Add database client to interpreter.

@@ -13,3 +13,6 @@ from information_value.models import Document, DocumentList, InformationValueRes
 from analyzers.wn_analyzer import WordNetAnalyzer
 from nltk.corpus import wordnet as wn
 
+from pymongo import MongoClient
+client = MongoClient()
+db = client[config.DATABASE_NAME]

### 2013-10-04 paper/paper.tex
Write paper abstract

@@
 \usepackage{amssymb,amsfonts,amsmath}
+\usepackage[utf8]{inputenc}
+\usepackage[activeacute, spanish]{babel}
+\selectlanguage{spanish}
 
@@
 
-\title{Almost sharp fronts for the surface geostrophic equation}
+\title{An analysis of Lenin's work: Revolution, war, and fruta}
 
-\author{Roberta Graff\affil{1}{University of Cambridge, Cambridge,
-United Kingdom},
-Javier de Ruiz Garcia\affil{2}{Universidad de Murcia, Bioquimica y Biologia
-Molecular, Murcia, Spain},
-\and
-Franklin Sonnery\affil{2}{}}
+\author{Leonardo Lázzaro,\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
+Julián Peller,\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
+Juan Manuel Pérez,\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
+}
 
@@
 \begin{abstract}
-We use heat kernels or eigenfunctions of the Laplacian to construct
-local coordinates on large classes of Euclidean domains and Riemannian
-manifolds (not necessarily smooth, e.g. with $\mathcal{C}^\alpha$
-metric). These coordinates are bi-Lipschitz on large neighborhoods of
-the domain or manifold, with  constants controlling the distortion and
-the size of the neighborhoods that depend only on natural geometric
-properties of the domain or manifold. The proof of these results relies
-on novel estimates, from above and below, for the heat kernel and its
-gradient, as well as for the eigenfunctions of the Laplacian and their
-gradient, that hold in the non-smooth category, and are stable with
-respect to perturbations within this category. Finally, these coordinate
-systems are intrinsic and efficiently computable, and are of value in
-applications. 
+In order to discover how much related to Russian History in nearly 20th century
+were Lenin works, we use the information value concept to extract the most important 
+words from them. Therefore, we find out how far are them from certain concepts such as
+war, revolution, theory, etc. We expected this concepts to be nearer and farther to concepts 
+treated in Lenin's works depending on the events ranging from 1900 to 1924.
 \end{abstract}
 
-\keywords{monolayer | structure | x-ray reflectivity | molecular electronics}
+\keywords{information value | natural language processing | lenin }
 
-\abbreviations{SAM, self-assembled monolayer; OTS,
-octadecyltrichlorosilane}
+\abbreviations{NLP}
 

### 2013-10-08 paper/paper.tex
Add introduction and appendix.

@@
 \begin{abstract}
-In order to discover how much related to Russian History in nearly 20th century
-were Lenin works, we use the information value concept to extract the most important 
-words from them. Therefore, we find out how far are them from certain concepts such as
+In order to discover how much related were Lenin Works to Russian History in nearly 20th century, we use the information value concept to extract the most important words from them.
+Therefore, we find out how far are them from certain concepts such as
 war, revolution, theory, etc. We expected this concepts to be nearer and farther to concepts 
@@
 
-\dropcap{I}n this article we study the evolution of ``almost-sharp'' fronts
-for the surface quasi-geostrophic equation. This 2-D active scalar
-equation reads for the surface quasi-geostrophic equation. 
+\dropcap{I}n this article we study distances in metric spaces consisting on words, and how we can
+represent a text (an ordered set of words) as a smaller subset of their most representative words.
+
+In \cite{DARWIN}, Zanette and Montemurro defined the information value of a word in a text. This is
+a real value that quantifies how much information that word carries according to the text. Let $T$ be a 
+text, and $T'$ a random shuffled version of $T$, and $w$ a word appearing in $T$. 
+By $S_T(w)$ we denote the Shannon Entropy of $w$ with respect to $T$ (See appendix for more info).
+
+The information value of $w$ in $T$ is
+
 \begin{equation}
-\mfrac{D \theta}{Dt}=\mfrac{\pr \theta}{\pr t} + u\cdot \nabla
-\theta=0 \label{qg1}
+  IV_T(w) = f_w* | S_T(w) - S_{T'}(w) | 
 \end{equation}
-where,
-\begin{equation}
- u=(u_1,u_2)=(-\mfrac{\pr \psi}{\pr y},\mfrac{\pr \psi}{\pr
-x})\label{qg2} \end{equation}
-and,
+
+where $f_w$ is the frequency of appearance of $w$ in $T$. This value captures, in some way, whether a word
+has a distribution in text that is not exactly uniform; an order of the word in the text that brings some sense to it.
+
+Having these value, we can pull the most representative words out of a text by selecting those of greater information value.
+
 \begin{equation} (-\triangle)^{\f12}\psi=\theta \, ,\label{qg3} \end{equation}
@@
 
-The main mathematical interest in the quasi-geostrophic equation
-lies in its strong similarities with the 3-Euler equations. These
-results were first proved by Constantin, Majda and Tabak, see
-\cite{1}, \cite{2} and \cite{3} for more details. There
-are several other research lines for this equation, both
-theoretical and numerical. See  \cite{4}, \cite{5}, and
-\cite{6}.
-The question
-about the regularity of the solutions for QG  remains as an open
-problem.
-
 Recently one of the authors has obtained the equation for the
 evolution of sharp fronts (in the periodic setting), proving its
-local well-posedness for that equation. (see \cite{ZhaZha} and
-\cite{TSL} for more details). This is a problem in contour
+local well-posedness for that equation. This is a problem in contour
 dynamics. Contour dynamics for other fluid equations has been
@@
 For these solutions we have the following
-
-\begin{definition}
-A bounded function $\theta$ is a weak solution of QG if for any
-$\phi\,\epsilon\,
-C_0^{\infty}(\fdb\times\mathbb{R}\times[0,\vep])$ we have
-\begin{eqnarray}
-&&  \int_{\mathbb{R}^+\times\fd\times\mathbb{R}} \hspace{-25pt}
- \theta(x,y,t)\, \pr_t \phi
-\,(x,y,t) dy dx dt+\nonumber\\
-  & +&\int_{\mathbb{R}^+\times\fd\times\mathbb{R}}
-\hspace{-26pt} \theta\,(x,y,t) u(x,y,t)\cdot\nabla\phi\,(x,y,t)
-dydxdt = 0 \label{weaksol} \end{eqnarray}
-where $u$ is determined by equations \eqref{qg2} and \eqref{qg3}.
-\end{definition}
 
@@
 
-\begin{theorem}
-If the active scalar $\theta$ is as in \eqref{theta} and satisfies
-the equation \eqref{weaksol}, then $\varphi$ satisfies the
-equation
-\begin{eqnarray}
-\mfrac{\pr \varphi}{\pr t}(x,t)&=&\hspace{-2pt}\dst
-\int_{\fd}\mfrac{\mfrac{\pr \varphi}{\pr x}(x,t)-\mfrac{\pr
-\varphi}{\pr
-u}(u,t)}{[(x-u)^{2}+(\varphi(x,t)-\varphi(u,t))^{2}]^{\f12}}\nonumber\\
-&&
-\chi(x-u,\varphi(x,t)-\varphi(u,t)) du \hspace{3pt} +
-\nonumber\\
-&+&\dst \int_{\fd} \Big{[}\mfrac{\pr \varphi} {\pr
-x}(x,t)-\mfrac{\pr \varphi}{\pr u} (u,t)\Big{]}
-\nonumber\\&&
-\eta(x-u,\varphi(x,t)-\varphi(u,t)) du + Error
-\end{eqnarray}
-with $|Error|\leq C\, \delta | log\delta| $ where $C$ depends only
-on $\|\theta\|_{L^{\infty}}$ and $\|
-\nabla\varphi\|_{L^{\infty}}$.
-\end{theorem}
-
 \begin{remark}
@@
 substitute the above expression for $\theta$ in the definition of
-a weak solution (see \eqref{weaksol}). We use the notation $X =O(
+a weak solution (see). We use the notation $X =O(
 Y)$ to indicate that $|X|\leq C |Y|$ where the constant $C$
@@
 
+\appendix[Entropy of a word in a text]
+
+Let's recall from \cite{DARWIN} and \cite{ENTROPIC} the concept of information value of a word. 
+Let $T$ be a text, which has been split into $P$ pieces $T_1, T_2, \dots, T_P$, $w$ be a word in $T$,
+and $f_i$ the frequency of appearance of $w$ in $T_i$.
+
+For each part $1 \leq i \leq P$, we could define:
+
+\begin{equation}
+  p_i = \frac{f_i}{\Sigma_{j=1}^{P}f_i}
+\end{equation}
+
+This quantity stands for probability of finding $w$ in $T_i$, given that it is present in the text. So, 
+we define the Shannon information entropy of $w$ in $T$ as
+
+\begin{equation}
+  S = -\frac{1}{ln P}\sum_{i=1}^{P}p_i ln p_i
+\end{equation}
+
 \appendix[Estimating the Spectral Norm of a Matrix]
@@
 \begin{thebibliography}{10}
-\bibitem{BN}
-M.~Belkin and P.~Niyogi, {\em Using manifold structure for partially
-  labelled classification}, Advances in NIPS, 15 (2003).
-
-\bibitem{BBG:EmbeddingRiemannianManifoldHeatKernel}
-P.~B\'erard, G.~Besson, and S.~Gallot, {\em Embedding {R}iemannian
-  manifolds by their heat kernel}, Geom. and Fun. Anal., 4 (1994),
-  pp.~374--398.
-
-\bibitem{CLAcha1}
-R.R.~Coifman and S.~Lafon, {\em Diffusion maps}, Appl. Comp. Harm. Anal.,
-  21 (2006), pp.~5--30.
-
-\bibitem{DiffusionPNAS}
-R.R.~Coifman, S.~Lafon, A.~Lee, M.~Maggioni, B.~Nadler, F.~Warner, and
-  S.~Zucker, {\em Geometric diffusions as a tool for harmonic analysis and
-  structure definition of data. {P}art {I}: Diffusion maps}, Proc. of Nat.
-  Acad. Sci.,  (2005), pp.~7426--7431.
-
-\bibitem{Clementi:LowDimensionaFreeEnergyLandscapesProteinFolding}
-P.~Das, M.~Moll, H.~Stamati, L.~Kavraki, and C.~Clementi, {\em
-  Low-dimensional, free-energy landscapes of protein-folding reactions by
-  nonlinear dimensionality reduction}, P.N.A.S., 103 (2006), pp.~9885--9890.
-
-\bibitem{DoGri}
-D.~Donoho and C.~Grimes, {\em Hessian eigenmaps: new locally linear
-  embedding techniques for high-dimensional data}, Proceedings of the National
-  Academy of Sciences, 100 (2003), pp.~5591--5596.
-
-\bibitem{DoGri:WhenDoesIsoMap}
-D.~L. Donoho and C.~Grimes, {\em When does isomap recover natural
-  parameterization of families of articulated images?}, Tech. Report Tech. Rep.
-  2002-27, Department of Statistics, Stanford University, August 2002.
-
-\bibitem{GruterWidman:GreenFunction}
-M.~Gr\"uter and K.-O. Widman, {\em The {G}reen function for uniformly
-  elliptic equations}, Man. Math., 37 (1982), pp.~303--342.
-
-\bibitem{Simon:NeumannEssentialSpectrum}
-R.~Hempel, L.~Seco, and B.~Simon, {\em The essential spectrum of neumann
-  laplacians on some bounded singular domains}, 1991.
-
-\bibitem{1}
-Kadison, R.\ V.\ and Singer, I.\ M.\ (1959)
-Extensions of pure states, {\it Amer.\ J.\ Math.\ \bf
-81}, 383-400.
-
-\bibitem{2}
-Anderson, J.\ (1981) A conjecture concerning the pure states of
-$B(H)$ and a related theorem. in {\it Topics in Modern Operator
-Theory}, Birkha\"user, pp.\ 27-43.
-
-\bibitem{3}
-Anderson, J.\ (1979) Extreme points in sets of
-positive linear maps on $B(H)$. {\it J.\ Funct.\
-Anal.\
-\bf 31}, 195-217.
-
-\bibitem{4}
-Anderson, J.\ (1979) Pathology in the Calkin algebra. {\it J.\
-Operator Theory \bf 2}, 159-167.
-
-\bibitem{5}
-Johnson, B.\ E.\ and Parrott, S.\ K.\ (1972) Operators commuting
-with a von Neumann algebra modulo the set of compact operators.
-{\it J.\ Funct.\ Anal.\ \bf 11}, 39-61.
-
-\bibitem{6}
-Akemann, C.\ and Weaver, N.\ (2004) Consistency of a
-counterexample to Naimark's problem. {\it Proc.\ Nat.\ Acad.\
-Sci.\ USA \bf 101}, 7522-7525.
-
-\bibitem{TSL}
-J.~Tenenbaum, V.~de~Silva, and J.~Langford, {\em A global geometric
-  framework for nonlinear dimensionality reduction}, Science, 290 (2000),
-  pp.~2319--2323.
-
-\bibitem{ZhaZha}
-Z.~Zhang and H.~Zha, {\em Principal manifolds and nonlinear dimension
-  reduction via local tangent space alignement}, Tech. Report CSE-02-019,
-  Department of computer science and engineering, Pennsylvania State
-  University, 2002.
+\bibitem{DARWIN}
+M.A. Montemurro and D. H. Zanette, {\em The statistics of meaning: Darwin, Gibbon and Moby Dick}, Significance, Dec. 2009, 165-169.
+\bibitem{ENTROPIC}
+M.A. Montemurro and D. H. Zanette, {\em Entropic analysis of the role of words in literary texts}, Adv. Complex Systems 5, September 27th 2001
 \end{thebibliography}

### 2013-10-16 paper/paper.tex
added sketch structure to paper.tex

@@
 
+\section{Introduction}
+
 \dropcap{I}n this article we study distances in metric spaces consisting on words, and how we can
@@
 Having these value, we can pull the most representative words out of a text by selecting those of greater information value.
+
+\section{Methods}
+\subsection{Corpus}
+*Scrapping marxists.org
+*Filtrado Obras chiquitas (cartas incluidas)
+*Números (obras totales obtenidas, promedio tokens)
+\subsection{Information Value Framework}
+*Aclarar settings de Zannette
+*Maximización, ventanas
+*Cálculo paralelo
+*Ajustes de parametros para que concuerden con los resultados de zanette
+*doc.top_words()
+  representación como set de palabras ponderadas por documento.
+
+\subsection{Wordnet analyzer}
+Consideremos el siguiente problema: ¿cómo calcular la similaridad o distancia de un documento a un cierto concepto?
+El enfoque que utilizamos en este trabajo es el de realizar una representación del documento como un conjunto de palabras, y en base a esto usar una noción topológica de similaridad/distancia .
+
+*WordnetAnalyzer
+  *Synset
+  *path, lch, wup
+*judge_word
+*judge_doc
+*judge_year
+Dado un conjunto de palabras, definimos la distancia de una palabra a este conjunto como
+
+S(x, C) = max { ... }
+
+Usamos la distancia path.
+
+Ahora, dado un documento, calculamos
+
+\section{Results}
+\subsection{Resultados sobre obras}
+* Tabla de top words de Estado y Revolución
+* Distancia a algunos conceptos de estado y revolución
+\subsection{Resultados sobre años}
+*
+* x = {años}, y = {concept value}
+
+\section{Discussion}
+* Zanette diferia en valores absolutos con los resultados nuestros. Moby Dick.
+
+\section{Acknowledgments}
+\section{Literature cited}
 

### 2013-10-29 information_value/calculator.py
Pep8.

@@ -7,105 +7,96 @@ import random
 import operator
 import nltk
 
+
 def print_probabilty(str, prob):
-	if random.random() < prob:
-		print str
+    if random.random() < prob:
+        print str
 
 
 def get_count(ctuple):
-	return ctuple[1]
+    return ctuple[1]
+
 
 class WindowSizeTooLarge(Exception):
-	pass
+    pass
 
 
 class InformationValueCalculator:
 
-	def __init__(self, tokens):
-		#se carga la lista de tokens
-		self.tokens = tokens
-		self.randomized_text = deepcopy(self.tokens)
-		shuffle(self.randomized_text)
-		self.word_fdist = nltk.FreqDist(self.tokens)
+    def __init__(self, tokens):
+        #se carga la lista de tokens
+        self.tokens = tokens
+        self.randomized_text = deepcopy(self.tokens)
+        shuffle(self.randomized_text)
+        self.word_fdist = nltk.FreqDist(self.tokens)
 
-	def number_of_windows(self, window_size):
-		return int(math.ceil(self.word_fdist.N() / window_size))
+    def number_of_windows(self, window_size):
+        return int(math.ceil(self.word_fdist.N() / window_size))
 
-	def get_frequencies(self, tokenized_text, window_size):
-		freq = dict((word, []) for word in self.word_fdist.samples())
-		P = self.number_of_windows(window_size)
-		for i in range(0,P):
-			window = get_window(tokenized_text, window_size=window_size, number_of_window=i)
-			window_fdist = nltk.FreqDist(window)
+    def get_frequencies(self, tokenized_text, window_size):
+        freq = dict((word, []) for word in self.word_fdist.samples())
+        P = self.number_of_windows(window_size)
+        for i in range(0, P):
+            window = get_window(tokenized_text, window_size=window_size, number_of_window=i)
+            window_fdist = nltk.FreqDist(window)
 
-			for word in self.word_fdist.samples():
-				freq[word].append(window_fdist.freq(word))
+            for word in self.word_fdist.samples():
+                freq[word].append(window_fdist.freq(word))
 
-		return freq
+        return freq
 
-	def occurrence_probability(self, window_size, tokenized_text):
-		P = self.number_of_windows(window_size)
-		if P == 0 or P == 1:
-			raise WindowSizeTooLarge("Ventana de tamaño %s para texto de tamaño %s" % (window_size, self.word_fdist.N()))
[…]

### 2013-10-29 information_value/models.py

@@ -4,10 +4,9 @@ import hashlib
 
 from pymongo.errors import DuplicateKeyError
 
-from ming import Session, create_datastore
+from ming import Session
 from ming import schema
 import operator
-from ming.session import Session
 from ming.odm import ODMSession
 from ming.odm import Mapper
 from ming.odm.mapper import MapperExtension
@@ -43,20 +42,19 @@ class DocumentWindowSizeDuplicateHash(MapperExtension):
 class InformationValueResult(MappedClass):
 
     def __init__(self, iv_words, sum_threshold=config.SUM_THRESHOLD, *args, **kwargs):
-      if type(iv_words) is dict:
-        iv_words = list(iv_words.iteritems())
-      super(InformationValueResult, self).__init__(*args, iv_words=iv_words, **kwargs)
+        if type(iv_words) is dict:
+            iv_words = list(iv_words.iteritems())
+        super(InformationValueResult, self).__init__(*args, iv_words=iv_words, **kwargs)
 
     @property
     def iv_sum(self, sum_threshold=config.SUM_THRESHOLD):
-      # Todo: improve performance of this...
-      sorted_ivs = sorted(map(operator.itemgetter(1), self.iv_words), reverse=True)
-      self.max_iv = sorted_ivs[0]
-      amount_to_be_taken = int(len(sorted_ivs) * sum_threshold) or 10
-      sorted_ivs = sorted_ivs[:amount_to_be_taken]
-      # Sum the reverse of sorted_words to improve numerical stability
-      return reduce(lambda x, y: x + y, reversed(sorted_ivs), 0)
-
+        # Todo: improve performance of this...
+        sorted_ivs = sorted(map(operator.itemgetter(1), self.iv_words), reverse=True)
+        self.max_iv = sorted_ivs[0]
+        amount_to_be_taken = int(len(sorted_ivs) * sum_threshold) or 10
+        sorted_ivs = sorted_ivs[:amount_to_be_taken]
+        # Sum the reverse of sorted_words to improve numerical stability
+        return reduce(lambda x, y: x + y, reversed(sorted_ivs), 0)
 
     class __mongometa__:
         session = odm_session
@@ -65,7 +63,7 @@ class InformationValueResult(MappedClass):
         extensions = [DocumentWindowSizeDuplicateHash]
 
     def __repr__(self):
-        return "IVR(%s window size, %s iv-words)" % (self.window_size,len(self.iv_words))
[…]

### 2013-10-29 information_value/models.py
Add total_words to Document model.

@@ -88,6 +88,7 @@ class Document(MappedClass):
     text = FieldProperty(schema.String)
     month = FieldProperty(schema.String)
     year = FieldProperty(schema.String)
+    number_of_words = FieldProperty(schema.Int)
     results = RelationProperty(InformationValueResult)
 
     def top_words(self, total_words=20, stop_words=stopwords.words('english'), greater_than_zero=True, window_size=None):

### 2013-10-29 information_value/models.py
Document list query more efficient.

@@ -194,7 +194,10 @@ class Document(MappedClass):
 class DocumentList(object):
 
     def __init__(self, name='State', only_with_results=False, year=None):
-        self.search_criterion = {'name': {'$regex': '.*'+name+'.*'}}
+        self.search_criterion = {
+            'name': {'$regex': '.*'+name+'.*'},
+            'number_of_words': {'$gte': MIN_TOKENS}
+        }
         if year is not None:
             self.search_criterion['year'] = year
         self.only_with_results = only_with_results
@@ -206,14 +209,7 @@ class DocumentList(object):
     def base_load(self):
         self.current = 0
         it = Document.query.find(self.search_criterion)
-
-        res = list()
-        for doc in it:
-            if not self.only_with_results or len(doc.results) > 0:
-                if doc.total_tokens > MIN_TOKENS:
-                    res.append(doc)
-
-        self.documents = res
+        self.documents = list(it)
 
     def add_month(self, month=None):
         if month is not None:

### 2013-10-29 plot/window_sizes.py

@@ -17,7 +17,7 @@ def plot_scatter_total_words_vs_window_sizes(documents):
     window_sizes = []
     total_words = []
     for document in documents:
-        best_iv = document.get_information_value_result(0.01)
+        best_iv = document.get_information_value_result()
         if best_iv:
             window_sizes.append(best_iv.window_size)
             total_words.append(len(document.text))

### 2013-10-29 paper/paper.tex
Add method section.

@@
 
-\section{Methods}
-\subsection{Corpus}
-*Scrapping marxists.org
-*Filtrado Obras chiquitas (cartas incluidas)
+\section{Method}
+\subsection{Text Corpus}
+We gathered Lenin's work from the "Marxists Internet Archive".
+This proved to be a difficult task as the works were not in a common HTML format.
+The tool we used to do this is Scrapy, a very comprehensive Python crawling framework.
+
+In order to reduce noise in the corpus, we filtered all the letters and works that were comparatively little.
+Our information value theory doesn't work very well with texts with little repetition of words, so we decided to remove texts with less than 1000 words.
+
 *Números (obras totales obtenidas, promedio tokens)
@@
 
-\begin{equation} (-\triangle)^{\f12}\psi=\theta \, ,\label{qg3} \end{equation}
-For simplicity we are considering fronts on the cylinder, i.e. we
-take $(x,y)$ in $\mathbb{R}/_{\displaystyle{\mathbb{Z}}}\times
-\mathbb{R}$. In this setting we define $-\triangle^{-\f12}$ that
-comes from inverting the third equation by convolution with the
-kernel. To avoid irrelevant considerations at $\infty$ we
-will take $\eta$ to be compactly supported
-\[
-\mfrac{\chi(u,v)}{(u^2+v^2)^{\f12}}+\eta(u,v)
-\]
-where $\chi (x,y)\ \epsilon\ C^{\infty}_{0},\,\,
-\chi(x,y)=1 \hspace{8pt} \mbox{in} \hspace{5pt} |x-y|\leq r \,\,
-\mbox{and}\,\, supp \chi$ is contained in $  \{|x-y|\leq R\} $
-with $0<r<R<\frac{1}{2}$. Also $ \eta\ \epsilon\ C^{\infty}_0$,
-$\eta(0,0)=0 $.
-
-Recently one of the authors has obtained the equation for the
-evolution of sharp fronts (in the periodic setting), proving its
-local well-posedness for that equation. This is a problem in contour
-dynamics. Contour dynamics for other fluid equations has been
-studied extensively.
-
 \section{Analysis of almost sharp fronts}
@@
 \delta$ is the thickness of the transition layer for $\theta$).
-
-\section{Discussion}
-\subsection{Cylindrical Case}
-We are going to consider the cylindrical case here. We consider a
-transition layer of thickness smaller than $2\delta$ in which
- $\theta$ changes from 0 to 1. (see Figure ).That means we are considering $\theta$  of the form
-\[
-\theta  = 1   \mbox{ if }\quad  y\geq \varphi(x,t)+\delta
-\]
-\[
-\theta \mbox{ bounded} \mbox{ if }\quad |\varphi(x,t)-y|\leq\delta
-\]
-\be \theta = 0  \mbox{ if }\quad  y\leq \varphi(x,t)-\delta
-\label{theta} \ee
-where $\varphi$ is a smooth periodic function and
-$0<\delta<\frac{1}{2}$.
-
-%For these solutions we have the following
-
-\begin{remark}
-Note that equation \eqref{theta} specifies  the function $\varphi$
-up to an error of order $\delta$. Theorem 1 provides an evolution
-equation for the function $\varphi$ up to an error of order
-$\delta |log \delta|$.
-\end{remark}
-
-In order to analyze the evolution of the ``almost-sharp'' front we
-substitute the above expression for $\theta$ in the definition of
-a weak solution (see). We use the notation $X =O(
-Y)$ to indicate that $|X|\leq C |Y|$ where the constant $C$
-depends only on $\|\theta\|_{L^{\infty}}$, $\|
-\nabla\varphi\|_{L^{\infty}}$ and $\|\phi\|_{C^1}$, where $\phi$
-is a test function appearing in Definition 1.
-
-We consider the 3 different regions defined by the form on
-$\theta$. Since $\theta=0$ in the region I the contribution from
-that region is 0, i.e.
-\[
-  \int_{I\times \mathbb{R}}
- \theta(x,y,t)\, \pr_t \phi
-\,(x,y,t) dy dx dt+  \]
-\[
-   +\int_{I\times \mathbb{R}}
- \theta\,(x,y,t) u(x,y,t)\cdot\nabla\phi\,(x,y,t) dydxdt = 0
-\]
-
-As for the region II
-\[
-\int_{II\times \mathbb{R}} \theta (x,y,t) \pr_t\phi (x,y,t)dx dy
-dt = O(\delta)
-\]
-since $\theta$ is bounded and hence $O(1)$, and the area of the
-region II is $O(\delta)$. As for the second term
-\[
-\int_{II\times \mathbb{R}} u \theta \nabla \phi dx dy dt =
-O(\delta log(\delta))
-\]
-
-To see this, we fix $t$. We must estimate
-\[
-\int_{\mathbb{R}^2} u\cdot(\mathbb{1}_{II}\theta\nabla\phi) dx dy
-\]
-We are left to estimate the terms
-\[
-\int_{III\times \mathbb{R}} \theta \pr_t\phi dx dy
-dt+\int_{III\times \mathbb{R}} \theta u_f\cdot \nabla \phi dx dy
-dt=:A+B
-\]
-
-\subsection{Observations}
-The following observations can be made form the numerical experiments
-described in this section, and are consistent with the results
-of more extensive experimentation performed by the authors:
-\begin{itemize}
-\item The CPU times in Tables 1--3 are compatible with the estimates in
-formulae {\bf 14}, {\bf 16}, and {\bf 23}.
-\item
-The precision produced by each of Algorithms {\bf I} and {\bf II}
-is similar to that provided by formula {\bf 3}, even when
-$\omega_{k+1}$ is close to the machine precision.
-\end{itemize}
 

### 2013-10-29 cccp.py
Add pylab to ccp.

@@ -85,7 +85,7 @@ def main():
     if args.notebook_server:
         subprocess.call("PYTHONPATH=$PYTHONPATH:$PWD; ipython notebook --notebook-dir=.", shell=True)
     if args.shell:
-        subprocess.call("ipython -i interpreter.py", shell=True)
+        subprocess.call("ipython -i interpreter.py --pylab", shell=True)
 
 
 def init_logging():

### 2013-10-29 plot/window_sizes.py

@@ -1,14 +1,10 @@
 # coding: utf-8
 import operator
 import logging
-from operator import itemgetter
-
 import matplotlib.pyplot as plt
 from scipy import average
 
-import config
 from information_value.models import Document
-from information_value.models import DocumentList
 log = logging.getLogger('lenin')
 
 

### 2013-10-29 information_value/models.py
Add number of works per year plot.

@@ -120,7 +120,7 @@ class Document(MappedClass):
     def get_information_value_result(self):
         iv_res = None
         best_iv = 0.0
-        sort = lambda iv_words: sorted(iv_words, key=operator.itemgetter(1), reverse=True)
+        #sort = lambda iv_words: sorted(iv_words, key=operator.itemgetter(1), reverse=True)
         for one_iv in self.results:
             sum_iv = sum(map(lambda (w, iv): iv, one_iv.iv_words))
             if best_iv <= sum_iv:

### 2013-10-29 information_value/models.py
Converted year to int.

@@ -87,7 +87,7 @@ class Document(MappedClass):
     name = FieldProperty(schema.String)
     text = FieldProperty(schema.String)
     month = FieldProperty(schema.String)
-    year = FieldProperty(schema.String)
+    year = FieldProperty(schema.Int)
     number_of_words = FieldProperty(schema.Int)
     results = RelationProperty(InformationValueResult)
 

### 2013-11-05 paper/paper.tex
Plot for works.

@@
 \usepackage[activeacute, spanish]{babel}
+\usepackage[dvips]{graphicx}
 \selectlanguage{spanish}
@@
 In order to reduce noise in the corpus, we filtered all the letters and works that were comparatively little.
-Our information value theory doesn't work very well with texts with little repetition of words, so we decided to remove texts with less than 1000 words.
+Our information value theory doesn't work very well with texts with little repetition of words, so we decided to remove texts with less than 2000 words.
 
-*Números (obras totales obtenidas, promedio tokens)
+\begin{figure}
+\centerline{\includegraphics[width=.4\textwidth]{figures/tokens_per_year.eps}}
+\caption{Number of tokens per year}\label{afoto}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=.4\textwidth]{figures/hist_tokens_small_works.eps}}
+\caption{Distribution of works with respect to size (small works)}\label{afoto}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=.4\textwidth]{figures/hist_tokens_big_works.eps}}
+\caption{Distribution of works with respect to size (big works)}\label{afoto}
+\end{figure}
+
+%*Números (obras totales obtenidas, promedio tokens)
 \subsection{Information Value Framework}
-*Aclarar settings de Zannette
-*Maximización, ventanas
-*Cálculo paralelo
-*Ajustes de parametros para que concuerden con los resultados de zanette
-*doc.top_words()
-  representación como set de palabras ponderadas por documento.
+%
+%*Aclarar settings de Zannette
+%*Maximización, ventanas
+%*Cálculo paralelo
+%*Ajustes de parametros para que concuerden con los resultados de zanette
+%*doc.top_words()
+%  representación como set de palabras ponderadas por documento.
 
@@
 
-*WordnetAnalyzer
-  *Synset
-  *path, lch, wup
-*judge_word
-*judge_doc
-*judge_year
-Dado un conjunto de palabras, definimos la distancia de una palabra a este conjunto como
-
+% *WordnetAnalyzer
+%   *Synset
+%   *path, lch, wup
+% *judge_word
+% *judge_doc
+% *judge_year
+% Dado un conjunto de palabras, definimos la distancia de una palabra a este conjunto como 
+% 
 S(x, C) = max { ... }

### 2013-11-05 paper/pnas.tex
Plot for works.

%% PNAStwoS.tex
%% Sample file to use for PNAS articles prepared in LaTeX
%% For two column PNAS articles
%% Version: Apr 15, 2008

%% BASIC CLASS FILE
\documentclass{pnastwo}

%% ADDITIONAL OPTIONAL STYLE FILES
\usepackage[dvips]{graphicx}
\usepackage{amssymb,amsfonts,amsmath}

%% OPTIONAL MACRO DEFINITIONS
\def\s{\sigma}

%%%%%%%%%%%%
%% For PNAS Only:
\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
\copyrightyear{2008}
\issuedate{Issue Date}
\volume{Volume}
\issuenumber{Issue Number}
%\setcounter{page}{2687} %Set page number here if desired
%%%%%%%%%%%%

\begin{document}

\title{Almost sharp fronts for the surface geostrophic equation}

\author{Roberta Graff\affil{1}{University of Cambridge, Cambridge,
United Kingdom},
Javier de Ruiz Garcia\affil{2}{Universidad de Murcia, Bioquimica y Biologia
Molecular, Murcia, Spain},
\and
Franklin Sonnery\affil{2}{}}

\contributor{Submitted to Proceedings of the National Academy of Sciences
of the United States of America}

\maketitle

\begin{article}
\begin{abstract}
We use heat kernels or eigenfunctions of the Laplacian to construct
local coordinates on large classes of Euclidean domains and Riemannian
manifolds (not necessarily smooth, e.g. with $\mathcal{C}^\alpha$
metric). These coordinates are bi-Lipschitz on large neighborhoods of
the domain or manifold, with  constants controlling the distortion and
the size of the neighborhoods that depend only on natural geometric
properties of the domain or manifold. The proof of these results relies
on novel estimates, from above and below, for the heat kernel and its
gradient, as well as for the eigenfunctions of the Laplacian and their
gradient, that hold in the non-smooth category, and are stable with
respect to perturbations within this category. Finally, these coordinate
systems are intrinsic and efficiently computable, and are of value in
applications. 
\end{abstract}

\keywords{monolayer | structure | x-ray reflectivity | molecular electronics}

\abbreviations{SAM, self-assembled monolayer; OTS,
octadecyltrichlorosilane}

\dropcap{I}n this article we study the evolution of ``almost-sharp'' fronts
for the surface quasi-geostrophic equation. This 2-D active scalar
equation reads for the surface quasi-geostrophic equation. 
\begin{equation}
\mfrac{D \theta}{Dt}=\mfrac{\pr \theta}{\pr t} + u\cdot \nabla
\theta=0 \label{qg1}
\end{equation}
where,
\begin{equation}
 u=(u_1,u_2)=(-\mfrac{\pr \psi}{\pr y},\mfrac{\pr \psi}{\pr
x})\label{qg2} \end{equation}
and,
\begin{equation} (-\triangle)^{\f12}\psi=\theta \, ,\label{qg3} \end{equation}
For simplicity we are considering fronts on the cylinder, i.e. we
take $(x,y)$ in $\mathbb{R}/_{\displaystyle{\mathbb{Z}}}\times
\mathbb{R}$. In this setting we define $-\triangle^{-\f12}$ that
comes from inverting the third equation by convolution with the
kernel. To avoid irrelevant considerations at $\infty$ we
will take $\eta$ to be compactly supported
\[
\mfrac{\chi(u,v)}{(u^2+v^2)^{\f12}}+\eta(u,v)
\]
where $\chi (x,y)\ \epsilon\ C^{\infty}_{0},\,\,
\chi(x,y)=1 \hspace{8pt} \mbox{in} \hspace{5pt} |x-y|\leq r \,\,
\mbox{and}\,\, supp \chi$ is contained in $  \{|x-y|\leq R\} $
with $0<r<R<\frac{1}{2}$. Also $ \eta\ \epsilon\ C^{\infty}_0$,
$\eta(0,0)=0 $.

The main mathematical interest in the quasi-geostrophic equation
lies in its strong similarities with the 3-Euler equations. These
results were first proved by Constantin, Majda and Tabak, see
\cite{1}, \cite{2} and \cite{3} for more details. There
are several other research lines for this equation, both
theoretical and numerical. See  \cite{4}, \cite{5}, and
\cite{6}.
The question
about the regularity of the solutions for QG  remains as an open
problem.

Recently one of the authors has obtained the equation for the
evolution of sharp fronts (in the periodic setting), proving its
local well-posedness for that equation. (see \cite{ZhaZha} and
\cite{TSL} for more details). This is a problem in contour
dynamics. Contour dynamics for other fluid equations has been
studied extensively.

\section{Analysis of almost sharp fronts}
We begin our analysis on almost sharp fronts for the
quasi-geostrophic equation recalling the notion of weak solution.

For these solutions we have the following

\begin{definition}
A bounded function $\theta$ is a weak solution of QG if for any
$\phi\,\epsilon\,
C_0^{\infty}(\fdb\times\mathbb{R}\times[0,\vep])$ we have
\begin{eqnarray}
&&  \int_{\mathbb{R}^+\times\fd\times\mathbb{R}} \hspace{-25pt}
 \theta(x,y,t)\, \pr_t \phi
\,(x,y,t) dy dx dt+\nonumber\\
  & +&\int_{\mathbb{R}^+\times\fd\times\mathbb{R}}
\hspace{-26pt} \theta\,(x,y,t) u(x,y,t)\cdot\nabla\phi\,(x,y,t)
dydxdt = 0 \label{weaksol} \end{eqnarray}
where $u$ is determined by equations \eqref{qg2} and \eqref{qg3}.
\end{definition}

\subsection{Data Sources}
We are interested in studying the evolution of almost sharp fronts
for the QG equation. These are weak solutions of the equation with
large gradient ($\sim \displaystyle{ \inlinefrac{1}{\delta}}$, where $2
\delta$ is the thickness of the transition layer for $\theta$).

\section{Discussion}
\subsection{Cylindrical Case}
We are going to consider the cylindrical case here. We consider a
transition layer of thickness smaller than $2\delta$ in which
 $\theta$ changes from 0 to 1. (see Figure ).That means we are considering $\theta$  of the form
\[
\theta  = 1   \mbox{ if }\quad  y\geq \varphi(x,t)+\delta
\]
\[
\theta \mbox{ bounded} \mbox{ if }\quad |\varphi(x,t)-y|\leq\delta
\]
\be \theta = 0  \mbox{ if }\quad  y\leq \varphi(x,t)-\delta
\label{theta} \ee
where $\varphi$ is a smooth periodic function and
$0<\delta<\frac{1}{2}$.

%For these solutions we have the following

\begin{theorem}
If the active scalar $\theta$ is as in \eqref{theta} and satisfies
the equation \eqref{weaksol}, then $\varphi$ satisfies the
equation
\begin{eqnarray}
\mfrac{\pr \varphi}{\pr t}(x,t)&=&\hspace{-2pt}\dst
\int_{\fd}\mfrac{\mfrac{\pr \varphi}{\pr x}(x,t)-\mfrac{\pr
\varphi}{\pr
u}(u,t)}{[(x-u)^{2}+(\varphi(x,t)-\varphi(u,t))^{2}]^{\f12}}\nonumber\\
&&
\chi(x-u,\varphi(x,t)-\varphi(u,t)) du \hspace{3pt} +
\nonumber\\
&+&\dst \int_{\fd} \Big{[}\mfrac{\pr \varphi} {\pr
x}(x,t)-\mfrac{\pr \varphi}{\pr u} (u,t)\Big{]}
\nonumber\\&&
\eta(x-u,\varphi(x,t)-\varphi(u,t)) du + Error
\end{eqnarray}
with $|Error|\leq C\, \delta | log\delta| $ where $C$ depends only
on $\|\theta\|_{L^{\infty}}$ and $\|
\nabla\varphi\|_{L^{\infty}}$.
\end{theorem}

\begin{remark}
Note that equation \eqref{theta} specifies  the function $\varphi$
up to an error of order $\delta$. Theorem 1 provides an evolution
equation for the function $\varphi$ up to an error of order
$\delta |log \delta|$.
\end{remark}

In order to analyze the evolution of the ``almost-sharp'' front we
substitute the above expression for $\theta$ in the definition of
a weak solution (see \eqref{weaksol}). We use the notation $X =O(
Y)$ to indicate that $|X|\leq C |Y|$ where the constant $C$
depends only on $\|\theta\|_{L^{\infty}}$, $\|
\nabla\varphi\|_{L^{\infty}}$ and $\|\phi\|_{C^1}$, where $\phi$
is a test function appearing in Definition 1.

We consider the 3 different regions defined by the form on
$\theta$. Since $\theta=0$ in the region I the contribution from
that region is 0, i.e.
\[
  \int_{I\times \mathbb{R}}
 \theta(x,y,t)\, \pr_t \phi
\,(x,y,t) dy dx dt+  \]
\[
   +\int_{I\times \mathbb{R}}
 \theta\,(x,y,t) u(x,y,t)\cdot\nabla\phi\,(x,y,t) dydxdt = 0
\]

As for the region II
\[
\int_{II\times \mathbb{R}} \theta (x,y,t) \pr_t\phi (x,y,t)dx dy
dt = O(\delta)
\]
since $\theta$ is bounded and hence $O(1)$, and the area of the
region II is $O(\delta)$. As for the second term
\[
\int_{II\times \mathbb{R}} u \theta \nabla \phi dx dy dt =
O(\delta log(\delta))
\]

To see this, we fix $t$. We must estimate
\[
\int_{\mathbb{R}^2} u\cdot(\mathbb{1}_{II}\theta\nabla\phi) dx dy
\]
We are left to estimate the terms
\[
\int_{III\times \mathbb{R}} \theta \pr_t\phi dx dy
dt+\int_{III\times \mathbb{R}} \theta u_f\cdot \nabla \phi dx dy
dt=:A+B
\]

\subsection{Observations}
The following observations can be made form the numerical experiments
described in this section, and are consistent with the results
of more extensive experimentation performed by the authors:
\begin{itemize}
\item The CPU times in Tables 1--3 are compatible with the estimates in
formulae {\bf 14}, {\bf 16}, and {\bf 23}.
\item
The precision produced by each of Algorithms {\bf I} and {\bf II}
is similar to that provided by formula {\bf 3}, even when
$\omega_{k+1}$ is close to the machine precision.
\end{itemize}

\begin{materials}
\section{Digital RNA SNP Analysis} A real-time PCR assay was designed
to amplify {\it PLAC4} mRNA, with the two SNP alleles being discriminated
by TaqMan probes. {\it PLAC4} mRNA concentrations were quantified in
extracted RNA samples followed by dilutions to approximately one target
template molecule of either type (i.e., either allele) per well.
Details are given in the {\it SI Materials and Methods}.

\section{Digital RCD Analysis} Extracted DNA was quantified by
spectrophotometry (NanoDrop Technologies, Wilmington, DE) and diluted to a
concentration of 
approximately one target template from either chr21 or ch1 per well.
\end{materials}

\appendix[Estimating the Spectral Norm of a Matrix]
In this appendix we describe a method for the estimation of the spectral norm
of matrix $A$. The method does not require access to the individual
entries of $A$; it requires only applications of $A$ and $A$* to vectors.
It is a version of the classical power method. Its probabilistic
analysis summarized below was introduced fairly recently in refs. 13
and 14. This appendix is included here for completeness.

\appendix
This is an example of an appendix without a title.

\begin{acknowledgments}
This work was partially supported by 
Spanish Ministry of Science and Technology Grant BFM2002-02042 (to D.C. and
J.L.R.) and by National Science Foundation Grand DMS-0245242 (to C.F.).
\end{acknowledgments}

\begin{thebibliography}{10}
\bibitem{BN}
M.~Belkin and P.~Niyogi, {\em Using manifold structure for partially
  labelled classification}, Advances in NIPS, 15 (2003).

\bibitem{BBG:EmbeddingRiemannianManifoldHeatKernel}
P.~B\'erard, G.~Besson, and S.~Gallot, {\em Embedding {R}iemannian
  manifolds by their heat kernel}, Geom. and Fun. Anal., 4 (1994),
  pp.~374--398.

\bibitem{CLAcha1}
R.R.~Coifman and S.~Lafon, {\em Diffusion maps}, Appl. Comp. Harm. Anal.,
  21 (2006), pp.~5--30.

\bibitem{DiffusionPNAS}
R.R.~Coifman, S.~Lafon, A.~Lee, M.~Maggioni, B.~Nadler, F.~Warner, and
  S.~Zucker, {\em Geometric diffusions as a tool for harmonic analysis and
  structure definition of data. {P}art {I}: Diffusion maps}, Proc. of Nat.
  Acad. Sci.,  (2005), pp.~7426--7431.

\bibitem{Clementi:LowDimensionaFreeEnergyLandscapesProteinFolding}
P.~Das, M.~Moll, H.~Stamati, L.~Kavraki, and C.~Clementi, {\em
  Low-dimensional, free-energy landscapes of protein-folding reactions by
  nonlinear dimensionality reduction}, P.N.A.S., 103 (2006), pp.~9885--9890.

\bibitem{DoGri}
D.~Donoho and C.~Grimes, {\em Hessian eigenmaps: new locally linear
  embedding techniques for high-dimensional data}, Proceedings of the National
  Academy of Sciences, 100 (2003), pp.~5591--5596.

\bibitem{DoGri:WhenDoesIsoMap}
D.~L. Donoho and C.~Grimes, {\em When does isomap recover natural
  parameterization of families of articulated images?}, Tech. Report Tech. Rep.
  2002-27, Department of Statistics, Stanford University, August 2002.

\bibitem{GruterWidman:GreenFunction}
M.~Gr\"uter and K.-O. Widman, {\em The {G}reen function for uniformly
  elliptic equations}, Man. Math., 37 (1982), pp.~303--342.

\bibitem{Simon:NeumannEssentialSpectrum}
R.~Hempel, L.~Seco, and B.~Simon, {\em The essential spectrum of neumann
  laplacians on some bounded singular domains}, 1991.

\bibitem{1}
Kadison, R.\ V.\ and Singer, I.\ M.\ (1959)
Extensions of pure states, {\it Amer.\ J.\ Math.\ \bf
81}, 383-400.

\bibitem{2}
Anderson, J.\ (1981) A conjecture concerning the pure states of
$B(H)$ and a related theorem. in {\it Topics in Modern Operator
Theory}, Birkha\"user, pp.\ 27-43.

\bibitem{3}
Anderson, J.\ (1979) Extreme points in sets of
positive linear maps on $B(H)$. {\it J.\ Funct.\
Anal.\
\bf 31}, 195-217.

\bibitem{4}
Anderson, J.\ (1979) Pathology in the Calkin algebra. {\it J.\
Operator Theory \bf 2}, 159-167.

\bibitem{5}
Johnson, B.\ E.\ and Parrott, S.\ K.\ (1972) Operators commuting
with a von Neumann algebra modulo the set of compact operators.
{\it J.\ Funct.\ Anal.\ \bf 11}, 39-61.

\bibitem{6}
Akemann, C.\ and Weaver, N.\ (2004) Consistency of a
counterexample to Naimark's problem. {\it Proc.\ Nat.\ Acad.\
Sci.\ USA \bf 101}, 7522-7525.

\bibitem{TSL}
J.~Tenenbaum, V.~de~Silva, and J.~Langford, {\em A global geometric
  framework for nonlinear dimensionality reduction}, Science, 290 (2000),
  pp.~2319--2323.

\bibitem{ZhaZha}
Z.~Zhang and H.~Zha, {\em Principal manifolds and nonlinear dimension
  reduction via local tangent space alignement}, Tech. Report CSE-02-019,
  Department of computer science and engineering, Pennsylvania State
  University, 2002.
\end{thebibliography}
\end{article}

\begin{figure}
\centerline{\includegraphics[width=.4\textwidth]{figsamp.eps}}
\caption{LKB1 phosphorylates Thr-172 of AMPK$\alpha$ \textit{in vitro}
and activates its kinase activity.}\label{afoto}
\end{figure}

\begin{figure*}[ht]
\begin{center}
\centerline{\includegraphics[width=.7\textwidth]{figsamp.eps}}
\caption{LKB1 phosphorylates Thr-172 of AMPK$\alpha$ \textit{in vitro}
and activates its kinase activity.}\label{afoto2}
\end{center}
\end{figure*}

\begin{table}[h]
\caption{Repeat length of longer allele by age of onset class.
This is what happens when the text continues.}
\begin{tabular}{@{\vrule height 10.5pt depth4pt  width0pt}lrcccc}
&\multicolumn5c{Repeat length}\\
\noalign{\vskip-11pt}
Age of onset,\\
\cline{2-6}
\vrule depth 6pt width 0pt years&\multicolumn1c{\it n}&Mean&SD&Range&Median\\
\hline
Juvenile, 2$-$20&40&60.15& 9.32&43$-$86&60\\
Typical, 21$-$50&377&45.72&2.97&40$-$58&45\\
Late, $>$50&26&41.85&1.56&40$-$45&42\tablenote{The no. of wells for all samples was 384. Genotypes were
determined by mass spectrometric assay. The $m_t$ value indicates the
average number of wells positive for the over represented allele.}
\\
\hline
\end{tabular}
\end{table}

\begin{table*}[ht]
\caption{Summary of the experimental results}
\begin{tabular*}{\hsize}
{@{\extracolsep{\fill}}rrrrrrrrrrrrr}
\multicolumn{3}{l}{Parameters}&
\multicolumn{5}{c}{Averaged Results}&
\multicolumn{5}{c}{Comparisons}\cr
\hline
\multicolumn1c{$n$}&\multicolumn1c{$S^*_{MAX}$}&
\multicolumn1c{$t_1$}&\multicolumn1c{\ $r_1$}&
\multicolumn1c{\ $m_1$}&\multicolumn1c{$t_2$}&
\multicolumn1c{$r_2$}&\multicolumn1c{$m_2$}
&\multicolumn1c{$t_{lb}$}&\multicolumn1c{\ \ $t_1/t_2$}&
$r_1/r_2$&$m_1/m_2$&
$t_1/t_{lb}$\cr
\hline
10\tablenote{Stanford Synchrotron Radiation Laboratory (Stanford University,
Stanford, CA)}&1\quad &4&.0007&4&4&.0020&4&4&1.000&.333&1.000&1.000\cr
10\tablenote{$R_{\rm FREE}=R$ factor for the $\sim 5$\% of the randomly
chosen unique ref\/lections not used in the ref\/inement.}&5\quad &50&.0008&8&50&.0020&12&49&.999&.417&.698&1.020\cr
100\tablenote{Calculated for all observed data}&20\quad &2840975&.0423&95&2871117&.1083&521&---&
.990&.390&.182&---\ \ \cr
\hline
\end{tabular*}
\end{table*}

\end{document}

### 2013-11-05 cccp.py

@@ -35,6 +35,7 @@ def main():
     parser.add_argument('--analysis', action='store_true', default=False, help="Add this flag for results calculation")
     parser.add_argument('--analysis-store-only-best', action='store_true', default=False, help="Add this flag for results calculation storing only the best result")
     parser.add_argument('--plot-iv-analysis', action='store_true', default=False, help="Shows some plot about Information Value Analysis")
+    parser.add_argument('--plot-works', action='store_true', default=False, help="Plot corpus information")
     parser.add_argument('--window_size_generator', default='WindowsHardCodedSizeGenerator', help="Select a Window Size generator Algorhitm")
     parser.add_argument('--calculate-results', action='store_true', default=False, help="Calculate Information Value Results for Documents")
     parser.add_argument('--documents', nargs='+', metavar=('name'), help='Selects documents from name regex')
@@ -56,6 +57,10 @@ def main():
     if args.calculate_results:
         from commands.database import calculate_results
         calculate_results()
+
+    if args.plot_works:
+        from plot import works_plots
+        works_plots.plot_all()
 
     doc_list = None
     if args.documents:
@@ -85,7 +90,7 @@ def main():
     if args.notebook_server:
         subprocess.call("PYTHONPATH=$PYTHONPATH:$PWD; ipython notebook --notebook-dir=.", shell=True)
     if args.shell:
-        subprocess.call("ipython -i interpreter.py --pylab", shell=True)
+        subprocess.call("ipython -i interpreter.py", shell=True)
 
 
 def init_logging():

### 2013-11-05 interpreter.py

@@ -1,6 +1,5 @@
 #! coding utf-8
-
-""" 
+"""
   Run this before opening a console
 """
 import ming

### 2013-11-05 plot/works_plots.py

@@ -1,0 +1,58 @@
+# coding: utf-8
+from interpreter import *
+import operator
+import logging
+import matplotlib.pyplot as plt
+from information_value.models import Document
+
+log = logging.getLogger('lenin')
+
+
+def plot_length_histogram(docs, title, number_of_bins):
+    num_tokens = [doc.number_of_words for doc in docs]
+    plt.title(title)
+    plt.xlabel("Number of words")
+    plt.ylabel("Amount of works")
+    plt.hist(num_tokens, bins=number_of_bins)
+
+
+def plot_small_documents():
+    docs = Document.query.find({'number_of_words': {'$gte': 2000, '$lte': 20000}})
+    plot_length_histogram(docs, number_of_bins=9, title="Histogram for works with <20k words")
+
+
+def plot_big_documents():
+    docs = Document.query.find({'number_of_words': {'$gte': 20000}})
+    plot_length_histogram(
+        docs,
+        title="Histogram for works with >20k words",
+        number_of_bins=10)
+
+
+def plot_tokens_per_year():
+    data = db.document.aggregate([
+        {"$group": {"_id": "$year", "number_of_works": {"$sum": 1}}}
+    ])['result']
+    data = sorted(data, key=lambda x: int(x["_id"]))
+    years = map(lambda x: int(x["_id"]), data)
+    number_of_works = map(operator.itemgetter("number_of_works"), data)
+
+    plt.title("Number of works per year")
+    plt.plot(years, number_of_works)
+
+
+BASE_DIR = "paper/figures/"
+
+
+def plot_all():
+    plot_small_documents()
+    plt.savefig(BASE_DIR + "hist_tokens_small_works.eps")
+    plt.close()
+
+    plot_big_documents()
+    plt.savefig(BASE_DIR + "hist_tokens_big_works.eps")
+    plt.close()
+
+    plot_tokens_per_year()
+    plt.savefig(BASE_DIR + "tokens_per_year.eps")
+    plt.close()

### 2013-11-05 plot/works_plots.py
Improved graphics ;)

@@ -8,25 +8,30 @@ from information_value.models import Document
 log = logging.getLogger('lenin')
 
 
-def plot_length_histogram(docs, title, number_of_bins):
+def plot_length_histogram(docs, title, **kwargs):
     num_tokens = [doc.number_of_words for doc in docs]
     plt.title(title)
     plt.xlabel("Number of words")
     plt.ylabel("Amount of works")
-    plt.hist(num_tokens, bins=number_of_bins)
+    plt.hist(num_tokens, **kwargs)
 
 
 def plot_small_documents():
     docs = Document.query.find({'number_of_words': {'$gte': 2000, '$lte': 20000}})
-    plot_length_histogram(docs, number_of_bins=9, title="Histogram for works with <20k words")
+    plot_length_histogram(
+        docs,
+        bins=9,
+        range=(2000, 20000),
+        title="Histogram for works with <20k words")
 
 
 def plot_big_documents():
     docs = Document.query.find({'number_of_words': {'$gte': 20000}})
     plot_length_histogram(
         docs,
+        range=(20000, 140000),
         title="Histogram for works with >20k words",
-        number_of_bins=10)
+        bins=12)
 
 
 def plot_tokens_per_year():

### 2013-11-08 paper/paper.tex
Fixed title.
paper method.wordnet subsection in spanish

@@
 \centerline{\includegraphics[width=.4\textwidth]{figures/tokens_per_year.eps}}
-\caption{Number of tokens per year}\label{afoto}
+\caption{Number of works per year}\label{afoto}
 \end{figure}
@@
 \subsection{Information Value Framework}
+\medskip
 %
@@
 \subsection{Wordnet analyzer}
-Consideremos el siguiente problema: ¿cómo calcular la similaridad o distancia de un documento a un cierto concepto?
-El enfoque que utilizamos en este trabajo es el de realizar una representación del documento como un conjunto de palabras, y en base a esto usar una noción topológica de similaridad/distancia .
+Consideremos el siguiente problema:
+\newline
+¿Cómo calcular la similaridad o distancia de un documento a un cierto concepto? 
+\newline
+El enfoque que utilizamos en este trabajo es el de realizar una representación del documento como un conjunto de palabras, y en base a esto usar una noción topológica de similaridad/distancia.
+La proyección del documento al espacio de palabras la realizamos utilizando la t\'ecnica de Information Value reci\'en descripta.
+En este espacio, utilizamos Wordnet para definir una noción de distancia entre el conjunto de palabras que representan al texto y diferentes conjuntos representando conceptos.
+\newline
+Para un documento dado, el módulo de information value genera una lista con lo $n$ términos más importantes y su iv.
+Estos valores se normalizan -dividiendo por la suma de los valores-, obteniendo así uno de los inputs del proceso siguiente.
+Recordemos, nuestro objetivo es asignar una distancia entre un documento y un concepto.
+Digamos, decidir cuán presente está o cuán importante es un concepto en un documento.
+\newline
+Wordnet es una base de datos de palabras, agrupadas en conjuntos de sinónimos (synsets), cada uno de los cuales posee una definición y diferentes relaciones semánticas con otros synsets (por ejemplo: hipernimia, hiponimia, meronimia, etc).
+Sobre estas relaciones semánticas es posible definir distintas métricas de distancia y similaridad entre synsets (Ver [1])
+\newline
+Utilizando las métricas disponibles en el módulo nltk de python para wordnet definimos la similaridad entre dos palabras como la máxima similaridad entre todos los synsets de ambas.
+(**NOTA Parametrizable: puede ser sólo el primer synset de ambos y puede no ser la máxima similaridad sino un promedio.
+También para algunas métricas quedan afuera los synsets que no son sustantivos).
+\begin{multline}
+S_w(w_1, w_2) = max \{ S_s(s_1, s_2) \}\\\ donde\ s_1 \in synsets(w_1), s_2 \in synsets(w_2)
+\end{multline}
+
+Para path similarity vale que $0 \leq S_w \leq 1$.
+
+Sobre $S_w$ (de word similarity) definimos la similaridad de un documento a un término como:
+
+\begin{equation}
+S_{dw}(d, w) = sum \{ S_w(d_i, w) \times p(d_i)  \} 
+\end{equation}
+
+donde las tuplas $(d_i , p(d_i))$ representan las palabras más importantes del documento $d$, y sus respectivos pesos normalizados. Vale que $0 \leq p(d_i) \leq 1$ pues está normalizado.
+
+Por ejemplo $S_dw$(“Estado y Revolución”, “guerra”) = NNN. $S_dw$ es una noción de cercanía entre un documento y una palabra.
+
+Finalmente, definimos la noción de similaridad entre un año y una palabra como el promedio de las similaridades ($S_{dw}$) 
+de los distintos documentos producidos durante ese año con la palabra en cuestión.
 
@@
 %
-S(x, C) = max { ... }
-
-Usamos la distancia path.
-
-Ahora, dado un documento, calculamos
 

### 2013-11-09 paper/paper.tex
paper.tex actualizado

@@
 \begin{multline}
-S_w(w_1, w_2) = max \{ S_s(s_1, s_2) \}\\\ donde\ s_1 \in synsets(w_1), s_2 \in synsets(w_2)
+S_w(w_1, w_2) = max \{ S_s(s_1, s_2) \}: s_1 \in synsets(w_1),\\ s_2 \in synsets(w_2)
 \end{multline}
@@
 
-Por ejemplo $S_dw$(“Estado y Revolución”, “guerra”) = NNN. $S_dw$ es una noción de cercanía entre un documento y una palabra.
+Por ejemplo $S_{dw}$(“Estado y Revolución”, “guerra”) = NNN. $S_{dw}$ es una noción de cercanía entre un documento y una palabra.
 
 Finalmente, definimos la noción de similaridad entre un año y una palabra como el promedio de las similaridades ($S_{dw}$) 
-de los distintos documentos producidos durante ese año con la palabra en cuestión.
+de los distintos documentos producidos durante ese año con la palabra en cuestión:
+\begin{equation}
+  S_{yw}(y, w) = mean \{ S_dw(y_i, w) \} : y_i \in docs(y) 
+\end{equation}
+
+Los resultados que presentaremos a continuaci\'on est\'an apoyados en distintas configuraciones de estas tres m\'etricas ($S_w$, $S_dw$ y $S_{yw}$).
 
@@
 * Tabla de top words de Estado y Revolución
+\begin{center}
+  \begin{tabular}{ | l | l | l |}
+    \hline
+    \multicolumn{3}{|c|}{Top words for `State and Revolution'} \\ \hline
+    \# & Word & Information Value \\ \hline
+    1 & War & 20  \\ \hline
+    2 & Revolution & Frula  \\ \hline
+    3 & 10C & 21C \\ \hline
+  \end{tabular}
+\end{center}
+
 * Distancia a algunos conceptos de estado y revolución
+
 \subsection{Resultados sobre años}
@@
 \section{Acknowledgments}
+
 \section{Literature cited}

### 2013-11-09 paper/paper.tex
tables

@@
 \subsection{Information Value Framework}
+
 \medskip
@@
     \# & Word & Information Value \\ \hline
-    1 & War & 20  \\ \hline
-    2 & Revolution & Frula  \\ \hline
-    3 & 10C & 21C \\ \hline
+    1 & kautsky & 0.10 \\ \hline
+    2 &  marx & 0.09 \\ \hline
+    3 &  revolution & 0.09 \\ \hline
+    4 &  works & 0.06 \\ \hline 
+    5 & engels & 0.06 \\ \hline
+    6 &  society & 0.06 \\ \hline
+    7 & power & 0.05 \\ \hline
+    8 &  party & 0.04 \\ \hline
+    9 &  social & 0.04 \\ \hline
+    10 &  experience & 0.03 \\ \hline 
+    11 & bernstein & 0.03 \\ \hline
+    12 &  question & 0.03 \\ \hline 
+    13 & equality & 0.03 \\ \hline
+    14 &  phase & 0.03 \\ \hline
+    15 & 1917 & 0.03 \\ \hline
+    16 & commune & 0.03 \\ \hline
+    17 & one & 0.03 \\ \hline
+    18 & republic & 0.03 \\ \hline
+    19 & class & 0.02 \\ \hline
+    20 & law & 0.02 \\ \hline
+  \end{tabular}
+\end{center}
+
+\begin{center}
+  \begin{tabular}{ | r |l |}
+    \hline
+    \multicolumn{2}{|c|}{$S_{dw}($`State and Revolution'$, w)$} \\ \hline
+      $w$ & $S_{dw}(d, w)$ \\ \hline
+      revolution &  0.177  \\ \hline
+      power &  0.169  \\ \hline
+      state &  0.154  \\ \hline
+      commune &  0.133  \\ \hline
+      republic &  0.123  \\ \hline
+      politics &  0.118  \\ \hline
+      music &  0.114  \\ \hline
+      war &  0.110  \\ \hline
+      philosophy &  0.094  \\ \hline
+      idealism &  0.084  \\ \hline
+      chicken &  0.092  \\ \hline
+      computer &  0.082  \\ \hline
+      mosquito &  0.044  \\ \hline
+      lion &  0.059  \\ \hline
+      alcohol &  0.067  \\ \hline
+      toilette &  0.069  \\ \hline
   \end{tabular}

### 2013-11-09 paper/paper.tex

@@
 \subsection{Information Value Framework}
-
 \medskip
@@
     \# & Word & Information Value \\ \hline
+
     1 & kautsky & 0.10 \\ \hline

### 2013-11-21 analyzers/tests/tests.py
Add some tests.

@@ -12,6 +12,7 @@ from information_value.models import DocumentList
 from analyzers.wn_analyzer import WordNetAnalyzer
 from analyzers.wn_analyzer import wn
 
+
 class TestAnalyzers(LeninTestCase):
 
   def test_war_analyzer(self):

### 2013-11-21 analyzers/tests/wn_analyzer_tests.py

@@ -1,0 +1,41 @@
+#! coding:utf-8
+from analyzers.wn_analyzer import WordNetAnalyzer
+from unittest import TestCase
+from nltk.corpus import wordnet as wn
+
+
+class GetWordSynsetsTest(TestCase):
+    def test_get_synsets_for_a_word_return_the_correct_amount_of_synsets(self):
+        word = "war"
+
+        self.assertEqual(len(WordNetAnalyzer.get_word_synsets(word)), 4)
+
+
+class GetInitSynsetsForWordTest(TestCase):
+    def test_get_init_synsets_returns_the_correct_amount_of_synsets_(self):
+        word = "war"
+
+        synsets = WordNetAnalyzer.get_init_synsets_for_word(word)
+
+        self.assertEqual(len(synsets), 4)
+        self.assertAlmostEqual(synsets[0][1], .25)
+
+class JudgeSynsetTest(TestCase):
+
+    def test_returns_1_for_synset_contained_in_set(self):
+        ponderated_war_synsets = WordNetAnalyzer.get_init_synsets_for_word("war")
+        analyzer = WordNetAnalyzer(ponderated_war_synsets)
+        # This synset should be in the initial war synset
+        war_synset = wn.synset("war.n.01")
+
+        self.assertAlmostEqual(analyzer.judge_synset(war_synset), 1.0)
+
+    def test_returns_less_than_1_for_synset_not_contained(self):
+        ponderated_war_synsets = WordNetAnalyzer.get_init_synsets_for_word("war")
+        analyzer = WordNetAnalyzer(ponderated_war_synsets)
+
+        music_synset = wn.synset("music.n.01")
+
+        self.assertTrue(analyzer.judge_synset(music_synset) < 1)        
+
+

### 2013-11-21 analyzers/wn_analyzer.py

@@ -65,14 +65,8 @@ class WordNetAnalyzer:
         paths = [syn.path_similarity(synset) for (syn, ponderacion) in self.synsets]
         path = max(paths)
 
-        lchs = [syn.lch_similarity(synset) for (syn, ponderacion) in self.synsets]
-        lch = max(lchs)
-
-        wups = [syn.wup_similarity(synset) for (syn, ponderacion) in self.synsets]
-        wup = max(wups)
-
-        return self.distance_measure(path, lch, wup)
-
+        return path
+        
     def distance_measure(self, path, lch, wup):
         if self.use_similarity == 'path':
             return path

### 2013-11-21 analyzers/tests/judge_synset_tests.py
Add tests for judge_synset and judge_word.

@@ -1,0 +1,22 @@
+#! coding:utf-8
+from analyzers.wn_analyzer import WordNetAnalyzer
+from unittest import TestCase
+from nltk.corpus import wordnet as wn
+
+class JudgeSynsetTest(TestCase):
+
+    def test_returns_1_for_synset_contained_in_set(self):
+        ponderated_war_synsets = WordNetAnalyzer.get_init_synsets_for_word("war")
+        analyzer = WordNetAnalyzer(ponderated_war_synsets)
+        # This synset should be in the initial war synset
+        war_synset = wn.synset("war.n.01")
+
+        self.assertAlmostEqual(analyzer.judge_synset(war_synset), 1.0)
+
+    def test_returns_less_than_1_for_synset_not_contained(self):
+        ponderated_war_synsets = WordNetAnalyzer.get_init_synsets_for_word("war")
+        analyzer = WordNetAnalyzer(ponderated_war_synsets)
+
+        music_synset = wn.synset("music.n.01")
+
+        self.assertTrue(analyzer.judge_synset(music_synset) < 1)   

### 2013-11-21 analyzers/tests/judge_word_tests.py

@@ -1,0 +1,16 @@
+#! coding:utf-8
+from analyzers.wn_analyzer import WordNetAnalyzer
+from unittest import TestCase
+
+class JudgeWordTests(TestCase):
+    def test_returns_1_for_same_word_as_synsets(self):
+        ponderated_war_synsets = WordNetAnalyzer.get_init_synsets_for_word("war")
+        analyzer = WordNetAnalyzer(ponderated_war_synsets)
+
+        self.assertAlmostEqual(analyzer.judge_word("war"), 1.0)
+
+    def test_returns_less_than_1_for_distinct_words(self):
+        ponderated_war_synsets = WordNetAnalyzer.get_init_synsets_for_word("war")
+        analyzer = WordNetAnalyzer(ponderated_war_synsets)
+
+        self.assertTrue(analyzer.judge_word("music") < 1.0)

### 2013-11-21 analyzers/tests/wn_analyzer_tests.py

@@ -19,23 +19,4 @@ class GetInitSynsetsForWordTest(TestCase):
 
         self.assertEqual(len(synsets), 4)
         self.assertAlmostEqual(synsets[0][1], .25)
-
-class JudgeSynsetTest(TestCase):
-
-    def test_returns_1_for_synset_contained_in_set(self):
-        ponderated_war_synsets = WordNetAnalyzer.get_init_synsets_for_word("war")
-        analyzer = WordNetAnalyzer(ponderated_war_synsets)
-        # This synset should be in the initial war synset
-        war_synset = wn.synset("war.n.01")
-
-        self.assertAlmostEqual(analyzer.judge_synset(war_synset), 1.0)
-
-    def test_returns_less_than_1_for_synset_not_contained(self):
-        ponderated_war_synsets = WordNetAnalyzer.get_init_synsets_for_word("war")
-        analyzer = WordNetAnalyzer(ponderated_war_synsets)
-
-        music_synset = wn.synset("music.n.01")
-
-        self.assertTrue(analyzer.judge_synset(music_synset) < 1)        
-
-
+     

### 2013-11-21 analyzers/wn_analyzer.py

@@ -65,8 +65,14 @@ class WordNetAnalyzer:
         paths = [syn.path_similarity(synset) for (syn, ponderacion) in self.synsets]
         path = max(paths)
 
-        return path
-        
+        lchs = [syn.lch_similarity(synset) for (syn, ponderacion) in self.synsets]
+        lch = max(lchs)
+
+        wups = [syn.wup_similarity(synset) for (syn, ponderacion) in self.synsets]
+        wup = max(wups)
+
+        return self.distance_measure(path, lch, wup)
+
     def distance_measure(self, path, lch, wup):
         if self.use_similarity == 'path':
             return path

### 2013-11-21 analyzers/tests/wn_analyzer_tests.py
Refactor test.

@@ -18,5 +18,7 @@ class GetInitSynsetsForWordTest(TestCase):
         synsets = WordNetAnalyzer.get_init_synsets_for_word(word)
 
         self.assertEqual(len(synsets), 4)
-        self.assertAlmostEqual(synsets[0][1], .25)
-     
+        self.assertAlmostEqual(synsets[0][1], .25)     
+        self.assertAlmostEqual(synsets[1][1], .25)
+        self.assertAlmostEqual(synsets[2][1], .25)
+        self.assertAlmostEqual(synsets[3][1], .25)

### 2013-11-21 analyzers/tests/wn_analyzer_tests.py
Several refactors.

@@ -22,3 +22,4 @@ class GetInitSynsetsForWordTest(TestCase):
         self.assertAlmostEqual(synsets[1][1], .25)
         self.assertAlmostEqual(synsets[2][1], .25)
         self.assertAlmostEqual(synsets[3][1], .25)
+

### 2013-11-21 analyzers/wn_analyzer.py

@@ -15,9 +15,9 @@ class WordNetAnalyzer:
   # synsets is a list((synset, ponderation))
   # sum(ponderation) must be 1
 
-    def __init__(self, synsets, document=None, use_similarity='path'):
-        self.document = document
-        self.synsets = synsets
+    def __init__(self, ponderated_synsets, use_similarity='path'):
+        self.document = None
+        self.ponderated_synsets = ponderated_synsets
         self.use_similarity = use_similarity
 
     def set_similarity(self, use_similarity):
@@ -35,9 +35,9 @@ class WordNetAnalyzer:
         return [(word, ponderation, self.judge_word(word)) for (word, ponderation) in self.top_words]
 
     # return a value between 0 and 1
-    def judge_doc(self, document=None):
-        if document:
-            self.document = document
+    def judge_doc(self, document):
+        self.document = document
+
         self.top_words = self.document.top_words(20)
         return sum([ponderation * result for (word, ponderation, result) in self.get_words_results()])
 
@@ -61,14 +61,13 @@ class WordNetAnalyzer:
         return synsets
 
     def judge_synset(self, synset):
+        synsets = [s[0] for s in self.ponderated_synsets]
+        path = similarity_synsets_to_synset(synsets, synset)
 
-        paths = [syn.path_similarity(synset) for (syn, ponderacion) in self.synsets]
-        path = max(paths)
-
-        lchs = [syn.lch_similarity(synset) for (syn, ponderacion) in self.synsets]
+        lchs = [syn.lch_similarity(synset) for (syn, ponderacion) in self.ponderated_synsets]
         lch = max(lchs)
 
-        wups = [syn.wup_similarity(synset) for (syn, ponderacion) in self.synsets]
+        wups = [syn.wup_similarity(synset) for (syn, ponderacion) in self.ponderated_synsets]
         wup = max(wups)
 
         return self.distance_measure(path, lch, wup)
@@ -92,6 +91,14 @@ class WordNetAnalyzer:
             return max(synsets_results)
         else:
             return 0
+
+"""
+Returns the similarity between a set of synsets, and a particular synset
+"""
+def similarity_synsets_to_synset(list_of_synsets, synset):
+    similarities = [synset.path_similarity(_synset) for _synset in list_of_synsets]
+    return max(similarities)
+
 
 
 def get_wnas():

### 2013-11-21 analyzers/wn_analyzer.py
Improve performance.

@@ -61,26 +61,15 @@ class WordNetAnalyzer:
         return synsets
 
     def judge_synset(self, synset):
-        synsets = [s[0] for s in self.ponderated_synsets]
-        path = similarity_synsets_to_synset(synsets, synset)
-
-        lchs = [syn.lch_similarity(synset) for (syn, ponderacion) in self.ponderated_synsets]
-        lch = max(lchs)
-
-        wups = [syn.wup_similarity(synset) for (syn, ponderacion) in self.ponderated_synsets]
-        wup = max(wups)
-
-        return self.distance_measure(path, lch, wup)
-
-    def distance_measure(self, path, lch, wup):
-        if self.use_similarity == 'path':
-            return path
-        elif self.use_similarity == 'lch':
-            return lch
+        if self.use_similarity == 'lch':
+            lchs = [syn.lch_similarity(synset) for (syn, ponderacion) in self.ponderated_synsets]
+            return max(lchs)
         elif self.use_similarity == 'wup':
-            return wup
+            wups = [syn.wup_similarity(synset) for (syn, ponderacion) in self.ponderated_synsets]
+            return max(wups)
         else:
-            return path
+            synsets = [s[0] for s in self.ponderated_synsets]
+            return similarity_synsets_to_synset(synsets, synset)
 
     # judge a word according to criterion
     #@return double a value between 1.0 and 0.0

### 2013-11-21 analyzers/tests/tests.py
Encapsulate creation of analyzer.

@@ -5,15 +5,12 @@ from test import LeninTestCase
 from unittest import TestCase
 from unittest import skip
 
-from information_value.models import Document
-from information_value.models import InformationValueResult
-from information_value.models import DocumentList
 
 from analyzers.wn_analyzer import WordNetAnalyzer
 from analyzers.wn_analyzer import wn
 
 
-class TestAnalyzers(LeninTestCase):
+class TestAnalyzers(TestCase):
 
   def test_war_analyzer(self):
     
@@ -31,7 +28,7 @@ class TestAnalyzers(LeninTestCase):
     self.assertEqual((wn.synset("war.n.03"), 0.25), all_war_synset_list[2])
     self.assertEqual((wn.synset("war.n.04"), 0.25), all_war_synset_list[3])
     
-    all_war_analyzer =  WordNetAnalyzer(all_war_synset_list)
+    all_war_analyzer =  WordNetAnalyzer.create_analyzer_for("war")
     one_war_analyzer =  WordNetAnalyzer(just_first_war_synset_list)
 
     self.assertEqual(1.0, one_war_analyzer.judge_synset(just_first_war_synset_list[0][0]), "compara el analizador contra su propio synset")

### 2013-11-21 analyzers/wn_analyzer.py

@@ -12,8 +12,14 @@ reload(config)
 # Similarity definitions:
 # http://nltk.googlecode.com/svn/trunk/doc/api/nltk.corpus.reader.wordnet.Synset-class.html#path_similarity
 class WordNetAnalyzer:
-  # synsets is a list((synset, ponderation))
-  # sum(ponderation) must be 1
+
+    @classmethod
+    def create_analyzer_for(cls, word):
+        ponderated_synsets = cls.get_init_synsets_for_word(word)
+        return cls(ponderated_synsets)  
+
+    # ponderated_synsets is a list((synset, ponderation))
+    # sum(ponderation) must be 1
 
     def __init__(self, ponderated_synsets, use_similarity='path'):
         self.document = None

### 2013-11-21 analyzers/wn_analyzer.py
Use generators instead of lists.

@@ -68,13 +68,13 @@ class WordNetAnalyzer:
 
     def judge_synset(self, synset):
         if self.use_similarity == 'lch':
-            lchs = [syn.lch_similarity(synset) for (syn, ponderacion) in self.ponderated_synsets]
+            lchs = (syn.lch_similarity(synset) for (syn, ponderacion) in self.ponderated_synsets)
             return max(lchs)
         elif self.use_similarity == 'wup':
-            wups = [syn.wup_similarity(synset) for (syn, ponderacion) in self.ponderated_synsets]
+            wups = (syn.wup_similarity(synset) for (syn, ponderacion) in self.ponderated_synsets)
             return max(wups)
         else:
-            synsets = [s[0] for s in self.ponderated_synsets]
+            synsets = (s[0] for s in self.ponderated_synsets)
             return similarity_synsets_to_synset(synsets, synset)
 
     # judge a word according to criterion

### 2013-11-21 paper/paper.tex

@@
 \medskip
-%
-%*Aclarar settings de Zannette
-%*Maximización, ventanas
-%*Cálculo paralelo
-%*Ajustes de parametros para que concuerden con los resultados de zanette
-%*doc.top_words()
-%  representación como set de palabras ponderadas por documento.
+
+\subsubsection{Optimal window size selection}
+As \cite{DARWIN} mentions, we should consider the window size which maximizes the information value per word, for some sense of it.
+
+Let's suppose we have a document, and a window size $W_S$ for which the information value algorithm returns a list $\{(w_1, v_1), (w_2, v_2), \dots ,(w_n, v_n) \}$ of word-information value pairs, in decreasing order of information value so that $v_1 \geq v_2 \geq \dots \geq v_n$.
+How would we assign some value to this pair of document-window size so we can choose the optimal window size?
+
+One possibility would be to take the greater information value, in this case $v_1$.
+This approach, however, gives all the value just to a single word.
+Another chance would be to take the average of all the information values, but this leads to a lot of noise added because of words without any value.
+
+The chosen approach is a tradeoff between both.
+We take the average not of all the words, but of a percentage of the most significative words.
+We call this percentage the \emph{sum threshold}.
+If $n$ is the number of words in the document, and $0 \leq ST \leq 1$ is the sum threshold, we calculate
+
+\begin{equation}
+  \frac{\sum_{i=1}^{[ST n]}v_i}{n} 
+\end{equation}
+
+The threshold value we used is $ST=0.001$, so it would consider only the $\frac{n}{1000}$ most significant words.
+The reason behind this was that it fitted the results from \cite{DARWIN} for the texts The origin of the species, Moby Dick, and  The Analysis of the mind.
 
@@
 
-Por ejemplo $S_{dw}$(“Estado y Revolución”, “guerra”) = NNN. $S_{dw}$ es una noción de cercanía entre un documento y una palabra.
+Por ejemplo $S_{dw}$(“Estado y Revolución”, “guerra”) = 0.110. $S_{dw}$ es una noción de cercanía entre un documento y una palabra.
 
@@
 
-\subsection{Data Sources}
-We are interested in studying the evolution of almost sharp fronts
-for the QG equation. These are weak solutions of the equation with
-large gradient ($\sim \displaystyle{ \inlinefrac{1}{\delta}}$, where $2
-\delta$ is the thickness of the transition layer for $\theta$).
-
-\begin{materials}
-\section{Digital RNA SNP Analysis} A real-time PCR assay was designed
-to amplify {\it PLAC4} mRNA, with the two SNP alleles being discriminated
-by TaqMan probes. {\it PLAC4} mRNA concentrations were quantified in
-extracted RNA samples followed by dilutions to approximately one target
-template molecule of either type (i.e., either allele) per well.
-Details are given in the {\it SI Materials and Methods}.
-
-\section{Digital RCD Analysis} Extracted DNA was quantified by
-spectrophotometry (NanoDrop Technologies, Wilmington, DE) and diluted to a
-concentration of 
-approximately one target template from either chr21 or ch1 per well.
-\end{materials}
+\appendix[Parallel calculus of information value]
 

### 2013-11-21 analyzers/wn_analyzer.py
music

@@ -155,6 +155,9 @@ def judge_list(doc_list, analyzer):
     return None
   return (sum([analyzer.judge_doc(doc)  for doc in doc_list]) / doc_list.total_docs)*100
  
+
+def wna_for(word):
+  return WordNetAnalyzer(WordNetAnalyzer.get_init_synsets_for_word(word))
 def year_vs_concept_data():
   wnas = get_wnas()
   
@@ -162,6 +165,9 @@ def year_vs_concept_data():
   idealism =  WordNetAnalyzer(WordNetAnalyzer.get_init_synsets_for_word("idealism"))
   rev =  WordNetAnalyzer(WordNetAnalyzer.get_init_synsets_for_word("revolution"))
   filo =  WordNetAnalyzer(WordNetAnalyzer.get_init_synsets_for_word("philosophy"))
+
+  music = wna_for("music")
+  entity = wna_for("entity")
 
   maximum = 0.0
   res = dict()
@@ -177,9 +183,11 @@ def year_vs_concept_data():
     res[year]  = {#'praxis':     judge_list(doc_list, wnas["praxis"]),
                   #'theory':     judge_list(doc_list, wnas["theory"]), 
                   'rev': (judge_list(doc_list, rev) -7),
-                  'filo': (judge_list(doc_list, filo)-7),
+                  #'filo': (judge_list(doc_list, filo)-7),
+                  'music': (judge_list(doc_list, music) -7),
+                  'entity': (judge_list(doc_list, entity) -7),
                   'war':       ( judge_list(doc_list, war) - 7),
-                  'idea':       ( judge_list(doc_list, idealism) - 7),
+                  #'idea':       ( judge_list(doc_list, idealism) - 7),
                   }
     print "year: %s, total docs: %s, war res: %s" % (year, doc_list.total_docs, res[year])
   return res

### 2013-11-22 analyzers/wn_analyzer.py
better interface for wn-plots

@@ -1,9 +1,12 @@
 # This Python file uses the following encoding: utf-8
 from __future__ import division
 import nltk
+import logging
+
 from nltk.corpus import wordnet as wn
 from information_value.models import *
 
+log = logging.getLogger('lenin')
 
 import config
 reload(config)
@@ -13,37 +16,46 @@ class WordNetAnalyzer:
 
   #synsets is a list((synset, ponderation))
   #sum(ponderation) must be 1
-  def __init__(self, synsets, document = None, use_similarity = 'path'):
-    self.document = document
-    self.synsets = synsets
+  def __init__(self, word, use_similarity = 'path'):
+
+    self.word = word
+    self.synsets = WordNetAnalyzer.get_init_synsets_for_word(word)
     self.use_similarity = use_similarity
-    assert sum([ponderation for (synset, ponderation) in self.synsets]) == 1.0
 
   def set_similarity(self, use_similarity):
+    '''
+    synset similarity measume
+    '''
     self.use_similarity = use_similarity
 
-  #creates the trivial synsets set for a given word
+
+  def distance_measure(self, path, lch, wup):
+      if self.use_similarity == 'path':
+        return path
+      elif self.use_similarity == 'lch':
+        return lch
+      elif self.use_similarity == 'wup':
+        return wup
+      else:
+        return path
+      #return (path + lch + wup) / 3
+       #others are not between 0 and 1
+
+
   @staticmethod
-  def get_init_synsets_for_word(word, take_only_first = False):
-    synsets = WordNetAnalyzer.get_word_synsets(word, take_only_first)
+  def get_init_synsets_for_word(word, only_first = False):
+    '''
+    creates the trivial synsets set for a given word
+    '''
+
+    synsets = WordNetAnalyzer.get_word_synsets(word, only_first)
     return [(synset, 1.0/ len(synsets)) for synset in synsets]
-
-  #return list((word, ponderation [between 0 and 1], result [between 0 and 1]))
-  def get_words_results(self):
-    return [(word, ponderation, self.judge_word(word) )  for (word, ponderation) in self.top_words]
-
-  #return a value between 0 and 1
-  def judge_doc(self, document = None):
-    if document != None:
-       self.document = document
-    self.top_words = self.document.top_words(20)
[…]

### 2013-11-22 cccp.py

@@ -38,6 +38,9 @@ def main():
     parser.add_argument('--window_size_generator', default='WindowsHardCodedSizeGenerator', help="Select a Window Size generator Algorhitm")
     parser.add_argument('--calculate-results', action='store_true', default=False, help="Calculate Information Value Results for Documents")
     parser.add_argument('--documents', nargs='+', metavar=('name'), help='Selects documents from name regex')
+    parser.add_argument('--concepts', nargs='+', metavar=('word'), help='Selects concepts to print (works with --plot)')
+    parser.add_argument('--min', metavar=('year'), help='year to start plot (works with --plot, default=1899)')
+    parser.add_argument('--max', metavar=('year'), help='year to end plot (works with --plot, default=1923)')
     parser.add_argument('--notebook-server', action='store_true', default=False, help='Starts notebook server')
     if len(sys.argv)==1:
         parser.print_help()
@@ -57,12 +60,15 @@ def main():
         from commands.database import calculate_results
         calculate_results()
 
+
     doc_list = None
     if args.documents:
         from information_value.models import DocumentList
         doc_list = DocumentList(args.documents[0])
+    
     if args.drop_iv:
         drop_iv()
+    
     if args.analysis:
         from commands.database import calculate_results
         documents = None
@@ -70,18 +76,36 @@ def main():
             documents = doc_list.documents
         calculate_results(documents=documents, window_size_algorithm=args.window_size_generator, store_only_best=False)
     if args.analysis_store_only_best:
+        
         from commands.database import calculate_results
         documents = None
         if doc_list:
             documents = doc_list.documents
         calculate_results(documents=documents, window_size_algorithm=args.window_size_generator, store_only_best=True)    
+   
     if args.plot:
-        #from plot import window_sizes
+        
         from plot import wn_plots
         #window_sizes.plot_scale_vs_information(doc_list.documents)
         #window_sizes.plot_len_vs_most_informative(doc_list.documents)
         import analyzers.wn_analyzer as wa
-        wn_plots.plot_year_vs_concept_value(wa.year_vs_concept_data())
+        
+        concepts = None
+        if args.concepts:
+            concepts = args.concepts
+        if args.min:
+            year_min = int(args.min)
+        else:
+            year_min = 1899
+
+        if args.max:
[…]

### 2013-11-22 information_value/models.py

@@ -100,7 +100,8 @@ class Document(MappedClass):
       iv_words = [(t[0], t[1]) for t in iv_words if t[0] not in stop_words and (not greater_than_zero or t[1] > 0.0)][:total_words]
 
       iv_sum = sum([iv_value for (word, iv_value) in iv_words])
-      return [(word, iv_value / iv_sum) for (word, iv_value) in iv_words]
+      #return [(word, iv_value / iv_sum) for (word, iv_value) in iv_words]
+      return [(word, 1) for (word, iv_value) in iv_words]
       #return [(word, 1.0 / total_words) for (word, iv_value) in iv_words]
 
     # calculator_class is poor man's dependency injection :)
@@ -143,7 +144,7 @@ class Document(MappedClass):
     @property
     def short_name(self):
       ss = self.name.replace("Lenin: ", "")
-      return ss[: 50 + ss[50:].find(" ")]+"..."
+      return ss[: 40 + ss[40:].find(" ")]+"..."
 
     #generators test
     def result_list(self):
@@ -214,6 +215,8 @@ class DocumentList(object):
     self.base_load()
     #print self
 
+  def first(self):
+    return self.documents[0]
 
   def base_load(self):
     self.current = 0
@@ -327,5 +330,12 @@ class DocumentList(object):
     #for text in self.texts:
     #  res+="\r\n"+text.__repr__()
     #return res+"\r\n"+self.__repr__()
+
+def doc_for(name):
+  doc_list = DocumentList(name)
+  if doc_list.total_docs == 0:
+    return None
+  else:
+    return doc_list.first()
 
 Mapper.compile_all()

### 2013-11-22 interpreter.py

@@ -9,10 +9,12 @@ import config
 ming_config = {'ming.document_store.uri': config.DATABASE_URL}
 ming.configure(**ming_config)
 
-from information_value.models import Document, DocumentList, InformationValueResult
-from analyzers.wn_analyzer import WordNetAnalyzer
+from information_value.models import Document, DocumentList, InformationValueResult, doc_for
+from analyzers.wn_analyzer import WordNetAnalyzer, year_vs_concept_data, wnas_for, wna_for
 from nltk.corpus import wordnet as wn
 
+from cccp import init_logging
 from pymongo import MongoClient
+init_logging()
 client = MongoClient()
 db = client[config.DATABASE_NAME]

### 2013-11-22 plot/wn_plots.py

@@ -6,8 +6,12 @@ from collections import defaultdict
 
 import numpy as np
 import matplotlib.pyplot as plt
+
+
+
 from matplotlib.pyplot import legend
 from scipy import average
+from scipy.interpolate import spline
 
 import config
 from information_value.models import Document
@@ -21,22 +25,29 @@ def plot_year_vs_concept_value(values):
         }
     """
 
-    x = sorted(map(int, values.keys()))
-    print x
+    years = np.array(sorted(map(int, values.keys())))
+    print years
     y_concepts = defaultdict(list)
-    for year in x: #esto da orden, sino no andaba
+    for year in years: #esto da orden, sino no andaba
     #for year, word_values in values.iteritems():
         word_values = values[year]
         for word, value in word_values.iteritems():
-            y_concepts[word].append(value)
+            #if value > 0.2:
+                y_concepts[word].append(value)
+            #else:
+            #    y_concepts[word].append(0.0)
 
     for key, y_concept in y_concepts.iteritems():
-        plt.plot(x, y_concept, '-o')
+
+        #xnew = np.linspace(years.min(),years.max(),300)
+        #y_concept_smooth = spline(years,y_concept,xnew)        
+        #plt.plot(xnew, y_concept_smooth)
+        plt.plot(years, y_concept)
 
     legend(y_concepts.keys())
 
-    ticks = np.arange(1899,1924, 6)
-    labels = np.arange(1899,1924, 6)
+    ticks = np.arange(years.min(),years.max(), 1)
+    labels = np.arange(years.min(),years.max(), 1)
     plt.xticks(ticks, labels)
     plt.title('Year vs Concept value')
     plt.xlabel('Year')

### 2013-12-21 paper/distance.tex
Add separate paper for distance function.

--- 2013-11-21 paper/paper.tex
@@
 In order to discover how much related were Lenin Works to Russian History in nearly 20th century, we use the information value concept to extract the most important words from them.
-Therefore, we find out how far are them from certain concepts such as
-war, revolution, theory, etc. We expected this concepts to be nearer and farther to concepts 
-treated in Lenin's works depending on the events ranging from 1900 to 1924.
+Therefore, we find out how far are them from certain words such as
+war, revolution, theory, etc giving a Wordnet-based similarity function. 
 \end{abstract}
@@
 Having these value, we can pull the most representative words out of a text by selecting those of greater information value.
+Now our question arises: how distant is a word from a text?
+We use here the notion of distance between a point and a set defined as:
+
+\begin{equation}
+  d(a, S) = min_{x \in S} d(a, x) 
+\end{equation}
+
+being $S$ the set of most representative words. Hence, we are ``projecting'' a text into the set of their top words.
 
@@
 \subsection{Text Corpus}
-We gathered Lenin's work from the "Marxists Internet Archive".
-This proved to be a difficult task as the works were not in a common HTML format.
-The tool we used to do this is Scrapy, a very comprehensive Python crawling framework.
+We selected some starred works from Lenin from the "Marxists Internet Archive".
+Those works are very different in topic, some of them being strictly phylosophical essays (such as ``Materialism and Empiriocriticism'') and other being more political, such as ``State and Revolution'', and finally an economy essay called ``Imperialism, the highest stage of capitalism''
 
-In order to reduce noise in the corpus, we filtered all the letters and works that were comparatively little.
-Our information value theory doesn't work very well with texts with little repetition of words, so we decided to remove texts with less than 2000 words.
-
-\begin{figure}
-\centerline{\includegraphics[width=.4\textwidth]{figures/tokens_per_year.eps}}
-\caption{Number of works per year}\label{afoto}
-\end{figure}
-
-\begin{figure}
-\centerline{\includegraphics[width=.4\textwidth]{figures/hist_tokens_small_works.eps}}
-\caption{Distribution of works with respect to size (small works)}\label{afoto}
-\end{figure}
-
-\begin{figure}
-\centerline{\includegraphics[width=.4\textwidth]{figures/hist_tokens_big_works.eps}}
-\caption{Distribution of works with respect to size (big works)}\label{afoto}
-\end{figure}
+\begin{itemize}
+  \item What is to be done(1901)
+  \item Materialism and Empiriocriticism (1908)
+  \item Imperialism, the highest stage of capitalism (1916)
+  \item State and Revolution (1917)
+\end{itemize}
 

### 2013-12-21 paper/distance.tex
Add another work to documents being analyzed.

@@
 has a distribution in text that is not exactly uniform; an order of the word in the text that brings some sense to it.
+Ordering the words by their information value results in a list of the text's most representative words.
 
-Having these value, we can pull the most representative words out of a text by selecting those of greater information value.
-Now our question arises: how distant is a word from a text?
+In order to measure the distance/similarity between two words, we use Wordnet (see \cite{WORDNET}), a lexical database in English.
+Using a subset of all the possible ``senses'' of both words , we test several similarity notions between them.
+
+Having a similarity notion between words, and the most valuable words from a text, our question arises: how distant is a word from a text?
 We use here the notion of distance between a point and a set defined as:
@@
   \item What is to be done(1901)
+  \item The Agrarian Programme of Social-Democracy in the First Russian Revolution, 1905-1907 (1907)
   \item Materialism and Empiriocriticism (1908)
@@
 The reason behind this was that it fitted the results from \cite{DARWIN} for the texts The origin of the species, Moby Dick, and  The Analysis of the mind.
+
+\subsection{Top words for given works}
+
+\begin{center}
+  \begin{tabular}{ | l | l | }
+    \hline
+    \multicolumn{2}{|c|}{State and Revolution} \\ \hline
+    \# & Word  \\ \hline
+1 & kautsky \\ \hline
+2 & marx \\ \hline
+3 & revolution \\ \hline
+4 & works \\ \hline
+5 & engels \\ \hline
+6 & society \\ \hline
+7 & power \\ \hline
+8 & party \\ \hline
+9 & social \\ \hline
+10 & experience \\ \hline
+11 & bernstein \\ \hline
+12 & question \\ \hline
+13 & equality \\ \hline
+14 & phase \\ \hline
+15 & 1917 \\ \hline
+16 & commune \\ \hline
+17 & one \\ \hline
+18 & republic \\ \hline
+19 & class \\ \hline
+20 & law \\ \hline
+  \end{tabular}
+\end{center}
+
+\begin{center}
+  \begin{tabular}{ | l | l | }
+    \hline
+    \multicolumn{2}{|c|}{Imperialism, the Highest ...} \\ \hline
+    \# & Word  \\ \hline
+1 & enterprises \\ \hline
+2 & bank \\ \hline
+3 & imperialism \\ \hline
+4 & world \\ \hline
+5 & million \\ \hline
+6 & colonies \\ \hline
+7 & kautsky \\ \hline
+8 & colonial \\ \hline
+9 & production \\ \hline
+10 & cent \\ \hline
+11 & economic \\ \hline
+12 & company \\ \hline
+13 & capitalist \\ \hline
+14 & monopoly \\ \hline
+15 & big \\ \hline
+16 & countries \\ \hline
+17 & policy \\ \hline
+18 & powers \\ \hline
+19 & 000 \\ \hline
+20 & banks \\ \hline
+  \end{tabular}
+\end{center}
+
+\begin{center}
+  \begin{tabular}{ | l | l | }
+    \hline
+\multicolumn{2}{|c|}{Materialism and Empirio-criticism} \\ \hline
+\# & Word  \\ \hline
+1 & physics \\ \hline
+2 & social \\ \hline
+3 & avenarius \\ \hline
+4 & space \\ \hline
+5 & time \\ \hline
+6 & dietzgen \\ \hline
+7 & berkeley \\ \hline
+8 & truth \\ \hline
+9 & rey \\ \hline
+10 & objective \\ \hline
+11 & sensation \\ \hline
+12 & experience \\ \hline
+13 & pp \\ \hline
+14 & engels \\ \hline
+15 & motion \\ \hline
+16 & marx \\ \hline
+17 & book \\ \hline
+18 & works \\ \hline
+19 & vol \\ \hline
+20 & general \\ \hline
+  \end{tabular}
+\end{center}
+
+\begin{center}
+  \begin{tabular}{ | l | l | }
+    \hline
+\multicolumn{2}{|c|}{What Is To Be Done?} \\ \hline
+\# & Word  \\ \hline
+1 & local \\ \hline
+2 & organisation \\ \hline
+3 & abroad \\ \hline
+4 & union \\ \hline
+5 & criticism \\ \hline
+6 & economic \\ \hline
+7 & political \\ \hline
+8 & revolutionaries \\ \hline
+9 & freedom \\ \hline
+10 & newspapers \\ \hline
+11 & workers \\ \hline
+12 & nadezhdin \\ \hline
+13 & consciousness \\ \hline
+14 & newspaper \\ \hline
+15 & bourgeois \\ \hline
+16 & masses \\ \hline
+17 & martynov \\ \hline
+18 & would \\ \hline
+19 & movement \\ \hline
+20 & german \\ \hline
+  \end{tabular}
+\end{center}
+
+\begin{center}
+  \begin{tabular}{ | l | l | }
+    \hline
+\multicolumn{2}{|c|}{The Agrarian Programme of ...} \\ \hline
+\# & Word  \\ \hline
+1 & rent \\ \hline
+2 & dessiatins \\ \hline
+3 & 000 \\ \hline
+4 & land \\ \hline
+5 & maslov \\ \hline
+6 & peasants \\ \hline
+7 & capital \\ \hline
+8 & revolution \\ \hline
+9 & marx \\ \hline
+10 & people \\ \hline
+11 & nationalisation \\ \hline
+12 & plekhanov \\ \hline
+13 & restoration \\ \hline
+14 & right \\ \hline
+15 & latifundia \\ \hline
+16 & private \\ \hline
+17 & farming \\ \hline
+18 & free \\ \hline
+19 & central \\ \hline
+20 & lands \\ \hline
+  \end{tabular}
+\end{center}
 
@@
 %
-
-\section{Results}
-\subsection{Resultados sobre obras}
-* Tabla de top words de Estado y Revolución
-\begin{center}
-  \begin{tabular}{ | l | l | l |}
-    \hline
-    \multicolumn{3}{|c|}{Top words for `State and Revolution'} \\ \hline
-    \# & Word & Information Value \\ \hline
-
-    1 & kautsky & 0.10 \\ \hline
-    2 &  marx & 0.09 \\ \hline
-    3 &  revolution & 0.09 \\ \hline
-    4 &  works & 0.06 \\ \hline 
-    5 & engels & 0.06 \\ \hline
-    6 &  society & 0.06 \\ \hline
-    7 & power & 0.05 \\ \hline
-    8 &  party & 0.04 \\ \hline
-    9 &  social & 0.04 \\ \hline
-    10 &  experience & 0.03 \\ \hline 
-    11 & bernstein & 0.03 \\ \hline
-    12 &  question & 0.03 \\ \hline 
-    13 & equality & 0.03 \\ \hline
-    14 &  phase & 0.03 \\ \hline
-    15 & 1917 & 0.03 \\ \hline
-    16 & commune & 0.03 \\ \hline
-    17 & one & 0.03 \\ \hline
-    18 & republic & 0.03 \\ \hline
-    19 & class & 0.02 \\ \hline
-    20 & law & 0.02 \\ \hline
-  \end{tabular}
-\end{center}
-
-\begin{center}
-  \begin{tabular}{ | r |l |}
-    \hline
-    \multicolumn{2}{|c|}{$S_{dw}($`State and Revolution'$, w)$} \\ \hline
-      $w$ & $S_{dw}(d, w)$ \\ \hline
-      revolution &  0.177  \\ \hline
-      power &  0.169  \\ \hline
-      state &  0.154  \\ \hline
-      commune &  0.133  \\ \hline
-      republic &  0.123  \\ \hline
-      politics &  0.118  \\ \hline
-      music &  0.114  \\ \hline
-      war &  0.110  \\ \hline
-      philosophy &  0.094  \\ \hline
-      idealism &  0.084  \\ \hline
-      chicken &  0.092  \\ \hline
-      computer &  0.082  \\ \hline
-      mosquito &  0.044  \\ \hline
-      lion &  0.059  \\ \hline
-      alcohol &  0.067  \\ \hline
-      toilette &  0.069  \\ \hline
-  \end{tabular}
-\end{center}
 
@@
 M.A. Montemurro and D. H. Zanette, {\em Entropic analysis of the role of words in literary texts}, Adv. Complex Systems 5, September 27th 2001
+\bibitem{WORDNET}
+George A. Miller, {\em WordNet: A Lexical Database for English }, COMMUNICATIONS OF THE ACM November 1995/Vol. 38, No. 11
+
 \end{thebibliography}

### 2014-01-15 information_value/models.py
Add persistence to top senses.

@@ -2,7 +2,7 @@
 import logging
 import hashlib
 
-from nltk.corpus import stopwords
+from nltk.corpus import stopwords, wordnet as wn
 from nltk import sent_tokenize
 
 from pymongo.errors import DuplicateKeyError
@@ -90,6 +90,7 @@ class Document(MappedClass):
     text = FieldProperty(schema.String)
     month = FieldProperty(schema.String)
     year = FieldProperty(schema.Int)
+    related_sense = FieldProperty(schema.Object)
     number_of_words = FieldProperty(schema.Int)
     results = RelationProperty(InformationValueResult)
 
@@ -104,15 +105,24 @@ class Document(MappedClass):
 
 
     def top_senses(self, total_senses=20):
-        top_words = self.top_words()
+        top_words = self.top_words(total_senses*2)
         senses = []
-        #import ipdb; ipdb.set_trace()
         for (word, _) in top_words:
             try:
-                senses.append(wisdom.lesk(self.text, word))
+                sense = self.__get_sense_for(word)
+                senses.append(sense)
+                if len(senses) >= total_senses:
+                    break
             except wisdom.NoSenseFound:
                 pass
-        return senses
+        odm_session.flush()
+        return senses        
+
+    def __get_sense_for(self, word):
+        if not self.related_sense.has_key(word):
+            sense = wisdom.lesk(self.text, word)
+            self.related_sense[word] = sense.name
+        return wn.synset(self.related_sense[word])
 
     # calculator_class is poor man's dependency injection :)
     def get_iv_by_window_size(self, window_size, calculator_class=InformationValueCalculator):

### 2014-01-15 information_value/tests/document_tests.py

@@ -29,13 +29,12 @@ class DocumentTest(LeninTestCase):
 
     def test_top_senses_for_one_top_word_returns_correct_sense(self):
         document = get_document_with_top_words([('bank', 1.0)], text='I went to the bank to deposit my money')       
-
         self.assertEqual([wn.synset('depository_financial_institution.n.01')],  document.top_senses()) 
 
 
 def get_document_with_top_words(top_words, **kwargs):
     document = DocumentFactory(**kwargs)
-    document.top_words = types.MethodType(lambda self: top_words, document)
+    document.top_words = types.MethodType(lambda self, num=20: top_words, document)
     return document
 
 

### 2014-01-15 information_value/models.py
Fix problem not finding related sense.

@@ -90,7 +90,7 @@ class Document(MappedClass):
     text = FieldProperty(schema.String)
     month = FieldProperty(schema.String)
     year = FieldProperty(schema.Int)
-    related_sense = FieldProperty(schema.Object)
+    related_sense = FieldProperty(schema.Anything)
     number_of_words = FieldProperty(schema.Int)
     results = RelationProperty(InformationValueResult)
 

### 2014-01-15 information_value/tests/document_tests.py

@@ -35,6 +35,7 @@ class DocumentTest(LeninTestCase):
 def get_document_with_top_words(top_words, **kwargs):
     document = DocumentFactory(**kwargs)
     document.top_words = types.MethodType(lambda self, num=20: top_words, document)
+    document.related_sense = {}
     return document
 
 

### 2014-01-17 analyzers/document_analyzer.py
Change name from Wn Analyzer to SynsetAnalyzer.

@@ -1,6 +1,6 @@
 #! encoding:utf-8
-import wn_analyzer
-from wn_analyzer import WordNetAnalyzer, maximum_judge_function
+import synset_analyzer
+from synset_analyzer import SynsetAnalyzer, maximum_judge_function
 import logging
 from similarity import path_similarity
 from interpreter import db
@@ -16,7 +16,7 @@ class DocumentAnalyzer(object):
         self.word_to_synsets = synsets
         self.similarity_function = similarity_function
         self.prefix = similarity_function.func_name
-        self.analyzers = dict((word, WordNetAnalyzer(synsets=synsets, 
+        self.analyzers = dict((word, SynsetAnalyzer(synsets=synsets, 
                 similarity_function=similarity_function, 
                 judge_function=maximum_judge_function))
             for word, synsets in self.word_to_synsets.iteritems())
@@ -49,6 +49,6 @@ class DocumentAnalyzer(object):
             return document_analysis[self.prefix][word]
         analyzer = self.analyzers[word]
         doc_analysis = analyzer.judge_doc(document)
-        self.best_word_for[word] = wn_analyzer.best_word
+        self.best_word_for[word] = synset_analyzer.best_word
         return doc_analysis
     

### 2014-01-17 analyzers/synset_analyzer.py

@@ -23,7 +23,7 @@ def maximum_judge_function(partial_results):
 
 # Similarity definitions:
 # http://nltk.googlecode.com/svn/trunk/doc/api/nltk.corpus.reader.wordnet.Synset-class.html#path_similarity
-class WordNetAnalyzer:
+class SynsetAnalyzer:
     def __init__(self, synsets, similarity_function = path_similarity, judge_function=ponderated_judge_function ):
         self.synsets = synsets
         self.judge_function = judge_function
@@ -40,19 +40,20 @@ class WordNetAnalyzer:
         return (sum(v for (d, v) in all_docs_with_values) / len(all_docs_with_values))   
 
 
-    def judge_doc(self, document):
+    def judge_doc(self, document, number_of_senses=20):
         '''
           returns a value between 0 and 1
         '''
-        top_words_with_ivs = document.top_words(20)
+        top_senses = document.top_words(number_of_senses)
 
         """
         Here we have in partial_results
         [(word, word_ponderation, similarity) for word in document.top_words]
         We pass this to the judge function
         """
-        partial_results = [(word, ponderation, self.judge_word(word)) for (word, ponderation) in top_words_with_ivs]
+        partial_results = [(word, ponderation, self.judge_word(word)) for (word, ponderation) in top_senses]
         return self.judge_function(partial_results)
+
 
     def judge_word(self, word):
         '''
@@ -62,7 +63,7 @@ class WordNetAnalyzer:
 
  
 def wna_for(word):
-    return WordNetAnalyzer(word)
+    return SynsetAnalyzer(word)
 
 
 

### 2014-01-17 analyzers/tests/judge_doc_tests.py

@@ -1,13 +1,13 @@
 #! coding:utf-8
 from nltk.corpus import wordnet as wn
-from analyzers.wn_analyzer import WordNetAnalyzer 
+from analyzers.synset_analyzer import SynsetAnalyzer 
 from unittest import TestCase
 from mock import Mock
 from utils import document_returning_top_words
 
 class JudgeDocTests(TestCase):
     def test_judge_doc_should_return_1_for_a_document_with_just_one_word(self):
-        wna = WordNetAnalyzer([wn.synset("war.n.01")])
+        wna = SynsetAnalyzer([wn.synset("war.n.01")])
         doc = Mock()
         doc.top_words.return_value = [("war", 1.0)]
     
@@ -15,7 +15,7 @@ class JudgeDocTests(TestCase):
 
 
     def test_judge_doc_should_return_1_for_a_document_with_two_equal_words(self):
-        wna = WordNetAnalyzer([wn.synset("war.n.01")])
+        wna = SynsetAnalyzer([wn.synset("war.n.01")])
         doc = Mock()
         doc.top_words.return_value = [("war", .5), ("war", .5)]
     
@@ -24,7 +24,7 @@ class JudgeDocTests(TestCase):
 
     def test_should_take_into_account_an_immediate_hypernym(self):
         # Action is a lemma of military action, which is an hypernym of war.n.01
-        wna = WordNetAnalyzer([wn.synset("military_action.n.01")])
+        wna = SynsetAnalyzer([wn.synset("military_action.n.01")])
         doc = document_returning_top_words(("war", 0.5), ("music", 0.4), ("fruit", 0.1))
 
         # As it is an hypernym, its similarity is 0.5

### 2014-01-17 analyzers/tests/judge_list_tests.py

@@ -2,17 +2,17 @@
 from unittest import TestCase, skip
 from nltk.corpus import wordnet as wn
 from analyzers.similarity import path_similarity
-from analyzers.wn_analyzer import WordNetAnalyzer 
+from analyzers.synset_analyzer import SynsetAnalyzer 
 from utils import document_returning_top_words, create_document_list
 
 class JudgeListTests(TestCase):
     def test_returns_0_for_no_documents(self):
-        wna = WordNetAnalyzer(synsets=[wn.synset("war.n.01")])
+        wna = SynsetAnalyzer(synsets=[wn.synset("war.n.01")])
         doc_list = create_document_list()
         self.assertAlmostEqual(wna.judge_list(doc_list), .0)
 
     def test_returns_1_for_document_with_one_top_word(self):
-        wna = WordNetAnalyzer(synsets=[wn.synset("war.n.01")])
+        wna = SynsetAnalyzer(synsets=[wn.synset("war.n.01")])
         doc_list = create_document_list(
             document_returning_top_words(("war", 1.0))
         )
@@ -20,7 +20,7 @@ class JudgeListTests(TestCase):
         self.assertAlmostEqual(wna.judge_list(doc_list), 1.0)
 
     def test_returns_0_for_document_with_one_distinct_top_word(self):
-        wna = WordNetAnalyzer(synsets=[wn.synset("war.n.01")])
+        wna = SynsetAnalyzer(synsets=[wn.synset("war.n.01")])
         doc_list = create_document_list(
             document_returning_top_words(("music", 1.0))
         )
@@ -28,14 +28,14 @@ class JudgeListTests(TestCase):
 
     @skip
     def test_returns_the_distance_ponderated_with_the_top_word_value(self):
-        wna = WordNetAnalyzer(synsets=[wn.synset("war.n.01")])
+        wna = SynsetAnalyzer(synsets=[wn.synset("war.n.01")])
         doc_list = create_document_list(
             document_returning_top_words(("music", .5), ("war", 0.5))
         )
         self.assertAlmostEqual(wna.judge_list(doc_list), .5)
 
     def test_with_two_documents(self):
-        wna = WordNetAnalyzer(synsets=[wn.synset("war.n.01")])
+        wna = SynsetAnalyzer(synsets=[wn.synset("war.n.01")])
         doc_list = create_document_list(
             document_returning_top_words(("war", 1.0)),
             document_returning_top_words(("music", 1.0))
[…]

### 2014-01-17 analyzers/tests/judge_word_tests.py

@@ -1,15 +1,15 @@
 #! coding:utf-8
 from nltk.corpus import wordnet as wn
-from analyzers.wn_analyzer import WordNetAnalyzer
+from analyzers.synset_analyzer import SynsetAnalyzer
 from unittest import TestCase
 
 class JudgeWordTests(TestCase):
     def test_returns_1_for_same_word_as_synsets(self):
-        analyzer = WordNetAnalyzer(synsets=[wn.synset("war.n.01")])
+        analyzer = SynsetAnalyzer(synsets=[wn.synset("war.n.01")])
 
         self.assertAlmostEqual(analyzer.judge_word("war"), 1.0)
 
     def test_returns_less_than_1_for_distinct_words(self):
-        analyzer = WordNetAnalyzer(synsets=[wn.synset("war.n.01")])
+        analyzer = SynsetAnalyzer(synsets=[wn.synset("war.n.01")])
 
         self.assertTrue(analyzer.judge_word("music") < 1.0)

### 2014-01-17 analyzers/tests/tests.py

@@ -5,14 +5,14 @@ from unittest import TestCase
 from unittest import skip
 
 from nltk.corpus import wordnet as wn
-from analyzers.wn_analyzer import WordNetAnalyzer
+from analyzers.synset_analyzer import SynsetAnalyzer
 
 
 
 class TestAnalyzers(TestCase):
 
   def test_war_analyzer(self):    
-    all_war_analyzer =  WordNetAnalyzer(synsets=[wn.synset("war.n.01")])
+    all_war_analyzer =  SynsetAnalyzer(synsets=[wn.synset("war.n.01")])
     
     self.assertEqual(1.0, all_war_analyzer.judge_word("war"))
 
@@ -22,17 +22,17 @@ class TestAnalyzers(TestCase):
     
 
   @skip
-  def test_simple_wn_analyzers(self):
+  def test_simple_synset_analyzers(self):
     politics_synsets = [(wn.synset('politics.n.01'), 1.0)]
     praxis_synsets = [(wn.synset('practice.n.03'), 1.0)]
     theory_synsets = [(wn.synset('theory.n.01'), 1.0)]
     
     rev_synsets = [(wn.synset('revolution.n.02'), 1.0)] #the overthrow of a government by those who are governed
     analyzers = {   
-                      'politics': WordNetAnalyzer(politics_synsets), 
-                      'theory': WordNetAnalyzer(theory_synsets),
-                      'praxis': WordNetAnalyzer(praxis_synsets),
-                      'revolution': WordNetAnalyzer(rev_synsets),
+                      'politics': SynsetAnalyzer(politics_synsets), 
+                      'theory': SynsetAnalyzer(theory_synsets),
+                      'praxis': SynsetAnalyzer(praxis_synsets),
+                      'revolution': SynsetAnalyzer(rev_synsets),
                   }
     self.assertAlmostEqual(0.1666, analyzers['revolution'].judge_word("revolution"), 3) #epic fail
       

### 2014-01-17 analyzers/year_analyzer.py

@@ -1,6 +1,6 @@
 #! coding: utf-8
 from information_value.models import DocumentList
-from wn_analyzer import wna_for
+from synset_analyzer import wna_for
 import logging
 from interpreter import db
 

### 2014-01-17 cccp.py

@@ -110,7 +110,7 @@ def main():
    
     if args.plot:
         from plot import wn_plots
-        import analyzers.wn_analyzer as wa
+        import analyzers.synset_analyzer as wa
         
         concepts = None
         if args.concepts:

### 2014-01-17 experiments.py

@@ -1,1 +1,1 @@
-# This Python file uses the following encoding: utf-8
from __future__ import division
from includes import tokenizer as tk
from includes import information_value as iv
from includes import zipf as zf
from includes import works as wk 
from includes import utils
from includes import preprocessor as pre
import nltk                   
from nltk.corpus import stopwords
from nltk.corpus import wordnet as wn
import wn_analyzer as wna
import matplotlib     
import matplotlib.pyplot as plt           
import pylab       

def get_a_work(year, number):
	works = wk.Works()
	works.load_dictionary()
	dict_1917 = works.get_year(str(year))
	one_work = dict_1917[number]
	return one_work

def run_zipf(work):	
	zipf = zf.Zipf(work['text'], work['name'], run=True)

def	run_iv(work,words):
	ivp = iv.InformationValue(work['text'], words)
	
	return ivp.information_value(100)
	
def get_window_size(work, words):
	x= iv.InformationValue(work['text'],words)
	
	print str(x.calculate_window_size())


	
def print_year(year, n = 20, verbose=False):
	zipf = utils.from_file('zipf_by_year.json')
	for x in zipf:
		if x['name'] == year:
			resume = x
			break
		
	data = utils.load_year_data(year, resume)
	wn = utils.from_file('by_year/'+year+'_wn.json')
	cant  = len(data['base'])
	linea = '---------------------------------------------------------------------------'
	print 'Año: '+year
	print 'Cantidad de textos: '+str(cant)
	print 'Palabras y vocabulario: '+str(data['zipf_resume']['total_words'])+', '+str(data['zipf_resume']['total_vocab'])
	if verbose:
		print 'Mas usadas: '+ ','.join(map(str, [u.encode('utf-8') for u in data['zipf_resume']['top_words'][:n]]))
	
	print 'Teoricidad  (iv,zipf,zipf_anual): '+str(round(wn['theory_iv'],3))+' , '+str(round(wn['theory_zipf'],3))+',  '+str(round(wn['zipf_resume']['theory'],3))
[…]

### 2014-01-17 includes/preprocessor.py

@@ -5,7 +5,7 @@ import config
 import information_value as iv
 import zipf as zf
 import utils
-from analyzers import wn_analyzer as wna
+from analyzers import synset_analyzer as wna
 
 class Preprocessor:
 	

### 2014-01-17 information_value/models.py

@@ -105,9 +105,9 @@ class Document(MappedClass):
 
 
     def top_senses(self, total_senses=20):
-        top_words = self.top_words(total_senses*2)
+        top_words = (word for word, _ in self.top_words(total_senses*2))
         senses = []
-        for (word, _) in top_words:
+        for word in top_words:
             try:
                 sense = self.__get_sense_for(word)
                 senses.append(sense)
@@ -119,6 +119,7 @@ class Document(MappedClass):
         return senses        
 
     def __get_sense_for(self, word):
+        
         if not self.related_sense.has_key(word):
             sense = wisdom.lesk(self.text, word)
             self.related_sense[word] = sense.name

### 2014-01-17 interpreter.py

@@ -11,7 +11,7 @@ ming_config = {'ming.document_store.uri': config.DATABASE_URL}
 ming.configure(**ming_config)
 
 from information_value.models import Document, DocumentList, InformationValueResult, doc_for
-from analyzers.wn_analyzer import WordNetAnalyzer, year_vs_concept_data, wnas_for, wna_for
+from analyzers.synset_analyzer import SynsetAnalyzer, year_vs_concept_data, wnas_for, wna_for
 from nltk.corpus import wordnet as wn
 
 from pymongo import MongoClient

### 2014-01-17 analyzers/analyzer.py
Remove unused file.

@@ -1,14 +1,0 @@
-
-
-class DocumentAnalyzer(object):
-
-  def __init__(self, document):
-    self.document = document
-    self.top_words = document.top_words()
-
-  def get_results(self):
-    pass
-
-  def judge_word(self, word):
-    pass
-

### 2014-01-17 analyzers/synset_analyzer.py
Add judge_synset.

@@ -54,6 +54,8 @@ class SynsetAnalyzer:
         partial_results = [(word, ponderation, self.judge_word(word)) for (word, ponderation) in top_senses]
         return self.judge_function(partial_results)
 
+    def judge_synset(self, synset):
+        return self.similarity_function(self.synsets, [synset])
 
     def judge_word(self, word):
         '''

### 2014-01-17 analyzers/tests/synset_analyzer_tests.py

@@ -1,0 +1,10 @@
+#! coding:utf-8
+from nltk.corpus import wordnet as wn
+from analyzers.synset_analyzer import SynsetAnalyzer
+from unittest import TestCase
+
+class JudgeSynsetTest(TestCase):
+    def test_returns_1_for_same_synset(self):
+        analyzer = SynsetAnalyzer(synsets=[wn.synset("war.n.01")])
+
+        self.assertAlmostEqual(analyzer.judge_synset(wn.synset("war.n.01")), 1.0)

### 2014-01-17 analyzers/tests/judge_doc_tests.py
Refactor tests.

@@ -1,33 +1,0 @@
-#! coding:utf-8
-from nltk.corpus import wordnet as wn
-from analyzers.synset_analyzer import SynsetAnalyzer 
-from unittest import TestCase
-from mock import Mock
-from utils import document_returning_top_words
-
-class JudgeDocTests(TestCase):
-    def test_judge_doc_should_return_1_for_a_document_with_just_one_word(self):
-        wna = SynsetAnalyzer([wn.synset("war.n.01")])
-        doc = Mock()
-        doc.top_words.return_value = [("war", 1.0)]
-    
-        self.assertAlmostEqual(wna.judge_doc(doc), 1.0)
-
-
-    def test_judge_doc_should_return_1_for_a_document_with_two_equal_words(self):
-        wna = SynsetAnalyzer([wn.synset("war.n.01")])
-        doc = Mock()
-        doc.top_words.return_value = [("war", .5), ("war", .5)]
-    
-        self.assertAlmostEqual(wna.judge_doc(doc), 1.0)
-
-
-    def test_should_take_into_account_an_immediate_hypernym(self):
-        # Action is a lemma of military action, which is an hypernym of war.n.01
-        wna = SynsetAnalyzer([wn.synset("military_action.n.01")])
-        doc = document_returning_top_words(("war", 0.5), ("music", 0.4), ("fruit", 0.1))
-
-        # As it is an hypernym, its similarity is 0.5
-        self.assertGreaterEqual(wna.judge_doc(doc), 0.25)
-
-

### 2014-01-17 analyzers/tests/judge_word_tests.py

@@ -1,15 +1,0 @@
-#! coding:utf-8
-from nltk.corpus import wordnet as wn
-from analyzers.synset_analyzer import SynsetAnalyzer
-from unittest import TestCase
-
-class JudgeWordTests(TestCase):
-    def test_returns_1_for_same_word_as_synsets(self):
-        analyzer = SynsetAnalyzer(synsets=[wn.synset("war.n.01")])
-
-        self.assertAlmostEqual(analyzer.judge_word("war"), 1.0)
-
-    def test_returns_less_than_1_for_distinct_words(self):
-        analyzer = SynsetAnalyzer(synsets=[wn.synset("war.n.01")])
-
-        self.assertTrue(analyzer.judge_word("music") < 1.0)

### 2014-01-17 analyzers/tests/synset_analyzer_tests.py

@@ -2,9 +2,41 @@
 from nltk.corpus import wordnet as wn
 from analyzers.synset_analyzer import SynsetAnalyzer
 from unittest import TestCase
+from mock import Mock
+from utils import document_returning_top_words
 
 class JudgeSynsetTest(TestCase):
     def test_returns_1_for_same_synset(self):
         analyzer = SynsetAnalyzer(synsets=[wn.synset("war.n.01")])
 
         self.assertAlmostEqual(analyzer.judge_synset(wn.synset("war.n.01")), 1.0)
+
+
+
+
+class JudgeDocTests(TestCase):
+    def test_judge_doc_should_return_1_for_a_document_with_just_one_word(self):
+        wna = SynsetAnalyzer([wn.synset("war.n.01")])
+        doc = Mock()
+        doc.top_words.return_value = [("war", 1.0)]
+    
+        self.assertAlmostEqual(wna.judge_doc(doc), 1.0)
+
+
+    def test_judge_doc_should_return_1_for_a_document_with_two_equal_words(self):
+        wna = SynsetAnalyzer([wn.synset("war.n.01")])
+        doc = Mock()
+        doc.top_words.return_value = [("war", .5), ("war", .5)]
+    
+        self.assertAlmostEqual(wna.judge_doc(doc), 1.0)
+
+
+    def test_should_take_into_account_an_immediate_hypernym(self):
+        # Action is a lemma of military action, which is an hypernym of war.n.01
+        wna = SynsetAnalyzer([wn.synset("military_action.n.01")])
+        doc = document_returning_top_words(("war", 0.5), ("music", 0.4), ("fruit", 0.1))
+
+        # As it is an hypernym, its similarity is 0.5
+        self.assertGreaterEqual(wna.judge_doc(doc), 0.25)
+
+

### 2014-01-18 analyzers/tests/judge_list_tests.py
Remove unused tests.

@@ -1,59 +1,0 @@
-#! coding:utf-8
-from unittest import TestCase, skip
-from nltk.corpus import wordnet as wn
-from analyzers.similarity import path_similarity
-from analyzers.synset_analyzer import SynsetAnalyzer 
-from utils import document_returning_top_words, create_document_list
-
-class JudgeListTests(TestCase):
-    def test_returns_0_for_no_documents(self):
-        wna = SynsetAnalyzer(synsets=[wn.synset("war.n.01")])
-        doc_list = create_document_list()
-        self.assertAlmostEqual(wna.judge_list(doc_list), .0)
-
-    def test_returns_1_for_document_with_one_top_word(self):
-        wna = SynsetAnalyzer(synsets=[wn.synset("war.n.01")])
-        doc_list = create_document_list(
-            document_returning_top_words(("war", 1.0))
-        )
-
-        self.assertAlmostEqual(wna.judge_list(doc_list), 1.0)
-
-    def test_returns_0_for_document_with_one_distinct_top_word(self):
-        wna = SynsetAnalyzer(synsets=[wn.synset("war.n.01")])
-        doc_list = create_document_list(
-            document_returning_top_words(("music", 1.0))
-        )
-        self.assertAlmostEqual(wna.judge_list(doc_list), path_similarity([wn.synset("war.n.01")], wn.synsets("music")))
-
-    @skip
-    def test_returns_the_distance_ponderated_with_the_top_word_value(self):
-        wna = SynsetAnalyzer(synsets=[wn.synset("war.n.01")])
-        doc_list = create_document_list(
-            document_returning_top_words(("music", .5), ("war", 0.5))
-        )
-        self.assertAlmostEqual(wna.judge_list(doc_list), .5)
-
-    def test_with_two_documents(self):
-        wna = SynsetAnalyzer(synsets=[wn.synset("war.n.01")])
-        doc_list = create_document_list(
-            document_returning_top_words(("war", 1.0)),
-            document_returning_top_words(("music", 1.0))
-        )
-
-        self.assertGreaterEqual(wna.judge_list(doc_list), 0.5 + 0.5 * path_similarity([wn.synset("war.n.01")], wn.synsets("music")))
-
-    @skip
-    def test_with_two_documents_with_several_top_words(self):
-        wna = SynsetAnalyzer(synsets=[wn.synset("war.n.01")])
-        doc_list = create_document_list(
-            # Both docs adds 0.25 of similarity
[…]

### 2014-01-18 analyzers/synset_analyzer.py
Remove judge_list from SynsetAnalyzer.

@@ -9,49 +9,34 @@ log = logging.getLogger('lenin')
 import config
 reload(config)
 
-
-def ponderated_judge_function(partial_results):
-    return sum(ponderation * similarity for (word, ponderation, similarity) in partial_results)
-
 #this is horrible
 best_word = None
 def maximum_judge_function(partial_results):
     global best_word
-    max_word, _, max_similarity  = max(partial_results, key=lambda x: x[2])
-    best_word = max_word
+    max_synset, max_similarity  = max(partial_results, key=lambda x: x[1])
+    best_word = max_synset
     return max_similarity
 
 # Similarity definitions:
 # http://nltk.googlecode.com/svn/trunk/doc/api/nltk.corpus.reader.wordnet.Synset-class.html#path_similarity
 class SynsetAnalyzer:
-    def __init__(self, synsets, similarity_function = path_similarity, judge_function=ponderated_judge_function ):
+    def __init__(self, synsets, similarity_function = path_similarity, judge_function=maximum_judge_function):
         self.synsets = synsets
         self.judge_function = judge_function
         self.similarity_function = similarity_function
-
-    def judge_list(self, doc_list):
-        if doc_list.total_docs == 0:
-            return None
-        all_docs_with_values = [(doc, self.judge_doc(doc))  for doc in doc_list ]
-
-        if len(all_docs_with_values) == 0:
-            return 0
-
-        return (sum(v for (d, v) in all_docs_with_values) / len(all_docs_with_values))   
-
 
     def judge_doc(self, document, number_of_senses=20):
         '''
           returns a value between 0 and 1
         '''
-        top_senses = document.top_words(number_of_senses)
+        top_senses = document.top_senses(number_of_senses)
 
         """
         Here we have in partial_results
         [(word, word_ponderation, similarity) for word in document.top_words]
         We pass this to the judge function
         """
-        partial_results = [(word, ponderation, self.judge_word(word)) for (word, ponderation) in top_senses]
+        partial_results = [(synset, self.judge_synset(synset)) for synset in top_senses]
         return self.judge_function(partial_results)
 
     def judge_synset(self, synset):

### 2014-01-18 analyzers/tests/document_analyzer_tests.py

@@ -3,7 +3,7 @@ from mock import patch
 from nltk.corpus import wordnet as wn
 from analyzers.document_analyzer import DocumentAnalyzer
 from unittest import TestCase
-from utils import document_returning_top_words
+from utils import document_returning_top_senses
 
 class DocumentAnalyzerTests(TestCase):
     def setUp(self):
@@ -16,13 +16,13 @@ class DocumentAnalyzerTests(TestCase):
 
     def test_creating_analyzer_with_no_concepts_return_empty_analysis(self):
         analyzer = DocumentAnalyzer(synsets={})
-        doc = document_returning_top_words(("war",1.0))
+        doc = document_returning_top_senses(wn.synset("war.n.01"))
 
         self.assertEquals({}, analyzer.analyze_document(doc))
 
     def test_analyze_a_concept(self):
         analyzer = DocumentAnalyzer(synsets={"war": [wn.synset("war.n.01")]})
 
-        doc = document_returning_top_words(("war", 1.0))
+        doc = document_returning_top_senses(wn.synset("war.n.01"))
 
         self.assertEquals({"war": 1.0}, analyzer.analyze_document(doc))

### 2014-01-18 analyzers/tests/synset_analyzer_tests.py

@@ -3,7 +3,7 @@ from nltk.corpus import wordnet as wn
 from analyzers.synset_analyzer import SynsetAnalyzer
 from unittest import TestCase
 from mock import Mock
-from utils import document_returning_top_words
+from utils import document_returning_top_senses
 
 class JudgeSynsetTest(TestCase):
     def test_returns_1_for_same_synset(self):
@@ -17,16 +17,14 @@ class JudgeSynsetTest(TestCase):
 class JudgeDocTests(TestCase):
     def test_judge_doc_should_return_1_for_a_document_with_just_one_word(self):
         wna = SynsetAnalyzer([wn.synset("war.n.01")])
-        doc = Mock()
-        doc.top_words.return_value = [("war", 1.0)]
-    
+        doc = document_returning_top_senses(wn.synset("war.n.01"))    
         self.assertAlmostEqual(wna.judge_doc(doc), 1.0)
 
 
     def test_judge_doc_should_return_1_for_a_document_with_two_equal_words(self):
         wna = SynsetAnalyzer([wn.synset("war.n.01")])
         doc = Mock()
-        doc.top_words.return_value = [("war", .5), ("war", .5)]
+        doc = document_returning_top_senses(wn.synset("war.n.01"), wn.synset("war.n.01"))    
     
         self.assertAlmostEqual(wna.judge_doc(doc), 1.0)
 
@@ -34,9 +32,9 @@ class JudgeDocTests(TestCase):
     def test_should_take_into_account_an_immediate_hypernym(self):
         # Action is a lemma of military action, which is an hypernym of war.n.01
         wna = SynsetAnalyzer([wn.synset("military_action.n.01")])
-        doc = document_returning_top_words(("war", 0.5), ("music", 0.4), ("fruit", 0.1))
+        doc = document_returning_top_senses(wn.synset("war.n.01"), wn.synset("music.n.01"), wn.synset("fruit.n.01"))    
 
         # As it is an hypernym, its similarity is 0.5
-        self.assertGreaterEqual(wna.judge_doc(doc), 0.25)
+        self.assertGreaterEqual(wna.judge_doc(doc), 0.5)
 
 

### 2014-01-18 analyzers/tests/utils.py

@@ -12,3 +12,8 @@ def document_returning_top_words(*ponderated_words):
     doc = Mock()
     doc.top_words.return_value = ponderated_words
     return doc
+
+def document_returning_top_senses(*top_senses):
+    doc = Mock()
+    doc.top_senses.return_value = top_senses
+    return doc

### 2014-01-18 analyzers/document_analyzer.py
Simplify some code.

@@ -13,42 +13,40 @@ class DocumentAnalyzer(object):
     @similarity_function = A similarity function from similarity module
     """
     def __init__(self, synsets, similarity_function=path_similarity):
-        self.word_to_synsets = synsets
+        self.synsets = synsets
         self.similarity_function = similarity_function
         self.prefix = similarity_function.func_name
-        self.analyzers = dict((word, SynsetAnalyzer(synsets=synsets, 
+        self.analyzers = dict(
+            (synset, SynsetAnalyzer(
+                synsets=synsets, 
                 similarity_function=similarity_function, 
-                judge_function=maximum_judge_function))
-            for word, synsets in self.word_to_synsets.iteritems())
+                judge_function=maximum_judge_function)
+            ) for synset in self.synsets)
  
     @property
     def name(self):
-        print self.similarity_function.func_name
+        print self.similarity_function.func_name + " document analyzer"
 
     def analyze_document(self, document):
-        document_analysis = self.__get_analysis_for(document)
+        document_analysis = {} #self.__get_analysis_for(document)[self.prefix]
         self.best_word_for = {}
-        for word, synsets in self.word_to_synsets.iteritems():
-            document_analysis[self.prefix][word] = self.__analyze_document_against_synsets(
-                word=word, synsets=synsets,
-                document=document, 
-                document_analysis=document_analysis)
-        
-        db.document_analysis.save(document_analysis)
-        return document_analysis[self.prefix]
 
+        for synset in self.synsets:
+            document_analysis[synset.name] = self.analyze_synset(synset=synset, document=document)
+        
+        #db.document_analysis.save(document_analysis)
+        return document_analysis
+
+   
+    def analyze_synset(self, document, synset):
+        # Only calculate in case there's no analysis done
+        analyzer = self.analyzers[synset]
+        doc_analysis = analyzer.judge_doc(document)
+        self.best_word_for[synset.name] = synset_analyzer.best_word
+        return doc_analysis
+    
     def __get_analysis_for(self, document):
         document_analysis = db.document_analysis.find_one({"document_id": document._id}) or {"document_id": document._id}
         if not self.prefix in document_analysis.keys():
             document_analysis[self.prefix] = {}
         return document_analysis
-
-    def __analyze_document_against_synsets(self, document, word, synsets, document_analysis):
-        # Only calculate in case there's no analysis done
-        if word in document_analysis[self.prefix].keys():
[…]

### 2014-01-18 analyzers/tests/document_analyzer_tests.py

@@ -21,8 +21,8 @@ class DocumentAnalyzerTests(TestCase):
         self.assertEquals({}, analyzer.analyze_document(doc))
 
     def test_analyze_a_concept(self):
-        analyzer = DocumentAnalyzer(synsets={"war": [wn.synset("war.n.01")]})
+        analyzer = DocumentAnalyzer(synsets=[wn.synset("war.n.01")])
 
         doc = document_returning_top_senses(wn.synset("war.n.01"))
 
-        self.assertEquals({"war": 1.0}, analyzer.analyze_document(doc))
+        self.assertEquals({"war.n.01": 1.0}, analyzer.analyze_document(doc))

### 2014-01-18 analyzers/tests/synset_analyzer_tests.py

@@ -12,14 +12,11 @@ class JudgeSynsetTest(TestCase):
         self.assertAlmostEqual(analyzer.judge_synset(wn.synset("war.n.01")), 1.0)
 
 
-
-
 class JudgeDocTests(TestCase):
     def test_judge_doc_should_return_1_for_a_document_with_just_one_word(self):
         wna = SynsetAnalyzer([wn.synset("war.n.01")])
         doc = document_returning_top_senses(wn.synset("war.n.01"))    
         self.assertAlmostEqual(wna.judge_doc(doc), 1.0)
-
 
     def test_judge_doc_should_return_1_for_a_document_with_two_equal_words(self):
         wna = SynsetAnalyzer([wn.synset("war.n.01")])
@@ -36,5 +33,3 @@ class JudgeDocTests(TestCase):
 
         # As it is an hypernym, its similarity is 0.5
         self.assertGreaterEqual(wna.judge_doc(doc), 0.5)
-
-

### 2014-01-18 information_value/models.py
Make lesk algorithm only ask for nouns.

@@ -121,7 +121,7 @@ class Document(MappedClass):
     def __get_sense_for(self, word):
         
         if not self.related_sense.has_key(word):
-            sense = wisdom.lesk(self.text, word)
+            sense = wisdom.lesk(self.text, word, pos='n')
             self.related_sense[word] = sense.name
         return wn.synset(self.related_sense[word])
 

### 2014-01-18 analyzers/document_analyzer.py
Fix error setting synsets.

@@ -18,7 +18,7 @@ class DocumentAnalyzer(object):
         self.prefix = similarity_function.func_name
         self.analyzers = dict(
             (synset, SynsetAnalyzer(
-                synsets=synsets, 
+                synsets=[synset], 
                 similarity_function=similarity_function, 
                 judge_function=maximum_judge_function)
             ) for synset in self.synsets)

### 2014-01-18 analyzers/tests/document_analyzer_tests.py

@@ -26,3 +26,10 @@ class DocumentAnalyzerTests(TestCase):
         doc = document_returning_top_senses(wn.synset("war.n.01"))
 
         self.assertEquals({"war.n.01": 1.0}, analyzer.analyze_document(doc))
+
+    def test_analyze_multiple_concepts(self):
+        analyzer = DocumentAnalyzer(synsets=[wn.synset("war.n.01"), wn.synset("music.n.01")])
+
+        doc = document_returning_top_senses(wn.synset("war.n.01"), wn.synset("music.n.01"))
+
+        self.assertEquals({"war.n.01": 1.0, "music.n.01": 1.0}, analyzer.analyze_document(doc))

### 2014-01-18 cccp.py
Add command to reset all senses.

@@ -6,6 +6,7 @@ import logging
 import analyzers
 import argparse
 import subprocess
+from commands.database import reset_senses
 from commands.year_analysis import calculate_year_analysis
 import ming
 
@@ -64,6 +65,7 @@ def main():
     parser.add_argument('--notebook-server', action='store_true', default=False, help='Starts notebook server')
     parser.add_argument('--set-number-of-tokens', action='store_true', default=False, help='Calculate number of words for each work')
     parser.add_argument('--analyze-documents', action='store_true', default=False, help="Do Document Analysis for given concepts (pass with --concepts)")
+    parser.add_argument('--reset-senses', action='store_true', default=False, help="Reset all senses calculated")
     if len(sys.argv)==1:
         parser.print_help()
         sys.exit(1)
@@ -136,6 +138,8 @@ def main():
         subprocess.call("PYTHONPATH=$PYTHONPATH:$PWD; ipython notebook --notebook-dir=.", shell=True)
     if args.shell:
         subprocess.call("ipython -i interpreter.py", shell=True)
+    if args.reset_senses:
+        reset_senses()
 
     if args.set_number_of_tokens:
         set_number_of_tokens()

### 2014-02-20 paper/refactor.tex
refactor.tex

--- 2013-12-21 paper/distance.tex
@@
 \usepackage[dvips]{graphicx}
+\usepackage{bookmark}
+\usepackage{color}
 \selectlanguage{spanish}
+
+\newcommand\dq[1]{\textquotedblleft #1\textquotedblright}
+\newcommand\sq[1]{\textquoteleft #1\textquoteright}
+\newcommand*{\allref}[1]{\ref{#1} \nameref{#1}}
 
@@
 %% For PNAS Only:
-\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
+%\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
 \copyrightyear{2008}
@@
 
-\title{An analysis of Lenin's work: Revolution, war, and fruta}
+\title{A word-sense representation for documents based on information value and word sense disambiguation}
 
@@
 
-\contributor{Submitted to Proceedings of the National Academy of Sciences
-of the United States of America}
+%&\contributor{Submitted to Proceedings of the National Academy of Sciences
+%of the United States of America}
 
@@
 \begin{abstract}
-In order to discover how much related were Lenin Works to Russian History in nearly 20th century, we use the information value concept to extract the most important words from them.
-Therefore, we find out how far are them from certain words such as
-war, revolution, theory, etc giving a Wordnet-based similarity function. 
+In this project we analyzed some Lenin works in order to identify the presence of some well known topics of his biography.
+To achieve this, we defined and implemented a simple distance metric between a word-sense and a document and confronted this metric using a evaluation set of word-senses against a reduced set of  documents with well known topics.
+During this work, we generated an indexed database of Lenin's complete works from a web site\cite{LENIN} and we applied a serie of well known syntactic, semantic and lexicographic tools in order to model the similarity between a document and a word-sense.
+We applied information value\cite{DARWIN} and a simple algorithm of word sense disambiguation\cite{LESK} based on wordnet\cite{WORDNET} in order to generate the \textit{top senses} (or principal senses) of a document.
+We compare this \textit{top senses} for some documents of well known topics agains some senses of interest (for example: revolution, war, government) and observed the shape of the results.
 \end{abstract}
 
-\keywords{information value | natural language processing | lenin }
+\keywords{information value | word sense disambiguation | natural language processing | information retrieval | polysemy }
 
-\abbreviations{NLP}
+%\abbreviations{NLP}
 
@@
 
-\dropcap{I}n this article we study distances in metric spaces consisting on words, and how we can
-represent a text (an ordered set of words) as a smaller subset of their most representative words.
+\dropcap{I}n this article we propose a simple distance metric between a word-sense and a text document using different well known tools from natural language processing.
+To achieve this, we extract a hierarchy of the most representative words of a document (\textit{top words}) using the concept of \textit{information value}, a statistical linguistic model based on Shannon's information theory and proposed by Zanette et al.
+in\cite{DARWIN}.
+Briefly, information value allows us to represent a document like a ranked set of words.
+
+But this ponderated set of top words has the problem of polysemy, tipical in the field of nlp.
+Polysemy occurs when a term has more than one sense or meaning, for example: the term 'bank' can refer to a financial institution or to a {\color{red}banco de plaza}, thus, it is polysemic.
+In order to resolve this limitation, we implement a basic algorithm of word-sense disambiguation based on wordnet's synsets and we apply it over the top words, using as disambiguation context the whole document.
+We obtain, then, the \textit{top senses} of a document, this is, a ranked set of wordnet synsets that work like a representation of the given document.
+
+Finally, we utilize different wordnet predefined metrics of similarity between synsets to define our own similarities between the top-sense representation of a document and any given word-sense (wordnet synset).
+In order to evaluate the behaviour of this metrics, we test the distances of the top-senses representation of some well known documents with very specific topics against a bounded set of relevant evaluation word-senses.
+
+\section{Method}
+Text Corpus.  Scrapping. Total de documentos. Total de documentos por año. Total de tokens promedio. Filtros (esto está!)
+\subsection{Text Corpus}
+
+We selected some starred works from Lenin from the "Marxists Internet Archive"\cite{LENIN}.
+Those works are very different in topic, some of them being strictly phylosophical essays (such as ``Materialism and Empiriocriticism'') and other being more political, such as ``State and Revolution'', and finally an economy essay called ``Imperialism, the highest stage of capitalism''.
+
+\begin{itemize}
+  \item What is to be done(1901)
+  \item The Agrarian Programme of Social-Democracy in the First Russian Revolution, 1905-1907 (1907)
+  \item Materialism and Empiriocriticism (1908)
+  \item Imperialism, the highest stage of capitalism (1916)
+  \item State and Revolution (1917)
+\end{itemize}
+
+%*Números (obras totales obtenidas, promedio tokens)
+\subsection{Semantic Analysis}
+\medskip
+\subsubsection{Information value}
+
+Having a similarity notion between words, and the most valuable words from a text, our question arises: how distant is a word from a text?
+We use here the notion of distance between a point and a set defined as:
+
+\begin{equation}
+  d(a, S) = min_{x \in S} d(a, x) 
+\end{equation}
+
+being $S$ the set of most representative words. Hence, we are ``projecting'' a text into the set of their top words.
 
@@
 
+\subsubsection{Wordnet synsets \& similarities}
+
 In order to measure the distance/similarity between two words, we use Wordnet (see \cite{WORDNET}), a lexical database in English.
@@
 
-Having a similarity notion between words, and the most valuable words from a text, our question arises: how distant is a word from a text?
-We use here the notion of distance between a point and a set defined as:
+\textbf{Old title: Wordnet analyzer}
+Consideremos el siguiente problema:
+\newline
+¿Cómo calcular la similaridad o distancia de un documento a un cierto concepto? 
+\newline
+El enfoque que utilizamos en este trabajo es el de realizar una representación del documento como un conjunto de palabras, y en base a esto usar una noción topológica de similaridad/distancia.
+La proyección del documento al espacio de palabras la realizamos utilizando la t\'ecnica de Information Value reci\'en descripta.
+En este espacio, utilizamos Wordnet para definir una noción de distancia entre el conjunto de palabras que representan al texto y diferentes conjuntos representando conceptos.
+\newline
+Para un documento dado, el módulo de information value genera una lista con lo $n$ términos más importantes y su iv.
+Estos valores se normalizan -dividiendo por la suma de los valores-, obteniendo así uno de los inputs del proceso siguiente.
+Recordemos, nuestro objetivo es asignar una distancia entre un documento y un concepto.
+Digamos, decidir cuán presente está o cuán importante es un concepto en un documento.
+\newline
+Wordnet es una base de datos de palabras, agrupadas en conjuntos de sinónimos (synsets), cada uno de los cuales posee una definición y diferentes relaciones semánticas con otros synsets (por ejemplo: hipernimia, hiponimia, meronimia, etc).
+Sobre estas relaciones semánticas es posible definir distintas métricas de distancia y similaridad entre synsets (Ver [1])
+\newline
+Utilizando las métricas disponibles en el módulo nltk de python para wordnet definimos la similaridad entre dos palabras como la máxima similaridad entre todos los synsets de ambas.
+(**NOTA Parametrizable: puede ser sólo el primer synset de ambos y puede no ser la máxima similaridad sino un promedio.
+También para algunas métricas quedan afuera los synsets que no son sustantivos).
+\begin{multline}
+S_w(w_1, w_2) = max \{ S_s(s_1, s_2) \}: s_1 \in synsets(w_1),\\ s_2 \in synsets(w_2)
+\end{multline}
+
+Para path similarity vale que $0 \leq S_w \leq 1$.
+
+Sobre $S_w$ (de word similarity) definimos la similaridad de un documento a un término como:
 
 \begin{equation}
-  d(a, S) = min_{x \in S} d(a, x) 
+S_{dw}(d, w) = sum \{ S_w(d_i, w) \times p(d_i)  \} 
 \end{equation}
 
-being $S$ the set of most representative words. Hence, we are ``projecting'' a text into the set of their top words.
+donde las tuplas $(d_i , p(d_i))$ representan las palabras más importantes del documento $d$, y sus respectivos pesos normalizados. Vale que $0 \leq p(d_i) \leq 1$ pues está normalizado.
 
-\section{Method}
-\subsection{Text Corpus}
-We selected some starred works from Lenin from the "Marxists Internet Archive".
-Those works are very different in topic, some of them being strictly phylosophical essays (such as ``Materialism and Empiriocriticism'') and other being more political, such as ``State and Revolution'', and finally an economy essay called ``Imperialism, the highest stage of capitalism''
+Por ejemplo $S_{dw}$(“Estado y Revolución”, “guerra”) = 0.110. $S_{dw}$ es una noción de cercanía entre un documento y una palabra.
 
-\begin{itemize}
-  \item What is to be done(1901)
-  \item The Agrarian Programme of Social-Democracy in the First Russian Revolution, 1905-1907 (1907)
-  \item Materialism and Empiriocriticism (1908)
-  \item Imperialism, the highest stage of capitalism (1916)
-  \item State and Revolution (1917)
-\end{itemize}
-
-%*Números (obras totales obtenidas, promedio tokens)
-\subsection{Information Value Framework}
-\medskip
-
-\subsubsection{Optimal window size selection}
-As \cite{DARWIN} mentions, we should consider the window size which maximizes the information value per word, for some sense of it.
-
-Let's suppose we have a document, and a window size $W_S$ for which the information value algorithm returns a list $\{(w_1, v_1), (w_2, v_2), \dots ,(w_n, v_n) \}$ of word-information value pairs, in decreasing order of information value so that $v_1 \geq v_2 \geq \dots \geq v_n$.
-How would we assign some value to this pair of document-window size so we can choose the optimal window size?
-
-One possibility would be to take the greater information value, in this case $v_1$.
-This approach, however, gives all the value just to a single word.
-Another chance would be to take the average of all the information values, but this leads to a lot of noise added because of words without any value.
-
-The chosen approach is a tradeoff between both.
-We take the average not of all the words, but of a percentage of the most significative words.
-We call this percentage the \emph{sum threshold}.
-If $n$ is the number of words in the document, and $0 \leq ST \leq 1$ is the sum threshold, we calculate
-
+Finalmente, definimos la noción de similaridad entre un año y una palabra como el promedio de las similaridades ($S_{dw}$) 
+de los distintos documentos producidos durante ese año con la palabra en cuestión:
 \begin{equation}
-  \frac{\sum_{i=1}^{[ST n]}v_i}{n} 
+  S_{yw}(y, w) = mean \{ S_dw(y_i, w) \} : y_i \in docs(y) 
 \end{equation}
 
-The threshold value we used is $ST=0.001$, so it would consider only the $\frac{n}{1000}$ most significant words.
-The reason behind this was that it fitted the results from \cite{DARWIN} for the texts The origin of the species, Moby Dick, and  The Analysis of the mind.
+Los resultados que presentaremos a continuaci\'on est\'an apoyados en distintas configuraciones de estas tres m\'etricas ($S_w$, $S_dw$ y $S_{yw}$).
 
-\subsection{Top words for given works}
+% *SynsetAnalyzer
+%   *Synset
+%   *path, lch, wup
+% *judge_word
+% *judge_doc
+% *judge_year
+% Dado un conjunto de palabras, definimos la distancia de una palabra a este conjunto como 
+%
+
+\subsubsection{Word sense disambiguation}
+
+\subsubsection{Top-sense definition}
+
+\section{Results}
+* Distancia a algunos conceptos de estado y revolución
+
+\subsection{Top senses for selected works}
+
+\subsection{Distances to evaluation sets}
+*
+* x = {años}, y = {concept value}
+
+\subsubsection{Observations}
+
+\section{Discussion}
+
+\subsection{Lesk for wsd: results and limitations}
+* Zanette diferia en valores absolutos con los resultados nuestros. Moby Dick.
+
+\subsection{Wordnet's synset distances}
+
+\section{Conclussion \& Future work}
+The original scope of this investigation was the definition of a measure of distance between the works of a whole year but we find a lot of complexities in the definition of that model.
+While we decide to reduce the scope of this work for mental health, we consider the metric defined in this article as a step into the concretion of the original goal.
+
+\appendix[All tables]
 
@@
 
-\subsection{Wordnet analyzer}
-Consideremos el siguiente problema:
-\newline
-¿Cómo calcular la similaridad o distancia de un documento a un cierto concepto? 
-\newline
-El enfoque que utilizamos en este trabajo es el de realizar una representación del documento como un conjunto de palabras, y en base a esto usar una noción topológica de similaridad/distancia.
-La proyección del documento al espacio de palabras la realizamos utilizando la t\'ecnica de Information Value reci\'en descripta.
-En este espacio, utilizamos Wordnet para definir una noción de distancia entre el conjunto de palabras que representan al texto y diferentes conjuntos representando conceptos.
-\newline
-Para un documento dado, el módulo de information value genera una lista con lo $n$ términos más importantes y su iv.
-Estos valores se normalizan -dividiendo por la suma de los valores-, obteniendo así uno de los inputs del proceso siguiente.
-Recordemos, nuestro objetivo es asignar una distancia entre un documento y un concepto.
-Digamos, decidir cuán presente está o cuán importante es un concepto en un documento.
-\newline
-Wordnet es una base de datos de palabras, agrupadas en conjuntos de sinónimos (synsets), cada uno de los cuales posee una definición y diferentes relaciones semánticas con otros synsets (por ejemplo: hipernimia, hiponimia, meronimia, etc).
-Sobre estas relaciones semánticas es posible definir distintas métricas de distancia y similaridad entre synsets (Ver [1])
-\newline
-Utilizando las métricas disponibles en el módulo nltk de python para wordnet definimos la similaridad entre dos palabras como la máxima similaridad entre todos los synsets de ambas.
-(**NOTA Parametrizable: puede ser sólo el primer synset de ambos y puede no ser la máxima similaridad sino un promedio.
-También para algunas métricas quedan afuera los synsets que no son sustantivos).
-\begin{multline}
-S_w(w_1, w_2) = max \{ S_s(s_1, s_2) \}: s_1 \in synsets(w_1),\\ s_2 \in synsets(w_2)
-\end{multline}
-
-Para path similarity vale que $0 \leq S_w \leq 1$.
-
-Sobre $S_w$ (de word similarity) definimos la similaridad de un documento a un término como:
-
-\begin{equation}
-S_{dw}(d, w) = sum \{ S_w(d_i, w) \times p(d_i)  \} 
-\end{equation}
-
-donde las tuplas $(d_i , p(d_i))$ representan las palabras más importantes del documento $d$, y sus respectivos pesos normalizados. Vale que $0 \leq p(d_i) \leq 1$ pues está normalizado.
-
-Por ejemplo $S_{dw}$(“Estado y Revolución”, “guerra”) = 0.110. $S_{dw}$ es una noción de cercanía entre un documento y una palabra.
-
-Finalmente, definimos la noción de similaridad entre un año y una palabra como el promedio de las similaridades ($S_{dw}$) 
-de los distintos documentos producidos durante ese año con la palabra en cuestión:
-\begin{equation}
-  S_{yw}(y, w) = mean \{ S_dw(y_i, w) \} : y_i \in docs(y) 
-\end{equation}
-
-Los resultados que presentaremos a continuaci\'on est\'an apoyados en distintas configuraciones de estas tres m\'etricas ($S_w$, $S_dw$ y $S_{yw}$).
-
-% *WordnetAnalyzer
-%   *Synset
-%   *path, lch, wup
-% *judge_word
-% *judge_doc
-% *judge_year
-% Dado un conjunto de palabras, definimos la distancia de una palabra a este conjunto como 
-%
-
-* Distancia a algunos conceptos de estado y revolución
-
-\subsection{Resultados sobre años}
-*
-* x = {años}, y = {concept value}
-
-\section{Discussion}
-* Zanette diferia en valores absolutos con los resultados nuestros. Moby Dick.
-
-\section{Acknowledgments}
-
-\section{Literature cited}
-
-\section{Analysis of almost sharp fronts}
-We begin our analysis on almost sharp fronts for the
-quasi-geostrophic equation recalling the notion of weak solution.
-
-For these solutions we have the following
-
-\appendix[Parallel calculus of information value]
-
 \appendix[Entropy of a word in a text]
-
+\label{appendix1}
 Let's recall from \cite{DARWIN} and \cite{ENTROPIC} the concept of information value of a word. 
@@
 
-\appendix[Estimating the Spectral Norm of a Matrix]
-In this appendix we describe a method for the estimation of the spectral norm
-of matrix $A$. The method does not require access to the individual
-entries of $A$; it requires only applications of $A$ and $A$* to vectors.
-It is a version of the classical power method. Its probabilistic
-analysis summarized below was introduced fairly recently in refs. 13
-and 14. This appendix is included here for completeness.
+\appendix[Optimal window size selection]
 
-\appendix
-This is an example of an appendix without a title.
+As \cite{DARWIN} mentions, we should consider the window size which maximizes the information value per word, for some sense of it.
 
-\begin{acknowledgments}
-This work was partially supported by 
-Spanish Ministry of Science and Technology Grant BFM2002-02042 (to D.C. and
-J.L.R.) and by National Science Foundation Grand DMS-0245242 (to C.F.).
-\end{acknowledgments}
+Let's suppose we have a document, and a window size $W_S$ for which the information value algorithm returns a list $\{(w_1, v_1), (w_2, v_2), \dots ,(w_n, v_n) \}$ of word-information value pairs, in decreasing order of information value so that $v_1 \geq v_2 \geq \dots \geq v_n$.
+How would we assign some value to this pair of document-window size so we can choose the optimal window size?
+
+One possibility would be to take the greater information value, in this case $v_1$.
+This approach, however, gives all the value just to a single word.
+Another chance would be to take the average of all the information values, but this leads to a lot of noise added because of words without any value.
+
+The chosen approach is a tradeoff between both.
+We take the average not of all the words, but of a percentage of the most significative words.
+We call this percentage the \emph{sum threshold}.
+If $n$ is the number of words in the document, and $0 \leq ST \leq 1$ is the sum threshold, we calculate
+
+\begin{equation}
+  \frac{\sum_{i=1}^{[ST n]}v_i}{n} 
+\end{equation}
+
+The threshold value we used is $ST=0.001$, so it would consider only the $\frac{n}{1000}$ most significant words.
+The reason behind this was that it fitted the results from \cite{DARWIN} for the texts The origin of the species, Moby Dick, and  The Analysis of the mind.
 
 \begin{thebibliography}{10}
+\bibitem{LENIN}
+Marxists Internet Archive, {\em www.marxists.org} %, No estaria pudiendo definir bien esta referencia
 \bibitem{DARWIN}
@@
 M.A. Montemurro and D. H. Zanette, {\em Entropic analysis of the role of words in literary texts}, Adv. Complex Systems 5, September 27th 2001
+\bibitem{MAS-ZANETTE}
 \bibitem{WORDNET}
 George A. Miller, {\em WordNet: A Lexical Database for English }, COMMUNICATIONS OF THE ACM November 1995/Vol. 38, No. 11
-
+\bibitem{LESK}
+Autor, {\em Nombre }, Publicación, No. %Buscar y poner
 \end{thebibliography}
 \end{article}
+\end{document}
 
-\begin{table}[h]
-\caption{Repeat length of longer allele by age of onset class.
-This is what happens when the text continues.}
-\begin{tabular}{@{\vrule height 10.5pt depth4pt  width0pt}lrcccc}
-&\multicolumn5c{Repeat length}\\
-\noalign{\vskip-11pt}
-Age of onset,\\
-\cline{2-6}
-\vrule depth 6pt width 0pt years&\multicolumn1c{\it n}&Mean&SD&Range&Median\\
-\hline
-Juvenile, 2$-$20&40&60.15& 9.32&43$-$86&60\\
-Typical, 21$-$50&377&45.72&2.97&40$-$58&45\\
-Late, $>$50&26&41.85&1.56&40$-$45&42\tablenote{The no. of wells for all samples was 384. Genotypes were
-determined by mass spectrometric assay. The $m_t$ value indicates the
-average number of wells positive for the over represented allele.}
-\\
-\hline
-\end{tabular}
-\end{table}
+%\section{Acknowledgments}
 
-\begin{table*}[ht]
-\caption{Summary of the experimental results}
-\begin{tabular*}{\hsize}
-{@{\extracolsep{\fill}}rrrrrrrrrrrrr}
-\multicolumn{3}{l}{Parameters}&
-\multicolumn{5}{c}{Averaged Results}&
-\multicolumn{5}{c}{Comparisons}\cr
-\hline
-\multicolumn1c{$n$}&\multicolumn1c{$S^*_{MAX}$}&
-\multicolumn1c{$t_1$}&\multicolumn1c{\ $r_1$}&
-\multicolumn1c{\ $m_1$}&\multicolumn1c{$t_2$}&
-\multicolumn1c{$r_2$}&\multicolumn1c{$m_2$}
-&\multicolumn1c{$t_{lb}$}&\multicolumn1c{\ \ $t_1/t_2$}&
-$r_1/r_2$&$m_1/m_2$&
-$t_1/t_{lb}$\cr
-\hline
-10\tablenote{Stanford Synchrotron Radiation Laboratory (Stanford University,
-Stanford, CA)}&1\quad &4&.0007&4&4&.0020&4&4&1.000&.333&1.000&1.000\cr
-10\tablenote{$R_{\rm FREE}=R$ factor for the $\sim 5$\% of the randomly
-chosen unique ref\/lections not used in the ref\/inement.}&5\quad &50&.0008&8&50&.0020&12&49&.999&.417&.698&1.020\cr
-100\tablenote{Calculated for all observed data}&20\quad &2840975&.0423&95&2871117&.1083&521&---&
-.990&.390&.182&---\ \ \cr
-\hline
-\end{tabular*}
-\end{table*}
+%\section{Literature cited}
 
-\end{document}
+% \section{Analysis of almost sharp fronts}
+% We begin our analysis on almost sharp fronts for the
+% quasi-geostrophic equation recalling the notion of weak solution.
+
+% For these solutions we have the following
+
+% \appendix[Parallel calculus of information value]
+
+% \begin{table}[h]
+% \caption{Repeat length of longer allele by age of onset class.
+% This is what happens when the text continues.}
+% \begin{tabular}{@{\vrule height 10.5pt depth4pt  width0pt}lrcccc}
+% &\multicolumn5c{Repeat length}\\
+% \noalign{\vskip-11pt}
+% Age of onset,\\
+% \cline{2-6}
+% \vrule depth 6pt width 0pt years&\multicolumn1c{\it n}&Mean&SD&Range&Median\\
+% \hline
+% Juvenile, 2$-$20&40&60.15& 9.32&43$-$86&60\\
+% Typical, 21$-$50&377&45.72&2.97&40$-$58&45\\
+% Late, $>$50&26&41.85&1.56&40$-$45&42\tablenote{The no. of wells for all samples was 384. Genotypes were
+% determined by mass spectrometric assay. The $m_t$ value indicates the
+% average number of wells positive for the over represented allele.}
+% \\
+% \hline
+% \end{tabular}
+% \end{table}
+
+% \begin{table*}[ht]
+% \caption{Summary of the experimental results}
+% \begin{tabular*}{\hsize}
+% {@{\extracolsep{\fill}}rrrrrrrrrrrrr}
+% \multicolumn{3}{l}{Parameters}&
+% \multicolumn{5}{c}{Averaged Results}&
+% \multicolumn{5}{c}{Comparisons}\cr
+% \hline
+% \multicolumn1c{$n$}&\multicolumn1c{$S^*_{MAX}$}&
+% \multicolumn1c{$t_1$}&\multicolumn1c{\ $r_1$}&
+% \multicolumn1c{\ $m_1$}&\multicolumn1c{$t_2$}&
+% \multicolumn1c{$r_2$}&\multicolumn1c{$m_2$}
+% &\multicolumn1c{$t_{lb}$}&\multicolumn1c{\ \ $t_1/t_2$}&
+% $r_1/r_2$&$m_1/m_2$&
+% $t_1/t_{lb}$\cr
+% \hline
+% 10\tablenote{Stanford Synchrotron Radiation Laboratory (Stanford University,
+% Stanford, CA)}&1\quad &4&.0007&4&4&.0020&4&4&1.000&.333&1.000&1.000\cr
+% 10\tablenote{$R_{\rm FREE}=R$ factor for the $\sim 5$\% of the randomly
+% chosen unique ref\/lections not used in the ref\/inement.}&5\quad &50&.0008&8&50&.0020&12&49&.999&.417&.698&1.020\cr
+% 100\tablenote{Calculated for all observed data}&20\quad &2840975&.0423&95&2871117&.1083&521&---&
+% .990&.390&.182&---\ \ \cr
+% \hline
+% \end{tabular*}
+% \end{table*}
+
+% \appendix[Estimating the Spectral Norm of a Matrix]
+% In this appendix we describe a method for the estimation of the spectral norm
+% of matrix $A$. The method does not require access to the individual
+% entries of $A$; it requires only applications of $A$ and $A$* to vectors.
+% It is a version of the classical power method. Its probabilistic
+% analysis summarized below was introduced fairly recently in refs. 13
+% and 14. This appendix is included here for completeness.
+
+% \appendix
+% This is an example of an appendix without a title.
+
+% \begin{acknowledgments}
+% algo
+% This work was partially supported by 
+% Spanish Ministry of Science and Technology Grant BFM2002-02042 (to D.C. and
+% J.L.R.) and by National Science Foundation Grand DMS-0245242 (to C.F.).
+% \end{acknowledgments}

### 2014-02-20 paper/wsd.tex
ass raw wsd text for the method part

Word sense disambiguation involves the association of a given word in a text or discourse with a definition or meaning.
On the other side by polysemy we refer to the fact that in different contexts or when used by different people the same term takes on varying referential significance.
We found that sense disambiguation was necessary to solve in one or another level the problem of polysemy.

Our approach for WSD was a classical Lesk implementation that uses wordnet as a definition source with some tweaks.
Basically Lesk is based on the idea that words that co–occur in a sentence are being used to refer to the same topic.
The Lesk alghorithm{11} takes the word definition or gloss that we want to disambiguate and it compares it gloss against the glosses of the other words in the context.
Then a word is assigned that sense whose gloss shares the largest number of words in common with the glosses of the other words.
This algorhitm suffers the problem that relies on the word definition and definitions usually uses as less words as possible.
Not only that sometimes two different words, but related ones, uses no words in common in their definitions.
As we use the nltk wordnet we immediately notice an improvement using the rich set of relationships that Wordnet gives to us.

BIO
M. Lesk. Automatic sense disambiguation using machine readable dictionaries: How to tell a pine cone from a ice cream cone. In Proceedings of SIGDOC ’86, 1986.

### 2014-02-20 paper/paper.tex
Change name from Wn Analyzer to SynsetAnalyzer.
fix in my surname

@@
 
-\author{Leonardo Lázzaro,\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
+\author{Leonardo Lazzaro,\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
 Julián Peller,\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
@@
 
-% *WordnetAnalyzer
+% *SynsetAnalyzer
 %   *Synset

### 2014-02-21 paper/wsd.tex
fix on pipeline year is integer

@@
 Basically Lesk is based on the idea that words that co–occur in a sentence are being used to refer to the same topic.
-The Lesk alghorithm{11} takes the word definition or gloss that we want to disambiguate and it compares it gloss against the glosses of the other words in the context.
+The Lesk alghorithm{BIO} takes the word definition or gloss that we want to disambiguate and it compares it gloss against the glosses of the other words in the context.
 Then a word is assigned that sense whose gloss shares the largest number of words in common with the glosses of the other words.
@@
 As we use the nltk wordnet we immediately notice an improvement using the rich set of relationships that Wordnet gives to us.
+We added to Lesk word stems, hypernyms, hyponyms.
+For the problem of short word description we modified the algorthim to use the definition of the word to disambiguate and to compare it against the context words directly.
+Finally our algorithm chooses the best synset from wordnet based on the context words.
 

### 2014-02-21 lenin/pipelines.py

@@ -21,7 +21,7 @@ class LeninPipeline(object):
                 url=item['url'],
                 text=item['text'],
                 month=item['month'],
-                year=item['year'],
+                year=int(item['year']),
                 )
         try:
             odm_session.flush()

### 2014-02-22 paper/distance.tex
Change name from Wn Analyzer to SynsetAnalyzer.
add new command for creating latex code to be included in the paper. remove brackets on wsd.tex

--- 2013-12-21 paper/distance.tex
@@
 The reason behind this was that it fitted the results from \cite{DARWIN} for the texts The origin of the species, Moby Dick, and  The Analysis of the mind.
+
+\subsubsection{Word Sense Disambiguation}
+\input{wsd}
+
+\subsection{Top senses for given works}
+\input{top_senses_the_state_and_revolution}
+\input{top_senses_lenin_imperialism_the_highest_stage_of_capitalism}
+\input{top_senses_lenin_materialism_and_empirio-criticism}
+\input{top_senses_lenin_the_agrarian_programme_of_social-democracy_in_the_first_russian_revolution_1905-1907}
+\input{top_senses_lenin_what_is_to_be_done?}
 

### 2014-02-22 paper/wsd.tex
add new command for creating latex code to be included in the paper. remove brackets on wsd.tex

@@
 Basically Lesk is based on the idea that words that co–occur in a sentence are being used to refer to the same topic.
-The Lesk alghorithm{BIO} takes the word definition or gloss that we want to disambiguate and it compares it gloss against the glosses of the other words in the context.
+The Lesk alghorithm (BIO) takes the word definition or gloss that we want to disambiguate and it compares it gloss against the glosses of the other words in the context.
 Then a word is assigned that sense whose gloss shares the largest number of words in common with the glosses of the other words.

### 2014-02-22 cccp.py

@@ -2,12 +2,11 @@
 # coding: utf-8
 import sys
 import config
-import logging
-import analyzers
 import argparse
 import subprocess
 from commands.database import reset_senses
 from commands.year_analysis import calculate_year_analysis
+from commands.top_senses_tables import create_top_sense_tables
 import ming
 
 reload(config)
@@ -17,6 +16,7 @@ reload(config)
 def scrap_all_works():
     ret = subprocess.call("scrapy crawl lenin -o lenin_work.json -t json", shell=True)
     print "Scrapy has returned %s" % ret
+
 
 def set_number_of_tokens():
     from includes.tokenizer import tokenize
@@ -28,6 +28,7 @@ def set_number_of_tokens():
         document['number_of_words'] = len(tokenize(document['text']))
         db.document.save(document)
 
+
 def drop_iv():
     from pymongo import MongoClient
     client = MongoClient()
@@ -35,15 +36,15 @@ def drop_iv():
     db = client.lenin
     db.drop_collection('information_value_result')
 
+
 def add_commands(parser):
     import analyzers.commands
 
     analyzers.commands.load_commands(parser)
 
+
 def main():
     parser = argparse.ArgumentParser(description='Central de Control de Comandos y Procesos para el TP de Analisis de Lenin.')
-
-    
 
     # Parameter to scrap all the works before or not
     parser.add_argument('--shell', action='store_true', default=False, help="Opens an ipython console with db configured")
@@ -66,7 +67,8 @@ def main():
     parser.add_argument('--set-number-of-tokens', action='store_true', default=False, help='Calculate number of words for each work')
     parser.add_argument('--analyze-documents', action='store_true', default=False, help="Do Document Analysis for given concepts (pass with --concepts)")
     parser.add_argument('--reset-senses', action='store_true', default=False, help="Reset all senses calculated")
-    if len(sys.argv)==1:
+    parser.add_argument('--latex-info', action='store_true', default=False, help="Creates LaTex information for paper")
+    if len(sys.argv) == 1:
         parser.print_help()
         sys.exit(1)
     # Parse args
@@ -92,10 +94,10 @@ def main():
     if args.documents:
         from information_value.models import DocumentList
         doc_list = DocumentList(args.documents[0])
-    
+
     if args.drop_iv:
         drop_iv()
-    
+
     if args.analysis:
         from commands.database import calculate_results
         documents = None
@@ -103,33 +105,33 @@ def main():
             documents = doc_list.documents
[…]

### 2014-02-22 commands/top_senses_tables.py

@@ -1,0 +1,40 @@
+from interpreter import *
+from commands.database import reset_senses
+import string
+
+
+def create_top_sense_tables():
+    state_and_revolution = Document.query.find({"name": {"$regex": "State and Revolution"}}).next()
+    imperialism_capitalism = Document.query.find({"name": {"$regex": "Imperialism.*Capitalism.*"}}).next()
+    materialism_criticism = Document.query.find({"name": "Lenin: MATERIALISM and EMPIRIO-CRITICISM"}).next()
+    what_is_to_be_done = Document.query.find({"name": {"$regex": ".*What Is To Be Done.*"}}).next()
+    agrarian_programme = Document.query.find({"name": u'Lenin: The Agrarian Programme of Social-Democracy in the First Russian Revolution, 1905-1907'}).next()
+    documents = [state_and_revolution, imperialism_capitalism, materialism_criticism, what_is_to_be_done, agrarian_programme]
+    reset_senses()
+    for document in documents:
+        print "=" * 80
+        print document.name
+        try:
+            for word, _ in document.top_words():
+                print word
+        except AttributeError:
+            print "No top words found. Trying to calculate them."
+            from commands.database import calculate_results
+            calculate_results(documents=[document], window_size_algorithm='WindowsHardCodedSizeGenerator', store_only_best=False)
+
+        with open("paper/top_senses_%s.tex" % document.name.replace(' ', '_').replace(':', '').replace(',', '').lower(), "w") as tex_table:
+            tex_table.write("""
+    \\begin{center}
+      \\begin{tabular}{ | l | l | }
+        \hline
+        \multicolumn{2}{|c|}{%s} \\\\ \hline
+        \# & Word  \\\\ \hline\n""" % document.name)
+            for index, sense in enumerate(document.top_senses(), start=1):
+                print "%s --  %s " % (string.rjust(sense.name, 35),
+                    string.rjust(sense.definition, 55))
+                tex_table.write("%s & %s \\\\ \hline \n" % (index, string.rjust(sense.name, 35).split('.')[0].strip()))
+
+            tex_table.write("""
+      \end{tabular}
+    \end{center}
+            """)

### 2014-02-24 paper/refactor.tex
various sections of the papers writed

@@
 \section{Method}
-Text Corpus.  Scrapping. Total de documentos. Total de documentos por año. Total de tokens promedio. Filtros (esto está!)
 \subsection{Text Corpus}
@@
 
+\begin{itemize}
+  \item Mention the crawler for the complete lenin works, pointing that finally we didn't used it but that the scrapper is available in the project at github
+  \item May be, point out some numbers of the db generated. (total documents, mean tokens per document, etc). It's my opinion, I understand that it's not the main line of the project.
+\end{itemize}
+
 %*Números (obras totales obtenidas, promedio tokens)
@@
 
-Having a similarity notion between words, and the most valuable words from a text, our question arises: how distant is a word from a text?
-We use here the notion of distance between a point and a set defined as:
-
-\begin{equation}
-  d(a, S) = min_{x \in S} d(a, x) 
-\end{equation}
-
-being $S$ the set of most representative words. Hence, we are ``projecting'' a text into the set of their top words.
-
-In \cite{DARWIN}, Zanette and Montemurro defined the information value of a word in a text. This is
-a real value that quantifies how much information that word carries according to the text. Let $T$ be a 
+The information value of a word for a given text is defined and tested by Zanette \textit{et al.} in \cite{DARWIN} and \cite{ENTROPIC}.
+It is a real value that quantifies how much information a word carries according to the text. Let $T$ be a 
 text, and $T'$ a random shuffled version of $T$, and $w$ a word appearing in $T$. 
@@
 Ordering the words by their information value results in a list of the text's most representative words.
+In the context of our research, we call the first $n$ words of a text -with $n$ fixed-, ordered by it's information value, the \textit{top words} of the document.
+
+\begin{equation}
+  top\_words_{n}(T) = \{w | max(IV_T(w))\}
+\end{equation}
 
@@
 
-In order to measure the distance/similarity between two words, we use Wordnet (see \cite{WORDNET}), a lexical database in English.
-Using a subset of all the possible ``senses'' of both words , we test several similarity notions between them.
+Having the \textit{top-words} representation of a document, we were interested in measuring the distance or similarity of that text to different words.
+In order to address this problem we used different similarity functions defined over wordnet in the python's library nltk\footnote{link a nltk}.
+Wordnet is a lexical resource known as thesaurus, i.
+e, a data base of terms grouped as sets of synonyms (synsets), each of which have a definition and different semantic relations with others synsets (for example: hypernymy, hyponymy, meronymy, etc).
+The similarity functions are defined over this network of semantic relations.
 
-\textbf{Old title: Wordnet analyzer}
-Consideremos el siguiente problema:
-\newline
-¿Cómo calcular la similaridad o distancia de un documento a un cierto concepto? 
-\newline
-El enfoque que utilizamos en este trabajo es el de realizar una representación del documento como un conjunto de palabras, y en base a esto usar una noción topológica de similaridad/distancia.
-La proyección del documento al espacio de palabras la realizamos utilizando la t\'ecnica de Information Value reci\'en descripta.
-En este espacio, utilizamos Wordnet para definir una noción de distancia entre el conjunto de palabras que representan al texto y diferentes conjuntos representando conceptos.
-\newline
-Para un documento dado, el módulo de information value genera una lista con lo $n$ términos más importantes y su iv.
-Estos valores se normalizan -dividiendo por la suma de los valores-, obteniendo así uno de los inputs del proceso siguiente.
-Recordemos, nuestro objetivo es asignar una distancia entre un documento y un concepto.
-Digamos, decidir cuán presente está o cuán importante es un concepto en un documento.
-\newline
-Wordnet es una base de datos de palabras, agrupadas en conjuntos de sinónimos (synsets), cada uno de los cuales posee una definición y diferentes relaciones semánticas con otros synsets (por ejemplo: hipernimia, hiponimia, meronimia, etc).
-Sobre estas relaciones semánticas es posible definir distintas métricas de distancia y similaridad entre synsets (Ver [1])
-\newline
-Utilizando las métricas disponibles en el módulo nltk de python para wordnet definimos la similaridad entre dos palabras como la máxima similaridad entre todos los synsets de ambas.
-(**NOTA Parametrizable: puede ser sólo el primer synset de ambos y puede no ser la máxima similaridad sino un promedio.
-También para algunas métricas quedan afuera los synsets que no son sustantivos).
-\begin{multline}
-S_w(w_1, w_2) = max \{ S_s(s_1, s_2) \}: s_1 \in synsets(w_1),\\ s_2 \in synsets(w_2)
-\end{multline}
+This functions aren' t defined over words but over synsets.
+A synset, briefly, is an abstract notion of sense, meaning or concept that is independent from it's linguistic formulation or spelling.
+Using synsets instead of words, the wordnet thesaurus solves two problems of ambiguity limited to the linguistic domain: polisemy and synonymy.
+Polisemy occurs when a unique term may refer to more than one concept (for example, bank may refer to a financial institution or to a {\color{red}banco de plaza}.
+In the other hand, synonymy occurs when different terms refer to the same concept (for example \sq{car} and \sq{automobile} refers, both, to the same concept).
 
-Para path similarity vale que $0 \leq S_w \leq 1$.
+The similarities defined in the nltk-api are the following:
 
-Sobre $S_w$ (de word similarity) definimos la similaridad de un documento a un término como:
-
-\begin{equation}
-S_{dw}(d, w) = sum \{ S_w(d_i, w) \times p(d_i)  \} 
-\end{equation}
-
-donde las tuplas $(d_i , p(d_i))$ representan las palabras más importantes del documento $d$, y sus respectivos pesos normalizados. Vale que $0 \leq p(d_i) \leq 1$ pues está normalizado.
-
-Por ejemplo $S_{dw}$(“Estado y Revolución”, “guerra”) = 0.110. $S_{dw}$ es una noción de cercanía entre un documento y una palabra.
-
-Finalmente, definimos la noción de similaridad entre un año y una palabra como el promedio de las similaridades ($S_{dw}$) 
-de los distintos documentos producidos durante ese año con la palabra en cuestión:
-\begin{equation}
-  S_{yw}(y, w) = mean \{ S_dw(y_i, w) \} : y_i \in docs(y) 
-\end{equation}
-
-Los resultados que presentaremos a continuaci\'on est\'an apoyados en distintas configuraciones de estas tres m\'etricas ($S_w$, $S_dw$ y $S_{yw}$).
-
-% *SynsetAnalyzer
-%   *Synset
-%   *path, lch, wup
-% *judge_word
-% *judge_doc
-% *judge_year
-% Dado un conjunto de palabras, definimos la distancia de una palabra a este conjunto como 
-%
+\begin{itemize}
+  \item Path Similarity: based on the shortest path that connects the senses in the is-a (hypernym/hypnoym) taxonomy. 
+  \item Leacock-Chodorow Similarity: based on the shortest path that connects the senses (as above) and the maximum depth of the taxonomy in which the senses occur.
+The relationship is given as -log(p/2d) where p is the shortest path length and d the taxonomy depth.
+  \item Wu-Palmer Similarity: based on the depth of the two senses in the taxonomy and that of their Least Common Subsumer (most specific ancestor node). 
+  \item Resnik Similarity: based on the Information Content (IC) of the Least Common Subsumer.
+Note that for any similarity measure that uses information content, the result is dependent on the corpus used to generate the information content and the specifics of how the information content was created.
+  \item Jiang-Conrath Similarity Return a score denoting how similar two word senses are, based on the Information Content (IC) of the Least Common Subsumer and that of the two input Synsets.
+The relationship is given by the equation 1 / (IC(s1) + IC(s2) - 2 * IC(lcs)).
+  \item Lin Similarity: Return a score denoting how similar two word senses are, based on the Information Content (IC) of the Least Common Subsumer and that of the two input Synsets.
+The relationship is given by the equation 2 * IC(lcs) / (IC(s1) + IC(s2)).
+\end{itemize}
 
@@
 \subsubsection{Top-sense definition}
+
+In a first approach, we pretend to measure the distance between a document (represented by it's \textit{top words}) and different words.
+To address this problem using the wordnet distances between synsets described before, we modeled the notion of \sq{word} as the sum of all its synsets.
+The results were pretty demotivating, so we refocused our energy in order to define our problem in the space of word-senses (and no more in the space of words).
+
+Using the WSD algorithm described in the previous section, we defined the notion of \textit{top senses} of a document as the word-senses resulting from the disambiguation of the \textit{top words} of the documents obtained with Zannete's information value approach.
+
+Given a document $T$ and an arbitrary integer $n$, the \textit{top senses} are defined as follow:
+\begin{equation}
+  top\_senses_{n}(T) = \{s | w \in top\_words_{n}(T) \wedge  s = wsd_T(w)\}
+\end{equation}
+
+Based on this definition, we evaluate the resultant \textit{top senses} of some texts and then check the results of the different similarities with well known concepts in the next sections.
 
@@
 
+\appendix[Old stuff of wordnet in spanish]
+Consideremos el siguiente problema:
+\newline
+¿Cómo calcular la similaridad o distancia de un documento a un cierto concepto? 
+\newline
+El enfoque que utilizamos en este trabajo es el de realizar una representación del documento como un conjunto de palabras, y en base a esto usar una noción topológica de similaridad/distancia.
+La proyección del documento al espacio de palabras la realizamos utilizando la t\'ecnica de Information Value reci\'en descripta.
+En este espacio, utilizamos Wordnet para definir una noción de distancia entre el conjunto de palabras que representan al texto y diferentes conjuntos representando conceptos.
+\newline
+Para un documento dado, el módulo de information value genera una lista con lo $n$ términos más importantes y su iv.
+Estos valores se normalizan -dividiendo por la suma de los valores-, obteniendo así uno de los inputs del proceso siguiente.
+Recordemos, nuestro objetivo es asignar una distancia entre un documento y un concepto.
+Digamos, decidir cuán presente está o cuán importante es un concepto en un documento.
+\newline
+Wordnet es una base de datos de palabras, agrupadas en conjuntos de sinónimos (synsets), cada uno de los cuales posee una definición y diferentes relaciones semánticas con otros synsets (por ejemplo: hipernimia, hiponimia, meronimia, etc).
+Sobre estas relaciones semánticas es posible definir distintas métricas de distancia y similaridad entre synsets (Ver [1])
+\newline
+Utilizando las métricas disponibles en el módulo nltk de python para wordnet definimos la similaridad entre dos palabras como la máxima similaridad entre todos los synsets de ambas.
+(**NOTA Parametrizable: puede ser sólo el primer synset de ambos y puede no ser la máxima similaridad sino un promedio.
+También para algunas métricas quedan afuera los synsets que no son sustantivos).
+\begin{multline}
+S_w(w_1, w_2) = max \{ S_s(s_1, s_2) \}: s_1 \in synsets(w_1),\\ s_2 \in synsets(w_2)
+\end{multline}
+
+Para path similarity vale que $0 \leq S_w \leq 1$.
+
+Sobre $S_w$ (de word similarity) definimos la similaridad de un documento a un término como:
+
+\begin{equation}
+S_{dw}(d, w) = sum \{ S_w(d_i, w) \times p(d_i)  \} 
+\end{equation}
+
+donde las tuplas $(d_i , p(d_i))$ representan las palabras más importantes del documento $d$, y sus respectivos pesos normalizados. Vale que $0 \leq p(d_i) \leq 1$ pues está normalizado.
+
+Por ejemplo $S_{dw}$(“Estado y Revolución”, “guerra”) = 0.110. $S_{dw}$ es una noción de cercanía entre un documento y una palabra.
+
+Finalmente, definimos la noción de similaridad entre un año y una palabra como el promedio de las similaridades ($S_{dw}$) 
+de los distintos documentos producidos durante ese año con la palabra en cuestión:
+\begin{equation}
+  S_{yw}(y, w) = mean \{ S_dw(y_i, w) \} : y_i \in docs(y) 
+\end{equation}
+
+Los resultados que presentaremos a continuaci\'on est\'an apoyados en distintas configuraciones de estas tres m\'etricas ($S_w$, $S_dw$ y $S_{yw}$).
+
+% *SynsetAnalyzer
+%   *Synset
+%   *path, lch, wup
+% *judge_word
+% *judge_doc
+% *judge_year
+% Dado un conjunto de palabras, definimos la distancia de una palabra a este conjunto como 
+%
+
 \begin{thebibliography}{10}

### 2014-02-24 cccp.py
some fixes on top senses Latex tables command

@@ -92,8 +92,10 @@ def main():
 
     doc_list = None
     if args.documents:
-        from information_value.models import DocumentList
-        doc_list = DocumentList(args.documents[0])
+        from interpreter import Document
+        doc_list = Document.query.find({"name": {"$regex": args.documents[0]}})
+        #from information_value.models import DocumentList
+        #doc_list = DocumentList(args.documents[0])
 
     if args.drop_iv:
         drop_iv()
@@ -101,8 +103,8 @@ def main():
     if args.analysis:
         from commands.database import calculate_results
         documents = None
-        if doc_list:
-            documents = doc_list.documents
+        if doc_list is not None:
+            documents = doc_list
         calculate_results(documents=documents, window_size_algorithm=args.window_size_generator, store_only_best=False)
     if args.analysis_store_only_best:
 

### 2014-02-24 commands/database.py

@@ -8,9 +8,8 @@ from pymongo.errors import DuplicateKeyError
 
 from information_value.models import odm_session
 from information_value.models import Document
-from information_value.models import DocumentList
 from includes.tokenizer import tokenize
-import includes.ws_generator
+from includes import ws_generator  # don't delete this line!
 from information_value.analysis import get_all_analysis
 
 
@@ -36,25 +35,24 @@ def populate_database():
                 log.info("Duplicate found skipping...")
         log.info("Done")
 
-def _get_windows_size_generators(class_name):
-  # used for search classes by name in ws_generator
-  res = []
-  for name, obj in inspect.getmembers(sys.modules['includes.ws_generator']):
-    if inspect.isclass(obj):
-        if name == class_name:
-            return obj
 
-def calculate_results(documents=None, window_size_algorithm='WindowsHardCodedSizeGenerator', store_only_best = False):
+def _get_windows_size_generators(class_name):
+    # used for search classes by name in ws_generator
+    for name, obj in inspect.getmembers(sys.modules['includes.ws_generator']):
+        if inspect.isclass(obj):
+            if name == class_name:
+                return obj
+
+
+def calculate_results(documents=None, window_size_algorithm='WindowsHardCodedSizeGenerator', store_only_best=False):
   algorithm_class = _get_windows_size_generators(window_size_algorithm)
   if documents is None:
       documents = Document.query.find().all()
-  log.info("Selected window size generator %s" % window_size_algorithm)
-  i = 1
-  for document in documents:
-    log.info("Calculating information values for document %s (%i/%i)" % (document.name, i,len(documents)))
-    i = i+1
 
-    
+  log.info("Selected window size generator %s" % window_size_algorithm)
+  for i, document in enumerate(documents):
+    log.info("Calculating information values for document %s (%i)" % (document.name, i ))
+
     if document.text:
         document.tokenizer = tokenize
         win_size_generator = algorithm_class(document)
@@ -63,16 +61,18 @@ def calculate_results(documents=None, window_size_algorithm='WindowsHardCodedSiz
         if store_only_best:
           _delete_non_best_analysis(document, window_sizes)
 
+
 def _delete_non_best_analysis(document, window_sizes):
   best_res = document.get_information_value_result()
   log.info("Best window size for %s: %s" % (document.name, best_res.window_size))
   log.info("Removing other results from mongo")
   for one_res in document.results:
[…]

### 2014-02-24 commands/top_senses_tables.py

@@ -1,6 +1,10 @@
-from interpreter import *
-from commands.database import reset_senses
 import string
+import logging
+
+from interpreter import *
+
+log = logging.getLogger('lenin')
+
 
 
 def create_top_sense_tables():
@@ -10,17 +14,18 @@ def create_top_sense_tables():
     what_is_to_be_done = Document.query.find({"name": {"$regex": ".*What Is To Be Done.*"}}).next()
     agrarian_programme = Document.query.find({"name": u'Lenin: The Agrarian Programme of Social-Democracy in the First Russian Revolution, 1905-1907'}).next()
     documents = [state_and_revolution, imperialism_capitalism, materialism_criticism, what_is_to_be_done, agrarian_programme]
-    reset_senses()
+
+#   reset_senses()
+    log.info("Top words")
+    log.info("=" * 80)
     for document in documents:
-        print "=" * 80
-        print document.name
+        log.info("=" * 80)
+        log.info(document.name)
         try:
             for word, _ in document.top_words():
-                print word
+                log.info(word)
         except AttributeError:
-            print "No top words found. Trying to calculate them."
-            from commands.database import calculate_results
-            calculate_results(documents=[document], window_size_algorithm='WindowsHardCodedSizeGenerator', store_only_best=False)
+            log.exception("No top words found. Trying to calculate them.")
 
         with open("paper/top_senses_%s.tex" % document.name.replace(' ', '_').replace(':', '').replace(',', '').lower(), "w") as tex_table:
             tex_table.write("""
@@ -30,8 +35,8 @@ def create_top_sense_tables():
         \multicolumn{2}{|c|}{%s} \\\\ \hline
         \# & Word  \\\\ \hline\n""" % document.name)
             for index, sense in enumerate(document.top_senses(), start=1):
-                print "%s --  %s " % (string.rjust(sense.name, 35),
-                    string.rjust(sense.definition, 55))
+                log.info("Sense %s --  %s " % (string.rjust(sense.name, 35),
+                    string.rjust(sense.definition, 55)))
                 tex_table.write("%s & %s \\\\ \hline \n" % (index, string.rjust(sense.name, 35).split('.')[0].strip()))
 
             tex_table.write("""

### 2014-02-24 information_value/models.py

@@ -95,6 +95,7 @@ class Document(MappedClass):
     results = RelationProperty(InformationValueResult)
 
     def top_words(self, total_words=20, stop_words=stopwords.words('english'), greater_than_zero=True, window_size=None):
+        log.info('Calculate top words. total %s' % total_words)
         if window_size is None:
             window_size = self.get_information_value_result().window_size
         iv_words = self.get_iv_by_window_size(window_size)
@@ -105,6 +106,7 @@ class Document(MappedClass):
 
 
     def top_senses(self, total_senses=20):
+        log.info('Calculate top senses. total %s' % total_senses)
         top_words = (word for word, _ in self.top_words(total_senses*2))
         senses = []
         for word in top_words:

### 2014-02-24 paper/refactor.tex
add wsd text with bio reference. add generated tables from code

@@
 \subsubsection{Word sense disambiguation}
-
+\input{wsd}
 \subsubsection{Top-sense definition}
@@
 \appendix[All tables]
-
-\begin{center}
-  \begin{tabular}{ | l | l | }
-    \hline
-    \multicolumn{2}{|c|}{State and Revolution} \\ \hline
-    \# & Word  \\ \hline
-1 & kautsky \\ \hline
-2 & marx \\ \hline
-3 & revolution \\ \hline
-4 & works \\ \hline
-5 & engels \\ \hline
-6 & society \\ \hline
-7 & power \\ \hline
-8 & party \\ \hline
-9 & social \\ \hline
-10 & experience \\ \hline
-11 & bernstein \\ \hline
-12 & question \\ \hline
-13 & equality \\ \hline
-14 & phase \\ \hline
-15 & 1917 \\ \hline
-16 & commune \\ \hline
-17 & one \\ \hline
-18 & republic \\ \hline
-19 & class \\ \hline
-20 & law \\ \hline
-  \end{tabular}
-\end{center}
-
-\begin{center}
-  \begin{tabular}{ | l | l | }
-    \hline
-    \multicolumn{2}{|c|}{Imperialism, the Highest ...} \\ \hline
-    \# & Word  \\ \hline
-1 & enterprises \\ \hline
-2 & bank \\ \hline
-3 & imperialism \\ \hline
-4 & world \\ \hline
-5 & million \\ \hline
-6 & colonies \\ \hline
-7 & kautsky \\ \hline
-8 & colonial \\ \hline
-9 & production \\ \hline
-10 & cent \\ \hline
-11 & economic \\ \hline
-12 & company \\ \hline
-13 & capitalist \\ \hline
-14 & monopoly \\ \hline
-15 & big \\ \hline
-16 & countries \\ \hline
-17 & policy \\ \hline
-18 & powers \\ \hline
-19 & 000 \\ \hline
-20 & banks \\ \hline
-  \end{tabular}
-\end{center}
-
-\begin{center}
-  \begin{tabular}{ | l | l | }
-    \hline
-\multicolumn{2}{|c|}{Materialism and Empirio-criticism} \\ \hline
-\# & Word  \\ \hline
-1 & physics \\ \hline
-2 & social \\ \hline
-3 & avenarius \\ \hline
-4 & space \\ \hline
-5 & time \\ \hline
-6 & dietzgen \\ \hline
-7 & berkeley \\ \hline
-8 & truth \\ \hline
-9 & rey \\ \hline
-10 & objective \\ \hline
-11 & sensation \\ \hline
-12 & experience \\ \hline
-13 & pp \\ \hline
-14 & engels \\ \hline
-15 & motion \\ \hline
-16 & marx \\ \hline
-17 & book \\ \hline
-18 & works \\ \hline
-19 & vol \\ \hline
-20 & general \\ \hline
-  \end{tabular}
-\end{center}
-
-\begin{center}
-  \begin{tabular}{ | l | l | }
-    \hline
-\multicolumn{2}{|c|}{What Is To Be Done?} \\ \hline
-\# & Word  \\ \hline
-1 & local \\ \hline
-2 & organisation \\ \hline
-3 & abroad \\ \hline
-4 & union \\ \hline
-5 & criticism \\ \hline
-6 & economic \\ \hline
-7 & political \\ \hline
-8 & revolutionaries \\ \hline
-9 & freedom \\ \hline
-10 & newspapers \\ \hline
-11 & workers \\ \hline
-12 & nadezhdin \\ \hline
-13 & consciousness \\ \hline
-14 & newspaper \\ \hline
-15 & bourgeois \\ \hline
-16 & masses \\ \hline
-17 & martynov \\ \hline
-18 & would \\ \hline
-19 & movement \\ \hline
-20 & german \\ \hline
-  \end{tabular}
-\end{center}
-
-\begin{center}
-  \begin{tabular}{ | l | l | }
-    \hline
-\multicolumn{2}{|c|}{The Agrarian Programme of ...} \\ \hline
-\# & Word  \\ \hline
-1 & rent \\ \hline
-2 & dessiatins \\ \hline
-3 & 000 \\ \hline
-4 & land \\ \hline
-5 & maslov \\ \hline
-6 & peasants \\ \hline
-7 & capital \\ \hline
-8 & revolution \\ \hline
-9 & marx \\ \hline
-10 & people \\ \hline
-11 & nationalisation \\ \hline
-12 & plekhanov \\ \hline
-13 & restoration \\ \hline
-14 & right \\ \hline
-15 & latifundia \\ \hline
-16 & private \\ \hline
-17 & farming \\ \hline
-18 & free \\ \hline
-19 & central \\ \hline
-20 & lands \\ \hline
-  \end{tabular}
-\end{center}
-
+\input{top_senses_the_state_and_revolution}
 \appendix[Entropy of a word in a text]
@@
 \bibitem{LESK}
-Autor, {\em Nombre }, Publicación, No. %Buscar y poner
+M. Lesk. Automatic sense disambiguation using machine readable dictionaries: How to tell a pine cone from a ice cream cone. In Proceedings of SIGDOC ’86, 1986.
 \end{thebibliography}

### 2014-02-24 paper/wsd.tex
add wsd text with bio reference. add generated tables from code

--- 2014-02-21 paper/wsd.tex
@@
 Basically Lesk is based on the idea that words that co–occur in a sentence are being used to refer to the same topic.
-The Lesk alghorithm{BIO} takes the word definition or gloss that we want to disambiguate and it compares it gloss against the glosses of the other words in the context.
+The Lesk alghorithm \cite{LESK} takes the word definition or gloss that we want to disambiguate and it compares it gloss against the glosses of the other words in the context.
 Then a word is assigned that sense whose gloss shares the largest number of words in common with the glosses of the other words.
@@
 BIO
-M. Lesk. Automatic sense disambiguation using machine readable dictionaries: How to tell a pine cone from a ice cream cone. In Proceedings of SIGDOC ’86, 1986.

### 2014-02-26 paper/refactor.tex
translate banco de plaza

@@
 But this ponderated set of top words has the problem of polysemy, tipical in the field of nlp.
-Polysemy occurs when a term has more than one sense or meaning, for example: the term 'bank' can refer to a financial institution or to a {\color{red}banco de plaza}, thus, it is polysemic.
+Polysemy occurs when a term has more than one sense or meaning, for example: the term 'bank' can refer to a financial institution or to the land formation, thus, it is polysemic.
 In order to resolve this limitation, we implement a basic algorithm of word-sense disambiguation based on wordnet's synsets and we apply it over the top words, using as disambiguation context the whole document.
@@
 Using synsets instead of words, the wordnet thesaurus solves two problems of ambiguity limited to the linguistic domain: polisemy and synonymy.
-Polisemy occurs when a unique term may refer to more than one concept (for example, bank may refer to a financial institution or to a {\color{red}banco de plaza}.
+Polisemy occurs when a unique term may refer to more than one concept (for example, bank may refer to a financial institution or to a the land formation.
 In the other hand, synonymy occurs when different terms refer to the same concept (for example \sq{car} and \sq{automobile} refers, both, to the same concept).

### 2014-02-27 commands/top_senses_tables.py
fix top senses tables

@@ -1,10 +1,9 @@
 import string
 import logging
 
-from interpreter import *
+from interpreter import Document
 
 log = logging.getLogger('lenin')
-
 
 
 def create_top_sense_tables():
@@ -33,13 +32,14 @@ def create_top_sense_tables():
       \\begin{tabular}{ | l | l | }
         \hline
         \multicolumn{2}{|c|}{%s} \\\\ \hline
-        \# & Word  \\\\ \hline\n""" % document.name)
-            for index, sense in enumerate(document.top_senses(), start=1):
+        \# & Word  \\\\ \hline\n""" % document.name[:30])
+            top_senses = document.top_senses()
+            last = len(top_senses)
+            for index, sense in enumerate(top_senses, start=1):
                 log.info("Sense %s --  %s " % (string.rjust(sense.name, 35),
                     string.rjust(sense.definition, 55)))
-                tex_table.write("%s & %s \\\\ \hline \n" % (index, string.rjust(sense.name, 35).split('.')[0].strip()))
+                tex_table.write("%s & %s \\\\ \hline" % (index, string.rjust(sense.name, 35).split('.')[0].strip().replace('_', '\_')))
+                if index != last:
+                    tex_table.write("\n")
 
-            tex_table.write("""
-      \end{tabular}
-    \end{center}
-            """)
+            tex_table.write("""\end{tabular}\n\end{center}""")

### 2014-02-27 paper/wsd.tex
clean up on WSD text
move Lesk cite

@@
 Word sense disambiguation involves the association of a given word in a text or discourse with a definition or meaning.
-On the other side by polysemy we refer to the fact that in different contexts or when used by different people the same term takes on varying referential significance.
 We found that sense disambiguation was necessary to solve in one or another level the problem of polysemy.
 
-Our approach for WSD was a classical Lesk implementation that uses wordnet as a definition source with some tweaks.
+Our approach for WSD was a classical Lesk\cite{LESK} implementation that uses wordnet as a definition source with some tweaks.
 Basically Lesk is based on the idea that words that co–occur in a sentence are being used to refer to the same topic.
-The Lesk alghorithm \cite{LESK} takes the word definition or gloss that we want to disambiguate and it compares it gloss against the glosses of the other words in the context.
+The Lesk alghorithm takes the word definition or gloss that we want to disambiguate and it compares it gloss against the glosses of the other words in the context.
 Then a word is assigned that sense whose gloss shares the largest number of words in common with the glosses of the other words.
@@
 Finally our algorithm chooses the best synset from wordnet based on the context words.
-
-BIO

### 2014-02-27 analyzers/commands.py
remove prints. return name for DocumentAnalyzer

@@ -1,14 +1,19 @@
 #! coding:utf-8
+import logging
 from information_value.models import DocumentList
 from document_analyzer import DocumentAnalyzer
 from guppy import hpy
+
+log = logging.getLogger('lenin')
+
+
 def analyze_documents(concepts):
     docs = DocumentList()
     analyzer = DocumentAnalyzer(concepts=concepts)
-    
+
     for doc in docs:
 
         res = analyzer.analyze_document(doc)
-        print res
+        log.info(res)
         h = hpy()
-        print h.heap()
+        log.info(h.heap())

### 2014-02-27 analyzers/document_analyzer.py

@@ -25,7 +25,9 @@ class DocumentAnalyzer(object):
  
     @property
     def name(self):
-        print self.similarity_function.func_name + " document analyzer"
+        name = self.similarity_function.func_name + "| document analyzer"
+        log.info(name)
+        return name
 
     def analyze_document(self, document):
         document_analysis = {} #self.__get_analysis_for(document)[self.prefix]

### 2014-02-27 analyzers/synset_analyzer.py

@@ -74,7 +74,7 @@ def year_vs_concept_data(concepts = None, year_min = 1899, year_max = 1923):
 
     analyzers = dict((concept, wna_for(concept)) for concept in concepts)
 
-    print "years {0} - {1} vs concepts: {2}. working...".format(year_min, year_max, concepts)
+    log.info("years {0} - {1} vs concepts: {2}. working...".format(year_min, year_max, concepts))
     for year in range(year_min, year_max):
         analyze_year(concepts, analyzers)
 
@@ -84,11 +84,11 @@ def analyze_year(concepts, analyzers):
     year_res = {}
     for concept in concepts:
       year_res[concept] = _year_vs_concept_analysis(concept, year, analyzers)
-    
+
     log.info("{2:.2f} = year-distance('{1}', '{0}') ".format(year, concept, res[year][concept]))
     output += "{0}: {1:.2f} ".format(concept, res[year][concept])
-  
-    print "year: {0}, #doc: {1}, res: {2}".format(year, doc_list.total_docs, output)
+
+    log.info("year: {0}, #doc: {1}, res: {2}".format(year, doc_list.total_docs, output))
 
 def _year_vs_concept_analysis(concept, year, analyzers):
     doc_list = DocumentList("", False, year)

### 2014-02-28 analyzers/document_analyzer.py
distance tables (big ones)

@@ -25,8 +25,8 @@ class DocumentAnalyzer(object):
  
     @property
     def name(self):
-        name = self.similarity_function.func_name + "| document analyzer"
-        log.info(name)
+        name = self.similarity_function.func_name
+        log.info(name + "| document analyzer")
         return name
 
     def analyze_document(self, document):

### 2014-02-28 cccp.py

@@ -6,7 +6,7 @@ import argparse
 import subprocess
 from commands.database import reset_senses
 from commands.year_analysis import calculate_year_analysis
-from commands.top_senses_tables import create_top_sense_tables
+from commands.top_senses_tables import create_tables
 import ming
 
 reload(config)
@@ -145,7 +145,7 @@ def main():
     if args.reset_senses:
         reset_senses()
     if args.latex_info:
-        create_top_sense_tables()
+        create_tables()
 
     if args.set_number_of_tokens:
         set_number_of_tokens()

### 2014-02-28 commands/top_senses_tables.py

@@ -1,20 +1,46 @@
 import string
 import logging
 
-from interpreter import Document
+from analyzers import similarity
+from interpreter import Document, wn
+from analyzers.document_analyzer import DocumentAnalyzer
+
+SIMILARITY_FUNCS = similarity.functions
 
 log = logging.getLogger('lenin')
 
+synsets = [wn.synset(word) for word in [
+           "war.n.01",
+           "capitalism.n.01",
+           "theory.n.01",
+           "toilet.n.04",
+           "imperialism.n.02",
+           "proletarian.n.01",
+           "practice.n.03",
+           "revolution.n.01",
+           "money.n.01",
+           "philosophy.n.02",
+           "idealism.n.01",
+           "strategy.n.02",
+           "materialism.n.02",
+           "lion.n.01",
+           "television_receiver.n.01",
+           "hair.n.01",
+           "sugar.n.01",
+           "car.n.01"]]
 
-def create_top_sense_tables():
+
+def document_list():
     state_and_revolution = Document.query.find({"name": {"$regex": "State and Revolution"}}).next()
     imperialism_capitalism = Document.query.find({"name": {"$regex": "Imperialism.*Capitalism.*"}}).next()
     materialism_criticism = Document.query.find({"name": "Lenin: MATERIALISM and EMPIRIO-CRITICISM"}).next()
     what_is_to_be_done = Document.query.find({"name": {"$regex": ".*What Is To Be Done.*"}}).next()
     agrarian_programme = Document.query.find({"name": u'Lenin: The Agrarian Programme of Social-Democracy in the First Russian Revolution, 1905-1907'}).next()
-    documents = [state_and_revolution, imperialism_capitalism, materialism_criticism, what_is_to_be_done, agrarian_programme]
+    return [state_and_revolution, imperialism_capitalism, materialism_criticism, what_is_to_be_done, agrarian_programme]
 
-#   reset_senses()
+
+def create_top_sense_tables():
+    documents = document_list()
     log.info("Top words")
     log.info("=" * 80)
     for document in documents:
@@ -36,10 +62,50 @@ def create_top_sense_tables():
             top_senses = document.top_senses()
             last = len(top_senses)
             for index, sense in enumerate(top_senses, start=1):
-                log.info("Sense %s --  %s " % (string.rjust(sense.name, 35),
-                    string.rjust(sense.definition, 55)))
+                log.info("Sense %s --  %s " % (string.rjust(sense.name, 35), string.rjust(sense.definition, 55)))
[…]

### 2014-02-28 analyzers/document_analyzer.py
pep8 fixes

@@ -18,11 +18,11 @@ class DocumentAnalyzer(object):
         self.prefix = similarity_function.func_name
         self.analyzers = dict(
             (synset, SynsetAnalyzer(
-                synsets=[synset], 
-                similarity_function=similarity_function, 
+                synsets=[synset],
+                similarity_function=similarity_function,
                 judge_function=judge_function)
             ) for synset in self.synsets)
- 
+
     @property
     def name(self):
         name = self.similarity_function.func_name
@@ -35,18 +35,18 @@ class DocumentAnalyzer(object):
 
         for synset in self.synsets:
             document_analysis[synset.name] = self.analyze_synset(synset=synset, document=document)
-        
+
         #db.document_analysis.save(document_analysis)
         return document_analysis
 
-   
+
     def analyze_synset(self, document, synset):
         # Only calculate in case there's no analysis done
         analyzer = self.analyzers[synset]
         doc_analysis = analyzer.judge_doc(document)
         self.best_word_for[synset.name] = synset_analyzer.best_word
         return doc_analysis
-    
+
     def __get_analysis_for(self, document):
         document_analysis = db.document_analysis.find_one({"document_id": document._id}) or {"document_id": document._id}
         if not self.prefix in document_analysis.keys():

### 2014-02-28 analyzers/similarity/similarities.py

@@ -1,13 +1,15 @@
 #! coding:utf-8
 from nltk.corpus import wordnet as wn
-from synsets import get_word_synsets
+
 
 def __max_similarity(synsets1, synsets2, similarity_function):
     similarities = [similarity_function(ss1, ss2) for ss1 in synsets1 for ss2 in synsets2]
     return max(similarities) if len(similarities) != 0 else .0
 
+
 def path_similarity(synsets1, synsets2):
     return __max_similarity(synsets1, synsets2, wn.path_similarity)
+
 
 def lch_similarity(synsets1, synsets2):
     return __max_similarity(synsets1, synsets2, wn.lch_similarity)
@@ -15,13 +17,16 @@ def lch_similarity(synsets1, synsets2):
 from nltk.corpus import wordnet_ic
 corpus = wordnet_ic.ic('ic-brown.dat')
 
+
 def lin_similarity(synsets1, synsets2):
     similarity_function = lambda ss1, ss2: wn.lin_similarity(ss1, ss2, corpus)
     return __max_similarity(synsets1, synsets2, similarity_function)
 
+
 def jcn_similarity(synsets1, synsets2):
     similarity_function = lambda ss1, ss2: wn.jcn_similarity(ss1, ss2, corpus)
     return __max_similarity(synsets1, synsets2, similarity_function)
+
 
 def res_similarity(synsets1, synsets2):
     similarity_function = lambda ss1, ss2: wn.res_similarity(ss1, ss2, corpus)

### 2014-02-28 analyzers/similarity/synsets.py

@@ -6,6 +6,7 @@ from nltk.corpus import wordnet as wn
 Get all the synsets for a word
 """
 
+
 def get_word_synsets(word, only_nouns=True):
     lemmas = wn.lemmas(word)
 
@@ -18,7 +19,7 @@ def get_word_synsets(word, only_nouns=True):
             return []
 
     #some distances doesn't handle not-noun words
-    synsets =  [lemma.synset for lemma in lemmas]
+    synsets = [lemma.synset for lemma in lemmas]
 
     if only_nouns:
         return [synset for synset in synsets if synset.name.split('.')[1] == 'n']

### 2014-02-28 analyzers/similarity/tests.py

@@ -4,7 +4,8 @@ from unittest import TestCase
 from analyzers.similarity import path_similarity
 from synsets import get_word_synsets
 
-class PathSimilarityTest(TestCase):    
+
+class PathSimilarityTest(TestCase):
     def test_similarity_between_the_same_word_should_return_1(self):
         war_ss = [wn.synset("war.n.01")]
         self.assertAlmostEqual(path_similarity(war_ss, war_ss), 1.0)

### 2014-02-28 analyzers/synset_analyzer.py

@@ -49,9 +49,9 @@ class SynsetAnalyzer:
         '''
           @returns double a value between 1.0 and 0.0
         '''
-        return self.similarity_function(self.synsets, get_word_synsets(word)) 
+        return self.similarity_function(self.synsets, get_word_synsets(word))
 
- 
+
 def wna_for(word):
     return SynsetAnalyzer(word)
 
@@ -66,7 +66,7 @@ def wnas_for(words):
 
 
 def year_vs_concept_data(concepts = None, year_min = 1899, year_max = 1923):
-  
+
     if not concepts:
         concepts = ["war", "idealism", "revolution", "philosophy"]
 

### 2014-02-28 information_value/analysis.py

@@ -85,18 +85,18 @@ def _get_window_size_analysis(window_size):
 def get_all_analysis(document, window_sizes, number_of_words=20):
     global __information_value_calculator
     global __number_of_words
-    global __document 
+    global __document
     __document = document
     __number_of_words = number_of_words
     __information_value_calculator = InformationValueCalculator(document.tokens)
-    
+
     pool = multiprocessing.Pool(processes=config.NUMBER_OF_THREADS)
     analysis = pool.map(_get_window_size_analysis, window_sizes)
     pool.close()
     pool.join()
 
     return filter(None, analysis)
-    
+
 def _get_all_analysis_single_threaded(document, window_sizes, number_of_words=20):
     global __information_value_calculator
     global __number_of_words
@@ -105,7 +105,7 @@ def _get_all_analysis_single_threaded(document, window_sizes, number_of_words=20
     __document = document
     __number_of_words = number_of_words
     __information_value_calculator = InformationValueCalculator(document.tokens)
-    
+
     analysis = map(_get_window_size_analysis, window_sizes)
 
     return filter(None, analysis)

### 2014-02-28 information_value/models.py

@@ -118,10 +118,10 @@ class Document(MappedClass):
             except wisdom.NoSenseFound:
                 pass
         odm_session.flush()
-        return senses        
+        return senses
 
     def __get_sense_for(self, word):
-        
+
         if not self.related_sense.has_key(word):
             sense = wisdom.lesk(self.text, word, pos='n')
             self.related_sense[word] = sense.name
@@ -228,7 +228,7 @@ class DocumentList(object):
         self.search_criterion = {
             'number_of_words': {'$gte': MIN_TOKENS}
         }
-        if name and name != '': 
+        if name and name != '':
             self.search_criterion['name'] = {'$regex': '.*'+name+'.*'},
 
         if year is not None:
@@ -246,7 +246,7 @@ class DocumentList(object):
 
     def __iter__(self):
         return self.documents_query
-        
+
     @property
     def total_docs(self):
         return self.documents_query.count()

### 2014-02-28 paper/analysis_lenin_imperialism_the_highest_.tex
add tex extension to analysis tables. add analysis tables also

    \begin{center}
      \begin{tabular}{ | l | l | l |}
        \hline
        Choosen Sensens & Closest Top Sense & similarity  \\ \hline
\multicolumn{3}{|c|}{Lenin: Imperialism, the Highes - path similarity} \\ \hline
capitalism.n.01 & capitalism.n.01 & 1.0 \\ \hline
proletarian.n.01 & great.n.01 & 0.2 \\ \hline
hair.n.01 & universe.n.01 & 0.2 \\ \hline
money.n.01 & penny.n.02 & 0.166666666667 \\ \hline
practice.n.03 & monopoly.n.01 & 0.166666666667 \\ \hline
toilet.n.04 & monopoly.n.01 & 0.142857142857 \\ \hline
war.n.01 & monopoly.n.01 & 0.142857142857 \\ \hline
revolution.n.01 & monopoly.n.01 & 0.125 \\ \hline
theory.n.01 & imperialism.n.01 & 0.125 \\ \hline
television receiver.n.01 & product.n.02 & 0.111111111111 \\ \hline
car.n.01 & product.n.02 & 0.111111111111 \\ \hline
philosophy.n.02 & policy.n.01 & 0.111111111111 \\ \hline
materialism.n.02 & policy.n.01 & 0.111111111111 \\ \hline
strategy.n.02 & policy.n.01 & 0.111111111111 \\ \hline
idealism.n.01 & policy.n.01 & 0.111111111111 \\ \hline
imperialism.n.02 & policy.n.01 & 0.1 \\ \hline
lion.n.01 & great.n.01 & 0.0769230769231 \\ \hline
sugar.n.01 & universe.n.01 & 0.0769230769231 \\ \hline
\multicolumn{3}{|c|}{Lenin: Imperialism, the Highes - lch similarity} \\ \hline
capitalism.n.01 & capitalism.n.01 & 3.63758615973 \\ \hline
proletarian.n.01 & great.n.01 & 2.02814824729 \\ \hline
hair.n.01 & universe.n.01 & 2.02814824729 \\ \hline
money.n.01 & penny.n.02 & 1.8458266905 \\ \hline
practice.n.03 & monopoly.n.01 & 1.8458266905 \\ \hline
toilet.n.04 & monopoly.n.01 & 1.69167601067 \\ \hline
war.n.01 & monopoly.n.01 & 1.69167601067 \\ \hline
revolution.n.01 & monopoly.n.01 & 1.55814461805 \\ \hline
theory.n.01 & imperialism.n.01 & 1.55814461805 \\ \hline
television receiver.n.01 & product.n.02 & 1.44036158239 \\ \hline
car.n.01 & product.n.02 & 1.44036158239 \\ \hline
philosophy.n.02 & policy.n.01 & 1.44036158239 \\ \hline
materialism.n.02 & policy.n.01 & 1.44036158239 \\ \hline
strategy.n.02 & policy.n.01 & 1.44036158239 \\ \hline
idealism.n.01 & policy.n.01 & 1.44036158239 \\ \hline
imperialism.n.02 & policy.n.01 & 1.33500106673 \\ \hline
lion.n.01 & great.n.01 & 1.07263680226 \\ \hline
sugar.n.01 & universe.n.01 & 1.07263680226 \\ \hline
\multicolumn{3}{|c|}{Lenin: Imperialism, the Highes - res similarity} \\ \hline
capitalism.n.01 & capitalism.n.01 & 11.6930111908 \\ \hline
money.n.01 & penny.n.02 & 6.2549318819 \\ \hline
theory.n.01 & imperialism.n.01 & 5.678990458 \\ \hline
hair.n.01 & universe.n.01 & 4.94037581121 \\ \hline
philosophy.n.02 & policy.n.01 & 3.29228159341 \\ \hline
materialism.n.02 & policy.n.01 & 3.29228159341 \\ \hline
strategy.n.02 & policy.n.01 & 3.29228159341 \\ \hline
idealism.n.01 & policy.n.01 & 3.29228159341 \\ \hline
toilet.n.04 & monopoly.n.01 & 3.14352023311 \\ \hline
imperialism.n.02 & imperialism.n.01 & 2.64452085446 \\ \hline
proletarian.n.01 & great.n.01 & 2.33354524374 \\ \hline
war.n.01 & monopoly.n.01 & 2.33223775508 \\ \hline
practice.n.03 & monopoly.n.01 & 2.33223775508 \\ \hline
television receiver.n.01 & product.n.02 & 2.30584873145 \\ \hline
car.n.01 & product.n.02 & 2.30584873145 \\ \hline
lion.n.01 & great.n.01 & 2.22415047123 \\ \hline
revolution.n.01 & monopoly.n.01 & 2.03632771779 \\ \hline
sugar.n.01 & universe.n.01 & 0.801759114954 \\ \hline
\multicolumn{3}{|c|}{Lenin: Imperialism, the Highes - jcn similarity} \\ \hline
capitalism.n.01 & capitalism.n.01 & 1e+300 \\ \hline
money.n.01 & penny.n.02 & 0.220543285308 \\ \hline
hair.n.01 & universe.n.01 & 0.185089245333 \\ \hline
car.n.01 & product.n.02 & 0.118562212358 \\ \hline
philosophy.n.02 & policy.n.01 & 0.0941972384174 \\ \hline
television receiver.n.01 & product.n.02 & 0.0922281130906 \\ \hline
theory.n.01 & imperialism.n.01 & 0.0849319922588 \\ \hline
proletarian.n.01 & product.n.02 & 0.0827408100653 \\ \hline
war.n.01 & monopoly.n.01 & 0.0769380100151 \\ \hline
lion.n.01 & product.n.02 & 0.0745010379336 \\ \hline
strategy.n.02 & policy.n.01 & 0.0729992753311 \\ \hline
practice.n.03 & monopoly.n.01 & 0.0696858132394 \\ \hline
toilet.n.04 & monopoly.n.01 & 0.0675356263653 \\ \hline
materialism.n.02 & policy.n.01 & 0.0673677474158 \\ \hline
sugar.n.01 & product.n.02 & 0.0665737679313 \\ \hline
revolution.n.01 & one.n.01 & 0.0654799767733 \\ \hline
idealism.n.01 & policy.n.01 & 0.063730003856 \\ \hline
imperialism.n.02 & policy.n.01 & 0.0574970955164 \\ \hline
\multicolumn{3}{|c|}{Lenin: Imperialism, the Highes - lin similarity} \\ \hline
capitalism.n.01 & capitalism.n.01 & 1.0 \\ \hline
money.n.01 & penny.n.02 & 0.733969426851 \\ \hline
hair.n.01 & universe.n.01 & 0.646495819603 \\ \hline
theory.n.01 & imperialism.n.01 & 0.491005027416 \\ \hline
philosophy.n.02 & policy.n.01 & 0.382810406388 \\ \hline
car.n.01 & product.n.02 & 0.353492745777 \\ \hline
strategy.n.02 & policy.n.01 & 0.324629309412 \\ \hline
materialism.n.02 & policy.n.01 & 0.307281190083 \\ \hline
television receiver.n.01 & product.n.02 & 0.298407179857 \\ \hline
toilet.n.04 & monopoly.n.01 & 0.298048188669 \\ \hline
idealism.n.01 & policy.n.01 & 0.295593207225 \\ \hline
war.n.01 & monopoly.n.01 & 0.264097390196 \\ \hline
proletarian.n.01 & great.n.01 & 0.262634686841 \\ \hline
practice.n.03 & monopoly.n.01 & 0.245310227149 \\ \hline
imperialism.n.02 & policy.n.01 & 0.233190306342 \\ \hline
lion.n.01 & great.n.01 & 0.232810355981 \\ \hline
revolution.n.01 & monopoly.n.01 & 0.205174493173 \\ \hline
sugar.n.01 & product.n.02 & 0.0964554176079 \\ \hline
\end{tabular}
\end{center}

### 2014-02-28 paper/analysis_lenin_materialism_and_empirio-.tex
add tex extension to analysis tables. add analysis tables also

    \begin{center}
      \begin{tabular}{ | l | l | l |}
        \hline
        Choosen Sensens & Closest Top Sense & similarity  \\ \hline
\multicolumn{3}{|c|}{Lenin: MATERIALISM and EMPIRIO - path similarity} \\ \hline
revolution.n.01 & experience.n.03 & 0.25 \\ \hline
proletarian.n.01 & matter.n.03 & 0.166666666667 \\ \hline
philosophy.n.02 & physics.n.01 & 0.166666666667 \\ \hline
war.n.01 & experience.n.03 & 0.166666666667 \\ \hline
strategy.n.02 & physics.n.01 & 0.166666666667 \\ \hline
practice.n.03 & experience.n.03 & 0.166666666667 \\ \hline
money.n.01 & beginning.n.02 & 0.142857142857 \\ \hline
materialism.n.02 & aim.n.02 & 0.142857142857 \\ \hline
idealism.n.01 & aim.n.02 & 0.142857142857 \\ \hline
imperialism.n.02 & aim.n.02 & 0.125 \\ \hline
sugar.n.01 & matter.n.03 & 0.125 \\ \hline
theory.n.01 & sensation.n.01 & 0.125 \\ \hline
hair.n.01 & space.n.02 & 0.125 \\ \hline
capitalism.n.01 & time.n.05 & 0.125 \\ \hline
toilet.n.04 & experience.n.03 & 0.111111111111 \\ \hline
television receiver.n.01 & space.n.02 & 0.0909090909091 \\ \hline
car.n.01 & space.n.02 & 0.0909090909091 \\ \hline
lion.n.01 & kant.n.01 & 0.0666666666667 \\ \hline
\multicolumn{3}{|c|}{Lenin: MATERIALISM and EMPIRIO - lch similarity} \\ \hline
revolution.n.01 & experience.n.03 & 2.25129179861 \\ \hline
proletarian.n.01 & matter.n.03 & 1.8458266905 \\ \hline
philosophy.n.02 & physics.n.01 & 1.8458266905 \\ \hline
war.n.01 & experience.n.03 & 1.8458266905 \\ \hline
strategy.n.02 & physics.n.01 & 1.8458266905 \\ \hline
practice.n.03 & experience.n.03 & 1.8458266905 \\ \hline
money.n.01 & beginning.n.02 & 1.69167601067 \\ \hline
materialism.n.02 & aim.n.02 & 1.69167601067 \\ \hline
idealism.n.01 & aim.n.02 & 1.69167601067 \\ \hline
imperialism.n.02 & aim.n.02 & 1.55814461805 \\ \hline
sugar.n.01 & matter.n.03 & 1.55814461805 \\ \hline
theory.n.01 & sensation.n.01 & 1.55814461805 \\ \hline
hair.n.01 & space.n.02 & 1.55814461805 \\ \hline
capitalism.n.01 & time.n.05 & 1.55814461805 \\ \hline
toilet.n.04 & experience.n.03 & 1.44036158239 \\ \hline
television receiver.n.01 & space.n.02 & 1.23969088693 \\ \hline
car.n.01 & space.n.02 & 1.23969088693 \\ \hline
lion.n.01 & kant.n.01 & 0.929535958624 \\ \hline
\multicolumn{3}{|c|}{Lenin: MATERIALISM and EMPIRIO - res similarity} \\ \hline
philosophy.n.02 & physics.n.01 & 5.58877614988 \\ \hline
strategy.n.02 & physics.n.01 & 5.58877614988 \\ \hline
theory.n.01 & sensation.n.01 & 4.38484522248 \\ \hline
revolution.n.01 & experience.n.03 & 4.05348916032 \\ \hline
sugar.n.01 & matter.n.03 & 3.3367059068 \\ \hline
materialism.n.02 & physics.n.01 & 3.29228159341 \\ \hline
idealism.n.01 & physics.n.01 & 3.29228159341 \\ \hline
capitalism.n.01 & sociable.n.01 & 2.85529368615 \\ \hline
money.n.01 & beginning.n.02 & 2.69110280536 \\ \hline
imperialism.n.02 & physics.n.01 & 2.64452085446 \\ \hline
proletarian.n.01 & kant.n.01 & 2.33354524374 \\ \hline
toilet.n.04 & motion.n.03 & 2.33223775508 \\ \hline
war.n.01 & motion.n.03 & 2.33223775508 \\ \hline
practice.n.03 & motion.n.03 & 2.33223775508 \\ \hline
television receiver.n.01 & book.n.01 & 2.30584873145 \\ \hline
car.n.01 & book.n.01 & 2.30584873145 \\ \hline
lion.n.01 & kant.n.01 & 2.22415047123 \\ \hline
hair.n.01 & kant.n.01 & 1.53183374322 \\ \hline
\multicolumn{3}{|c|}{Lenin: MATERIALISM and EMPIRIO - jcn similarity} \\ \hline
philosophy.n.02 & physics.n.01 & 0.145932703696 \\ \hline
theory.n.01 & sensation.n.01 & 0.128286683846 \\ \hline
sugar.n.01 & matter.n.03 & 0.127664075736 \\ \hline
revolution.n.01 & experience.n.03 & 0.111569245855 \\ \hline
money.n.01 & moment.n.01 & 0.107804699133 \\ \hline
car.n.01 & matter.n.03 & 0.107243331568 \\ \hline
hair.n.01 & matter.n.03 & 0.104557075904 \\ \hline
strategy.n.02 & physics.n.01 & 0.100652051627 \\ \hline
war.n.01 & motion.n.03 & 0.100254651557 \\ \hline
practice.n.03 & motion.n.03 & 0.0882827134582 \\ \hline
proletarian.n.01 & matter.n.03 & 0.0875035868175 \\ \hline
television receiver.n.01 & matter.n.03 & 0.085230569567 \\ \hline
lion.n.01 & matter.n.03 & 0.0783404338338 \\ \hline
materialism.n.02 & aim.n.02 & 0.0778269817906 \\ \hline
toilet.n.04 & motion.n.03 & 0.0745896410117 \\ \hline
idealism.n.01 & aim.n.02 & 0.0730123547216 \\ \hline
capitalism.n.01 & sociable.n.01 & 0.0678992095349 \\ \hline
imperialism.n.02 & aim.n.02 & 0.0649464570442 \\ \hline
\multicolumn{3}{|c|}{Lenin: MATERIALISM and EMPIRIO - lin similarity} \\ \hline
philosophy.n.02 & physics.n.01 & 0.619941000616 \\ \hline
strategy.n.02 & physics.n.01 & 0.529421413479 \\ \hline
theory.n.01 & sensation.n.01 & 0.529419405948 \\ \hline
revolution.n.01 & experience.n.03 & 0.474924895953 \\ \hline
sugar.n.01 & matter.n.03 & 0.460030062094 \\ \hline
money.n.01 & moment.n.01 & 0.367179548114 \\ \hline
materialism.n.02 & aim.n.02 & 0.33882403792 \\ \hline
idealism.n.01 & aim.n.02 & 0.324668589607 \\ \hline
war.n.01 & motion.n.03 & 0.318631846502 \\ \hline
car.n.01 & book.n.01 & 0.308668677605 \\ \hline
practice.n.03 & motion.n.03 & 0.291680639247 \\ \hline
capitalism.n.01 & sociable.n.01 & 0.27940619133 \\ \hline
television receiver.n.01 & book.n.01 & 0.265820778874 \\ \hline
toilet.n.04 & motion.n.03 & 0.258117063881 \\ \hline
imperialism.n.02 & aim.n.02 & 0.255677978749 \\ \hline
hair.n.01 & book.n.01 & 0.20182033649 \\ \hline
proletarian.n.01 & kant.n.01 & 0.198875753057 \\ \hline
lion.n.01 & kant.n.01 & 0.179337574844 \\ \hline
\end{tabular}
\end{center}

### 2014-02-28 paper/analysis_lenin_the_agrarian_programme_o.tex
add tex extension to analysis tables. add analysis tables also

    \begin{center}
      \begin{tabular}{ | l | l | l |}
        \hline
        Choosen Sensens & Closest Top Sense & similarity  \\ \hline
\multicolumn{3}{|c|}{Lenin: The Agrarian Programme  - path similarity} \\ \hline
revolution.n.01 & revolution.n.01 & 1.0 \\ \hline
proletarian.n.01 & peasant.n.01 & 0.25 \\ \hline
money.n.01 & bill.n.03 & 0.2 \\ \hline
war.n.01 & nationalization.n.03 & 0.2 \\ \hline
practice.n.03 & nationalization.n.03 & 0.166666666667 \\ \hline
capitalism.n.01 & people.n.01 & 0.166666666667 \\ \hline
hair.n.01 & land.n.04 & 0.142857142857 \\ \hline
toilet.n.04 & nationalization.n.03 & 0.111111111111 \\ \hline
philosophy.n.02 & absolute.n.01 & 0.111111111111 \\ \hline
materialism.n.02 & absolute.n.01 & 0.111111111111 \\ \hline
strategy.n.02 & absolute.n.01 & 0.111111111111 \\ \hline
idealism.n.01 & absolute.n.01 & 0.111111111111 \\ \hline
imperialism.n.02 & people.n.01 & 0.111111111111 \\ \hline
television receiver.n.01 & land.n.04 & 0.1 \\ \hline
car.n.01 & land.n.04 & 0.1 \\ \hline
theory.n.01 & people.n.01 & 0.1 \\ \hline
sugar.n.01 & land.n.04 & 0.0909090909091 \\ \hline
lion.n.01 & land.n.04 & 0.0714285714286 \\ \hline
\multicolumn{3}{|c|}{Lenin: The Agrarian Programme  - lch similarity} \\ \hline
revolution.n.01 & revolution.n.01 & 3.63758615973 \\ \hline
proletarian.n.01 & peasant.n.01 & 2.25129179861 \\ \hline
money.n.01 & bill.n.03 & 2.02814824729 \\ \hline
war.n.01 & nationalization.n.03 & 2.02814824729 \\ \hline
practice.n.03 & nationalization.n.03 & 1.8458266905 \\ \hline
capitalism.n.01 & people.n.01 & 1.8458266905 \\ \hline
hair.n.01 & land.n.04 & 1.69167601067 \\ \hline
toilet.n.04 & nationalization.n.03 & 1.44036158239 \\ \hline
philosophy.n.02 & absolute.n.01 & 1.44036158239 \\ \hline
materialism.n.02 & absolute.n.01 & 1.44036158239 \\ \hline
strategy.n.02 & absolute.n.01 & 1.44036158239 \\ \hline
idealism.n.01 & absolute.n.01 & 1.44036158239 \\ \hline
imperialism.n.02 & people.n.01 & 1.44036158239 \\ \hline
television receiver.n.01 & land.n.04 & 1.33500106673 \\ \hline
car.n.01 & land.n.04 & 1.33500106673 \\ \hline
theory.n.01 & people.n.01 & 1.33500106673 \\ \hline
sugar.n.01 & land.n.04 & 1.23969088693 \\ \hline
lion.n.01 & land.n.04 & 0.998528830111 \\ \hline
\multicolumn{3}{|c|}{Lenin: The Agrarian Programme  - res similarity} \\ \hline
revolution.n.01 & revolution.n.01 & 10.3880624692 \\ \hline
proletarian.n.01 & peasant.n.01 & 9.00601439892 \\ \hline
money.n.01 & bill.n.03 & 6.2549318819 \\ \hline
war.n.01 & nationalization.n.03 & 4.52385364841 \\ \hline
philosophy.n.02 & absolute.n.01 & 3.29228159341 \\ \hline
materialism.n.02 & absolute.n.01 & 3.29228159341 \\ \hline
strategy.n.02 & absolute.n.01 & 3.29228159341 \\ \hline
idealism.n.01 & absolute.n.01 & 3.29228159341 \\ \hline
capitalism.n.01 & people.n.01 & 2.85529368615 \\ \hline
imperialism.n.02 & absolute.n.01 & 2.64452085446 \\ \hline
theory.n.01 & absolute.n.01 & 2.64452085446 \\ \hline
toilet.n.04 & nationalization.n.03 & 2.33223775508 \\ \hline
practice.n.03 & nationalization.n.03 & 2.33223775508 \\ \hline
lion.n.01 & peasant.n.01 & 2.22415047123 \\ \hline
television receiver.n.01 & peasant.n.01 & 1.53183374322 \\ \hline
car.n.01 & peasant.n.01 & 1.53183374322 \\ \hline
hair.n.01 & peasant.n.01 & 1.53183374322 \\ \hline
sugar.n.01 & land.n.04 & 0.801759114954 \\ \hline
\multicolumn{3}{|c|}{Lenin: The Agrarian Programme  - jcn similarity} \\ \hline
revolution.n.01 & revolution.n.01 & 1e+300 \\ \hline
proletarian.n.01 & peasant.n.01 & 0.363995193783 \\ \hline
money.n.01 & bill.n.03 & 0.30619633675 \\ \hline
war.n.01 & farming.n.01 & 0.102813269009 \\ \hline
car.n.01 & land.n.04 & 0.0903577501322 \\ \hline
hair.n.01 & land.n.04 & 0.0884432572523 \\ \hline
capitalism.n.01 & people.n.01 & 0.0880782305893 \\ \hline
philosophy.n.02 & people.n.01 & 0.0801894085342 \\ \hline
television receiver.n.01 & land.n.04 & 0.0742092466431 \\ \hline
theory.n.01 & people.n.01 & 0.0738644334041 \\ \hline
practice.n.03 & people.n.01 & 0.0728246934249 \\ \hline
lion.n.01 & land.n.04 & 0.0689306688111 \\ \hline
strategy.n.02 & people.n.01 & 0.0642953740963 \\ \hline
sugar.n.01 & land.n.04 & 0.0640122327597 \\ \hline
toilet.n.04 & people.n.01 & 0.0632469161145 \\ \hline
materialism.n.02 & people.n.01 & 0.0598861536358 \\ \hline
idealism.n.01 & people.n.01 & 0.056994188175 \\ \hline
imperialism.n.02 & people.n.01 & 0.055706849963 \\ \hline
\multicolumn{3}{|c|}{Lenin: The Agrarian Programme  - lin similarity} \\ \hline
revolution.n.01 & revolution.n.01 & 1.0 \\ \hline
proletarian.n.01 & peasant.n.01 & 0.867659956556 \\ \hline
money.n.01 & bill.n.03 & 0.792980998294 \\ \hline
war.n.01 & farming.n.01 & 0.481925511595 \\ \hline
philosophy.n.02 & absolute.n.01 & 0.341316252969 \\ \hline
capitalism.n.01 & people.n.01 & 0.334654457361 \\ \hline
strategy.n.02 & absolute.n.01 & 0.294289762784 \\ \hline
materialism.n.02 & absolute.n.01 & 0.279961229282 \\ \hline
idealism.n.01 & absolute.n.01 & 0.270226260066 \\ \hline
theory.n.01 & absolute.n.01 & 0.259782259686 \\ \hline
practice.n.03 & restoration.n.02 & 0.240021453557 \\ \hline
toilet.n.04 & restoration.n.02 & 0.216821056563 \\ \hline
imperialism.n.02 & absolute.n.01 & 0.213506139286 \\ \hline
lion.n.01 & peasant.n.01 & 0.20131688425 \\ \hline
car.n.01 & land.n.04 & 0.18905393848 \\ \hline
hair.n.01 & land.n.04 & 0.185792500123 \\ \hline
television receiver.n.01 & land.n.04 & 0.160696186575 \\ \hline
sugar.n.01 & land.n.04 & 0.0930896185493 \\ \hline
\end{tabular}
\end{center}

### 2014-02-28 paper/analysis_lenin_what_is_to_be_done?.tex
add tex extension to analysis tables. add analysis tables also

    \begin{center}
      \begin{tabular}{ | l | l | l |}
        \hline
        Choosen Sensens & Closest Top Sense & similarity  \\ \hline
\multicolumn{3}{|c|}{Lenin: What Is To Be Done? - path similarity} \\ \hline
imperialism.n.02 & political orientation.n.01 & 0.5 \\ \hline
proletarian.n.01 & worker.n.01 & 0.25 \\ \hline
war.n.01 & conflict.n.01 & 0.25 \\ \hline
practice.n.03 & conflict.n.01 & 0.2 \\ \hline
revolution.n.01 & conflict.n.01 & 0.166666666667 \\ \hline
toilet.n.04 & trade.n.02 & 0.142857142857 \\ \hline
money.n.01 & mass.n.01 & 0.142857142857 \\ \hline
capitalism.n.01 & organization.n.01 & 0.142857142857 \\ \hline
hair.n.01 & working.n.01 & 0.125 \\ \hline
television receiver.n.01 & working.n.01 & 0.111111111111 \\ \hline
car.n.01 & working.n.01 & 0.111111111111 \\ \hline
philosophy.n.02 & political orientation.n.01 & 0.111111111111 \\ \hline
materialism.n.02 & political orientation.n.01 & 0.111111111111 \\ \hline
strategy.n.02 & political orientation.n.01 & 0.111111111111 \\ \hline
idealism.n.01 & political orientation.n.01 & 0.111111111111 \\ \hline
theory.n.01 & political orientation.n.01 & 0.111111111111 \\ \hline
sugar.n.01 & local anesthetic.n.01 & 0.0909090909091 \\ \hline
lion.n.01 & worker.n.01 & 0.0833333333333 \\ \hline
\multicolumn{3}{|c|}{Lenin: What Is To Be Done? - lch similarity} \\ \hline
imperialism.n.02 & political orientation.n.01 & 2.94443897917 \\ \hline
proletarian.n.01 & worker.n.01 & 2.25129179861 \\ \hline
war.n.01 & conflict.n.01 & 2.25129179861 \\ \hline
practice.n.03 & conflict.n.01 & 2.02814824729 \\ \hline
revolution.n.01 & conflict.n.01 & 1.8458266905 \\ \hline
toilet.n.04 & trade.n.02 & 1.69167601067 \\ \hline
money.n.01 & mass.n.01 & 1.69167601067 \\ \hline
capitalism.n.01 & organization.n.01 & 1.69167601067 \\ \hline
hair.n.01 & working.n.01 & 1.55814461805 \\ \hline
television receiver.n.01 & working.n.01 & 1.44036158239 \\ \hline
car.n.01 & working.n.01 & 1.44036158239 \\ \hline
philosophy.n.02 & political orientation.n.01 & 1.44036158239 \\ \hline
materialism.n.02 & political orientation.n.01 & 1.44036158239 \\ \hline
strategy.n.02 & political orientation.n.01 & 1.44036158239 \\ \hline
idealism.n.01 & political orientation.n.01 & 1.44036158239 \\ \hline
theory.n.01 & political orientation.n.01 & 1.44036158239 \\ \hline
sugar.n.01 & local anesthetic.n.01 & 1.23969088693 \\ \hline
lion.n.01 & worker.n.01 & 1.15267950994 \\ \hline
\multicolumn{3}{|c|}{Lenin: What Is To Be Done? - res similarity} \\ \hline
imperialism.n.02 & political orientation.n.01 & 8.60196873746 \\ \hline
sugar.n.01 & local anesthetic.n.01 & 4.61519673162 \\ \hline
war.n.01 & conflict.n.01 & 4.52385364841 \\ \hline
television receiver.n.01 & newspaper.n.01 & 3.25767902589 \\ \hline
car.n.01 & newspaper.n.01 & 3.25767902589 \\ \hline
toilet.n.04 & trade.n.02 & 3.14352023311 \\ \hline
capitalism.n.01 & organization.n.01 & 2.85529368615 \\ \hline
money.n.01 & mass.n.01 & 2.69110280536 \\ \hline
philosophy.n.02 & political orientation.n.01 & 2.64452085446 \\ \hline
materialism.n.02 & political orientation.n.01 & 2.64452085446 \\ \hline
strategy.n.02 & political orientation.n.01 & 2.64452085446 \\ \hline
idealism.n.01 & political orientation.n.01 & 2.64452085446 \\ \hline
theory.n.01 & political orientation.n.01 & 2.64452085446 \\ \hline
proletarian.n.01 & worker.n.01 & 2.33354524374 \\ \hline
practice.n.03 & trade.n.02 & 2.33223775508 \\ \hline
lion.n.01 & worker.n.01 & 2.22415047123 \\ \hline
revolution.n.01 & trade.n.02 & 2.03632771779 \\ \hline
hair.n.01 & worker.n.01 & 1.53183374322 \\ \hline
\multicolumn{3}{|c|}{Lenin: What Is To Be Done? - jcn similarity} \\ \hline
imperialism.n.02 & political orientation.n.01 & 0.193405491818 \\ \hline
war.n.01 & conflict.n.01 & 0.152829762599 \\ \hline
car.n.01 & worker.n.01 & 0.110550521246 \\ \hline
hair.n.01 & worker.n.01 & 0.107698235698 \\ \hline
proletarian.n.01 & worker.n.01 & 0.104758893715 \\ \hline
capitalism.n.01 & organization.n.01 & 0.101121795595 \\ \hline
sugar.n.01 & local anesthetic.n.01 & 0.0929714058017 \\ \hline
money.n.01 & organization.n.01 & 0.0929667353193 \\ \hline
philosophy.n.02 & organization.n.01 & 0.0908595602215 \\ \hline
lion.n.01 & worker.n.01 & 0.0900802228812 \\ \hline
practice.n.03 & motion.n.03 & 0.0882827134582 \\ \hline
television receiver.n.01 & worker.n.01 & 0.0873062903722 \\ \hline
theory.n.01 & organization.n.01 & 0.0828237113739 \\ \hline
revolution.n.01 & motion.n.03 & 0.0784056470694 \\ \hline
toilet.n.04 & motion.n.03 & 0.0745896410117 \\ \hline
strategy.n.02 & organization.n.01 & 0.0709786674118 \\ \hline
materialism.n.02 & organization.n.01 & 0.0656431911358 \\ \hline
idealism.n.01 & organization.n.01 & 0.0621845289629 \\ \hline
\multicolumn{3}{|c|}{Lenin: What Is To Be Done? - lin similarity} \\ \hline
imperialism.n.02 & political orientation.n.01 & 0.768910941363 \\ \hline
war.n.01 & conflict.n.01 & 0.580318438615 \\ \hline
sugar.n.01 & local anesthetic.n.01 & 0.461833980698 \\ \hline
car.n.01 & newspaper.n.01 & 0.411156952767 \\ \hline
capitalism.n.01 & organization.n.01 & 0.366071452787 \\ \hline
television receiver.n.01 & newspaper.n.01 & 0.356914166707 \\ \hline
money.n.01 & mass.n.01 & 0.331362497131 \\ \hline
proletarian.n.01 & worker.n.01 & 0.328371898491 \\ \hline
philosophy.n.02 & political orientation.n.01 & 0.31307622756 \\ \hline
toilet.n.04 & trade.n.02 & 0.312879932381 \\ \hline
theory.n.01 & political orientation.n.01 & 0.294463460062 \\ \hline
practice.n.03 & motion.n.03 & 0.291680639247 \\ \hline
lion.n.01 & worker.n.01 & 0.286073258452 \\ \hline
strategy.n.02 & political orientation.n.01 & 0.264762834975 \\ \hline
materialism.n.02 & political orientation.n.01 & 0.25040844726 \\ \hline
hair.n.01 & worker.n.01 & 0.248092928538 \\ \hline
revolution.n.01 & motion.n.03 & 0.242033306584 \\ \hline
idealism.n.01 & political orientation.n.01 & 0.240750703939 \\ \hline
\end{tabular}
\end{center}

### 2014-02-28 paper/analysis_the_state_and_revolution.tex
add tex extension to analysis tables. add analysis tables also

    \begin{center}
      \begin{tabular}{ | l | l | l |}
        \hline
        Choosen Sensens & Closest Top Sense & similarity  \\ \hline
\multicolumn{3}{|c|}{The State and Revolution - path similarity} \\ \hline
revolution.n.01 & revolution.n.01 & 1.0 \\ \hline
imperialism.n.02 & communism.n.02 & 0.333333333333 \\ \hline
proletarian.n.01 & peer.n.01 & 0.25 \\ \hline
practice.n.03 & work.n.01 & 0.2 \\ \hline
toilet.n.04 & work.n.01 & 0.166666666667 \\ \hline
war.n.01 & work.n.01 & 0.166666666667 \\ \hline
money.n.01 & phase.n.01 & 0.125 \\ \hline
philosophy.n.02 & law.n.04 & 0.125 \\ \hline
materialism.n.02 & law.n.04 & 0.125 \\ \hline
strategy.n.02 & law.n.04 & 0.125 \\ \hline
idealism.n.01 & law.n.04 & 0.125 \\ \hline
capitalism.n.01 & democracy.n.02 & 0.125 \\ \hline
hair.n.01 & peer.n.01 & 0.111111111111 \\ \hline
theory.n.01 & experience.n.03 & 0.1 \\ \hline
television receiver.n.01 & peer.n.01 & 0.0833333333333 \\ \hline
car.n.01 & peer.n.01 & 0.0833333333333 \\ \hline
lion.n.01 & peer.n.01 & 0.0833333333333 \\ \hline
sugar.n.01 & peer.n.01 & 0.0833333333333 \\ \hline
\multicolumn{3}{|c|}{The State and Revolution - lch similarity} \\ \hline
revolution.n.01 & revolution.n.01 & 3.63758615973 \\ \hline
imperialism.n.02 & communism.n.02 & 2.53897387106 \\ \hline
proletarian.n.01 & peer.n.01 & 2.25129179861 \\ \hline
practice.n.03 & work.n.01 & 2.02814824729 \\ \hline
toilet.n.04 & work.n.01 & 1.8458266905 \\ \hline
war.n.01 & work.n.01 & 1.8458266905 \\ \hline
money.n.01 & phase.n.01 & 1.55814461805 \\ \hline
philosophy.n.02 & law.n.04 & 1.55814461805 \\ \hline
materialism.n.02 & law.n.04 & 1.55814461805 \\ \hline
strategy.n.02 & law.n.04 & 1.55814461805 \\ \hline
idealism.n.01 & law.n.04 & 1.55814461805 \\ \hline
capitalism.n.01 & democracy.n.02 & 1.55814461805 \\ \hline
hair.n.01 & peer.n.01 & 1.44036158239 \\ \hline
theory.n.01 & experience.n.03 & 1.33500106673 \\ \hline
television receiver.n.01 & peer.n.01 & 1.15267950994 \\ \hline
car.n.01 & peer.n.01 & 1.15267950994 \\ \hline
lion.n.01 & peer.n.01 & 1.15267950994 \\ \hline
sugar.n.01 & peer.n.01 & 1.15267950994 \\ \hline
\multicolumn{3}{|c|}{The State and Revolution - res similarity} \\ \hline
revolution.n.01 & revolution.n.01 & 10.3880624692 \\ \hline
imperialism.n.02 & communism.n.02 & 8.60196873746 \\ \hline
philosophy.n.02 & law.n.04 & 3.29228159341 \\ \hline
materialism.n.02 & law.n.04 & 3.29228159341 \\ \hline
strategy.n.02 & law.n.04 & 3.29228159341 \\ \hline
idealism.n.01 & law.n.04 & 3.29228159341 \\ \hline
toilet.n.04 & work.n.01 & 3.14352023311 \\ \hline
capitalism.n.01 & club.n.02 & 2.85529368615 \\ \hline
money.n.01 & phase.n.01 & 2.69110280536 \\ \hline
theory.n.01 & law.n.04 & 2.64452085446 \\ \hline
proletarian.n.01 & engels.n.01 & 2.33354524374 \\ \hline
war.n.01 & work.n.01 & 2.33223775508 \\ \hline
practice.n.03 & work.n.01 & 2.33223775508 \\ \hline
lion.n.01 & engels.n.01 & 2.22415047123 \\ \hline
television receiver.n.01 & engels.n.01 & 1.53183374322 \\ \hline
car.n.01 & engels.n.01 & 1.53183374322 \\ \hline
hair.n.01 & engels.n.01 & 1.53183374322 \\ \hline
sugar.n.01 & engels.n.01 & 0.801759114954 \\ \hline
\multicolumn{3}{|c|}{The State and Revolution - jcn similarity} \\ \hline
revolution.n.01 & revolution.n.01 & 1e+300 \\ \hline
imperialism.n.02 & communism.n.02 & 0.14975874591 \\ \hline
war.n.01 & work.n.01 & 0.119881984187 \\ \hline
philosophy.n.02 & law.n.04 & 0.103411969458 \\ \hline
practice.n.03 & work.n.01 & 0.103154641506 \\ \hline
toilet.n.04 & work.n.01 & 0.0985118809398 \\ \hline
money.n.01 & phase.n.01 & 0.0916158054473 \\ \hline
theory.n.01 & work.n.01 & 0.0910758552239 \\ \hline
car.n.01 & peer.n.01 & 0.0887294617483 \\ \hline
hair.n.01 & peer.n.01 & 0.0868826421077 \\ \hline
proletarian.n.01 & peer.n.01 & 0.0849595683478 \\ \hline
strategy.n.02 & law.n.04 & 0.07841412673 \\ \hline
lion.n.01 & peer.n.01 & 0.0750424463326 \\ \hline
television receiver.n.01 & peer.n.01 & 0.0731074093034 \\ \hline
capitalism.n.01 & club.n.02 & 0.0729022081709 \\ \hline
materialism.n.02 & law.n.04 & 0.0719531280061 \\ \hline
idealism.n.01 & law.n.04 & 0.0678185221973 \\ \hline
sugar.n.01 & work.n.01 & 0.0625959407953 \\ \hline
\multicolumn{3}{|c|}{The State and Revolution - lin similarity} \\ \hline
revolution.n.01 & revolution.n.01 & 1.0 \\ \hline
imperialism.n.02 & communism.n.02 & 0.720392353354 \\ \hline
philosophy.n.02 & law.n.04 & 0.405088626962 \\ \hline
toilet.n.04 & work.n.01 & 0.382467580972 \\ \hline
war.n.01 & work.n.01 & 0.35863993877 \\ \hline
strategy.n.02 & law.n.04 & 0.340509805473 \\ \hline
money.n.01 & phase.n.01 & 0.330250297796 \\ \hline
practice.n.03 & work.n.01 & 0.324854541172 \\ \hline
materialism.n.02 & law.n.04 & 0.321472637881 \\ \hline
idealism.n.01 & law.n.04 & 0.308702564543 \\ \hline
theory.n.01 & law.n.04 & 0.305328480717 \\ \hline
capitalism.n.01 & club.n.02 & 0.29394209418 \\ \hline
proletarian.n.01 & peer.n.01 & 0.28393127113 \\ \hline
lion.n.01 & peer.n.01 & 0.250268807542 \\ \hline
car.n.01 & peer.n.01 & 0.213736072979 \\ \hline
hair.n.01 & peer.n.01 & 0.210222579299 \\ \hline
television receiver.n.01 & peer.n.01 & 0.182991045418 \\ \hline
sugar.n.01 & peer.n.01 & 0.0895207954547 \\ \hline
\end{tabular}
\end{center}

### 2014-02-28 commands/top_senses_tables.py

@@ -93,7 +93,7 @@ def create_analysis_tables():
                                                     analyzer.best_word_for[synset].name))
 
         doc_name = doc.name.replace(' ', '_').replace(':', '').replace(',', '').lower()[:30]
-        with open('paper/analysis_%s' % (doc_name), 'w') as analysis_output:
+        with open('paper/analysis_%s.tex' % (doc_name), 'w') as analysis_output:
             analysis_output.write("""
     \\begin{center}
       \\begin{tabular}{ | l | l | l |}

### 2014-02-28 cccp.py
add support for fetching url from internet (cccp.py --wget url). latex-info supports optional parameter documents now.

@@ -4,10 +4,13 @@ import sys
 import config
 import argparse
 import subprocess
+
+import ming
+
 from commands.database import reset_senses
 from commands.year_analysis import calculate_year_analysis
 from commands.top_senses_tables import create_tables
-import ming
+from commands.wget import wget
 
 reload(config)
 
@@ -68,6 +71,8 @@ def main():
     parser.add_argument('--analyze-documents', action='store_true', default=False, help="Do Document Analysis for given concepts (pass with --concepts)")
     parser.add_argument('--reset-senses', action='store_true', default=False, help="Reset all senses calculated")
     parser.add_argument('--latex-info', action='store_true', default=False, help="Creates LaTex information for paper")
+    parser.add_argument('--wget', metavar=('url'), help="Fetches the url and creates a Document")
+
     if len(sys.argv) == 1:
         parser.print_help()
         sys.exit(1)
@@ -145,7 +150,9 @@ def main():
     if args.reset_senses:
         reset_senses()
     if args.latex_info:
-        create_tables()
+        create_tables(doc_list)
+    if args.wget:
+        wget(args.wget)
 
     if args.set_number_of_tokens:
         set_number_of_tokens()

### 2014-02-28 commands/top_senses_tables.py

@@ -30,7 +30,7 @@ synsets = [wn.synset(word) for word in [
            "car.n.01"]]
 
 
-def document_list():
+def default_document_list():
     state_and_revolution = Document.query.find({"name": {"$regex": "State and Revolution"}}).next()
     imperialism_capitalism = Document.query.find({"name": {"$regex": "Imperialism.*Capitalism.*"}}).next()
     materialism_criticism = Document.query.find({"name": "Lenin: MATERIALISM and EMPIRIO-CRITICISM"}).next()
@@ -39,8 +39,11 @@ def document_list():
     return [state_and_revolution, imperialism_capitalism, materialism_criticism, what_is_to_be_done, agrarian_programme]
 
 
-def create_top_sense_tables():
-    documents = document_list()
+def create_top_sense_tables(doc_list):
+    documents = doc_list
+    if documents is None:
+        documents = default_document_list()
+
     log.info("Top words")
     log.info("=" * 80)
     for document in documents:
@@ -70,11 +73,13 @@ def create_top_sense_tables():
             tex_table.write("""\end{tabular}\n\end{center}""")
 
 
-def create_analysis_tables():
+def create_analysis_tables(doc_list):
+
+    documents = doc_list
+    if documents is None:
+        documents = default_document_list()
 
     analyzers = [DocumentAnalyzer(synsets=synsets, similarity_function=sim_fun) for sim_fun in SIMILARITY_FUNCS]
-
-    documents = document_list()
 
     for doc in documents:
         full_analysis = {}
@@ -106,6 +111,6 @@ def create_analysis_tables():
             analysis_output.write("""\end{tabular}\n\end{center}""")
 
 
-def create_tables():
-    create_top_sense_tables()
-    create_analysis_tables()
+def create_tables(doc_list):
+    create_top_sense_tables(doc_list)
+    create_analysis_tables(doc_list)

### 2014-02-28 commands/wget.py

@@ -1,0 +1,18 @@
+import logging
+import requests
+
+from information_value.models import Document
+from information_value.models import odm_session
+
+log = logging.getLogger('lenin')
+
+
+def wget(url):
+    log.info('Trying to fetch url: %s' % url)
+    response = requests.get(url)
+    Document(
+                url=url,
+                name=url,
+                text=response.text,
+    )
+    odm_session.flush()

### 2014-02-28 commands/top_senses_tables.py
add clean filename method

@@ -38,6 +38,9 @@ def default_document_list():
     agrarian_programme = Document.query.find({"name": u'Lenin: The Agrarian Programme of Social-Democracy in the First Russian Revolution, 1905-1907'}).next()
     return [state_and_revolution, imperialism_capitalism, materialism_criticism, what_is_to_be_done, agrarian_programme]
 
+def clean_name(name):
+    name.replace(' ', '_').replace(':', '').replace(',', '').replace('.','_').replace('/','_').lower()
+    return name
 
 def create_top_sense_tables(doc_list):
     documents = doc_list
@@ -55,7 +58,7 @@ def create_top_sense_tables(doc_list):
         except AttributeError:
             log.exception("No top words found. Trying to calculate them.")
 
-        with open("paper/top_senses_%s.tex" % document.name.replace(' ', '_').replace(':', '').replace(',', '').lower(), "w") as tex_table:
+        with open("paper/top_senses_%s.tex" % clean_name(document.name), "w") as tex_table:
             tex_table.write("""
     \\begin{center}
       \\begin{tabular}{ | l | l | }
@@ -98,7 +101,7 @@ def create_analysis_tables(doc_list):
                                                     analyzer.best_word_for[synset].name))
 
         doc_name = doc.name.replace(' ', '_').replace(':', '').replace(',', '').lower()[:30]
-        with open('paper/analysis_%s.tex' % (doc_name), 'w') as analysis_output:
+        with open('paper/analysis_%s.tex' % (clean_name(doc_name)), 'w') as analysis_output:
             analysis_output.write("""
     \\begin{center}
       \\begin{tabular}{ | l | l | l |}

### 2014-03-01 paper/analysis_lenin_imperialism_the_highest_.tex
add graph that compares each sense against each other. add definition to top senses tables

@@
     \begin{center}
-      \begin{tabular}{ | l | l | l |}
+      \begin{tabular}{ | l | l | l | l |}
         \hline
-        Choosen Sensens & Closest Top Sense & similarity  \\ \hline
-\multicolumn{3}{|c|}{Lenin: Imperialism, the Highes - path similarity} \\ \hline
-capitalism.n.01 & capitalism.n.01 & 1.0 \\ \hline
-proletarian.n.01 & great.n.01 & 0.2 \\ \hline
-hair.n.01 & universe.n.01 & 0.2 \\ \hline
-money.n.01 & penny.n.02 & 0.166666666667 \\ \hline
-practice.n.03 & monopoly.n.01 & 0.166666666667 \\ \hline
-toilet.n.04 & monopoly.n.01 & 0.142857142857 \\ \hline
-war.n.01 & monopoly.n.01 & 0.142857142857 \\ \hline
-revolution.n.01 & monopoly.n.01 & 0.125 \\ \hline
-theory.n.01 & imperialism.n.01 & 0.125 \\ \hline
-television receiver.n.01 & product.n.02 & 0.111111111111 \\ \hline
-car.n.01 & product.n.02 & 0.111111111111 \\ \hline
-philosophy.n.02 & policy.n.01 & 0.111111111111 \\ \hline
-materialism.n.02 & policy.n.01 & 0.111111111111 \\ \hline
-strategy.n.02 & policy.n.01 & 0.111111111111 \\ \hline
-idealism.n.01 & policy.n.01 & 0.111111111111 \\ \hline
-imperialism.n.02 & policy.n.01 & 0.1 \\ \hline
-lion.n.01 & great.n.01 & 0.0769230769231 \\ \hline
-sugar.n.01 & universe.n.01 & 0.0769230769231 \\ \hline
-\multicolumn{3}{|c|}{Lenin: Imperialism, the Highes - lch similarity} \\ \hline
-capitalism.n.01 & capitalism.n.01 & 3.63758615973 \\ \hline
-proletarian.n.01 & great.n.01 & 2.02814824729 \\ \hline
-hair.n.01 & universe.n.01 & 2.02814824729 \\ \hline
-money.n.01 & penny.n.02 & 1.8458266905 \\ \hline
-practice.n.03 & monopoly.n.01 & 1.8458266905 \\ \hline
-toilet.n.04 & monopoly.n.01 & 1.69167601067 \\ \hline
-war.n.01 & monopoly.n.01 & 1.69167601067 \\ \hline
-revolution.n.01 & monopoly.n.01 & 1.55814461805 \\ \hline
-theory.n.01 & imperialism.n.01 & 1.55814461805 \\ \hline
-television receiver.n.01 & product.n.02 & 1.44036158239 \\ \hline
-car.n.01 & product.n.02 & 1.44036158239 \\ \hline
-philosophy.n.02 & policy.n.01 & 1.44036158239 \\ \hline
-materialism.n.02 & policy.n.01 & 1.44036158239 \\ \hline
-strategy.n.02 & policy.n.01 & 1.44036158239 \\ \hline
-idealism.n.01 & policy.n.01 & 1.44036158239 \\ \hline
-imperialism.n.02 & policy.n.01 & 1.33500106673 \\ \hline
-lion.n.01 & great.n.01 & 1.07263680226 \\ \hline
-sugar.n.01 & universe.n.01 & 1.07263680226 \\ \hline
-\multicolumn{3}{|c|}{Lenin: Imperialism, the Highes - res similarity} \\ \hline
-capitalism.n.01 & capitalism.n.01 & 11.6930111908 \\ \hline
-money.n.01 & penny.n.02 & 6.2549318819 \\ \hline
-theory.n.01 & imperialism.n.01 & 5.678990458 \\ \hline
-hair.n.01 & universe.n.01 & 4.94037581121 \\ \hline
-philosophy.n.02 & policy.n.01 & 3.29228159341 \\ \hline
-materialism.n.02 & policy.n.01 & 3.29228159341 \\ \hline
-strategy.n.02 & policy.n.01 & 3.29228159341 \\ \hline
-idealism.n.01 & policy.n.01 & 3.29228159341 \\ \hline
-toilet.n.04 & monopoly.n.01 & 3.14352023311 \\ \hline
-imperialism.n.02 & imperialism.n.01 & 2.64452085446 \\ \hline
-proletarian.n.01 & great.n.01 & 2.33354524374 \\ \hline
-war.n.01 & monopoly.n.01 & 2.33223775508 \\ \hline
-practice.n.03 & monopoly.n.01 & 2.33223775508 \\ \hline
-television receiver.n.01 & product.n.02 & 2.30584873145 \\ \hline
-car.n.01 & product.n.02 & 2.30584873145 \\ \hline
-lion.n.01 & great.n.01 & 2.22415047123 \\ \hline
-revolution.n.01 & monopoly.n.01 & 2.03632771779 \\ \hline
-sugar.n.01 & universe.n.01 & 0.801759114954 \\ \hline
-\multicolumn{3}{|c|}{Lenin: Imperialism, the Highes - jcn similarity} \\ \hline
-capitalism.n.01 & capitalism.n.01 & 1e+300 \\ \hline
-money.n.01 & penny.n.02 & 0.220543285308 \\ \hline
-hair.n.01 & universe.n.01 & 0.185089245333 \\ \hline
-car.n.01 & product.n.02 & 0.118562212358 \\ \hline
-philosophy.n.02 & policy.n.01 & 0.0941972384174 \\ \hline
-television receiver.n.01 & product.n.02 & 0.0922281130906 \\ \hline
-theory.n.01 & imperialism.n.01 & 0.0849319922588 \\ \hline
-proletarian.n.01 & product.n.02 & 0.0827408100653 \\ \hline
-war.n.01 & monopoly.n.01 & 0.0769380100151 \\ \hline
-lion.n.01 & product.n.02 & 0.0745010379336 \\ \hline
-strategy.n.02 & policy.n.01 & 0.0729992753311 \\ \hline
-practice.n.03 & monopoly.n.01 & 0.0696858132394 \\ \hline
-toilet.n.04 & monopoly.n.01 & 0.0675356263653 \\ \hline
-materialism.n.02 & policy.n.01 & 0.0673677474158 \\ \hline
-sugar.n.01 & product.n.02 & 0.0665737679313 \\ \hline
-revolution.n.01 & one.n.01 & 0.0654799767733 \\ \hline
-idealism.n.01 & policy.n.01 & 0.063730003856 \\ \hline
-imperialism.n.02 & policy.n.01 & 0.0574970955164 \\ \hline
-\multicolumn{3}{|c|}{Lenin: Imperialism, the Highes - lin similarity} \\ \hline
-capitalism.n.01 & capitalism.n.01 & 1.0 \\ \hline
-money.n.01 & penny.n.02 & 0.733969426851 \\ \hline
-hair.n.01 & universe.n.01 & 0.646495819603 \\ \hline
-theory.n.01 & imperialism.n.01 & 0.491005027416 \\ \hline
-philosophy.n.02 & policy.n.01 & 0.382810406388 \\ \hline
-car.n.01 & product.n.02 & 0.353492745777 \\ \hline
-strategy.n.02 & policy.n.01 & 0.324629309412 \\ \hline
-materialism.n.02 & policy.n.01 & 0.307281190083 \\ \hline
-television receiver.n.01 & product.n.02 & 0.298407179857 \\ \hline
-toilet.n.04 & monopoly.n.01 & 0.298048188669 \\ \hline
-idealism.n.01 & policy.n.01 & 0.295593207225 \\ \hline
-war.n.01 & monopoly.n.01 & 0.264097390196 \\ \hline
-proletarian.n.01 & great.n.01 & 0.262634686841 \\ \hline
-practice.n.03 & monopoly.n.01 & 0.245310227149 \\ \hline
-imperialism.n.02 & policy.n.01 & 0.233190306342 \\ \hline
-lion.n.01 & great.n.01 & 0.232810355981 \\ \hline
-revolution.n.01 & monopoly.n.01 & 0.205174493173 \\ \hline
-sugar.n.01 & product.n.02 & 0.0964554176079 \\ \hline
+        Choosen Sensens & Closest Top Sense & similarity & Top Sense Gloss \\ \hline
+\multicolumn{4}{|c|}{Lenin: Imperialism, the Highes - path similarity} \\ \hline
+capitalism.n.01 & capitalism.n.01 & 1.0 & an economic system based on private ownership of capital\\ \hline
+proletarian.n.01 & great.n.01 & 0.2 & a person who has achieved distinction and honor in some field\\ \hline
+hair.n.01 & universe.n.01 & 0.2 & everything that exists anywhere\\ \hline
+money.n.01 & penny.n.02 & 0.166666666667 & a coin worth one-hundredth of the value of the basic unit\\ \hline
+practice.n.03 & monopoly.n.01 & 0.166666666667 & (economics) a market in which there are many buyers but only one seller\\ \hline
+toilet.n.04 & monopoly.n.01 & 0.142857142857 & (economics) a market in which there are many buyers but only one seller\\ \hline
+war.n.01 & monopoly.n.01 & 0.142857142857 & (economics) a market in which there are many buyers but only one seller\\ \hline
+revolution.n.01 & monopoly.n.01 & 0.125 & (economics) a market in which there are many buyers but only one seller\\ \hline
+theory.n.01 & imperialism.n.01 & 0.125 & a policy of extending your rule over foreign countries\\ \hline
+television receiver.n.01 & product.n.02 & 0.111111111111 & an artifact that has been created by someone or some process\\ \hline
+car.n.01 & product.n.02 & 0.111111111111 & an artifact that has been created by someone or some process\\ \hline
+philosophy.n.02 & policy.n.01 & 0.111111111111 & a plan of action adopted by an individual or social group\\ \hline
+materialism.n.02 & policy.n.01 & 0.111111111111 & a plan of action adopted by an individual or social group\\ \hline
+strategy.n.02 & policy.n.01 & 0.111111111111 & a plan of action adopted by an individual or social group\\ \hline
+idealism.n.01 & policy.n.01 & 0.111111111111 & a plan of action adopted by an individual or social group\\ \hline
+imperialism.n.02 & policy.n.01 & 0.1 & a plan of action adopted by an individual or social group\\ \hline
+lion.n.01 & great.n.01 & 0.0769230769231 & a person who has achieved distinction and honor in some field\\ \hline
+sugar.n.01 & universe.n.01 & 0.0769230769231 & everything that exists anywhere\\ \hline
+\multicolumn{4}{|c|}{Lenin: Imperialism, the Highes - lch similarity} \\ \hline
+capitalism.n.01 & capitalism.n.01 & 3.63758615973 & an economic system based on private ownership of capital\\ \hline
+proletarian.n.01 & great.n.01 & 2.02814824729 & a person who has achieved distinction and honor in some field\\ \hline
+hair.n.01 & universe.n.01 & 2.02814824729 & everything that exists anywhere\\ \hline
+money.n.01 & penny.n.02 & 1.8458266905 & a coin worth one-hundredth of the value of the basic unit\\ \hline
+practice.n.03 & monopoly.n.01 & 1.8458266905 & (economics) a market in which there are many buyers but only one seller\\ \hline
+toilet.n.04 & monopoly.n.01 & 1.69167601067 & (economics) a market in which there are many buyers but only one seller\\ \hline
+war.n.01 & monopoly.n.01 & 1.69167601067 & (economics) a market in which there are many buyers but only one seller\\ \hline
+revolution.n.01 & monopoly.n.01 & 1.55814461805 & (economics) a market in which there are many buyers but only one seller\\ \hline
+theory.n.01 & imperialism.n.01 & 1.55814461805 & a policy of extending your rule over foreign countries\\ \hline
+television receiver.n.01 & product.n.02 & 1.44036158239 & an artifact that has been created by someone or some process\\ \hline
+car.n.01 & product.n.02 & 1.44036158239 & an artifact that has been created by someone or some process\\ \hline
+philosophy.n.02 & policy.n.01 & 1.44036158239 & a plan of action adopted by an individual or social group\\ \hline
+materialism.n.02 & policy.n.01 & 1.44036158239 & a plan of action adopted by an individual or social group\\ \hline
+strategy.n.02 & policy.n.01 & 1.44036158239 & a plan of action adopted by an individual or social group\\ \hline
+idealism.n.01 & policy.n.01 & 1.44036158239 & a plan of action adopted by an individual or social group\\ \hline
+imperialism.n.02 & policy.n.01 & 1.33500106673 & a plan of action adopted by an individual or social group\\ \hline
+lion.n.01 & great.n.01 & 1.07263680226 & a person who has achieved distinction and honor in some field\\ \hline
+sugar.n.01 & universe.n.01 & 1.07263680226 & everything that exists anywhere\\ \hline
+\multicolumn{4}{|c|}{Lenin: Imperialism, the Highes - res similarity} \\ \hline
+capitalism.n.01 & capitalism.n.01 & 11.6930111908 & an economic system based on private ownership of capital\\ \hline
+money.n.01 & penny.n.02 & 6.2549318819 & a coin worth one-hundredth of the value of the basic unit\\ \hline
+theory.n.01 & imperialism.n.01 & 5.678990458 & a policy of extending your rule over foreign countries\\ \hline
+hair.n.01 & universe.n.01 & 4.94037581121 & everything that exists anywhere\\ \hline
+philosophy.n.02 & policy.n.01 & 3.29228159341 & a plan of action adopted by an individual or social group\\ \hline
+materialism.n.02 & policy.n.01 & 3.29228159341 & a plan of action adopted by an individual or social group\\ \hline
+strategy.n.02 & policy.n.01 & 3.29228159341 & a plan of action adopted by an individual or social group\\ \hline
+idealism.n.01 & policy.n.01 & 3.29228159341 & a plan of action adopted by an individual or social group\\ \hline
+toilet.n.04 & monopoly.n.01 & 3.14352023311 & (economics) a market in which there are many buyers but only one seller\\ \hline
+imperialism.n.02 & imperialism.n.01 & 2.64452085446 & a policy of extending your rule over foreign countries\\ \hline
+proletarian.n.01 & great.n.01 & 2.33354524374 & a person who has achieved distinction and honor in some field\\ \hline
+war.n.01 & monopoly.n.01 & 2.33223775508 & (economics) a market in which there are many buyers but only one seller\\ \hline
+practice.n.03 & monopoly.n.01 & 2.33223775508 & (economics) a market in which there are many buyers but only one seller\\ \hline
+television receiver.n.01 & product.n.02 & 2.30584873145 & an artifact that has been created by someone or some process\\ \hline
+car.n.01 & product.n.02 & 2.30584873145 & an artifact that has been created by someone or some process\\ \hline
+lion.n.01 & great.n.01 & 2.22415047123 & a person who has achieved distinction and honor in some field\\ \hline
+revolution.n.01 & monopoly.n.01 & 2.03632771779 & (economics) a market in which there are many buyers but only one seller\\ \hline
+sugar.n.01 & universe.n.01 & 0.801759114954 & everything that exists anywhere\\ \hline
+\multicolumn{4}{|c|}{Lenin: Imperialism, the Highes - jcn similarity} \\ \hline
+capitalism.n.01 & capitalism.n.01 & 1e+300 & an economic system based on private ownership of capital\\ \hline
+money.n.01 & penny.n.02 & 0.220543285308 & a coin worth one-hundredth of the value of the basic unit\\ \hline
+hair.n.01 & universe.n.01 & 0.185089245333 & everything that exists anywhere\\ \hline
+car.n.01 & product.n.02 & 0.118562212358 & an artifact that has been created by someone or some process\\ \hline
+philosophy.n.02 & policy.n.01 & 0.0941972384174 & a plan of action adopted by an individual or social group\\ \hline
+television receiver.n.01 & product.n.02 & 0.0922281130906 & an artifact that has been created by someone or some process\\ \hline
+theory.n.01 & imperialism.n.01 & 0.0849319922588 & a policy of extending your rule over foreign countries\\ \hline
+proletarian.n.01 & product.n.02 & 0.0827408100653 & an artifact that has been created by someone or some process\\ \hline
+war.n.01 & monopoly.n.01 & 0.0769380100151 & (economics) a market in which there are many buyers but only one seller\\ \hline
+lion.n.01 & product.n.02 & 0.0745010379336 & an artifact that has been created by someone or some process\\ \hline
+strategy.n.02 & policy.n.01 & 0.0729992753311 & a plan of action adopted by an individual or social group\\ \hline
+practice.n.03 & monopoly.n.01 & 0.0696858132394 & (economics) a market in which there are many buyers but only one seller\\ \hline
+toilet.n.04 & monopoly.n.01 & 0.0675356263653 & (economics) a market in which there are many buyers but only one seller\\ \hline
+materialism.n.02 & policy.n.01 & 0.0673677474158 & a plan of action adopted by an individual or social group\\ \hline
+sugar.n.01 & product.n.02 & 0.0665737679313 & an artifact that has been created by someone or some process\\ \hline
+revolution.n.01 & one.n.01 & 0.0654799767733 & the smallest whole number or a numeral representing this number\\ \hline
+idealism.n.01 & policy.n.01 & 0.063730003856 & a plan of action adopted by an individual or social group\\ \hline
+imperialism.n.02 & policy.n.01 & 0.0574970955164 & a plan of action adopted by an individual or social group\\ \hline
+\multicolumn{4}{|c|}{Lenin: Imperialism, the Highes - lin similarity} \\ \hline
+capitalism.n.01 & capitalism.n.01 & 1.0 & an economic system based on private ownership of capital\\ \hline
+money.n.01 & penny.n.02 & 0.733969426851 & a coin worth one-hundredth of the value of the basic unit\\ \hline
+hair.n.01 & universe.n.01 & 0.646495819603 & everything that exists anywhere\\ \hline
+theory.n.01 & imperialism.n.01 & 0.491005027416 & a policy of extending your rule over foreign countries\\ \hline
+philosophy.n.02 & policy.n.01 & 0.382810406388 & a plan of action adopted by an individual or social group\\ \hline
+car.n.01 & product.n.02 & 0.353492745777 & an artifact that has been created by someone or some process\\ \hline
+strategy.n.02 & policy.n.01 & 0.324629309412 & a plan of action adopted by an individual or social group\\ \hline
+materialism.n.02 & policy.n.01 & 0.307281190083 & a plan of action adopted by an individual or social group\\ \hline
+television receiver.n.01 & product.n.02 & 0.298407179857 & an artifact that has been created by someone or some process\\ \hline
+toilet.n.04 & monopoly.n.01 & 0.298048188669 & (economics) a market in which there are many buyers but only one seller\\ \hline
+idealism.n.01 & policy.n.01 & 0.295593207225 & a plan of action adopted by an individual or social group\\ \hline
+war.n.01 & monopoly.n.01 & 0.264097390196 & (economics) a market in which there are many buyers but only one seller\\ \hline
+proletarian.n.01 & great.n.01 & 0.262634686841 & a person who has achieved distinction and honor in some field\\ \hline
+practice.n.03 & monopoly.n.01 & 0.245310227149 & (economics) a market in which there are many buyers but only one seller\\ \hline
+imperialism.n.02 & policy.n.01 & 0.233190306342 & a plan of action adopted by an individual or social group\\ \hline
+lion.n.01 & great.n.01 & 0.232810355981 & a person who has achieved distinction and honor in some field\\ \hline
+revolution.n.01 & monopoly.n.01 & 0.205174493173 & (economics) a market in which there are many buyers but only one seller\\ \hline
+sugar.n.01 & product.n.02 & 0.0964554176079 & an artifact that has been created by someone or some process\\ \hline
 \end{tabular}

### 2014-03-01 paper/analysis_lenin_materialism_and_empirio-.tex
add graph that compares each sense against each other. add definition to top senses tables

@@
     \begin{center}
-      \begin{tabular}{ | l | l | l |}
+      \begin{tabular}{ | l | l | l | l |}
         \hline
-        Choosen Sensens & Closest Top Sense & similarity  \\ \hline
-\multicolumn{3}{|c|}{Lenin: MATERIALISM and EMPIRIO - path similarity} \\ \hline
-revolution.n.01 & experience.n.03 & 0.25 \\ \hline
-proletarian.n.01 & matter.n.03 & 0.166666666667 \\ \hline
-philosophy.n.02 & physics.n.01 & 0.166666666667 \\ \hline
-war.n.01 & experience.n.03 & 0.166666666667 \\ \hline
-strategy.n.02 & physics.n.01 & 0.166666666667 \\ \hline
-practice.n.03 & experience.n.03 & 0.166666666667 \\ \hline
-money.n.01 & beginning.n.02 & 0.142857142857 \\ \hline
-materialism.n.02 & aim.n.02 & 0.142857142857 \\ \hline
-idealism.n.01 & aim.n.02 & 0.142857142857 \\ \hline
-imperialism.n.02 & aim.n.02 & 0.125 \\ \hline
-sugar.n.01 & matter.n.03 & 0.125 \\ \hline
-theory.n.01 & sensation.n.01 & 0.125 \\ \hline
-hair.n.01 & space.n.02 & 0.125 \\ \hline
-capitalism.n.01 & time.n.05 & 0.125 \\ \hline
-toilet.n.04 & experience.n.03 & 0.111111111111 \\ \hline
-television receiver.n.01 & space.n.02 & 0.0909090909091 \\ \hline
-car.n.01 & space.n.02 & 0.0909090909091 \\ \hline
-lion.n.01 & kant.n.01 & 0.0666666666667 \\ \hline
-\multicolumn{3}{|c|}{Lenin: MATERIALISM and EMPIRIO - lch similarity} \\ \hline
-revolution.n.01 & experience.n.03 & 2.25129179861 \\ \hline
-proletarian.n.01 & matter.n.03 & 1.8458266905 \\ \hline
-philosophy.n.02 & physics.n.01 & 1.8458266905 \\ \hline
-war.n.01 & experience.n.03 & 1.8458266905 \\ \hline
-strategy.n.02 & physics.n.01 & 1.8458266905 \\ \hline
-practice.n.03 & experience.n.03 & 1.8458266905 \\ \hline
-money.n.01 & beginning.n.02 & 1.69167601067 \\ \hline
-materialism.n.02 & aim.n.02 & 1.69167601067 \\ \hline
-idealism.n.01 & aim.n.02 & 1.69167601067 \\ \hline
-imperialism.n.02 & aim.n.02 & 1.55814461805 \\ \hline
-sugar.n.01 & matter.n.03 & 1.55814461805 \\ \hline
-theory.n.01 & sensation.n.01 & 1.55814461805 \\ \hline
-hair.n.01 & space.n.02 & 1.55814461805 \\ \hline
-capitalism.n.01 & time.n.05 & 1.55814461805 \\ \hline
-toilet.n.04 & experience.n.03 & 1.44036158239 \\ \hline
-television receiver.n.01 & space.n.02 & 1.23969088693 \\ \hline
-car.n.01 & space.n.02 & 1.23969088693 \\ \hline
-lion.n.01 & kant.n.01 & 0.929535958624 \\ \hline
-\multicolumn{3}{|c|}{Lenin: MATERIALISM and EMPIRIO - res similarity} \\ \hline
-philosophy.n.02 & physics.n.01 & 5.58877614988 \\ \hline
-strategy.n.02 & physics.n.01 & 5.58877614988 \\ \hline
-theory.n.01 & sensation.n.01 & 4.38484522248 \\ \hline
-revolution.n.01 & experience.n.03 & 4.05348916032 \\ \hline
-sugar.n.01 & matter.n.03 & 3.3367059068 \\ \hline
-materialism.n.02 & physics.n.01 & 3.29228159341 \\ \hline
-idealism.n.01 & physics.n.01 & 3.29228159341 \\ \hline
-capitalism.n.01 & sociable.n.01 & 2.85529368615 \\ \hline
-money.n.01 & beginning.n.02 & 2.69110280536 \\ \hline
-imperialism.n.02 & physics.n.01 & 2.64452085446 \\ \hline
-proletarian.n.01 & kant.n.01 & 2.33354524374 \\ \hline
-toilet.n.04 & motion.n.03 & 2.33223775508 \\ \hline
-war.n.01 & motion.n.03 & 2.33223775508 \\ \hline
-practice.n.03 & motion.n.03 & 2.33223775508 \\ \hline
-television receiver.n.01 & book.n.01 & 2.30584873145 \\ \hline
-car.n.01 & book.n.01 & 2.30584873145 \\ \hline
-lion.n.01 & kant.n.01 & 2.22415047123 \\ \hline
-hair.n.01 & kant.n.01 & 1.53183374322 \\ \hline
-\multicolumn{3}{|c|}{Lenin: MATERIALISM and EMPIRIO - jcn similarity} \\ \hline
-philosophy.n.02 & physics.n.01 & 0.145932703696 \\ \hline
-theory.n.01 & sensation.n.01 & 0.128286683846 \\ \hline
-sugar.n.01 & matter.n.03 & 0.127664075736 \\ \hline
-revolution.n.01 & experience.n.03 & 0.111569245855 \\ \hline
-money.n.01 & moment.n.01 & 0.107804699133 \\ \hline
-car.n.01 & matter.n.03 & 0.107243331568 \\ \hline
-hair.n.01 & matter.n.03 & 0.104557075904 \\ \hline
-strategy.n.02 & physics.n.01 & 0.100652051627 \\ \hline
-war.n.01 & motion.n.03 & 0.100254651557 \\ \hline
-practice.n.03 & motion.n.03 & 0.0882827134582 \\ \hline
-proletarian.n.01 & matter.n.03 & 0.0875035868175 \\ \hline
-television receiver.n.01 & matter.n.03 & 0.085230569567 \\ \hline
-lion.n.01 & matter.n.03 & 0.0783404338338 \\ \hline
-materialism.n.02 & aim.n.02 & 0.0778269817906 \\ \hline
-toilet.n.04 & motion.n.03 & 0.0745896410117 \\ \hline
-idealism.n.01 & aim.n.02 & 0.0730123547216 \\ \hline
-capitalism.n.01 & sociable.n.01 & 0.0678992095349 \\ \hline
-imperialism.n.02 & aim.n.02 & 0.0649464570442 \\ \hline
-\multicolumn{3}{|c|}{Lenin: MATERIALISM and EMPIRIO - lin similarity} \\ \hline
-philosophy.n.02 & physics.n.01 & 0.619941000616 \\ \hline
-strategy.n.02 & physics.n.01 & 0.529421413479 \\ \hline
-theory.n.01 & sensation.n.01 & 0.529419405948 \\ \hline
-revolution.n.01 & experience.n.03 & 0.474924895953 \\ \hline
-sugar.n.01 & matter.n.03 & 0.460030062094 \\ \hline
-money.n.01 & moment.n.01 & 0.367179548114 \\ \hline
-materialism.n.02 & aim.n.02 & 0.33882403792 \\ \hline
-idealism.n.01 & aim.n.02 & 0.324668589607 \\ \hline
-war.n.01 & motion.n.03 & 0.318631846502 \\ \hline
-car.n.01 & book.n.01 & 0.308668677605 \\ \hline
-practice.n.03 & motion.n.03 & 0.291680639247 \\ \hline
-capitalism.n.01 & sociable.n.01 & 0.27940619133 \\ \hline
-television receiver.n.01 & book.n.01 & 0.265820778874 \\ \hline
-toilet.n.04 & motion.n.03 & 0.258117063881 \\ \hline
-imperialism.n.02 & aim.n.02 & 0.255677978749 \\ \hline
-hair.n.01 & book.n.01 & 0.20182033649 \\ \hline
-proletarian.n.01 & kant.n.01 & 0.198875753057 \\ \hline
-lion.n.01 & kant.n.01 & 0.179337574844 \\ \hline
+        Choosen Sensens & Closest Top Sense & similarity & Top Sense Gloss \\ \hline
+\multicolumn{4}{|c|}{Lenin: MATERIALISM and EMPIRIO - path similarity} \\ \hline
+revolution.n.01 & experience.n.03 & 0.25 & an event as apprehended\\ \hline
+proletarian.n.01 & matter.n.03 & 0.166666666667 & that which has mass and occupies space\\ \hline
+philosophy.n.02 & physics.n.01 & 0.166666666667 & the science of matter and energy and their interactions\\ \hline
+war.n.01 & experience.n.03 & 0.166666666667 & an event as apprehended\\ \hline
+strategy.n.02 & physics.n.01 & 0.166666666667 & the science of matter and energy and their interactions\\ \hline
+practice.n.03 & experience.n.03 & 0.166666666667 & an event as apprehended\\ \hline
+money.n.01 & beginning.n.02 & 0.142857142857 & the time at which something is supposed to begin\\ \hline
+materialism.n.02 & aim.n.02 & 0.142857142857 & the goal intended to be attained (and which is believed to be attainable)\\ \hline
+idealism.n.01 & aim.n.02 & 0.142857142857 & the goal intended to be attained (and which is believed to be attainable)\\ \hline
+imperialism.n.02 & aim.n.02 & 0.125 & the goal intended to be attained (and which is believed to be attainable)\\ \hline
+sugar.n.01 & matter.n.03 & 0.125 & that which has mass and occupies space\\ \hline
+theory.n.01 & sensation.n.01 & 0.125 & an unelaborated elementary awareness of stimulation\\ \hline
+hair.n.01 & space.n.02 & 0.125 & an empty area (usually bounded in some way between things)\\ \hline
+capitalism.n.01 & time.n.05 & 0.125 & the continuum of experience in which events pass from the future through the present to the past\\ \hline
+toilet.n.04 & experience.n.03 & 0.111111111111 & an event as apprehended\\ \hline
+television receiver.n.01 & space.n.02 & 0.0909090909091 & an empty area (usually bounded in some way between things)\\ \hline
+car.n.01 & space.n.02 & 0.0909090909091 & an empty area (usually bounded in some way between things)\\ \hline
+lion.n.01 & kant.n.01 & 0.0666666666667 & influential German idealist philosopher (1724-1804)\\ \hline
+\multicolumn{4}{|c|}{Lenin: MATERIALISM and EMPIRIO - lch similarity} \\ \hline
+revolution.n.01 & experience.n.03 & 2.25129179861 & an event as apprehended\\ \hline
+proletarian.n.01 & matter.n.03 & 1.8458266905 & that which has mass and occupies space\\ \hline
+philosophy.n.02 & physics.n.01 & 1.8458266905 & the science of matter and energy and their interactions\\ \hline
+war.n.01 & experience.n.03 & 1.8458266905 & an event as apprehended\\ \hline
+strategy.n.02 & physics.n.01 & 1.8458266905 & the science of matter and energy and their interactions\\ \hline
+practice.n.03 & experience.n.03 & 1.8458266905 & an event as apprehended\\ \hline
+money.n.01 & beginning.n.02 & 1.69167601067 & the time at which something is supposed to begin\\ \hline
+materialism.n.02 & aim.n.02 & 1.69167601067 & the goal intended to be attained (and which is believed to be attainable)\\ \hline
+idealism.n.01 & aim.n.02 & 1.69167601067 & the goal intended to be attained (and which is believed to be attainable)\\ \hline
+imperialism.n.02 & aim.n.02 & 1.55814461805 & the goal intended to be attained (and which is believed to be attainable)\\ \hline
+sugar.n.01 & matter.n.03 & 1.55814461805 & that which has mass and occupies space\\ \hline
+theory.n.01 & sensation.n.01 & 1.55814461805 & an unelaborated elementary awareness of stimulation\\ \hline
+hair.n.01 & space.n.02 & 1.55814461805 & an empty area (usually bounded in some way between things)\\ \hline
+capitalism.n.01 & time.n.05 & 1.55814461805 & the continuum of experience in which events pass from the future through the present to the past\\ \hline
+toilet.n.04 & experience.n.03 & 1.44036158239 & an event as apprehended\\ \hline
+television receiver.n.01 & space.n.02 & 1.23969088693 & an empty area (usually bounded in some way between things)\\ \hline
+car.n.01 & space.n.02 & 1.23969088693 & an empty area (usually bounded in some way between things)\\ \hline
+lion.n.01 & kant.n.01 & 0.929535958624 & influential German idealist philosopher (1724-1804)\\ \hline
+\multicolumn{4}{|c|}{Lenin: MATERIALISM and EMPIRIO - res similarity} \\ \hline
+philosophy.n.02 & physics.n.01 & 5.58877614988 & the science of matter and energy and their interactions\\ \hline
+strategy.n.02 & physics.n.01 & 5.58877614988 & the science of matter and energy and their interactions\\ \hline
+theory.n.01 & sensation.n.01 & 4.38484522248 & an unelaborated elementary awareness of stimulation\\ \hline
+revolution.n.01 & experience.n.03 & 4.05348916032 & an event as apprehended\\ \hline
+sugar.n.01 & matter.n.03 & 3.3367059068 & that which has mass and occupies space\\ \hline
+materialism.n.02 & physics.n.01 & 3.29228159341 & the science of matter and energy and their interactions\\ \hline
+idealism.n.01 & physics.n.01 & 3.29228159341 & the science of matter and energy and their interactions\\ \hline
+capitalism.n.01 & sociable.n.01 & 2.85529368615 & a party of people assembled to promote sociability and communal activity\\ \hline
+money.n.01 & beginning.n.02 & 2.69110280536 & the time at which something is supposed to begin\\ \hline
+imperialism.n.02 & physics.n.01 & 2.64452085446 & the science of matter and energy and their interactions\\ \hline
+proletarian.n.01 & kant.n.01 & 2.33354524374 & influential German idealist philosopher (1724-1804)\\ \hline
+toilet.n.04 & motion.n.03 & 2.33223775508 & a change of position that does not entail a change of location\\ \hline
+war.n.01 & motion.n.03 & 2.33223775508 & a change of position that does not entail a change of location\\ \hline
+practice.n.03 & motion.n.03 & 2.33223775508 & a change of position that does not entail a change of location\\ \hline
+television receiver.n.01 & book.n.01 & 2.30584873145 & a written work or composition that has been published (printed on pages bound together)\\ \hline
+car.n.01 & book.n.01 & 2.30584873145 & a written work or composition that has been published (printed on pages bound together)\\ \hline
+lion.n.01 & kant.n.01 & 2.22415047123 & influential German idealist philosopher (1724-1804)\\ \hline
+hair.n.01 & kant.n.01 & 1.53183374322 & influential German idealist philosopher (1724-1804)\\ \hline
+\multicolumn{4}{|c|}{Lenin: MATERIALISM and EMPIRIO - jcn similarity} \\ \hline
+philosophy.n.02 & physics.n.01 & 0.145932703696 & the science of matter and energy and their interactions\\ \hline
+theory.n.01 & sensation.n.01 & 0.128286683846 & an unelaborated elementary awareness of stimulation\\ \hline
+sugar.n.01 & matter.n.03 & 0.127664075736 & that which has mass and occupies space\\ \hline
+revolution.n.01 & experience.n.03 & 0.111569245855 & an event as apprehended\\ \hline
+money.n.01 & moment.n.01 & 0.107804699133 & a particular point in time\\ \hline
+car.n.01 & matter.n.03 & 0.107243331568 & that which has mass and occupies space\\ \hline
+hair.n.01 & matter.n.03 & 0.104557075904 & that which has mass and occupies space\\ \hline
+strategy.n.02 & physics.n.01 & 0.100652051627 & the science of matter and energy and their interactions\\ \hline
+war.n.01 & motion.n.03 & 0.100254651557 & a change of position that does not entail a change of location\\ \hline
+practice.n.03 & motion.n.03 & 0.0882827134582 & a change of position that does not entail a change of location\\ \hline
+proletarian.n.01 & matter.n.03 & 0.0875035868175 & that which has mass and occupies space\\ \hline
+television receiver.n.01 & matter.n.03 & 0.085230569567 & that which has mass and occupies space\\ \hline
+lion.n.01 & matter.n.03 & 0.0783404338338 & that which has mass and occupies space\\ \hline
+materialism.n.02 & aim.n.02 & 0.0778269817906 & the goal intended to be attained (and which is believed to be attainable)\\ \hline
+toilet.n.04 & motion.n.03 & 0.0745896410117 & a change of position that does not entail a change of location\\ \hline
+idealism.n.01 & aim.n.02 & 0.0730123547216 & the goal intended to be attained (and which is believed to be attainable)\\ \hline
+capitalism.n.01 & sociable.n.01 & 0.0678992095349 & a party of people assembled to promote sociability and communal activity\\ \hline
+imperialism.n.02 & aim.n.02 & 0.0649464570442 & the goal intended to be attained (and which is believed to be attainable)\\ \hline
+\multicolumn{4}{|c|}{Lenin: MATERIALISM and EMPIRIO - lin similarity} \\ \hline
+philosophy.n.02 & physics.n.01 & 0.619941000616 & the science of matter and energy and their interactions\\ \hline
+strategy.n.02 & physics.n.01 & 0.529421413479 & the science of matter and energy and their interactions\\ \hline
+theory.n.01 & sensation.n.01 & 0.529419405948 & an unelaborated elementary awareness of stimulation\\ \hline
+revolution.n.01 & experience.n.03 & 0.474924895953 & an event as apprehended\\ \hline
+sugar.n.01 & matter.n.03 & 0.460030062094 & that which has mass and occupies space\\ \hline
+money.n.01 & moment.n.01 & 0.367179548114 & a particular point in time\\ \hline
+materialism.n.02 & aim.n.02 & 0.33882403792 & the goal intended to be attained (and which is believed to be attainable)\\ \hline
+idealism.n.01 & aim.n.02 & 0.324668589607 & the goal intended to be attained (and which is believed to be attainable)\\ \hline
+war.n.01 & motion.n.03 & 0.318631846502 & a change of position that does not entail a change of location\\ \hline
+car.n.01 & book.n.01 & 0.308668677605 & a written work or composition that has been published (printed on pages bound together)\\ \hline
+practice.n.03 & motion.n.03 & 0.291680639247 & a change of position that does not entail a change of location\\ \hline
+capitalism.n.01 & sociable.n.01 & 0.27940619133 & a party of people assembled to promote sociability and communal activity\\ \hline
+television receiver.n.01 & book.n.01 & 0.265820778874 & a written work or composition that has been published (printed on pages bound together)\\ \hline
+toilet.n.04 & motion.n.03 & 0.258117063881 & a change of position that does not entail a change of location\\ \hline
+imperialism.n.02 & aim.n.02 & 0.255677978749 & the goal intended to be attained (and which is believed to be attainable)\\ \hline
+hair.n.01 & book.n.01 & 0.20182033649 & a written work or composition that has been published (printed on pages bound together)\\ \hline
+proletarian.n.01 & kant.n.01 & 0.198875753057 & influential German idealist philosopher (1724-1804)\\ \hline
+lion.n.01 & kant.n.01 & 0.179337574844 & influential German idealist philosopher (1724-1804)\\ \hline
 \end{tabular}

### 2014-03-01 paper/analysis_lenin_the_agrarian_programme_o.tex
add graph that compares each sense against each other. add definition to top senses tables

@@
     \begin{center}
-      \begin{tabular}{ | l | l | l |}
+      \begin{tabular}{ | l | l | l | l |}
         \hline
-        Choosen Sensens & Closest Top Sense & similarity  \\ \hline
-\multicolumn{3}{|c|}{Lenin: The Agrarian Programme  - path similarity} \\ \hline
-revolution.n.01 & revolution.n.01 & 1.0 \\ \hline
-proletarian.n.01 & peasant.n.01 & 0.25 \\ \hline
-money.n.01 & bill.n.03 & 0.2 \\ \hline
-war.n.01 & nationalization.n.03 & 0.2 \\ \hline
-practice.n.03 & nationalization.n.03 & 0.166666666667 \\ \hline
-capitalism.n.01 & people.n.01 & 0.166666666667 \\ \hline
-hair.n.01 & land.n.04 & 0.142857142857 \\ \hline
-toilet.n.04 & nationalization.n.03 & 0.111111111111 \\ \hline
-philosophy.n.02 & absolute.n.01 & 0.111111111111 \\ \hline
-materialism.n.02 & absolute.n.01 & 0.111111111111 \\ \hline
-strategy.n.02 & absolute.n.01 & 0.111111111111 \\ \hline
-idealism.n.01 & absolute.n.01 & 0.111111111111 \\ \hline
-imperialism.n.02 & people.n.01 & 0.111111111111 \\ \hline
-television receiver.n.01 & land.n.04 & 0.1 \\ \hline
-car.n.01 & land.n.04 & 0.1 \\ \hline
-theory.n.01 & people.n.01 & 0.1 \\ \hline
-sugar.n.01 & land.n.04 & 0.0909090909091 \\ \hline
-lion.n.01 & land.n.04 & 0.0714285714286 \\ \hline
-\multicolumn{3}{|c|}{Lenin: The Agrarian Programme  - lch similarity} \\ \hline
-revolution.n.01 & revolution.n.01 & 3.63758615973 \\ \hline
-proletarian.n.01 & peasant.n.01 & 2.25129179861 \\ \hline
-money.n.01 & bill.n.03 & 2.02814824729 \\ \hline
-war.n.01 & nationalization.n.03 & 2.02814824729 \\ \hline
-practice.n.03 & nationalization.n.03 & 1.8458266905 \\ \hline
-capitalism.n.01 & people.n.01 & 1.8458266905 \\ \hline
-hair.n.01 & land.n.04 & 1.69167601067 \\ \hline
-toilet.n.04 & nationalization.n.03 & 1.44036158239 \\ \hline
-philosophy.n.02 & absolute.n.01 & 1.44036158239 \\ \hline
-materialism.n.02 & absolute.n.01 & 1.44036158239 \\ \hline
-strategy.n.02 & absolute.n.01 & 1.44036158239 \\ \hline
-idealism.n.01 & absolute.n.01 & 1.44036158239 \\ \hline
-imperialism.n.02 & people.n.01 & 1.44036158239 \\ \hline
-television receiver.n.01 & land.n.04 & 1.33500106673 \\ \hline
-car.n.01 & land.n.04 & 1.33500106673 \\ \hline
-theory.n.01 & people.n.01 & 1.33500106673 \\ \hline
-sugar.n.01 & land.n.04 & 1.23969088693 \\ \hline
-lion.n.01 & land.n.04 & 0.998528830111 \\ \hline
-\multicolumn{3}{|c|}{Lenin: The Agrarian Programme  - res similarity} \\ \hline
-revolution.n.01 & revolution.n.01 & 10.3880624692 \\ \hline
-proletarian.n.01 & peasant.n.01 & 9.00601439892 \\ \hline
-money.n.01 & bill.n.03 & 6.2549318819 \\ \hline
-war.n.01 & nationalization.n.03 & 4.52385364841 \\ \hline
-philosophy.n.02 & absolute.n.01 & 3.29228159341 \\ \hline
-materialism.n.02 & absolute.n.01 & 3.29228159341 \\ \hline
-strategy.n.02 & absolute.n.01 & 3.29228159341 \\ \hline
-idealism.n.01 & absolute.n.01 & 3.29228159341 \\ \hline
-capitalism.n.01 & people.n.01 & 2.85529368615 \\ \hline
-imperialism.n.02 & absolute.n.01 & 2.64452085446 \\ \hline
-theory.n.01 & absolute.n.01 & 2.64452085446 \\ \hline
-toilet.n.04 & nationalization.n.03 & 2.33223775508 \\ \hline
-practice.n.03 & nationalization.n.03 & 2.33223775508 \\ \hline
-lion.n.01 & peasant.n.01 & 2.22415047123 \\ \hline
-television receiver.n.01 & peasant.n.01 & 1.53183374322 \\ \hline
-car.n.01 & peasant.n.01 & 1.53183374322 \\ \hline
-hair.n.01 & peasant.n.01 & 1.53183374322 \\ \hline
-sugar.n.01 & land.n.04 & 0.801759114954 \\ \hline
-\multicolumn{3}{|c|}{Lenin: The Agrarian Programme  - jcn similarity} \\ \hline
-revolution.n.01 & revolution.n.01 & 1e+300 \\ \hline
-proletarian.n.01 & peasant.n.01 & 0.363995193783 \\ \hline
-money.n.01 & bill.n.03 & 0.30619633675 \\ \hline
-war.n.01 & farming.n.01 & 0.102813269009 \\ \hline
-car.n.01 & land.n.04 & 0.0903577501322 \\ \hline
-hair.n.01 & land.n.04 & 0.0884432572523 \\ \hline
-capitalism.n.01 & people.n.01 & 0.0880782305893 \\ \hline
-philosophy.n.02 & people.n.01 & 0.0801894085342 \\ \hline
-television receiver.n.01 & land.n.04 & 0.0742092466431 \\ \hline
-theory.n.01 & people.n.01 & 0.0738644334041 \\ \hline
-practice.n.03 & people.n.01 & 0.0728246934249 \\ \hline
-lion.n.01 & land.n.04 & 0.0689306688111 \\ \hline
-strategy.n.02 & people.n.01 & 0.0642953740963 \\ \hline
-sugar.n.01 & land.n.04 & 0.0640122327597 \\ \hline
-toilet.n.04 & people.n.01 & 0.0632469161145 \\ \hline
-materialism.n.02 & people.n.01 & 0.0598861536358 \\ \hline
-idealism.n.01 & people.n.01 & 0.056994188175 \\ \hline
-imperialism.n.02 & people.n.01 & 0.055706849963 \\ \hline
-\multicolumn{3}{|c|}{Lenin: The Agrarian Programme  - lin similarity} \\ \hline
-revolution.n.01 & revolution.n.01 & 1.0 \\ \hline
-proletarian.n.01 & peasant.n.01 & 0.867659956556 \\ \hline
-money.n.01 & bill.n.03 & 0.792980998294 \\ \hline
-war.n.01 & farming.n.01 & 0.481925511595 \\ \hline
-philosophy.n.02 & absolute.n.01 & 0.341316252969 \\ \hline
-capitalism.n.01 & people.n.01 & 0.334654457361 \\ \hline
-strategy.n.02 & absolute.n.01 & 0.294289762784 \\ \hline
-materialism.n.02 & absolute.n.01 & 0.279961229282 \\ \hline
-idealism.n.01 & absolute.n.01 & 0.270226260066 \\ \hline
-theory.n.01 & absolute.n.01 & 0.259782259686 \\ \hline
-practice.n.03 & restoration.n.02 & 0.240021453557 \\ \hline
-toilet.n.04 & restoration.n.02 & 0.216821056563 \\ \hline
-imperialism.n.02 & absolute.n.01 & 0.213506139286 \\ \hline
-lion.n.01 & peasant.n.01 & 0.20131688425 \\ \hline
-car.n.01 & land.n.04 & 0.18905393848 \\ \hline
-hair.n.01 & land.n.04 & 0.185792500123 \\ \hline
-television receiver.n.01 & land.n.04 & 0.160696186575 \\ \hline
-sugar.n.01 & land.n.04 & 0.0930896185493 \\ \hline
+        Choosen Sensens & Closest Top Sense & similarity & Top Sense Gloss \\ \hline
+\multicolumn{4}{|c|}{Lenin: The Agrarian Programme  - path similarity} \\ \hline
+revolution.n.01 & revolution.n.01 & 1.0 & a drastic and far-reaching change in ways of thinking and behaving\\ \hline
+proletarian.n.01 & peasant.n.01 & 0.25 & a country person\\ \hline
+money.n.01 & bill.n.03 & 0.2 & a piece of paper money (especially one issued by a central bank)\\ \hline
+war.n.01 & nationalization.n.03 & 0.2 & changing something from private to state ownership or control\\ \hline
+practice.n.03 & nationalization.n.03 & 0.166666666667 & changing something from private to state ownership or control\\ \hline
+capitalism.n.01 & people.n.01 & 0.166666666667 & (plural) any group of human beings (men or women or children) collectively\\ \hline
+hair.n.01 & land.n.04 & 0.142857142857 & the solid part of the earth's surface\\ \hline
+toilet.n.04 & nationalization.n.03 & 0.111111111111 & changing something from private to state ownership or control\\ \hline
+philosophy.n.02 & absolute.n.01 & 0.111111111111 & something that is conceived or that exists independently and not in relation to other things; something that does not depend on anything else and is beyond human control; something that is not relative\\ \hline
+materialism.n.02 & absolute.n.01 & 0.111111111111 & something that is conceived or that exists independently and not in relation to other things; something that does not depend on anything else and is beyond human control; something that is not relative\\ \hline
+strategy.n.02 & absolute.n.01 & 0.111111111111 & something that is conceived or that exists independently and not in relation to other things; something that does not depend on anything else and is beyond human control; something that is not relative\\ \hline
+idealism.n.01 & absolute.n.01 & 0.111111111111 & something that is conceived or that exists independently and not in relation to other things; something that does not depend on anything else and is beyond human control; something that is not relative\\ \hline
+imperialism.n.02 & people.n.01 & 0.111111111111 & (plural) any group of human beings (men or women or children) collectively\\ \hline
+television receiver.n.01 & land.n.04 & 0.1 & the solid part of the earth's surface\\ \hline
+car.n.01 & land.n.04 & 0.1 & the solid part of the earth's surface\\ \hline
+theory.n.01 & people.n.01 & 0.1 & (plural) any group of human beings (men or women or children) collectively\\ \hline
+sugar.n.01 & land.n.04 & 0.0909090909091 & the solid part of the earth's surface\\ \hline
+lion.n.01 & land.n.04 & 0.0714285714286 & the solid part of the earth's surface\\ \hline
+\multicolumn{4}{|c|}{Lenin: The Agrarian Programme  - lch similarity} \\ \hline
+revolution.n.01 & revolution.n.01 & 3.63758615973 & a drastic and far-reaching change in ways of thinking and behaving\\ \hline
+proletarian.n.01 & peasant.n.01 & 2.25129179861 & a country person\\ \hline
+money.n.01 & bill.n.03 & 2.02814824729 & a piece of paper money (especially one issued by a central bank)\\ \hline
+war.n.01 & nationalization.n.03 & 2.02814824729 & changing something from private to state ownership or control\\ \hline
+practice.n.03 & nationalization.n.03 & 1.8458266905 & changing something from private to state ownership or control\\ \hline
+capitalism.n.01 & people.n.01 & 1.8458266905 & (plural) any group of human beings (men or women or children) collectively\\ \hline
+hair.n.01 & land.n.04 & 1.69167601067 & the solid part of the earth's surface\\ \hline
+toilet.n.04 & nationalization.n.03 & 1.44036158239 & changing something from private to state ownership or control\\ \hline
+philosophy.n.02 & absolute.n.01 & 1.44036158239 & something that is conceived or that exists independently and not in relation to other things; something that does not depend on anything else and is beyond human control; something that is not relative\\ \hline
+materialism.n.02 & absolute.n.01 & 1.44036158239 & something that is conceived or that exists independently and not in relation to other things; something that does not depend on anything else and is beyond human control; something that is not relative\\ \hline
+strategy.n.02 & absolute.n.01 & 1.44036158239 & something that is conceived or that exists independently and not in relation to other things; something that does not depend on anything else and is beyond human control; something that is not relative\\ \hline
+idealism.n.01 & absolute.n.01 & 1.44036158239 & something that is conceived or that exists independently and not in relation to other things; something that does not depend on anything else and is beyond human control; something that is not relative\\ \hline
+imperialism.n.02 & people.n.01 & 1.44036158239 & (plural) any group of human beings (men or women or children) collectively\\ \hline
+television receiver.n.01 & land.n.04 & 1.33500106673 & the solid part of the earth's surface\\ \hline
+car.n.01 & land.n.04 & 1.33500106673 & the solid part of the earth's surface\\ \hline
+theory.n.01 & people.n.01 & 1.33500106673 & (plural) any group of human beings (men or women or children) collectively\\ \hline
+sugar.n.01 & land.n.04 & 1.23969088693 & the solid part of the earth's surface\\ \hline
+lion.n.01 & land.n.04 & 0.998528830111 & the solid part of the earth's surface\\ \hline
+\multicolumn{4}{|c|}{Lenin: The Agrarian Programme  - res similarity} \\ \hline
+revolution.n.01 & revolution.n.01 & 10.3880624692 & a drastic and far-reaching change in ways of thinking and behaving\\ \hline
+proletarian.n.01 & peasant.n.01 & 9.00601439892 & a country person\\ \hline
+money.n.01 & bill.n.03 & 6.2549318819 & a piece of paper money (especially one issued by a central bank)\\ \hline
+war.n.01 & nationalization.n.03 & 4.52385364841 & changing something from private to state ownership or control\\ \hline
+philosophy.n.02 & absolute.n.01 & 3.29228159341 & something that is conceived or that exists independently and not in relation to other things; something that does not depend on anything else and is beyond human control; something that is not relative\\ \hline
+materialism.n.02 & absolute.n.01 & 3.29228159341 & something that is conceived or that exists independently and not in relation to other things; something that does not depend on anything else and is beyond human control; something that is not relative\\ \hline
+strategy.n.02 & absolute.n.01 & 3.29228159341 & something that is conceived or that exists independently and not in relation to other things; something that does not depend on anything else and is beyond human control; something that is not relative\\ \hline
+idealism.n.01 & absolute.n.01 & 3.29228159341 & something that is conceived or that exists independently and not in relation to other things; something that does not depend on anything else and is beyond human control; something that is not relative\\ \hline
+capitalism.n.01 & people.n.01 & 2.85529368615 & (plural) any group of human beings (men or women or children) collectively\\ \hline
+imperialism.n.02 & absolute.n.01 & 2.64452085446 & something that is conceived or that exists independently and not in relation to other things; something that does not depend on anything else and is beyond human control; something that is not relative\\ \hline
+theory.n.01 & absolute.n.01 & 2.64452085446 & something that is conceived or that exists independently and not in relation to other things; something that does not depend on anything else and is beyond human control; something that is not relative\\ \hline
+toilet.n.04 & nationalization.n.03 & 2.33223775508 & changing something from private to state ownership or control\\ \hline
+practice.n.03 & nationalization.n.03 & 2.33223775508 & changing something from private to state ownership or control\\ \hline
+lion.n.01 & peasant.n.01 & 2.22415047123 & a country person\\ \hline
+television receiver.n.01 & peasant.n.01 & 1.53183374322 & a country person\\ \hline
+car.n.01 & peasant.n.01 & 1.53183374322 & a country person\\ \hline
+hair.n.01 & peasant.n.01 & 1.53183374322 & a country person\\ \hline
+sugar.n.01 & land.n.04 & 0.801759114954 & the solid part of the earth's surface\\ \hline
+\multicolumn{4}{|c|}{Lenin: The Agrarian Programme  - jcn similarity} \\ \hline
+revolution.n.01 & revolution.n.01 & 1e+300 & a drastic and far-reaching change in ways of thinking and behaving\\ \hline
+proletarian.n.01 & peasant.n.01 & 0.363995193783 & a country person\\ \hline
+money.n.01 & bill.n.03 & 0.30619633675 & a piece of paper money (especially one issued by a central bank)\\ \hline
+war.n.01 & farming.n.01 & 0.102813269009 & the practice of cultivating the land or raising stock\\ \hline
+car.n.01 & land.n.04 & 0.0903577501322 & the solid part of the earth's surface\\ \hline
+hair.n.01 & land.n.04 & 0.0884432572523 & the solid part of the earth's surface\\ \hline
+capitalism.n.01 & people.n.01 & 0.0880782305893 & (plural) any group of human beings (men or women or children) collectively\\ \hline
+philosophy.n.02 & people.n.01 & 0.0801894085342 & (plural) any group of human beings (men or women or children) collectively\\ \hline
+television receiver.n.01 & land.n.04 & 0.0742092466431 & the solid part of the earth's surface\\ \hline
+theory.n.01 & people.n.01 & 0.0738644334041 & (plural) any group of human beings (men or women or children) collectively\\ \hline
+practice.n.03 & people.n.01 & 0.0728246934249 & (plural) any group of human beings (men or women or children) collectively\\ \hline
+lion.n.01 & land.n.04 & 0.0689306688111 & the solid part of the earth's surface\\ \hline
+strategy.n.02 & people.n.01 & 0.0642953740963 & (plural) any group of human beings (men or women or children) collectively\\ \hline
+sugar.n.01 & land.n.04 & 0.0640122327597 & the solid part of the earth's surface\\ \hline
+toilet.n.04 & people.n.01 & 0.0632469161145 & (plural) any group of human beings (men or women or children) collectively\\ \hline
+materialism.n.02 & people.n.01 & 0.0598861536358 & (plural) any group of human beings (men or women or children) collectively\\ \hline
+idealism.n.01 & people.n.01 & 0.056994188175 & (plural) any group of human beings (men or women or children) collectively\\ \hline
+imperialism.n.02 & people.n.01 & 0.055706849963 & (plural) any group of human beings (men or women or children) collectively\\ \hline
+\multicolumn{4}{|c|}{Lenin: The Agrarian Programme  - lin similarity} \\ \hline
+revolution.n.01 & revolution.n.01 & 1.0 & a drastic and far-reaching change in ways of thinking and behaving\\ \hline
+proletarian.n.01 & peasant.n.01 & 0.867659956556 & a country person\\ \hline
+money.n.01 & bill.n.03 & 0.792980998294 & a piece of paper money (especially one issued by a central bank)\\ \hline
+war.n.01 & farming.n.01 & 0.481925511595 & the practice of cultivating the land or raising stock\\ \hline
+philosophy.n.02 & absolute.n.01 & 0.341316252969 & something that is conceived or that exists independently and not in relation to other things; something that does not depend on anything else and is beyond human control; something that is not relative\\ \hline
+capitalism.n.01 & people.n.01 & 0.334654457361 & (plural) any group of human beings (men or women or children) collectively\\ \hline
+strategy.n.02 & absolute.n.01 & 0.294289762784 & something that is conceived or that exists independently and not in relation to other things; something that does not depend on anything else and is beyond human control; something that is not relative\\ \hline
+materialism.n.02 & absolute.n.01 & 0.279961229282 & something that is conceived or that exists independently and not in relation to other things; something that does not depend on anything else and is beyond human control; something that is not relative\\ \hline
+idealism.n.01 & absolute.n.01 & 0.270226260066 & something that is conceived or that exists independently and not in relation to other things; something that does not depend on anything else and is beyond human control; something that is not relative\\ \hline
+theory.n.01 & absolute.n.01 & 0.259782259686 & something that is conceived or that exists independently and not in relation to other things; something that does not depend on anything else and is beyond human control; something that is not relative\\ \hline
+practice.n.03 & restoration.n.02 & 0.240021453557 & the act of restoring something or someone to a satisfactory state\\ \hline
+toilet.n.04 & restoration.n.02 & 0.216821056563 & the act of restoring something or someone to a satisfactory state\\ \hline
+imperialism.n.02 & absolute.n.01 & 0.213506139286 & something that is conceived or that exists independently and not in relation to other things; something that does not depend on anything else and is beyond human control; something that is not relative\\ \hline
+lion.n.01 & peasant.n.01 & 0.20131688425 & a country person\\ \hline
+car.n.01 & land.n.04 & 0.18905393848 & the solid part of the earth's surface\\ \hline
+hair.n.01 & land.n.04 & 0.185792500123 & the solid part of the earth's surface\\ \hline
+television receiver.n.01 & land.n.04 & 0.160696186575 & the solid part of the earth's surface\\ \hline
+sugar.n.01 & land.n.04 & 0.0930896185493 & the solid part of the earth's surface\\ \hline
 \end{tabular}

### 2014-03-01 paper/analysis_lenin_what_is_to_be_done?.tex
add graph that compares each sense against each other. add definition to top senses tables

@@
     \begin{center}
-      \begin{tabular}{ | l | l | l |}
+      \begin{tabular}{ | l | l | l | l |}
         \hline
-        Choosen Sensens & Closest Top Sense & similarity  \\ \hline
-\multicolumn{3}{|c|}{Lenin: What Is To Be Done? - path similarity} \\ \hline
-imperialism.n.02 & political orientation.n.01 & 0.5 \\ \hline
-proletarian.n.01 & worker.n.01 & 0.25 \\ \hline
-war.n.01 & conflict.n.01 & 0.25 \\ \hline
-practice.n.03 & conflict.n.01 & 0.2 \\ \hline
-revolution.n.01 & conflict.n.01 & 0.166666666667 \\ \hline
-toilet.n.04 & trade.n.02 & 0.142857142857 \\ \hline
-money.n.01 & mass.n.01 & 0.142857142857 \\ \hline
-capitalism.n.01 & organization.n.01 & 0.142857142857 \\ \hline
-hair.n.01 & working.n.01 & 0.125 \\ \hline
-television receiver.n.01 & working.n.01 & 0.111111111111 \\ \hline
-car.n.01 & working.n.01 & 0.111111111111 \\ \hline
-philosophy.n.02 & political orientation.n.01 & 0.111111111111 \\ \hline
-materialism.n.02 & political orientation.n.01 & 0.111111111111 \\ \hline
-strategy.n.02 & political orientation.n.01 & 0.111111111111 \\ \hline
-idealism.n.01 & political orientation.n.01 & 0.111111111111 \\ \hline
-theory.n.01 & political orientation.n.01 & 0.111111111111 \\ \hline
-sugar.n.01 & local anesthetic.n.01 & 0.0909090909091 \\ \hline
-lion.n.01 & worker.n.01 & 0.0833333333333 \\ \hline
-\multicolumn{3}{|c|}{Lenin: What Is To Be Done? - lch similarity} \\ \hline
-imperialism.n.02 & political orientation.n.01 & 2.94443897917 \\ \hline
-proletarian.n.01 & worker.n.01 & 2.25129179861 \\ \hline
-war.n.01 & conflict.n.01 & 2.25129179861 \\ \hline
-practice.n.03 & conflict.n.01 & 2.02814824729 \\ \hline
-revolution.n.01 & conflict.n.01 & 1.8458266905 \\ \hline
-toilet.n.04 & trade.n.02 & 1.69167601067 \\ \hline
-money.n.01 & mass.n.01 & 1.69167601067 \\ \hline
-capitalism.n.01 & organization.n.01 & 1.69167601067 \\ \hline
-hair.n.01 & working.n.01 & 1.55814461805 \\ \hline
-television receiver.n.01 & working.n.01 & 1.44036158239 \\ \hline
-car.n.01 & working.n.01 & 1.44036158239 \\ \hline
-philosophy.n.02 & political orientation.n.01 & 1.44036158239 \\ \hline
-materialism.n.02 & political orientation.n.01 & 1.44036158239 \\ \hline
-strategy.n.02 & political orientation.n.01 & 1.44036158239 \\ \hline
-idealism.n.01 & political orientation.n.01 & 1.44036158239 \\ \hline
-theory.n.01 & political orientation.n.01 & 1.44036158239 \\ \hline
-sugar.n.01 & local anesthetic.n.01 & 1.23969088693 \\ \hline
-lion.n.01 & worker.n.01 & 1.15267950994 \\ \hline
-\multicolumn{3}{|c|}{Lenin: What Is To Be Done? - res similarity} \\ \hline
-imperialism.n.02 & political orientation.n.01 & 8.60196873746 \\ \hline
-sugar.n.01 & local anesthetic.n.01 & 4.61519673162 \\ \hline
-war.n.01 & conflict.n.01 & 4.52385364841 \\ \hline
-television receiver.n.01 & newspaper.n.01 & 3.25767902589 \\ \hline
-car.n.01 & newspaper.n.01 & 3.25767902589 \\ \hline
-toilet.n.04 & trade.n.02 & 3.14352023311 \\ \hline
-capitalism.n.01 & organization.n.01 & 2.85529368615 \\ \hline
-money.n.01 & mass.n.01 & 2.69110280536 \\ \hline
-philosophy.n.02 & political orientation.n.01 & 2.64452085446 \\ \hline
-materialism.n.02 & political orientation.n.01 & 2.64452085446 \\ \hline
-strategy.n.02 & political orientation.n.01 & 2.64452085446 \\ \hline
-idealism.n.01 & political orientation.n.01 & 2.64452085446 \\ \hline
-theory.n.01 & political orientation.n.01 & 2.64452085446 \\ \hline
-proletarian.n.01 & worker.n.01 & 2.33354524374 \\ \hline
-practice.n.03 & trade.n.02 & 2.33223775508 \\ \hline
-lion.n.01 & worker.n.01 & 2.22415047123 \\ \hline
-revolution.n.01 & trade.n.02 & 2.03632771779 \\ \hline
-hair.n.01 & worker.n.01 & 1.53183374322 \\ \hline
-\multicolumn{3}{|c|}{Lenin: What Is To Be Done? - jcn similarity} \\ \hline
-imperialism.n.02 & political orientation.n.01 & 0.193405491818 \\ \hline
-war.n.01 & conflict.n.01 & 0.152829762599 \\ \hline
-car.n.01 & worker.n.01 & 0.110550521246 \\ \hline
-hair.n.01 & worker.n.01 & 0.107698235698 \\ \hline
-proletarian.n.01 & worker.n.01 & 0.104758893715 \\ \hline
-capitalism.n.01 & organization.n.01 & 0.101121795595 \\ \hline
-sugar.n.01 & local anesthetic.n.01 & 0.0929714058017 \\ \hline
-money.n.01 & organization.n.01 & 0.0929667353193 \\ \hline
-philosophy.n.02 & organization.n.01 & 0.0908595602215 \\ \hline
-lion.n.01 & worker.n.01 & 0.0900802228812 \\ \hline
-practice.n.03 & motion.n.03 & 0.0882827134582 \\ \hline
-television receiver.n.01 & worker.n.01 & 0.0873062903722 \\ \hline
-theory.n.01 & organization.n.01 & 0.0828237113739 \\ \hline
-revolution.n.01 & motion.n.03 & 0.0784056470694 \\ \hline
-toilet.n.04 & motion.n.03 & 0.0745896410117 \\ \hline
-strategy.n.02 & organization.n.01 & 0.0709786674118 \\ \hline
-materialism.n.02 & organization.n.01 & 0.0656431911358 \\ \hline
-idealism.n.01 & organization.n.01 & 0.0621845289629 \\ \hline
-\multicolumn{3}{|c|}{Lenin: What Is To Be Done? - lin similarity} \\ \hline
-imperialism.n.02 & political orientation.n.01 & 0.768910941363 \\ \hline
-war.n.01 & conflict.n.01 & 0.580318438615 \\ \hline
-sugar.n.01 & local anesthetic.n.01 & 0.461833980698 \\ \hline
-car.n.01 & newspaper.n.01 & 0.411156952767 \\ \hline
-capitalism.n.01 & organization.n.01 & 0.366071452787 \\ \hline
-television receiver.n.01 & newspaper.n.01 & 0.356914166707 \\ \hline
-money.n.01 & mass.n.01 & 0.331362497131 \\ \hline
-proletarian.n.01 & worker.n.01 & 0.328371898491 \\ \hline
-philosophy.n.02 & political orientation.n.01 & 0.31307622756 \\ \hline
-toilet.n.04 & trade.n.02 & 0.312879932381 \\ \hline
-theory.n.01 & political orientation.n.01 & 0.294463460062 \\ \hline
-practice.n.03 & motion.n.03 & 0.291680639247 \\ \hline
-lion.n.01 & worker.n.01 & 0.286073258452 \\ \hline
-strategy.n.02 & political orientation.n.01 & 0.264762834975 \\ \hline
-materialism.n.02 & political orientation.n.01 & 0.25040844726 \\ \hline
-hair.n.01 & worker.n.01 & 0.248092928538 \\ \hline
-revolution.n.01 & motion.n.03 & 0.242033306584 \\ \hline
-idealism.n.01 & political orientation.n.01 & 0.240750703939 \\ \hline
+        Choosen Sensens & Closest Top Sense & similarity & Top Sense Gloss \\ \hline
+\multicolumn{4}{|c|}{Lenin: What Is To Be Done? - path similarity} \\ \hline
+imperialism.n.02 & political orientation.n.01 & 0.5 & an orientation that characterizes the thinking of a group or nation\\ \hline
+proletarian.n.01 & worker.n.01 & 0.25 & a person who works at a specific occupation\\ \hline
+war.n.01 & conflict.n.01 & 0.25 & an open clash between two opposing groups (or individuals)\\ \hline
+practice.n.03 & conflict.n.01 & 0.2 & an open clash between two opposing groups (or individuals)\\ \hline
+revolution.n.01 & conflict.n.01 & 0.166666666667 & an open clash between two opposing groups (or individuals)\\ \hline
+toilet.n.04 & trade.n.02 & 0.142857142857 & the skilled practice of a practical occupation\\ \hline
+money.n.01 & mass.n.01 & 0.142857142857 & the property of a body that causes it to have weight in a gravitational field\\ \hline
+capitalism.n.01 & organization.n.01 & 0.142857142857 & a group of people who work together\\ \hline
+hair.n.01 & working.n.01 & 0.125 & a mine or quarry that is being or has been worked\\ \hline
+television receiver.n.01 & working.n.01 & 0.111111111111 & a mine or quarry that is being or has been worked\\ \hline
+car.n.01 & working.n.01 & 0.111111111111 & a mine or quarry that is being or has been worked\\ \hline
+philosophy.n.02 & political orientation.n.01 & 0.111111111111 & an orientation that characterizes the thinking of a group or nation\\ \hline
+materialism.n.02 & political orientation.n.01 & 0.111111111111 & an orientation that characterizes the thinking of a group or nation\\ \hline
+strategy.n.02 & political orientation.n.01 & 0.111111111111 & an orientation that characterizes the thinking of a group or nation\\ \hline
+idealism.n.01 & political orientation.n.01 & 0.111111111111 & an orientation that characterizes the thinking of a group or nation\\ \hline
+theory.n.01 & political orientation.n.01 & 0.111111111111 & an orientation that characterizes the thinking of a group or nation\\ \hline
+sugar.n.01 & local anesthetic.n.01 & 0.0909090909091 & anesthetic that numbs a particular area of the body\\ \hline
+lion.n.01 & worker.n.01 & 0.0833333333333 & a person who works at a specific occupation\\ \hline
+\multicolumn{4}{|c|}{Lenin: What Is To Be Done? - lch similarity} \\ \hline
+imperialism.n.02 & political orientation.n.01 & 2.94443897917 & an orientation that characterizes the thinking of a group or nation\\ \hline
+proletarian.n.01 & worker.n.01 & 2.25129179861 & a person who works at a specific occupation\\ \hline
+war.n.01 & conflict.n.01 & 2.25129179861 & an open clash between two opposing groups (or individuals)\\ \hline
+practice.n.03 & conflict.n.01 & 2.02814824729 & an open clash between two opposing groups (or individuals)\\ \hline
+revolution.n.01 & conflict.n.01 & 1.8458266905 & an open clash between two opposing groups (or individuals)\\ \hline
+toilet.n.04 & trade.n.02 & 1.69167601067 & the skilled practice of a practical occupation\\ \hline
+money.n.01 & mass.n.01 & 1.69167601067 & the property of a body that causes it to have weight in a gravitational field\\ \hline
+capitalism.n.01 & organization.n.01 & 1.69167601067 & a group of people who work together\\ \hline
+hair.n.01 & working.n.01 & 1.55814461805 & a mine or quarry that is being or has been worked\\ \hline
+television receiver.n.01 & working.n.01 & 1.44036158239 & a mine or quarry that is being or has been worked\\ \hline
+car.n.01 & working.n.01 & 1.44036158239 & a mine or quarry that is being or has been worked\\ \hline
+philosophy.n.02 & political orientation.n.01 & 1.44036158239 & an orientation that characterizes the thinking of a group or nation\\ \hline
+materialism.n.02 & political orientation.n.01 & 1.44036158239 & an orientation that characterizes the thinking of a group or nation\\ \hline
+strategy.n.02 & political orientation.n.01 & 1.44036158239 & an orientation that characterizes the thinking of a group or nation\\ \hline
+idealism.n.01 & political orientation.n.01 & 1.44036158239 & an orientation that characterizes the thinking of a group or nation\\ \hline
+theory.n.01 & political orientation.n.01 & 1.44036158239 & an orientation that characterizes the thinking of a group or nation\\ \hline
+sugar.n.01 & local anesthetic.n.01 & 1.23969088693 & anesthetic that numbs a particular area of the body\\ \hline
+lion.n.01 & worker.n.01 & 1.15267950994 & a person who works at a specific occupation\\ \hline
+\multicolumn{4}{|c|}{Lenin: What Is To Be Done? - res similarity} \\ \hline
+imperialism.n.02 & political orientation.n.01 & 8.60196873746 & an orientation that characterizes the thinking of a group or nation\\ \hline
+sugar.n.01 & local anesthetic.n.01 & 4.61519673162 & anesthetic that numbs a particular area of the body\\ \hline
+war.n.01 & conflict.n.01 & 4.52385364841 & an open clash between two opposing groups (or individuals)\\ \hline
+television receiver.n.01 & newspaper.n.01 & 3.25767902589 & a daily or weekly publication on folded sheets; contains news and articles and advertisements\\ \hline
+car.n.01 & newspaper.n.01 & 3.25767902589 & a daily or weekly publication on folded sheets; contains news and articles and advertisements\\ \hline
+toilet.n.04 & trade.n.02 & 3.14352023311 & the skilled practice of a practical occupation\\ \hline
+capitalism.n.01 & organization.n.01 & 2.85529368615 & a group of people who work together\\ \hline
+money.n.01 & mass.n.01 & 2.69110280536 & the property of a body that causes it to have weight in a gravitational field\\ \hline
+philosophy.n.02 & political orientation.n.01 & 2.64452085446 & an orientation that characterizes the thinking of a group or nation\\ \hline
+materialism.n.02 & political orientation.n.01 & 2.64452085446 & an orientation that characterizes the thinking of a group or nation\\ \hline
+strategy.n.02 & political orientation.n.01 & 2.64452085446 & an orientation that characterizes the thinking of a group or nation\\ \hline
+idealism.n.01 & political orientation.n.01 & 2.64452085446 & an orientation that characterizes the thinking of a group or nation\\ \hline
+theory.n.01 & political orientation.n.01 & 2.64452085446 & an orientation that characterizes the thinking of a group or nation\\ \hline
+proletarian.n.01 & worker.n.01 & 2.33354524374 & a person who works at a specific occupation\\ \hline
+practice.n.03 & trade.n.02 & 2.33223775508 & the skilled practice of a practical occupation\\ \hline
+lion.n.01 & worker.n.01 & 2.22415047123 & a person who works at a specific occupation\\ \hline
+revolution.n.01 & trade.n.02 & 2.03632771779 & the skilled practice of a practical occupation\\ \hline
+hair.n.01 & worker.n.01 & 1.53183374322 & a person who works at a specific occupation\\ \hline
+\multicolumn{4}{|c|}{Lenin: What Is To Be Done? - jcn similarity} \\ \hline
+imperialism.n.02 & political orientation.n.01 & 0.193405491818 & an orientation that characterizes the thinking of a group or nation\\ \hline
+war.n.01 & conflict.n.01 & 0.152829762599 & an open clash between two opposing groups (or individuals)\\ \hline
+car.n.01 & worker.n.01 & 0.110550521246 & a person who works at a specific occupation\\ \hline
+hair.n.01 & worker.n.01 & 0.107698235698 & a person who works at a specific occupation\\ \hline
+proletarian.n.01 & worker.n.01 & 0.104758893715 & a person who works at a specific occupation\\ \hline
+capitalism.n.01 & organization.n.01 & 0.101121795595 & a group of people who work together\\ \hline
+sugar.n.01 & local anesthetic.n.01 & 0.0929714058017 & anesthetic that numbs a particular area of the body\\ \hline
+money.n.01 & organization.n.01 & 0.0929667353193 & a group of people who work together\\ \hline
+philosophy.n.02 & organization.n.01 & 0.0908595602215 & a group of people who work together\\ \hline
+lion.n.01 & worker.n.01 & 0.0900802228812 & a person who works at a specific occupation\\ \hline
+practice.n.03 & motion.n.03 & 0.0882827134582 & a change of position that does not entail a change of location\\ \hline
+television receiver.n.01 & worker.n.01 & 0.0873062903722 & a person who works at a specific occupation\\ \hline
+theory.n.01 & organization.n.01 & 0.0828237113739 & a group of people who work together\\ \hline
+revolution.n.01 & motion.n.03 & 0.0784056470694 & a change of position that does not entail a change of location\\ \hline
+toilet.n.04 & motion.n.03 & 0.0745896410117 & a change of position that does not entail a change of location\\ \hline
+strategy.n.02 & organization.n.01 & 0.0709786674118 & a group of people who work together\\ \hline
+materialism.n.02 & organization.n.01 & 0.0656431911358 & a group of people who work together\\ \hline
+idealism.n.01 & organization.n.01 & 0.0621845289629 & a group of people who work together\\ \hline
+\multicolumn{4}{|c|}{Lenin: What Is To Be Done? - lin similarity} \\ \hline
+imperialism.n.02 & political orientation.n.01 & 0.768910941363 & an orientation that characterizes the thinking of a group or nation\\ \hline
+war.n.01 & conflict.n.01 & 0.580318438615 & an open clash between two opposing groups (or individuals)\\ \hline
+sugar.n.01 & local anesthetic.n.01 & 0.461833980698 & anesthetic that numbs a particular area of the body\\ \hline
+car.n.01 & newspaper.n.01 & 0.411156952767 & a daily or weekly publication on folded sheets; contains news and articles and advertisements\\ \hline
+capitalism.n.01 & organization.n.01 & 0.366071452787 & a group of people who work together\\ \hline
+television receiver.n.01 & newspaper.n.01 & 0.356914166707 & a daily or weekly publication on folded sheets; contains news and articles and advertisements\\ \hline
+money.n.01 & mass.n.01 & 0.331362497131 & the property of a body that causes it to have weight in a gravitational field\\ \hline
+proletarian.n.01 & worker.n.01 & 0.328371898491 & a person who works at a specific occupation\\ \hline
+philosophy.n.02 & political orientation.n.01 & 0.31307622756 & an orientation that characterizes the thinking of a group or nation\\ \hline
+toilet.n.04 & trade.n.02 & 0.312879932381 & the skilled practice of a practical occupation\\ \hline
+theory.n.01 & political orientation.n.01 & 0.294463460062 & an orientation that characterizes the thinking of a group or nation\\ \hline
+practice.n.03 & motion.n.03 & 0.291680639247 & a change of position that does not entail a change of location\\ \hline
+lion.n.01 & worker.n.01 & 0.286073258452 & a person who works at a specific occupation\\ \hline
+strategy.n.02 & political orientation.n.01 & 0.264762834975 & an orientation that characterizes the thinking of a group or nation\\ \hline
+materialism.n.02 & political orientation.n.01 & 0.25040844726 & an orientation that characterizes the thinking of a group or nation\\ \hline
+hair.n.01 & worker.n.01 & 0.248092928538 & a person who works at a specific occupation\\ \hline
+revolution.n.01 & motion.n.03 & 0.242033306584 & a change of position that does not entail a change of location\\ \hline
+idealism.n.01 & political orientation.n.01 & 0.240750703939 & an orientation that characterizes the thinking of a group or nation\\ \hline
 \end{tabular}

### 2014-03-01 paper/analysis_the_state_and_revolution.tex
add graph that compares each sense against each other. add definition to top senses tables

@@
     \begin{center}
-      \begin{tabular}{ | l | l | l |}
+      \begin{tabular}{ | l | l | l | l |}
         \hline
-        Choosen Sensens & Closest Top Sense & similarity  \\ \hline
-\multicolumn{3}{|c|}{The State and Revolution - path similarity} \\ \hline
-revolution.n.01 & revolution.n.01 & 1.0 \\ \hline
-imperialism.n.02 & communism.n.02 & 0.333333333333 \\ \hline
-proletarian.n.01 & peer.n.01 & 0.25 \\ \hline
-practice.n.03 & work.n.01 & 0.2 \\ \hline
-toilet.n.04 & work.n.01 & 0.166666666667 \\ \hline
-war.n.01 & work.n.01 & 0.166666666667 \\ \hline
-money.n.01 & phase.n.01 & 0.125 \\ \hline
-philosophy.n.02 & law.n.04 & 0.125 \\ \hline
-materialism.n.02 & law.n.04 & 0.125 \\ \hline
-strategy.n.02 & law.n.04 & 0.125 \\ \hline
-idealism.n.01 & law.n.04 & 0.125 \\ \hline
-capitalism.n.01 & democracy.n.02 & 0.125 \\ \hline
-hair.n.01 & peer.n.01 & 0.111111111111 \\ \hline
-theory.n.01 & experience.n.03 & 0.1 \\ \hline
-television receiver.n.01 & peer.n.01 & 0.0833333333333 \\ \hline
-car.n.01 & peer.n.01 & 0.0833333333333 \\ \hline
-lion.n.01 & peer.n.01 & 0.0833333333333 \\ \hline
-sugar.n.01 & peer.n.01 & 0.0833333333333 \\ \hline
-\multicolumn{3}{|c|}{The State and Revolution - lch similarity} \\ \hline
-revolution.n.01 & revolution.n.01 & 3.63758615973 \\ \hline
-imperialism.n.02 & communism.n.02 & 2.53897387106 \\ \hline
-proletarian.n.01 & peer.n.01 & 2.25129179861 \\ \hline
-practice.n.03 & work.n.01 & 2.02814824729 \\ \hline
-toilet.n.04 & work.n.01 & 1.8458266905 \\ \hline
-war.n.01 & work.n.01 & 1.8458266905 \\ \hline
-money.n.01 & phase.n.01 & 1.55814461805 \\ \hline
-philosophy.n.02 & law.n.04 & 1.55814461805 \\ \hline
-materialism.n.02 & law.n.04 & 1.55814461805 \\ \hline
-strategy.n.02 & law.n.04 & 1.55814461805 \\ \hline
-idealism.n.01 & law.n.04 & 1.55814461805 \\ \hline
-capitalism.n.01 & democracy.n.02 & 1.55814461805 \\ \hline
-hair.n.01 & peer.n.01 & 1.44036158239 \\ \hline
-theory.n.01 & experience.n.03 & 1.33500106673 \\ \hline
-television receiver.n.01 & peer.n.01 & 1.15267950994 \\ \hline
-car.n.01 & peer.n.01 & 1.15267950994 \\ \hline
-lion.n.01 & peer.n.01 & 1.15267950994 \\ \hline
-sugar.n.01 & peer.n.01 & 1.15267950994 \\ \hline
-\multicolumn{3}{|c|}{The State and Revolution - res similarity} \\ \hline
-revolution.n.01 & revolution.n.01 & 10.3880624692 \\ \hline
-imperialism.n.02 & communism.n.02 & 8.60196873746 \\ \hline
-philosophy.n.02 & law.n.04 & 3.29228159341 \\ \hline
-materialism.n.02 & law.n.04 & 3.29228159341 \\ \hline
-strategy.n.02 & law.n.04 & 3.29228159341 \\ \hline
-idealism.n.01 & law.n.04 & 3.29228159341 \\ \hline
-toilet.n.04 & work.n.01 & 3.14352023311 \\ \hline
-capitalism.n.01 & club.n.02 & 2.85529368615 \\ \hline
-money.n.01 & phase.n.01 & 2.69110280536 \\ \hline
-theory.n.01 & law.n.04 & 2.64452085446 \\ \hline
-proletarian.n.01 & engels.n.01 & 2.33354524374 \\ \hline
-war.n.01 & work.n.01 & 2.33223775508 \\ \hline
-practice.n.03 & work.n.01 & 2.33223775508 \\ \hline
-lion.n.01 & engels.n.01 & 2.22415047123 \\ \hline
-television receiver.n.01 & engels.n.01 & 1.53183374322 \\ \hline
-car.n.01 & engels.n.01 & 1.53183374322 \\ \hline
-hair.n.01 & engels.n.01 & 1.53183374322 \\ \hline
-sugar.n.01 & engels.n.01 & 0.801759114954 \\ \hline
-\multicolumn{3}{|c|}{The State and Revolution - jcn similarity} \\ \hline
-revolution.n.01 & revolution.n.01 & 1e+300 \\ \hline
-imperialism.n.02 & communism.n.02 & 0.14975874591 \\ \hline
-war.n.01 & work.n.01 & 0.119881984187 \\ \hline
-philosophy.n.02 & law.n.04 & 0.103411969458 \\ \hline
-practice.n.03 & work.n.01 & 0.103154641506 \\ \hline
-toilet.n.04 & work.n.01 & 0.0985118809398 \\ \hline
-money.n.01 & phase.n.01 & 0.0916158054473 \\ \hline
-theory.n.01 & work.n.01 & 0.0910758552239 \\ \hline
-car.n.01 & peer.n.01 & 0.0887294617483 \\ \hline
-hair.n.01 & peer.n.01 & 0.0868826421077 \\ \hline
-proletarian.n.01 & peer.n.01 & 0.0849595683478 \\ \hline
-strategy.n.02 & law.n.04 & 0.07841412673 \\ \hline
-lion.n.01 & peer.n.01 & 0.0750424463326 \\ \hline
-television receiver.n.01 & peer.n.01 & 0.0731074093034 \\ \hline
-capitalism.n.01 & club.n.02 & 0.0729022081709 \\ \hline
-materialism.n.02 & law.n.04 & 0.0719531280061 \\ \hline
-idealism.n.01 & law.n.04 & 0.0678185221973 \\ \hline
-sugar.n.01 & work.n.01 & 0.0625959407953 \\ \hline
-\multicolumn{3}{|c|}{The State and Revolution - lin similarity} \\ \hline
-revolution.n.01 & revolution.n.01 & 1.0 \\ \hline
-imperialism.n.02 & communism.n.02 & 0.720392353354 \\ \hline
-philosophy.n.02 & law.n.04 & 0.405088626962 \\ \hline
-toilet.n.04 & work.n.01 & 0.382467580972 \\ \hline
-war.n.01 & work.n.01 & 0.35863993877 \\ \hline
-strategy.n.02 & law.n.04 & 0.340509805473 \\ \hline
-money.n.01 & phase.n.01 & 0.330250297796 \\ \hline
-practice.n.03 & work.n.01 & 0.324854541172 \\ \hline
-materialism.n.02 & law.n.04 & 0.321472637881 \\ \hline
-idealism.n.01 & law.n.04 & 0.308702564543 \\ \hline
-theory.n.01 & law.n.04 & 0.305328480717 \\ \hline
-capitalism.n.01 & club.n.02 & 0.29394209418 \\ \hline
-proletarian.n.01 & peer.n.01 & 0.28393127113 \\ \hline
-lion.n.01 & peer.n.01 & 0.250268807542 \\ \hline
-car.n.01 & peer.n.01 & 0.213736072979 \\ \hline
-hair.n.01 & peer.n.01 & 0.210222579299 \\ \hline
-television receiver.n.01 & peer.n.01 & 0.182991045418 \\ \hline
-sugar.n.01 & peer.n.01 & 0.0895207954547 \\ \hline
+        Choosen Sensens & Closest Top Sense & similarity & Top Sense Gloss \\ \hline
+\multicolumn{4}{|c|}{The State and Revolution - path similarity} \\ \hline
+revolution.n.01 & revolution.n.01 & 1.0 & a drastic and far-reaching change in ways of thinking and behaving\\ \hline
+imperialism.n.02 & communism.n.02 & 0.333333333333 & a political theory favoring collectivism in a classless society\\ \hline
+proletarian.n.01 & peer.n.01 & 0.25 & a person who is of equal standing with another in a group\\ \hline
+practice.n.03 & work.n.01 & 0.2 & activity directed toward making or doing something\\ \hline
+toilet.n.04 & work.n.01 & 0.166666666667 & activity directed toward making or doing something\\ \hline
+war.n.01 & work.n.01 & 0.166666666667 & activity directed toward making or doing something\\ \hline
+money.n.01 & phase.n.01 & 0.125 & any distinct time period in a sequence of events\\ \hline
+philosophy.n.02 & law.n.04 & 0.125 & a generalization that describes recurring facts or events in nature\\ \hline
+materialism.n.02 & law.n.04 & 0.125 & a generalization that describes recurring facts or events in nature\\ \hline
+strategy.n.02 & law.n.04 & 0.125 & a generalization that describes recurring facts or events in nature\\ \hline
+idealism.n.01 & law.n.04 & 0.125 & a generalization that describes recurring facts or events in nature\\ \hline
+capitalism.n.01 & democracy.n.02 & 0.125 & a political system in which the supreme power lies in a body of citizens who can elect people to represent them\\ \hline
+hair.n.01 & peer.n.01 & 0.111111111111 & a person who is of equal standing with another in a group\\ \hline
+theory.n.01 & experience.n.03 & 0.1 & an event as apprehended\\ \hline
+television receiver.n.01 & peer.n.01 & 0.0833333333333 & a person who is of equal standing with another in a group\\ \hline
+car.n.01 & peer.n.01 & 0.0833333333333 & a person who is of equal standing with another in a group\\ \hline
+lion.n.01 & peer.n.01 & 0.0833333333333 & a person who is of equal standing with another in a group\\ \hline
+sugar.n.01 & peer.n.01 & 0.0833333333333 & a person who is of equal standing with another in a group\\ \hline
+\multicolumn{4}{|c|}{The State and Revolution - lch similarity} \\ \hline
+revolution.n.01 & revolution.n.01 & 3.63758615973 & a drastic and far-reaching change in ways of thinking and behaving\\ \hline
+imperialism.n.02 & communism.n.02 & 2.53897387106 & a political theory favoring collectivism in a classless society\\ \hline
+proletarian.n.01 & peer.n.01 & 2.25129179861 & a person who is of equal standing with another in a group\\ \hline
+practice.n.03 & work.n.01 & 2.02814824729 & activity directed toward making or doing something\\ \hline
+toilet.n.04 & work.n.01 & 1.8458266905 & activity directed toward making or doing something\\ \hline
+war.n.01 & work.n.01 & 1.8458266905 & activity directed toward making or doing something\\ \hline
+money.n.01 & phase.n.01 & 1.55814461805 & any distinct time period in a sequence of events\\ \hline
+philosophy.n.02 & law.n.04 & 1.55814461805 & a generalization that describes recurring facts or events in nature\\ \hline
+materialism.n.02 & law.n.04 & 1.55814461805 & a generalization that describes recurring facts or events in nature\\ \hline
+strategy.n.02 & law.n.04 & 1.55814461805 & a generalization that describes recurring facts or events in nature\\ \hline
+idealism.n.01 & law.n.04 & 1.55814461805 & a generalization that describes recurring facts or events in nature\\ \hline
+capitalism.n.01 & democracy.n.02 & 1.55814461805 & a political system in which the supreme power lies in a body of citizens who can elect people to represent them\\ \hline
+hair.n.01 & peer.n.01 & 1.44036158239 & a person who is of equal standing with another in a group\\ \hline
+theory.n.01 & experience.n.03 & 1.33500106673 & an event as apprehended\\ \hline
+television receiver.n.01 & peer.n.01 & 1.15267950994 & a person who is of equal standing with another in a group\\ \hline
+car.n.01 & peer.n.01 & 1.15267950994 & a person who is of equal standing with another in a group\\ \hline
+lion.n.01 & peer.n.01 & 1.15267950994 & a person who is of equal standing with another in a group\\ \hline
+sugar.n.01 & peer.n.01 & 1.15267950994 & a person who is of equal standing with another in a group\\ \hline
+\multicolumn{4}{|c|}{The State and Revolution - res similarity} \\ \hline
+revolution.n.01 & revolution.n.01 & 10.3880624692 & a drastic and far-reaching change in ways of thinking and behaving\\ \hline
+imperialism.n.02 & communism.n.02 & 8.60196873746 & a political theory favoring collectivism in a classless society\\ \hline
+philosophy.n.02 & law.n.04 & 3.29228159341 & a generalization that describes recurring facts or events in nature\\ \hline
+materialism.n.02 & law.n.04 & 3.29228159341 & a generalization that describes recurring facts or events in nature\\ \hline
+strategy.n.02 & law.n.04 & 3.29228159341 & a generalization that describes recurring facts or events in nature\\ \hline
+idealism.n.01 & law.n.04 & 3.29228159341 & a generalization that describes recurring facts or events in nature\\ \hline
+toilet.n.04 & work.n.01 & 3.14352023311 & activity directed toward making or doing something\\ \hline
+capitalism.n.01 & club.n.02 & 2.85529368615 & a formal association of people with similar interests\\ \hline
+money.n.01 & phase.n.01 & 2.69110280536 & any distinct time period in a sequence of events\\ \hline
+theory.n.01 & law.n.04 & 2.64452085446 & a generalization that describes recurring facts or events in nature\\ \hline
+proletarian.n.01 & engels.n.01 & 2.33354524374 & socialist who wrote the Communist Manifesto with Karl Marx in 1848 (1820-1895)\\ \hline
+war.n.01 & work.n.01 & 2.33223775508 & activity directed toward making or doing something\\ \hline
+practice.n.03 & work.n.01 & 2.33223775508 & activity directed toward making or doing something\\ \hline
+lion.n.01 & engels.n.01 & 2.22415047123 & socialist who wrote the Communist Manifesto with Karl Marx in 1848 (1820-1895)\\ \hline
+television receiver.n.01 & engels.n.01 & 1.53183374322 & socialist who wrote the Communist Manifesto with Karl Marx in 1848 (1820-1895)\\ \hline
+car.n.01 & engels.n.01 & 1.53183374322 & socialist who wrote the Communist Manifesto with Karl Marx in 1848 (1820-1895)\\ \hline
+hair.n.01 & engels.n.01 & 1.53183374322 & socialist who wrote the Communist Manifesto with Karl Marx in 1848 (1820-1895)\\ \hline
+sugar.n.01 & engels.n.01 & 0.801759114954 & socialist who wrote the Communist Manifesto with Karl Marx in 1848 (1820-1895)\\ \hline
+\multicolumn{4}{|c|}{The State and Revolution - jcn similarity} \\ \hline
+revolution.n.01 & revolution.n.01 & 1e+300 & a drastic and far-reaching change in ways of thinking and behaving\\ \hline
+imperialism.n.02 & communism.n.02 & 0.14975874591 & a political theory favoring collectivism in a classless society\\ \hline
+war.n.01 & work.n.01 & 0.119881984187 & activity directed toward making or doing something\\ \hline
+philosophy.n.02 & law.n.04 & 0.103411969458 & a generalization that describes recurring facts or events in nature\\ \hline
+practice.n.03 & work.n.01 & 0.103154641506 & activity directed toward making or doing something\\ \hline
+toilet.n.04 & work.n.01 & 0.0985118809398 & activity directed toward making or doing something\\ \hline
+money.n.01 & phase.n.01 & 0.0916158054473 & any distinct time period in a sequence of events\\ \hline
+theory.n.01 & work.n.01 & 0.0910758552239 & activity directed toward making or doing something\\ \hline
+car.n.01 & peer.n.01 & 0.0887294617483 & a person who is of equal standing with another in a group\\ \hline
+hair.n.01 & peer.n.01 & 0.0868826421077 & a person who is of equal standing with another in a group\\ \hline
+proletarian.n.01 & peer.n.01 & 0.0849595683478 & a person who is of equal standing with another in a group\\ \hline
+strategy.n.02 & law.n.04 & 0.07841412673 & a generalization that describes recurring facts or events in nature\\ \hline
+lion.n.01 & peer.n.01 & 0.0750424463326 & a person who is of equal standing with another in a group\\ \hline
+television receiver.n.01 & peer.n.01 & 0.0731074093034 & a person who is of equal standing with another in a group\\ \hline
+capitalism.n.01 & club.n.02 & 0.0729022081709 & a formal association of people with similar interests\\ \hline
+materialism.n.02 & law.n.04 & 0.0719531280061 & a generalization that describes recurring facts or events in nature\\ \hline
+idealism.n.01 & law.n.04 & 0.0678185221973 & a generalization that describes recurring facts or events in nature\\ \hline
+sugar.n.01 & work.n.01 & 0.0625959407953 & activity directed toward making or doing something\\ \hline
+\multicolumn{4}{|c|}{The State and Revolution - lin similarity} \\ \hline
+revolution.n.01 & revolution.n.01 & 1.0 & a drastic and far-reaching change in ways of thinking and behaving\\ \hline
+imperialism.n.02 & communism.n.02 & 0.720392353354 & a political theory favoring collectivism in a classless society\\ \hline
+philosophy.n.02 & law.n.04 & 0.405088626962 & a generalization that describes recurring facts or events in nature\\ \hline
+toilet.n.04 & work.n.01 & 0.382467580972 & activity directed toward making or doing something\\ \hline
+war.n.01 & work.n.01 & 0.35863993877 & activity directed toward making or doing something\\ \hline
+strategy.n.02 & law.n.04 & 0.340509805473 & a generalization that describes recurring facts or events in nature\\ \hline
+money.n.01 & phase.n.01 & 0.330250297796 & any distinct time period in a sequence of events\\ \hline
+practice.n.03 & work.n.01 & 0.324854541172 & activity directed toward making or doing something\\ \hline
+materialism.n.02 & law.n.04 & 0.321472637881 & a generalization that describes recurring facts or events in nature\\ \hline
+idealism.n.01 & law.n.04 & 0.308702564543 & a generalization that describes recurring facts or events in nature\\ \hline
+theory.n.01 & law.n.04 & 0.305328480717 & a generalization that describes recurring facts or events in nature\\ \hline
+capitalism.n.01 & club.n.02 & 0.29394209418 & a formal association of people with similar interests\\ \hline
+proletarian.n.01 & peer.n.01 & 0.28393127113 & a person who is of equal standing with another in a group\\ \hline
+lion.n.01 & peer.n.01 & 0.250268807542 & a person who is of equal standing with another in a group\\ \hline
+car.n.01 & peer.n.01 & 0.213736072979 & a person who is of equal standing with another in a group\\ \hline
+hair.n.01 & peer.n.01 & 0.210222579299 & a person who is of equal standing with another in a group\\ \hline
+television receiver.n.01 & peer.n.01 & 0.182991045418 & a person who is of equal standing with another in a group\\ \hline
+sugar.n.01 & peer.n.01 & 0.0895207954547 & a person who is of equal standing with another in a group\\ \hline
 \end{tabular}

### 2014-03-01 commands/top_senses_tables.py

@@ -1,15 +1,25 @@
 import string
 import logging
+from collections import defaultdict
+from random import random
+
+import networkx as nx
+from nltk.corpus import wordnet as wn
+import matplotlib.pyplot as plt
+from nltk.corpus import wordnet_ic
+
 
 from analyzers import similarity
-from interpreter import Document, wn
+from interpreter import Document
 from analyzers.document_analyzer import DocumentAnalyzer
 
 SIMILARITY_FUNCS = similarity.functions
 
 log = logging.getLogger('lenin')
 
-synsets = [wn.synset(word) for word in [
+CORPUS = wordnet_ic.ic('ic-brown.dat')
+
+SYNSETS = [wn.synset(word) for word in [
            "war.n.01",
            "capitalism.n.01",
            "theory.n.01",
@@ -29,6 +39,8 @@ synsets = [wn.synset(word) for word in [
            "sugar.n.01",
            "car.n.01"]]
 
+ANALYZERS = [DocumentAnalyzer(synsets=SYNSETS, similarity_function=sim_fun) for sim_fun in SIMILARITY_FUNCS]
+
 
 def default_document_list():
     state_and_revolution = Document.query.find({"name": {"$regex": "State and Revolution"}}).next()
@@ -38,9 +50,10 @@ def default_document_list():
     agrarian_programme = Document.query.find({"name": u'Lenin: The Agrarian Programme of Social-Democracy in the First Russian Revolution, 1905-1907'}).next()
     return [state_and_revolution, imperialism_capitalism, materialism_criticism, what_is_to_be_done, agrarian_programme]
 
+
 def clean_name(name):
-    name.replace(' ', '_').replace(':', '').replace(',', '').replace('.','_').replace('/','_').lower()
-    return name
+    return name.replace(' ', '_').replace(':', '').replace(',', '').replace('.', '_').replace('/', '_').lower()
+
 
 def create_top_sense_tables(doc_list):
     documents = doc_list
@@ -61,15 +74,15 @@ def create_top_sense_tables(doc_list):
         with open("paper/top_senses_%s.tex" % clean_name(document.name), "w") as tex_table:
             tex_table.write("""
     \\begin{center}
-      \\begin{tabular}{ | l | l | }
+      \\begin{tabular}{ | l | l | l | }
         \hline
-        \multicolumn{2}{|c|}{%s} \\\\ \hline
+        \multicolumn{3}{|c|}{%s} \\\\ \hline
[…]

### 2014-03-01 commands/top_senses_tables.py
some improvement on graphs. added against_to. compare against politics, economy and philosophy. also add graph that compares out chosen synsets

@@ -126,7 +126,7 @@ def create_analysis_tables(doc_list):
             analysis_output.write("""\end{tabular}\n\end{center}""")
 
 
-def create_graph_top_senses(doc_list):
+def create_graphs(doc_list):
     documents = doc_list
     if documents is None:
         documents = default_document_list()
@@ -142,7 +142,54 @@ def create_graph_top_senses(doc_list):
     for doc in documents:
         for sense in doc.top_senses():
             all_senses.append((sense, doc.name))
+    against_colors = ['r', 'b', 'g']
+    against_to = [wn.synset(word) for word in ["economy.n.01", "philosophy.n.02", "politics.n.01"]]
+    create_against_graph('phyl_eco_pol', documents, all_senses, against_to, distance_functions, against_colors)
 
+    against_to = SYNSETS
+
+    against_colors = [(random(), random(), random()) for _i in range(0, len(SYNSETS))]
+    create_against_graph('handpicked', documents, all_senses, against_to, distance_functions, against_colors)
+
+    create_graph_top_senses(documents, all_senses, distance_functions)
+
+
+def create_against_graph(file_prefix, documents, all_senses, against_to, distance_functions, against_colors):
+    doc_senses = defaultdict(list)
+    node_list_against_to = [sense.name for sense in against_to]
+
+    for sense, doc_name in all_senses:
+        #this is used for give colors that corresponds to each document
+        doc_senses[doc_name].append(sense.name)
+
+    for function_name, distance_function in distance_functions:
+        G = nx.Graph()
+        for sense, doc_name in all_senses:
+            G.add_node(sense.name)
+        for node_against_name in node_list_against_to:
+            G.add_node(node_against_name)
+
+        for sense_1, doc_name in all_senses:
+            for sense_2 in against_to:
+                if sense_1 != sense_2:
+                    G.add_edge(sense_1.name, sense_2.name, weight=distance_function(sense_1, sense_2))
+
+        pos = nx.spring_layout(G, iterations=50)
+        # lets put the colors for each doc
+        colors = [(random(), random(), random()) for _i in range(0, len(doc_senses.keys()))]
+        for index, doc_name in enumerate(doc_senses):
+            nx.draw_networkx_nodes(G, pos, node_size=60, linewidths=0, nodelist=doc_senses[doc_name], node_color=colors[index])
[…]

### 2014-03-02 commands/top_senses_tables.py
fix a bug: for edge weigth it was used similarity. however this wasn't correct since we wanted small number of weigth to represent how close are nodes (top senses) are

@@ -132,11 +132,11 @@ def create_graphs(doc_list):
         documents = default_document_list()
 
     distance_functions = [
-        ('lch', lambda sense_1, sense_2: wn.lch_similarity(sense_1, sense_2)),
-        ('lin', lambda sense_1, sense_2: wn.lin_similarity(sense_1, sense_2, CORPUS)),
-        ('res', lambda sense_1, sense_2: wn.res_similarity(sense_1, sense_2, CORPUS)),
-        ('jcn', lambda sense_1, sense_2: wn.jcn_similarity(sense_1, sense_2, CORPUS)),
-        ('path', lambda sense_1, sense_2: wn.path_similarity(sense_1, sense_2)),
+        (wn.lch_similarity(SYNSETS[0], SYNSETS[0]), 'lch', lambda sense_1, sense_2: wn.lch_similarity(sense_1, sense_2)),
+        (1.0, 'lin', lambda sense_1, sense_2: wn.lin_similarity(sense_1, sense_2, CORPUS)),
+        (10.636958516573292, 'res', lambda sense_1, sense_2: wn.res_similarity(sense_1, sense_2, CORPUS)),
+        (wn.jcn_similarity(SYNSETS[0], SYNSETS[0], CORPUS), 'jcn', lambda sense_1, sense_2: wn.jcn_similarity(sense_1, sense_2, CORPUS)),
+        (1.0, 'path', lambda sense_1, sense_2: wn.path_similarity(sense_1, sense_2)),
     ]
     all_senses = []
     for doc in documents:
@@ -162,7 +162,7 @@ def create_against_graph(file_prefix, documents, all_senses, against_to, distanc
         #this is used for give colors that corresponds to each document
         doc_senses[doc_name].append(sense.name)
 
-    for function_name, distance_function in distance_functions:
+    for max_value, function_name, distance_function in distance_functions:
         G = nx.Graph()
         for sense, doc_name in all_senses:
             G.add_node(sense.name)
@@ -172,7 +172,7 @@ def create_against_graph(file_prefix, documents, all_senses, against_to, distanc
         for sense_1, doc_name in all_senses:
             for sense_2 in against_to:
                 if sense_1 != sense_2:
-                    G.add_edge(sense_1.name, sense_2.name, weight=distance_function(sense_1, sense_2))
+                    G.add_edge(sense_1.name, sense_2.name, weight=max_value - distance_function(sense_1, sense_2))
 
         pos = nx.spring_layout(G, iterations=50)
         # lets put the colors for each doc
[…]

### 2014-03-02 paper/results.tex
add initial results to the paper

* Distancia a algunos conceptos de estado y revolución
% \input{analysis_the_state_and_revolution}

For each work we executed the algorithm and then we obtained five different similarities for the top senses.
We compared the similarity of top sense against each other and against a list handpicked synsets \ref{handpicked_synsets}

First we show the results obtained after the execution for some works , then we analyze the results of similarity.

\begin{table}[h!]
    \begin{center}
        \begin{tabular}{ | L{2cm} | L{5cm} |}
            \hline
            Synset & Gloss \\ \hline
            \multicolumn{2}{|c|}{Human handpicked concepts to compare against top senses} \\ \hline
war & the waging of armed conflict against an enemy \\ \hline
capitalism & an economic system based on private ownership of capital\\ \hline
theory & a well-substantiated explanation of some aspect of the natural world \\ \hline
toilet & the act of dressing and preparing yourself \\ \hline
imperialism & a political orientation that advocates imperial interests \\ \hline
proletarian & a member of the working class (not necessarily employed) \\ \hline
practice & translating an idea into action \\ \hline
revolution & a drastic and far-reaching change in ways of thinking and behaving \\ \hline
money & the most common medium of exchange; functions as legal tender \\ \hline
philosophy & the rational investigation of questions about existence and knowledge and ethics \\ \hline
idealism & (philosophy) the philosophical theory that ideas are the only reality \\ \hline
strategy & the branch of military science dealing with military command and the planning and conduct of a war \\ \hline
materialism & (philosophy) the philosophical theory that matter is the only reality \\ \hline
lion & large gregarious predatory feline of Africa and India having a tawny coat with a shaggy mane in the male \\ \hline
television_receiver. & an electronic device that receives television signals and displays them on a screen \\ \hline
hair & a covering for the body (or parts of it) consisting of a dense growth of threadlike structures (as on the human head); helps to prevent heat loss \\ \hline
sugar & a white crystalline carbohydrate used as a sweetener and preservative \\ \hline
car & a motor vehicle with four wheels; usually propelled by an internal combustion engine \\ \hline
            \multicolumn{2}{|c|}{Categories} \\ \hline
economy & the system of production and distribution and consumption \\ \hline
philosophy & the rational investigation of questions about existence and knowledge and ethics \\ \hline
politics & social relations involving intrigue to gain authority or power \\ \hline
        \end{tabular}
    \end{center}
    \label{table:handpicked_synsets}
    \caption{Caption test}
\end{table}

\begin{table}[h!]
    \begin{center}
        \begin{tabular}{ | L{2cm} | L{5cm} |}
            \hline
            Top Sense & Sense Detected \\ \hline
            \multicolumn{2}{|c|}{The State and Revolution} \\ \hline
    engels & socialist who wrote the Communist Manifesto with Karl Marx in 1848 (1820-1895) \\ \hline
    work & activity directed toward making or doing something \\ \hline
    club & a formal association of people with similar interests \\ \hline
    democracy & a political system in which the supreme power lies in a body of citizens who can elect people to represent them \\ \hline
            \multicolumn{2}{|c|}{MATERIALISM and EMPIRIO} \\ \hline
    physics & the science of matter and energy and their interactions \\ \hline
    sociable & a party of people assembled to promote sociability and communal activity \\ \hline
    kant & influential German idealist philosopher (1724-1804) \\ \hline
    time & the continuum of experience in which events pass from the future through the present to the past \\ \hline
    space & an empty area (usually bounded in some way between things) \\ \hline
            \multicolumn{2}{|c|}{Imperialism, the highest stage of capitalism} \\ \hline
 enterprise & an organization created for business ventures \\ \hline
 depository\_financial\_institution & a financial institution that accepts deposits and channels the money into lending activities \\ \hline
 depository\_financial\_institution & a financial institution that accepts deposits and channels the money into lending activities \\ \hline
 imperialism & a policy of extending your rule over foreign countries \\ \hline
 universe & everything that exists anywhere \\ \hline
        \end{tabular}
    \end{center}
    \label{table:top_senses}
    \caption{Caption test}
\end{table}

In the next Table we can observe the best top sense matches for our handpicked synsets.
\input{analysis_the_state_and_revolution}

After a careful analysis of out results we found some problems with pronouns that we show in \ref{table:pronouns}
We think that this mismatch could be a cause of our Lesk algorithm modification to check against to context words directly.

\begin{table}[h!]
    \begin{center}
        \begin{tabular}{ | L{3cm} | L{1cm} | L{3cm} |}
            \hline
            Text &  Top Sense & Sense Detected \\ \hline
            \multicolumn{3}{|c|}{Strange detections} \\ \hline
    The Agrarian Programme & marx & United States comedian; one of four brothers who made motion pictures together (1901-1979) \\ \hline

    The State and Revolution & bernstein & United States conductor and composer (1918-1990) \\ \hline
        \end{tabular}
    \end{center}
    \caption{Caption test}
    \label{table:pronouns}
\end{table}

One interesting thing to observe is the distance between the all the top senses of all texts.

\begin{figure}[h!]
    \caption{Top senses lch distance of all Lenin works.}
    \centering
    \includegraphics[width=0.5\textwidth]{lch_sim_graph.png}
    \label{fig:lch_sim_graph}
\end{figure}

Now our question is. how far are the top senses from the concepts we wanted to compare to?
To answer that question we find interesting to study what happens if we add pylosophical, political and economic senses in out graph and calculate form those synsets the similarity to top senses.

\begin{figure}[h!]
    \caption{Top senses against economy philosophy and politics using LCH similarity}
    \centering
    \includegraphics[width=0.5\textwidth]{phyl_eco_pol_lch_sim_graph.png}
    \label{fig:phyl_eco_pol_lch_sim_graph}
\end{figure}

At ~\ref{fig:phyl_eco_pol_lch_sim_graph} we notw that the synsets phylosophy, economic and politics are very close to each other

We tried several similarity measures and most of them gave that phylosophy, economic and politics are similar synsets.
However when we tried JCN similarity we found that those synsets were far enough from each other \ref{fig:phyl_eco_pol_jcn_sim_graph}. We can\'t get any concise results since nodes in \ref{fig:phyl_eco_pol_jcn_sim_graph} seems to be very dispersed.

\begin{figure}[h!]
    \caption{Top senses against economy philosophy and politics using JCN similarity}
    \centering
    \includegraphics[width=0.5\textwidth]{phyl_eco_pol_jcn_sim_graph.png}
    \label{fig:phyl_eco_pol_jcn_sim_graph}
\end{figure}

FALTAN LOS GRAFICOS DE LOS HANDPICKED

### 2014-03-02 commands/top_senses_tables.py

@@ -116,13 +116,14 @@ def create_analysis_tables(doc_list):
         with open('paper/analysis_%s.tex' % (clean_name(doc_name)), 'w') as analysis_output:
             analysis_output.write("""
     \\begin{center}
-      \\begin{tabular}{ | l | l | l | l |}
+      \\begin{tabular}{ | l | l | l |}
         \hline
-        Choosen Sensens & Closest Top Sense & similarity & Top Sense Gloss \\\\ \hline\n""")
+        Choosen Sensens & Closest Top Sense & similarity  \\\\ \hline\n""")
             for key in full_analysis.keys():
-                analysis_output.write("\multicolumn{4}{|c|}{%s - %s} \\\\ \hline\n" % (doc.name[:30], key.replace('_', ' ')))
+                analysis_output.write("\multicolumn{3}{|c|}{%s - %s} \\\\ \hline\n" % (doc.name[:30], key.replace('_', ' ')))
                 for value in full_analysis[key]:
-                    analysis_output.write("%s & %s & %s & %s\\\\ \hline\n" % (value[0].replace('_', ' '), value[2].replace('_', ' '), value[1].replace('_', ' '), value[3].replace('_', ' ')))
+                    analysis_output.write("%s & %s & %s\\\\ \hline\n" % (value[0].replace('_', ' '), value[2].replace('_', ' '), value[1].replace('_', ' ')))
+                    #analysis_output.write("%s & %s & %s & %s\\\\ \hline\n" % (value[0].replace('_', ' '), value[2].replace('_', ' '), value[1].replace('_', ' '), value[3].replace('_', ' ')))
             analysis_output.write("""\end{tabular}\n\end{center}""")
 
 
@@ -218,5 +219,5 @@ def create_graph_top_senses(documents, all_senses, distance_functions):
 
 def create_tables(doc_list):
 #    create_top_sense_tables(doc_list)
-#    create_analysis_tables(doc_list)
-    create_graphs(doc_list)
+    create_analysis_tables(doc_list)
+#    create_graphs(doc_list)

### 2014-03-08 paper/handpicked_table.tex
add handpicked table

--- 2014-03-02 paper/results.tex
@@
-* Distancia a algunos conceptos de estado y revolución
-% \input{analysis_the_state_and_revolution}
-
-For each work we executed the algorithm and then we obtained five different similarities for the top senses.
-We compared the similarity of top sense against each other and against a list handpicked synsets \ref{handpicked_synsets}
-
-First we show the results obtained after the execution for some works , then we analyze the results of similarity.
-
-\begin{table}[h!]
-    \begin{center}
 \begin{tabular}{ | L{2cm} | L{5cm} |}
@@
             car & a motor vehicle with four wheels; usually propelled by an internal combustion engine \\ \hline
-            \multicolumn{2}{|c|}{Categories} \\ \hline
-economy & the system of production and distribution and consumption \\ \hline
-philosophy & the rational investigation of questions about existence and knowledge and ethics \\ \hline
-politics & social relations involving intrigue to gain authority or power \\ \hline
 \end{tabular}
-    \end{center}
-    \label{table:handpicked_synsets}
-    \caption{Caption test}
-\end{table}
-
-\begin{table}[h!]
-    \begin{center}
-        \begin{tabular}{ | L{2cm} | L{5cm} |}
-            \hline
-            Top Sense & Sense Detected \\ \hline
-            \multicolumn{2}{|c|}{The State and Revolution} \\ \hline
-    engels & socialist who wrote the Communist Manifesto with Karl Marx in 1848 (1820-1895) \\ \hline
-    work & activity directed toward making or doing something \\ \hline
-    club & a formal association of people with similar interests \\ \hline
-    democracy & a political system in which the supreme power lies in a body of citizens who can elect people to represent them \\ \hline
-            \multicolumn{2}{|c|}{MATERIALISM and EMPIRIO} \\ \hline
-    physics & the science of matter and energy and their interactions \\ \hline
-    sociable & a party of people assembled to promote sociability and communal activity \\ \hline
-    kant & influential German idealist philosopher (1724-1804) \\ \hline
-    time & the continuum of experience in which events pass from the future through the present to the past \\ \hline
-    space & an empty area (usually bounded in some way between things) \\ \hline
-            \multicolumn{2}{|c|}{Imperialism, the highest stage of capitalism} \\ \hline
- enterprise & an organization created for business ventures \\ \hline
- depository\_financial\_institution & a financial institution that accepts deposits and channels the money into lending activities \\ \hline
- depository\_financial\_institution & a financial institution that accepts deposits and channels the money into lending activities \\ \hline
- imperialism & a policy of extending your rule over foreign countries \\ \hline
- universe & everything that exists anywhere \\ \hline
-        \end{tabular}
-    \end{center}
-    \label{table:top_senses}
-    \caption{Caption test}
-\end{table}
-
-In the next Table we can observe the best top sense matches for our handpicked synsets.
-\input{analysis_the_state_and_revolution}
-
-After a careful analysis of out results we found some problems with pronouns that we show in \ref{table:pronouns}
-We think that this mismatch could be a cause of our Lesk algorithm modification to check against to context words directly.
-
-\begin{table}[h!]
-    \begin{center}
-        \begin{tabular}{ | L{3cm} | L{1cm} | L{3cm} |}
-            \hline
-            Text &  Top Sense & Sense Detected \\ \hline
-            \multicolumn{3}{|c|}{Strange detections} \\ \hline
-    The Agrarian Programme & marx & United States comedian; one of four brothers who made motion pictures together (1901-1979) \\ \hline
-
-    The State and Revolution & bernstein & United States conductor and composer (1918-1990) \\ \hline
-        \end{tabular}
-    \end{center}
-    \caption{Caption test}
-    \label{table:pronouns}
-\end{table}
-
-One interesting thing to observe is the distance between the all the top senses of all texts.
-
-\begin{figure}[h!]
-    \caption{Top senses lch distance of all Lenin works.}
-    \centering
-    \includegraphics[width=0.5\textwidth]{lch_sim_graph.png}
-    \label{fig:lch_sim_graph}
-\end{figure}
-
-Now our question is. how far are the top senses from the concepts we wanted to compare to?
-To answer that question we find interesting to study what happens if we add pylosophical, political and economic senses in out graph and calculate form those synsets the similarity to top senses.
-
-\begin{figure}[h!]
-    \caption{Top senses against economy philosophy and politics using LCH similarity}
-    \centering
-    \includegraphics[width=0.5\textwidth]{phyl_eco_pol_lch_sim_graph.png}
-    \label{fig:phyl_eco_pol_lch_sim_graph}
-\end{figure}
-
-At ~\ref{fig:phyl_eco_pol_lch_sim_graph} we notw that the synsets phylosophy, economic and politics are very close to each other
-
-We tried several similarity measures and most of them gave that phylosophy, economic and politics are similar synsets.
-However when we tried JCN similarity we found that those synsets were far enough from each other \ref{fig:phyl_eco_pol_jcn_sim_graph}.
-We can\'t get any concise results since nodes in \ref{fig:phyl_eco_pol_jcn_sim_graph} seems to be very dispersed.
-
-\begin{figure}[h!]
-    \caption{Top senses against economy philosophy and politics using JCN similarity}
-    \centering
-    \includegraphics[width=0.5\textwidth]{phyl_eco_pol_jcn_sim_graph.png}
-    \label{fig:phyl_eco_pol_jcn_sim_graph}
-\end{figure}
-
-FALTAN LOS GRAFICOS DE LOS HANDPICKED

### 2014-03-15 paper/handpicked_table.tex
fix some spelling

@@
             lion & large gregarious predatory feline of Africa and India having a tawny coat with a shaggy mane in the male \\ \hline
-            television_receiver. & an electronic device that receives television signals and displays them on a screen \\ \hline
+            television\_receiver. & an electronic device that receives television signals and displays them on a screen \\ \hline
             hair & a covering for the body (or parts of it) consisting of a dense growth of threadlike structures (as on the human head); helps to prevent heat loss \\ \hline

### 2014-03-15 paper/refactor.tex
fix top senses tables
add initial results to the paper
fix some spelling

@@
 \selectlanguage{spanish}
+\usepackage{array}
+\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
 
@@
 
-But this ponderated set of top words has the problem of polysemy, tipical in the field of nlp.
+But this weighted set of top words has the problem of polysemy, typical in the field of nlp.
 Polysemy occurs when a term has more than one sense or meaning, for example: the term 'bank' can refer to a financial institution or to the land formation, thus, it is polysemic.
@@
 \section{Results}
-* Distancia a algunos conceptos de estado y revolución
-
+\input{results}
 \subsection{Top senses for selected works}
@@
 \appendix[All tables]
-\input{top_senses_the_state_and_revolution}
+% \input{top_senses_the_state_and_revolution}
+% \input{top_senses_lenin_imperialism_the_highest_stage_of_capitalism}
+% \input{top_senses_lenin_materialism_and_empirio-criticism}
+% \input{top_senses_lenin_the_agrarian_programme_of_social-democracy_in_the_first_russian_revolution_1905-1907}
+% \input{top_senses_lenin_what_is_to_be_done?}
+
 \appendix[Entropy of a word in a text]

### 2014-03-15 paper/wsd.tex
fix some spelling

@@
 Word sense disambiguation involves the association of a given word in a text or discourse with a definition or meaning.
-We found that sense disambiguation was necessary to solve in one or another level the problem of polysemy.
 
@@
 Basically Lesk is based on the idea that words that co–occur in a sentence are being used to refer to the same topic.
-The Lesk alghorithm takes the word definition or gloss that we want to disambiguate and it compares it gloss against the glosses of the other words in the context.
+The Lesk algorithm takes the word definition or gloss that we want to disambiguate and it compares it gloss against the glosses of the other words in the context.
 Then a word is assigned that sense whose gloss shares the largest number of words in common with the glosses of the other words.
-This algorhitm suffers the problem that relies on the word definition and definitions usually uses as less words as possible.
+This algorithm suffers the problem that relies on the word definition and definitions usually uses as less words as possible.
 Not only that sometimes two different words, but related ones, uses no words in common in their definitions.
@@
 We added to Lesk word stems, hypernyms, hyponyms.
-For the problem of short word description we modified the algorthim to use the definition of the word to disambiguate and to compare it against the context words directly.
+For the problem of short word description we modified the algorithm to use the definition of the word to disambiguate and to compare it against the context words directly.
 Finally our algorithm chooses the best synset from wordnet based on the context words.

### 2014-03-15 paper/handpicked_table.tex
add top senses tables with definitions

--- 2014-03-08 paper/handpicked_table.tex
@@
-\begin{tabular}{ | L{2cm} | L{5cm} |}
-    \hline
-    Synset & Gloss \\ \hline
-    \multicolumn{2}{|c|}{Human handpicked concepts to compare against top senses} \\ \hline
-            war & the waging of armed conflict against an enemy \\ \hline
-            capitalism & an economic system based on private ownership of capital\\ \hline
-            theory & a well-substantiated explanation of some aspect of the natural world \\ \hline
-            toilet & the act of dressing and preparing yourself \\ \hline
-            imperialism & a political orientation that advocates imperial interests \\ \hline
-            proletarian & a member of the working class (not necessarily employed) \\ \hline
-            practice & translating an idea into action \\ \hline
-            revolution & a drastic and far-reaching change in ways of thinking and behaving \\ \hline
-            money & the most common medium of exchange; functions as legal tender \\ \hline
-            philosophy & the rational investigation of questions about existence and knowledge and ethics \\ \hline
-            idealism & (philosophy) the philosophical theory that ideas are the only reality \\ \hline
-            strategy & the branch of military science dealing with military command and the planning and conduct of a war \\ \hline
-            materialism & (philosophy) the philosophical theory that matter is the only reality \\ \hline
-            lion & large gregarious predatory feline of Africa and India having a tawny coat with a shaggy mane in the male \\ \hline
-            television_receiver. & an electronic device that receives television signals and displays them on a screen \\ \hline
-            hair & a covering for the body (or parts of it) consisting of a dense growth of threadlike structures (as on the human head); helps to prevent heat loss \\ \hline
-            sugar & a white crystalline carbohydrate used as a sweetener and preservative \\ \hline
-            car & a motor vehicle with four wheels; usually propelled by an internal combustion engine \\ \hline
+Handpicked concepts to compare against top senses\\
+
+\begin{tabular}{ p{2cm} p{5cm} }
+    \toprule
+    Synset & Gloss \\
+    \midrule
+            war & the waging of armed conflict against an enemy \\
+            capitalism & an economic system based on private ownership of capital\\
+            theory & a well-substantiated explanation of some aspect of the natural world \\
+            toilet & the act of dressing and preparing yourself \\
+            imperialism & a political orientation that advocates imperial interests \\
+            proletarian & a member of the working class (not necessarily employed) \\
+            practice & translating an idea into action \\
+            revolution & a drastic and far-reaching change in ways of thinking and behaving \\
+            money & the most common medium of exchange; functions as legal tender \\
+            philosophy & the rational investigation of questions about existence and knowledge and ethics \\
+            idealism & (philosophy) the philosophical theory that ideas are the only reality \\
+            strategy & the branch of military science dealing with military command and the planning and conduct of a war \\
+            materialism & (philosophy) the philosophical theory that matter is the only reality \\
+            lion & large gregarious predatory f of Africa and India having a tawny coat with a shaggy mane in the male \\
+            television\_receiver. & an electronic device that receives television signals and displays them on a screen \\
+            hair & a covering for the body (or parts of it) consisting of a dense growth of threadlike structures (as on the human head); helps to prevent heat loss \\
+            sugar & a white crysta carbohydrate used as a sweetener and preservative \\
+            car & a motor vehicle with four wheels; usually propelled by an internal combustion engine \\
+
+    \bottomrule
 \end{tabular}

### 2014-03-15 paper/results.tex
add top senses tables with definitions

@@
-* Distancia a algunos conceptos de estado y revolución
-% \input{analysis_the_state_and_revolution}
+\begin{tabular}{p{1.1cm} p{1.1cm} p{1.1cm} p{1.5cm} p{1.5cm}}
+        \toprule
+        Work 1 & Work 2 & Work 3 & Work 4 & Work 5 \\
+%        \multicolumn{2}{c}{Work 1} & \multicolumn{2}{c}{Work 2} & \multicolumn{2}{c}{Work 3} & \multicolumn{2}{c}{Work 4} & \multicolumn{2}{c}{Work 5} \\
+        \midrule
+        marx & enterprise & physics & local\_anesthetic & rent \\
+        revolution & depository\_financial\_institution & sociable & organization  & land \\
+        plant & imperialism & space & marriage & peasant \\
+        engels & universe & time  & criticism & capital \\
+        club & million & berkeley & revolutionist & revolution \\
+        power & colony & truth & freedom & marx \\
+        party & colonial &  aim & newspaper & people \\
+        sociable &  product & sensation & worker & nationalization \\
+        experience & penny & experience & consciousness & restoration \\
+        bernstein & company  & engels & newspaper & right \\
+        question & capitalist & motion & businessperson & private  \\
+        equality & monopoly & marx & mass & farming \\
+        phase & area &  book & motion & free \\
+        commune & policy &  plant & german  & central \\
+        one &  power & general & goverment & land \\
+        democracy & banks &  helmholtz & political\_orientation & capitalism \\
+        class &  worker & neccesity & party & democracy \\
+        law &  imperialist & law & secret & landlord \\
+        communism & company & sensation & working & farming \\
+        peer & boards & energy & class & agency \\
+        \bottomrule
+    \end{tabular}
+\newline
+%aWork1 : The State and Revolution
+%work2: Lenin: Imperialism, the Highest Stage of Capitalism
+%Work3: Lenin: MATERIALISM and EMPIRIO-CRITICISM
+%Work4: Lenin: What Is To Be Done?
+%wotk5: Lenin: The Agrarian Programme of Social-Democracy in the First Russian Revolution, 1905-1907
 
-For each work we executed the algorithm and then we obtained five different similarities for the top senses.
-We compared the similarity of top sense against each other and against a list handpicked synsets \ref{handpicked_synsets}
+    \begin{tabular}{ p{2cm} p{2cm} p{3cm}}
+    \toprule
+    Text &  Top Sense & Sense Detected \\
+    \midrule
+The Agrarian Programme & marx & United States comedian; one of four brothers who made motion pictures together (1901-1979) \\
+    \midrule
+The State and Revolution & bernstein & United States conductor and composer (1918-1990) \\
+    \bottomrule
+\end{tabular}
 
-First we show the results obtained after the execution for some works , then we analyze the results of similarity.
-
-\begin{table}[h!]
-    \begin{center}
-        \begin{tabular}{ | L{2cm} | L{5cm} |}
-            \hline
-            Synset & Gloss \\ \hline
-            \multicolumn{2}{|c|}{Human handpicked concepts to compare against top senses} \\ \hline
-war & the waging of armed conflict against an enemy \\ \hline
-capitalism & an economic system based on private ownership of capital\\ \hline
-theory & a well-substantiated explanation of some aspect of the natural world \\ \hline
-toilet & the act of dressing and preparing yourself \\ \hline
-imperialism & a political orientation that advocates imperial interests \\ \hline
-proletarian & a member of the working class (not necessarily employed) \\ \hline
-practice & translating an idea into action \\ \hline
-revolution & a drastic and far-reaching change in ways of thinking and behaving \\ \hline
-money & the most common medium of exchange; functions as legal tender \\ \hline
-philosophy & the rational investigation of questions about existence and knowledge and ethics \\ \hline
-idealism & (philosophy) the philosophical theory that ideas are the only reality \\ \hline
-strategy & the branch of military science dealing with military command and the planning and conduct of a war \\ \hline
-materialism & (philosophy) the philosophical theory that matter is the only reality \\ \hline
-lion & large gregarious predatory feline of Africa and India having a tawny coat with a shaggy mane in the male \\ \hline
-television_receiver. & an electronic device that receives television signals and displays them on a screen \\ \hline
-hair & a covering for the body (or parts of it) consisting of a dense growth of threadlike structures (as on the human head); helps to prevent heat loss \\ \hline
-sugar & a white crystalline carbohydrate used as a sweetener and preservative \\ \hline
-car & a motor vehicle with four wheels; usually propelled by an internal combustion engine \\ \hline
-            \multicolumn{2}{|c|}{Categories} \\ \hline
-economy & the system of production and distribution and consumption \\ \hline
-philosophy & the rational investigation of questions about existence and knowledge and ethics \\ \hline
-politics & social relations involving intrigue to gain authority or power \\ \hline
-        \end{tabular}
-    \end{center}
-    \label{table:handpicked_synsets}
-    \caption{Caption test}
-\end{table}
-
-\begin{table}[h!]
-    \begin{center}
-        \begin{tabular}{ | L{2cm} | L{5cm} |}
-            \hline
-            Top Sense & Sense Detected \\ \hline
-            \multicolumn{2}{|c|}{The State and Revolution} \\ \hline
-    engels & socialist who wrote the Communist Manifesto with Karl Marx in 1848 (1820-1895) \\ \hline
-    work & activity directed toward making or doing something \\ \hline
-    club & a formal association of people with similar interests \\ \hline
-    democracy & a political system in which the supreme power lies in a body of citizens who can elect people to represent them \\ \hline
-            \multicolumn{2}{|c|}{MATERIALISM and EMPIRIO} \\ \hline
-    physics & the science of matter and energy and their interactions \\ \hline
-    sociable & a party of people assembled to promote sociability and communal activity \\ \hline
-    kant & influential German idealist philosopher (1724-1804) \\ \hline
-    time & the continuum of experience in which events pass from the future through the present to the past \\ \hline
-    space & an empty area (usually bounded in some way between things) \\ \hline
-            \multicolumn{2}{|c|}{Imperialism, the highest stage of capitalism} \\ \hline
- enterprise & an organization created for business ventures \\ \hline
- depository\_financial\_institution & a financial institution that accepts deposits and channels the money into lending activities \\ \hline
- depository\_financial\_institution & a financial institution that accepts deposits and channels the money into lending activities \\ \hline
- imperialism & a policy of extending your rule over foreign countries \\ \hline
- universe & everything that exists anywhere \\ \hline
-        \end{tabular}
-    \end{center}
-    \label{table:top_senses}
-    \caption{Caption test}
-\end{table}
-
-In the next Table we can observe the best top sense matches for our handpicked synsets.
-\input{analysis_the_state_and_revolution}
-
-After a careful analysis of out results we found some problems with pronouns that we show in \ref{table:pronouns}
-We think that this mismatch could be a cause of our Lesk algorithm modification to check against to context words directly.
-
-\begin{table}[h!]
-    \begin{center}
-        \begin{tabular}{ | L{3cm} | L{1cm} | L{3cm} |}
-            \hline
-            Text &  Top Sense & Sense Detected \\ \hline
-            \multicolumn{3}{|c|}{Strange detections} \\ \hline
-    The Agrarian Programme & marx & United States comedian; one of four brothers who made motion pictures together (1901-1979) \\ \hline
-
-    The State and Revolution & bernstein & United States conductor and composer (1918-1990) \\ \hline
-        \end{tabular}
-    \end{center}
-    \caption{Caption test}
-    \label{table:pronouns}
-\end{table}
-
-One interesting thing to observe is the distance between the all the top senses of all texts.
-
-\begin{figure}[h!]
-    \caption{Top senses lch distance of all Lenin works.}
-    \centering
-    \includegraphics[width=0.5\textwidth]{lch_sim_graph.png}
-    \label{fig:lch_sim_graph}
-\end{figure}
-
-Now our question is. how far are the top senses from the concepts we wanted to compare to?
-To answer that question we find interesting to study what happens if we add pylosophical, political and economic senses in out graph and calculate form those synsets the similarity to top senses.
-
-\begin{figure}[h!]
-    \caption{Top senses against economy philosophy and politics using LCH similarity}
-    \centering
-    \includegraphics[width=0.5\textwidth]{phyl_eco_pol_lch_sim_graph.png}
-    \label{fig:phyl_eco_pol_lch_sim_graph}
-\end{figure}
-
-At ~\ref{fig:phyl_eco_pol_lch_sim_graph} we notw that the synsets phylosophy, economic and politics are very close to each other
-
-We tried several similarity measures and most of them gave that phylosophy, economic and politics are similar synsets.
-However when we tried JCN similarity we found that those synsets were far enough from each other \ref{fig:phyl_eco_pol_jcn_sim_graph}.
-We can\'t get any concise results since nodes in \ref{fig:phyl_eco_pol_jcn_sim_graph} seems to be very dispersed.
-
-\begin{figure}[h!]
-    \caption{Top senses against economy philosophy and politics using JCN similarity}
-    \centering
-    \includegraphics[width=0.5\textwidth]{phyl_eco_pol_jcn_sim_graph.png}
-    \label{fig:phyl_eco_pol_jcn_sim_graph}
-\end{figure}
-
-FALTAN LOS GRAFICOS DE LOS HANDPICKED
+\input{top_senses_definitions}

### 2014-03-15 paper/top_senses_definitions.tex
add top senses tables with definitions

%\begin{tabular}{ p{2cm} p{5cm} }
\begin{tabular*}{\hsize}{@{\extracolsep{\fill}}p{2.5cm} p{5.3cm}}
    \toprule
    Synset & Gloss  \cr
    \hline
\midrule  \multicolumn{2}{c}{Lenin: The Agrarian Programme}  \\  \midrule
rent.n.01 & a payment or series of payments made by the lessee to an owner for use of some property, facility, equipment, or service \\
land.n.04 & the solid part of the earth's surface \\
peasant.n.01 & a country person \\
capital.n.01 & assets available for use in the production of further assets \\
revolution.n.01 & a drastic and far-reaching change in ways of thinking and behaving \\
\midrule  \multicolumn{2}{c}{The State and Revolution} \\  \midrule
marx.n.03 & United States comedian; one of four brothers who made motion pictures together (1891-1961) \\
revolution.n.01 & a drastic and far-reaching change in ways of thinking and behaving \\
plant.n.01 & buildings for carrying on industrial labor \\
engels.n.01 & socialist who wrote the Communist Manifesto with Karl Marx in 1848 (1820-1895) \\
club.n.02 & a formal association of people with similar interests \\
\midrule  \multicolumn{2}{c}{Lenin: MATERIALISM and EMPIRIO-CRITICISM} \\  \midrule
physics.n.01 & the science of matter and energy and their interactions \\
sociable.n.01 & a party of people assembled to promote sociability and communal activity \\
space.n.02 & an empty area (usually bounded in some way between things) \\
time.n.05 & the continuum of experience in which events pass from the future through the present to the past \\
berkeley.n.01 & Irish philosopher and Anglican bishop who opposed the materialism of Thomas Hobbes (1685-1753) \\
\midrule  \multicolumn{2}{c}{Lenin: Imperialism, the Highest Stage of Capitalism} \\  \midrule
enterprise.n.02 & an organization created for business ventures \\
depository\_financial\_institution.n.01 & a financial institution that accepts deposits and channels the money into lending activities \\
imperialism.n.01 & a policy of extending your rule over foreign countries \\
universe.n.01 & everything that exists anywhere \\
million.n.01 & the number that is represented as a one followed by 6 zeros \\
\midrule  \multicolumn{2}{c}{Lenin: What Is To Be Done?} \\  \midrule
local\_anesthetic.n.01 & anesthetic that numbs a particular area of the body \\
organization.n.01 & a group of people who work together \\
marriage.n.01 & the state of being a married couple voluntarily joined for life (or until divorce) \\
criticism.n.03 & a written evaluation of a work of literature \\
revolutionist.n.01 & a radical supporter of political or social revolution \\
    \bottomrule
\end{tabular*}

### 2014-03-15 paper/wsd.tex
some fixes on wsd text

@@
 
-Our approach for WSD was a classical Lesk\cite{LESK} implementation that uses wordnet as a definition source with some tweaks.
-Basically Lesk is based on the idea that words that co–occur in a sentence are being used to refer to the same topic.
-The Lesk algorithm takes the word definition or gloss that we want to disambiguate and it compares it gloss against the glosses of the other words in the context.
-Then a word is assigned that sense whose gloss shares the largest number of words in common with the glosses of the other words.
+Our approach for WSD was a classical Lesk\cite{LESK} implementation that uses wordnet as a definition source with some tweaks.\\
+Basically Lesk is based on the idea that words that co–occur in a sentence are being used to refer to the same topic. \\
+The Lesk algorithm takes the word definition or gloss that we want to disambiguate and it compares it gloss against the glosses of the other words in the context, then a word is assigned that sense whose gloss shares the largest number of words in common with the glosses of the other words.\\
 This algorithm suffers the problem that relies on the word definition and definitions usually uses as less words as possible.
 Not only that sometimes two different words, but related ones, uses no words in common in their definitions.
-As we use the nltk wordnet we immediately notice an improvement using the rich set of relationships that Wordnet gives to us.
-We added to Lesk word stems, hypernyms, hyponyms.
+\\
+As we use the nltk wordnet we immediately notice an improvement using the rich set of relationships that Wordnet gives to us, so we added to our Lesk implementation word stems, hypernyms, hyponyms.
 For the problem of short word description we modified the algorithm to use the definition of the word to disambiguate and to compare it against the context words directly.
-Finally our algorithm chooses the best synset from wordnet based on the context words.
+Finally our algorithm chooses the best synset from wordnet based on the context words. \\
+We had choosen the whole text as context for all runs.

### 2014-03-15 paper/refactor.tex
add top senses tables with definitions
Add wsd discussion.

@@
 \usepackage[utf8]{inputenc}
-\usepackage[activeacute, spanish]{babel}
 \usepackage[dvips]{graphicx}
@@
 \usepackage{color}
-\selectlanguage{spanish}
 \usepackage{array}
+\usepackage{setspace}
+\usepackage{longtable}
+\usepackage[hmargin=2cm,vmargin=2.5cm]{geometry}
+\usepackage{booktabs}
+\usepackage{colortbl}
 \newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+\newcommand{\myrowcolour}{\rowcolor[gray]{0.925}}
+  \newcommand{\cheading}[2]{\textbf{#1\hfill #2}}
 
@@
 Based on this definition, we evaluate the resultant \textit{top senses} of some texts and then check the results of the different similarities with well known concepts in the next sections.
+\input{handpicked_table}
+\section{Results}
 
-\section{Results}
+% \subsubsection{Top senses for selected works}
+
 \input{results}
-\subsection{Top senses for selected works}
-
-\subsection{Distances to evaluation sets}
-*
-* x = {años}, y = {concept value}
 
@@
 
-\subsection{Lesk for wsd: results and limitations}
-* Zanette diferia en valores absolutos con los resultados nuestros. Moby Dick.
+\subsection{Top senses of a text}
+The method used here, as explained before, was intended just to present the model of creating a list of top senses out of a list of top words.
+In spite of being quite elemental, the method worked fairly well with most texts, having some expected problems.
 
+The main issues concern about Lesk Algorithm's flaws.
+One of these is the sensitivity of the context, for which the appearance or not of a single word in the gloss/context can radically change the selected sense for the word.
+Moreover, we strongly depend on glosses defined by Wordnet, which tend to be short.
+
+Another issue is Wordnet itself.
+While it has overwhelming information for nouns and their relationships, the resources for verbs and adjectives are not as extensive.
+This fact was a problem not only for the construction of the glosses for Lesk, but also for measuring distances between synsets and works.
 \subsection{Wordnet's synset distances}

### 2014-03-17 paper/refactor.tex
Add discussion for two works.

@@
 This fact was a problem not only for the construction of the glosses for Lesk, but also for measuring distances between synsets and works.
+
 \subsection{Wordnet's synset distances}
+
+As in the WSD problem, we also here just present a simple model to the problem of measuring a distance between a document and a -synset.
+The path similarity is a very simple similarity measure, which is based only in the distance between two synsets.
+Other
+
+For ``State and Revolution'', the distance worked as expected, matching with a high similarity those concepts highly related to the topics of the text, and putting down those unrelated.
+However, we must note that many synsets were extremely close of ``law.n.04'', which is a problem carried by a wrong disambiguation (the definition for it has to do with ``natural laws'', nothing to do with the text).
+
+For ``Imperialism ...
+'', we suffered the appearance of a very general sense (universe.n.01) which made a nonrelated sense as hair to appear second in the ranking.
+Also, a very characteristic concept of the  as \textbf{capitalism} appears unrelated, because it is not very close (in the hypernyms/hyponyms taxonomy) to the top senses of this work.
 
@@
 M. Lesk. Automatic sense disambiguation using machine readable dictionaries: How to tell a pine cone from a ice cream cone. In Proceedings of SIGDOC ’86, 1986.
+\bibitem{BUDANITSKY}
+Evaluating WordNet-based Measures of Lexical Semantic Relatedness
+http://aclweb.org/anthology//J/J06/J06-1003.pdf
 \end{thebibliography}

### 2014-03-17 paper/refactor.tex
Finish discussion part.

@@
 Also, a very characteristic concept of the  as \textbf{capitalism} appears unrelated, because it is not very close (in the hypernyms/hyponyms taxonomy) to the top senses of this work.
+``Materialism ...
+'' had the same problem but the other way around: \textbf{revolution} was just very close to \textbf{experience}, but had nothing to do with the text in general.
+
+Notice that, in order to use the path similarity, we had to select only noun senses for the top words.
+This is because verbs, adjectives and nouns are in different taxonomies in Wordnet, and hence are not comparable with this similarity.
 

### 2014-03-18 paper/refactor.tex
first essay for method-text for handpicked concepts

@@
 Based on this definition, we evaluate the resultant \textit{top senses} of some texts and then check the results of the different similarities with well known concepts in the next sections.
+
+The selected concepts are shown in the table below.
+We can distinguish three subsets in this selection: concepts related to practical situations like geopolitics and state management (like ...), concepts more related to the theoretical world (like...) and finally, concepts not related to Lenin works (like...).
+The motivation behind the selection of the two first groups is to check some easy hipotheses (such as "State and Revolution" talk a lot about "state" and "revolution", the motivation behind the third group is to chenk our methods for false positives, i.e., a high ranking in our metrics for a concept assumed not related to the works.
+
 \input{handpicked_table}

### 2014-03-19 paper/refactor.tex
Paragraph added.

--- 2014-03-17 paper/refactor.tex
@@
 
-For ``Imperialism ...
+In ``Imperialism ...
 '', we suffered the appearance of a very general sense (universe.n.01) which made a nonrelated sense as hair to appear second in the ranking.
@@
 
+Many of these problems come from the fact that path similarity is not a good measure of semantic similarity.
+Of course, two senses which have a high path similarity are similar (they are very close in terms of hypernyms/hyponyms), but the other way round is not valid.
+For instance, meronimy is not taken into account in this metric.
+
 Notice that, in order to use the path similarity, we had to select only noun senses for the top words.
@@
 \section{Conclussion \& Future work}
-The original scope of this investigation was the definition of a measure of distance between the works of a whole year but we find a lot of complexities in the definition of that model.
-While we decide to reduce the scope of this work for mental health, we consider the metric defined in this article as a step into the concretion of the original goal.
+The original scope of this investigation was the definition of a measure of distance between the works of a whole year and a concept; so we could measure whether the literary production of Lenin in some year was close to ``revolution'', ``theory'', etc.
 

### 2014-03-19 paper/refactor.tex
Add extra paragraph to discussion.

@@
 The original scope of this investigation was the definition of a measure of distance between the works of a whole year and a concept; so we could measure whether the literary production of Lenin in some year was close to ``revolution'', ``theory'', etc.
+With this purpose, we defined the \textbf{top senses} of a text, and measured the distance between them and other senses in a topological way.
 

### 2014-03-19 paper/refactor.tex

@@
 \section{Conclussion \& Future work}
-The original scope of this investigation was the definition of a measure of distance between the works of a whole year and a concept; so we could measure whether the literary production of Lenin in some year was close to ``revolution'', ``theory'', etc.
-With this purpose, we defined the \textbf{top senses} of a text, and measured the distance between them and other senses in a topological way.
+The original scope of this investigation was the definit'ion of a measure of distance between the works of a whole year and a concept; so we could measure whether the literary production of Lenin in some year was close to ``revolution'', ``theory'', etc.
 

### 2014-03-19 paper/refactor.tex

--- 2014-03-19 paper/refactor.tex
@@
 \section{Conclussion \& Future work}
+
 The original scope of this investigation was the definition of a measure of distance between the works of a whole year and a concept; so we could measure whether the literary production of Lenin in some year was close to ``revolution'', ``theory'', etc.
 With this purpose, we defined the \textbf{top senses} of a text, and measured the distance between them and other senses in a topological way.
+
+Although the final results were not the expected, some tools we developed in our way proved to be promising.
+The hybrid method for extracting top senses of the text based in entropy analisis plus sense disambiguation worked in an acceptable fashion, with lot of room for improvement by using better WSD algorithms.
+In the other hand, the topological representation of a text as a set of senses has yet to experimented with better semantic similarity functions than the one used here.
 

### 2014-03-19 paper/top_senses_definitions.tex
some improvements on tables
fix top 5 senses table!

@@
-%\begin{tabular}{ p{2cm} p{5cm} }
-\begin{tabular*}{\hsize}{@{\extracolsep{\fill}}p{2.5cm} p{5.3cm}}
+\begin{table*}[ht]
+\caption{Top 5 Senses with Closest Handpicked Synset}
+\centering
+\begin{tabular}{ p{2.5cm} p{9cm} p{2.5cm}}
     \toprule
-    Synset & Gloss  \cr
+    Synset & Gloss  & Handpicked \cr
     \hline
-\midrule  \multicolumn{2}{c}{Lenin: The Agrarian Programme}  \\  \midrule
-rent.n.01 & a payment or series of payments made by the lessee to an owner for use of some property, facility, equipment, or service \\
-land.n.04 & the solid part of the earth's surface \\
-peasant.n.01 & a country person \\
-capital.n.01 & assets available for use in the production of further assets \\
-revolution.n.01 & a drastic and far-reaching change in ways of thinking and behaving \\
-\midrule  \multicolumn{2}{c}{The State and Revolution} \\  \midrule
-marx.n.03 & United States comedian; one of four brothers who made motion pictures together (1891-1961) \\
-revolution.n.01 & a drastic and far-reaching change in ways of thinking and behaving \\
-plant.n.01 & buildings for carrying on industrial labor \\
-engels.n.01 & socialist who wrote the Communist Manifesto with Karl Marx in 1848 (1820-1895) \\
-club.n.02 & a formal association of people with similar interests \\
-\midrule  \multicolumn{2}{c}{Lenin: MATERIALISM and EMPIRIO-CRITICISM} \\  \midrule
-physics.n.01 & the science of matter and energy and their interactions \\
-sociable.n.01 & a party of people assembled to promote sociability and communal activity \\
-space.n.02 & an empty area (usually bounded in some way between things) \\
-time.n.05 & the continuum of experience in which events pass from the future through the present to the past \\
-berkeley.n.01 & Irish philosopher and Anglican bishop who opposed the materialism of Thomas Hobbes (1685-1753) \\
-\midrule  \multicolumn{2}{c}{Lenin: Imperialism, the Highest Stage of Capitalism} \\  \midrule
-enterprise.n.02 & an organization created for business ventures \\
-depository\_financial\_institution.n.01 & a financial institution that accepts deposits and channels the money into lending activities \\
-imperialism.n.01 & a policy of extending your rule over foreign countries \\
-universe.n.01 & everything that exists anywhere \\
-million.n.01 & the number that is represented as a one followed by 6 zeros \\
-\midrule  \multicolumn{2}{c}{Lenin: What Is To Be Done?} \\  \midrule
-local\_anesthetic.n.01 & anesthetic that numbs a particular area of the body \\
-organization.n.01 & a group of people who work together \\
-marriage.n.01 & the state of being a married couple voluntarily joined for life (or until divorce) \\
-criticism.n.03 & a written evaluation of a work of literature \\
-revolutionist.n.01 & a radical supporter of political or social revolution \\
+    \midrule  \multicolumn{3}{c}{The State and Revolution} \\  \midrule
+    revolution.n.01 & a drastic and far-reaching change in ways of thinking and behaving & revolution.n.01\\
+    imperialism.n.02 & a political orientation that advocates imperial interests & communism.n.02\\
+    proletarian.n.01 & a member of the working class (not necessarily employed) & peer.n.01\\
+    war.n.01 & the waging of armed conflict against an enemy & experience.n.03\\
+    practice.n.03 & translating an idea into action & experience.n.03\\
+    \midrule  \multicolumn{3}{c}{Lenin: Imperialism, the Highest Stage of Capitalism} \\  \midrule
+    proletarian.n.01 & a member of the working class (not necessarily employed) & capitalist.n.02\\
+    hair.n.01 & a covering for the body (or parts of it) consisting of a dense growth of threadlike structures (as on the human head); helps to prevent heat loss & universe.n.01\\
+    money.n.01 & the most common medium of exchange; functions as legal tender & penny.n.02\\
+    practice.n.03 & translating an idea into action & monopoly.n.01\\
+    toilet.n.04 & the act of dressing and preparing yourself & monopoly.n.01\\
+    \midrule  \multicolumn{3}{c}{Lenin: MATERIALISM and EMPIRIO-CRITICISM} \\  \midrule
+    revolution.n.01 & a drastic and far-reaching change in ways of thinking and behaving & experience.n.03\\
+    proletarian.n.01 & a member of the working class (not necessarily employed) & helmholtz.n.01\\
+    philosophy.n.02 & the rational investigation of questions about existence and knowledge and ethics & physics.n.01\\
+    war.n.01 & the waging of armed conflict against an enemy & experience.n.03\\
+    strategy.n.02 & the branch of military science dealing with military command and the planning and conduct of a war & physics.n.01\\
+    \midrule  \multicolumn{3}{c}{Lenin: What Is To Be Done?} \\  \midrule
+    imperialism.n.02 & a political orientation that advocates imperial interests & political\_orientation.n.01\\
+    proletarian.n.01 & a member of the working class (not necessarily employed) & worker.n.01\\
+    practice.n.03 & translating an idea into action & motion.n.03\\
+    money.n.01 & the most common medium of exchange; functions as legal tender & mass.n.01\\
+    war.n.01 & the waging of armed conflict against an enemy & motion.n.03\\
+
+    \midrule  \multicolumn{3}{c}{Lenin: The Agrarian Programme of Social-Democracy in the First Russian Revolution, 1905-1907} \\  \midrule
+    revolution.n.01 & a drastic and far-reaching change in ways of thinking and behaving & revolution.n.01\\
+    capitalism.n.01 & an economic system based on private ownership of capital & capitalism.n.01\\
+    proletarian.n.01 & a member of the working class (not necessarily employed) & peasant.n.01\\
+    war.n.01 & the waging of armed conflict against an enemy & nationalization.n.03\\
+    practice.n.03 & translating an idea into action & nationalization.n.03\\
+
     \bottomrule
-\end{tabular*}
+\end{tabular}
+\end{table*}

### 2014-03-19 paper/handpicked_table.tex
add captions to tables
reorder handpicked_table and correct some typos

@@
-Handpicked concepts to compare against top senses\\
-
-\begin{tabular}{ p{2cm} p{5cm} }
+\begin{table*}[ht]
+\caption*{Handpicked concepts to compare against top senses}
+\centering
+%\begin{tabular}{p{0.25\linewidth}p{0.25\linewidth}p{0.25\linewidth}}
+\begin{tabular}{ p{2.5cm} p{15cm} }
     \toprule
@@
             war & the waging of armed conflict against an enemy \\
-            capitalism & an economic system based on private ownership of capital\\
-            theory & a well-substantiated explanation of some aspect of the natural world \\
-            toilet & the act of dressing and preparing yourself \\
+            strategy & the branch of military science dealing with military command and the planning and conduct of a war \\
+            practice & translating an idea into action \\
+            money & the most common medium of exchange; functions as legal tender \\
             imperialism & a political orientation that advocates imperial interests \\
             proletarian & a member of the working class (not necessarily employed) \\
-            practice & translating an idea into action \\
             revolution & a drastic and far-reaching change in ways of thinking and behaving \\
-            money & the most common medium of exchange; functions as legal tender \\
+            capitalism & an economic system based on private ownership of capital\\
+            materialism & (philosophy) the philosophical theory that matter is the only reality \\
+            theory & a well-substantiated explanation of some aspect of the natural world \\
             philosophy & the rational investigation of questions about existence and knowledge and ethics \\
             idealism & (philosophy) the philosophical theory that ideas are the only reality \\
-            strategy & the branch of military science dealing with military command and the planning and conduct of a war \\
-            materialism & (philosophy) the philosophical theory that matter is the only reality \\
             lion & large gregarious predatory f of Africa and India having a tawny coat with a shaggy mane in the male \\
-            television\_receiver. & an electronic device that receives television signals and displays them on a screen \\
+            toilet & the act of dressing and preparing yourself \\
+            television\_receiver & an electronic device that receives television signals and displays them on a screen \\
             hair & a covering for the body (or parts of it) consisting of a dense growth of threadlike structures (as on the human head); helps to prevent heat loss \\
-            sugar & a white crysta carbohydrate used as a sweetener and preservative \\
+            sugar & a white crystal carbohydrate used as a sweetener and preservative \\
             car & a motor vehicle with four wheels; usually propelled by an internal combustion engine \\
@@
 \end{tabular}
+
+\end{table*}

### 2014-03-19 paper/refactor.tex
add subsubsection 'Word-senses evaluation set' to 'Method'

@@
 
+\subsubsection{Word-senses evaluation set}
+
 Based on this definition, we evaluate the resultant \textit{top senses} of some texts and then check the results of the different similarities with well known concepts in the next sections.
@@
 The selected concepts are shown in the table below.
-We can distinguish three subsets in this selection: concepts related to practical situations like geopolitics and state management (like ...), concepts more related to the theoretical world (like...) and finally, concepts not related to Lenin works (like...).
-The motivation behind the selection of the two first groups is to check some easy hipotheses (such as "State and Revolution" talk a lot about "state" and "revolution", the motivation behind the third group is to chenk our methods for false positives, i.e., a high ranking in our metrics for a concept assumed not related to the works.
+We can distinguish three subsets in this selection: concepts related to practical situations like geopolitics and state management (like 'war', 'strategy', 'money'), concepts more related to the theoretical world (like 'philosophy', 'idealism', 'theory') and finally, concepts not related to Lenin's works (like 'sugar', 'car', 'television\_receiver').
+The motivation behind the selection of the two first groups is to check some easy hipotheses (such as "State and Revolution" talks a lot about "state" and "revolution", the motivation behind the third group is to check our methods looking for false positives, i.e., a high ranking in the metrics for a concept assumed not related to the works.
+The distinction between the two first groups and the third in pretty taxative, while the distinction between first and second group is more smooth.
 

### 2014-03-19 paper/refactor.tex
include new tables in paper structure
delete itemize of similarities and add a paragraph explaining the selection of path

@@
 
-The similarities defined in the nltk-api are the following:
+The similarities defined in the nltk-api are the following: Path similarity, Leacock-Chodorow similarity, Resnik similarity, Jiang-Conrath similarity and Lin similarity.
+\textbf{fill me with shit from the paper}\cite{BUDANITSKY}.
+In this project, we present the results measured with path similarity because the idea is to present a proof of concept of a representation for documents (and not a 'productive' one).
+Path similarity was the best in the trade off between the complexity of the measure and the obtained results.
+This similarity represents the distance between two nodes in Wordnet based on the shortest path that connects the senses in the is-a (hypernym/hypnoym) taxonomy.
 
-\begin{itemize}
-  \item Path Similarity: based on the shortest path that connects the senses in the is-a (hypernym/hypnoym) taxonomy.
-  \item Leacock-Chodorow Similarity: based on the shortest path that connects the senses (as above) and the maximum depth of the taxonomy in which the senses occur.
+%   \item Leacock-Chodorow Similarity: based on the shortest path that connects the senses (as above) and the maximum depth of the taxonomy in which the senses occur.
 The relationship is given as -log(p/2d) where p is the shortest path length and d the taxonomy depth.
-  \item Wu-Palmer Similarity: based on the depth of the two senses in the taxonomy and that of their Least Common Subsumer (most specific ancestor node). 
-  \item Resnik Similarity: based on the Information Content (IC) of the Least Common Subsumer.
+%   \item Wu-Palmer Similarity: based on the depth of the two senses in the taxonomy and that of their Least Common Subsumer (most specific ancestor node). 
+%   \item Resnik Similarity: based on the Information Content (IC) of the Least Common Subsumer.
 Note that for any similarity measure that uses information content, the result is dependent on the corpus used to generate the information content and the specifics of how the information content was created.
-  \item Jiang-Conrath Similarity Return a score denoting how similar two word senses are, based on the Information Content (IC) of the Least Common Subsumer and that of the two input Synsets.
+%   \item Jiang-Conrath Similarity Return a score denoting how similar two word senses are, based on the Information Content (IC) of the Least Common Subsumer and that of the two input Synsets.
 The relationship is given by the equation 1 / (IC(s1) + IC(s2) - 2 * IC(lcs)).
-  \item Lin Similarity: Return a score denoting how similar two word senses are, based on the Information Content (IC) of the Least Common Subsumer and that of the two input Synsets.
+%   \item Lin Similarity: Return a score denoting how similar two word senses are, based on the Information Content (IC) of the Least Common Subsumer and that of the two input Synsets.
 The relationship is given by the equation 2 * IC(lcs) / (IC(s1) + IC(s2)).
-\end{itemize}
+% \end{itemize}
 
@@
 \section{Results}
+This section is divided in two: first, we present the \textit{top senses} of the documents listed in "Text corpus"; second, we present the similarities between the documents and the word-senses evaluation set.
 
-% \subsubsection{Top senses for selected works}
+%\subsubsection{Top senses for selected works}
+\input{results}
 
-\input{results}
+%\subsubsection{Similarities with chosen concepts}
+\input{results_sim_tables}
 

### 2014-03-21 paper/refactor.tex
word-sense-document similarity formula
BUDANITSKY_2 added to bibliography

@@
 The similarities defined in the nltk-api are the following: Path similarity, Leacock-Chodorow similarity, Resnik similarity, Jiang-Conrath similarity and Lin similarity.
-\textbf{fill me with shit from the paper}\cite{BUDANITSKY}.
+\textbf{fill me with shit from the paper}\cite{BUDANITSKY}\cite{BUDANITSKY_2}.
 In this project, we present the results measured with path similarity because the idea is to present a proof of concept of a representation for documents (and not a 'productive' one).
@@
 The distinction between the two first groups and the third in pretty taxative, while the distinction between first and second group is more smooth.
+
+Finally, we define the similarity between a document and a word-sense as follows:
+
+\begin{equation}
+  similarity(w, T) = max(path\_similarity(w, top\_senses_n(T)))
+\end{equation}
 
@@
 http://aclweb.org/anthology//J/J06/J06-1003.pdf
+\bibitem{BUDANITSKY_2}
+Semantic distance in WordNet: An experimental, application-oriented evaluation of five measures
+ftp://learning.cs.utoronto.ca/pub/gh/Budanitsky+Hirst-2001.pdf
 \end{thebibliography}

### 2014-03-21 paper/refactor.tex
finished wordnet and similarities subsubsection, added some references

@@
 Having the \textit{top-words} representation of a document, we were interested in measuring the distance or similarity of that text to different words.
-In order to address this problem we used different similarity functions defined over wordnet in the python's library nltk\footnote{link a nltk}.
+In order to address this problem we used different similarity functions defined over wordnet in the python's library nltk\footnote{\url{http://www.nltk.org/}}.
 Wordnet is a lexical resource known as thesaurus, i.
@@
 
-The similarities defined in the nltk-api are the following: Path similarity, Leacock-Chodorow similarity, Resnik similarity, Jiang-Conrath similarity and Lin similarity.
-\textbf{fill me with shit from the paper}\cite{BUDANITSKY}\cite{BUDANITSKY_2}.
+The similarities defined in the nltk-api are the following: Path similarity, Leacock-Chodorow similarity, Wu-Palmer similarity, Resnik similarity, Jiang-Conrath similarity and Lin similarity.
+The former three are analytical, this is, their calculus is based only in the semantic relations of the thesaurus, meanwhile, the last three are analytical but also use statistics from a corpus.\cite{BUDANITSKY}\cite{BUDANITSKY_2}.
 In this project, we present the results measured with path similarity because the idea is to present a proof of concept of a representation for documents (and not a 'productive' one).

### 2014-03-21 paper/refactor.tex
fix some grammar stuff

@@
 But this weighted set of top words has the problem of polysemy, typical in the field of nlp.
-Polysemy occurs when a term has more than one sense or meaning, for example: the term 'bank' can refer to a financial institution or to the land formation, thus, it is polysemic.
+Polysemy occurs when a term has more than one sense or meaning, for example: the term 'bank' can refer to a financial institution or to a land formation, thus, it is polysemic.
 In order to resolve this limitation, we implement a basic algorithm of word-sense disambiguation based on wordnet's synsets and we apply it over the top words, using as disambiguation context the whole document.
@@
 Using synsets instead of words, the wordnet thesaurus solves two problems of ambiguity limited to the linguistic domain: polisemy and synonymy.
-Polisemy occurs when a unique term may refer to more than one concept (for example, bank may refer to a financial institution or to a the land formation.
+Polisemy occurs when a unique term may refer to more than one concept (for example, bank may refer to a financial institution or to a land formation.
 In the other hand, synonymy occurs when different terms refer to the same concept (for example \sq{car} and \sq{automobile} refers, both, to the same concept).

### 2014-03-21 paper/refactor.tex
Remove some comments.|

@@
 
-\begin{itemize}
-  \item Mention the crawler for the complete lenin works, pointing that finally we didn't used it but that the scrapper is available in the project at github
-  \item May be, point out some numbers of the db generated. (total documents, mean tokens per document, etc). It's my opinion, I understand that it's not the main line of the project.
-\end{itemize}
+For this purpose, we developed a web crawler to fetch the works from the \cite{LENIN}, but ended up using only these works.
 

### 2014-03-22 paper/refactor.tex
add and standarize bibliography. also fix typos

@@
 
-\author{Leonardo Lazzaro,\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
-Julián Peller,\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
-Juan Manuel Pérez,\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
+\author{Leonardo Lazzaro\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
+Julián Peller\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
+Juan Manuel Pérez\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina}
 }
-
-%&\contributor{Submitted to Proceedings of the National Academy of Sciences
-%of the United States of America}
 
@@
 We selected some starred works from Lenin from the "Marxists Internet Archive"\cite{LENIN}.
-Those works are very different in topic, some of them being strictly phylosophical essays (such as ``Materialism and Empiriocriticism'') and other being more political, such as ``State and Revolution'', and finally an economy essay called ``Imperialism, the highest stage of capitalism''.
+Those works are very different in topic, some of them being strictly phylosophical essays (such as ``Materialism and Empiriocriticism'') and other being more political, such as ``State and Revolution'', and finally an economic essay called ``Imperialism, the highest stage of capitalism''.
 
@@
 In this project, we present the results measured with path similarity because the idea is to present a proof of concept of a representation for documents (and not a 'productive' one).
-Path similarity was the best in the trade off between the complexity of the measure and the obtained results.
 This similarity represents the distance between two nodes in Wordnet based on the shortest path that connects the senses in the is-a (hypernym/hypnoym) taxonomy.
@@
 \bibitem{LENIN}
-Marxists Internet Archive, {\em www.marxists.org} %, No estaria pudiendo definir bien esta referencia
+Marxists Internet Archive (\url{http://www.marxists.org})
 \bibitem{DARWIN}
-M.A. Montemurro and D. H. Zanette, {\em The statistics of meaning: Darwin, Gibbon and Moby Dick}, Significance, Dec. 2009, 165-169.
+M.A. Montemurro \& D. H. Zanette, 2009, {\em The statistics of meaning: Darwin, Gibbon and Moby Dick}, Significance, Dec. 2009, 165-169.
 \bibitem{ENTROPIC}
-M.A. Montemurro and D. H. Zanette, {\em Entropic analysis of the role of words in literary texts}, Adv. Complex Systems 5, September 27th 2001
+M.A. Montemurro \& D. H. Zanette, 2001, {\em Entropic analysis of the role of words in literary texts}, Adv. Complex Systems Vol. 5, September 27th 2001
 \bibitem{MAS-ZANETTE}
+M.A. Montemurro \& D. H. Zanette, 2010, {\em Towards the quantification of the semantic information encoded in written language}, Adv. Complex Systems Vol. 13.
 \bibitem{WORDNET}
-George A. Miller, {\em WordNet: A Lexical Database for English }, COMMUNICATIONS OF THE ACM November 1995/Vol. 38, No. 11
+George A. Miller, 1995, {\em WordNet: A Lexical Database for English }, COMMUNICATIONS OF THE ACM November 1995/Vol. 38, No. 11
 \bibitem{LESK}
-M. Lesk. Automatic sense disambiguation using machine readable dictionaries: How to tell a pine cone from a ice cream cone. In Proceedings of SIGDOC ’86, 1986.
+M. Lesk., 1986, {\em Automatic sense disambiguation using machine readable dictionaries: How to tell a pine cone from a ice cream cone}. In Proceedings of SIGDOC ’86.
 \bibitem{BUDANITSKY}
-Evaluating WordNet-based Measures of Lexical Semantic Relatedness
-http://aclweb.org/anthology//J/J06/J06-1003.pdf
+Budanitsky \& Hirst, 2004, {\em Evaluating WordNet-based Measures of Lexical Semantic Relatedness}
+%\url{http://aclweb.org/anthology//J/J06/J06-1003.pdf}
 \bibitem{BUDANITSKY_2}
-Semantic distance in WordNet: An experimental, application-oriented evaluation of five measures
-ftp://learning.cs.utoronto.ca/pub/gh/Budanitsky+Hirst-2001.pdf
+Budanitsky \& Hirst, 2001, {\em Semantic distance in WordNet: An experimental, application-oriented evaluation of five measures}
+%\bibitem{SLEZAK}
+%C. Diuk, D. Slezak et al., 2013, {\em A quantitative philology of introspection}, Frontiers in Integrative Neuroscience Vol. 8
 \end{thebibliography}

### 2014-03-22 paper/results.tex
some improvements on tables
add captions to tables
remove everything but page number from footer

@@
-\begin{tabular}{p{1.1cm} p{1.1cm} p{1.1cm} p{1.5cm} p{1.5cm}}
+\begin{table*}[ht]
+\caption*{Top sense for all Lenin works}
+\centering
+\begin{tabular}{p{3cm} p{3cm} p{3cm} p{3cm} p{3cm}}
         \toprule
-        Work 1 & Work 2 & Work 3 & Work 4 & Work 5 \\
+        The State and Revolution & Imperialism,the Highest .. & Materialism and ... & What Is To Be Done? &  The Agrarian Programme ... \\
 %        \multicolumn{2}{c}{Work 1} & \multicolumn{2}{c}{Work 2} & \multicolumn{2}{c}{Work 3} & \multicolumn{2}{c}{Work 4} & \multicolumn{2}{c}{Work 5} \\
@@
         \bottomrule
+        \multicolumn{5}{p{\linewidth}}{The table shows $top-senses$ obtained from the choosen works.
+Each $top-sense$ is ordered according to the information value score that we obtained previous to apply the $WSD$ algorithm.
+Most of the senses found by our algorithm were the senses related to the works, except for some of them.
+On Whats is to be done?
+local\_anesthetic was matched as sense.
+On State and revolution Marx was matched with a United States comedian and the same result we got with Berstein that was matched with a composer} \\
     \end{tabular}
-\newline
-%aWork1 : The State and Revolution
-%work2: Lenin: Imperialism, the Highest Stage of Capitalism
-%Work3: Lenin: MATERIALISM and EMPIRIO-CRITICISM
-%Work4: Lenin: What Is To Be Done?
-%wotk5: Lenin: The Agrarian Programme of Social-Democracy in the First Russian Revolution, 1905-1907
-
-    \begin{tabular}{ p{2cm} p{2cm} p{3cm}}
-    \toprule
-    Text &  Top Sense & Sense Detected \\
-    \midrule
-The Agrarian Programme & marx & United States comedian; one of four brothers who made motion pictures together (1901-1979) \\
-    \midrule
-The State and Revolution & bernstein & United States conductor and composer (1918-1990) \\
-    \bottomrule
-\end{tabular}
-
-\input{top_senses_definitions}
+\end{table*}

### 2014-03-22 paper/top_senses_definitions.tex
add captions to tables
remove everything but page number from footer

@@
 \begin{table*}[ht]
-\caption{Top 5 Senses with Closest Handpicked Synset}
+    \caption*{Top 5 Senses with Closest Handpicked Synset (Path Distance)}
 \centering
@@
     \bottomrule
+    \multicolumn{3}{p{\linewidth}}{Top-senses for each work are shown on the first column.
+The gloss that our algorithm calculated is on the second column.
+Third column shows the closest handpicked sense using path distance.
+On imperialism notice the appareance of hair.n.01 and the matched sense universe.n.01.
+On Materialism and Empirio-criticism first sense was matched with experience.n.03.
+Note that many synsets were close to law.n.04 (TODO: necesito mostrar esto en la tabla usando los top7 creo)} \\
 \end{tabular}

### 2014-03-31 paper/refactor.tex
Fix ill formed quotations.

@@
 
-%   \item Leacock-Chodorow Similarity: based on the shortest path that connects the senses (as above) and the maximum depth of the taxonomy in which the senses occur.
-The relationship is given as -log(p/2d) where p is the shortest path length and d the taxonomy depth.
-%   \item Wu-Palmer Similarity: based on the depth of the two senses in the taxonomy and that of their Least Common Subsumer (most specific ancestor node). 
-%   \item Resnik Similarity: based on the Information Content (IC) of the Least Common Subsumer.
-Note that for any similarity measure that uses information content, the result is dependent on the corpus used to generate the information content and the specifics of how the information content was created.
-%   \item Jiang-Conrath Similarity Return a score denoting how similar two word senses are, based on the Information Content (IC) of the Least Common Subsumer and that of the two input Synsets.
-The relationship is given by the equation 1 / (IC(s1) + IC(s2) - 2 * IC(lcs)).
-%   \item Lin Similarity: Return a score denoting how similar two word senses are, based on the Information Content (IC) of the Least Common Subsumer and that of the two input Synsets.
-The relationship is given by the equation 2 * IC(lcs) / (IC(s1) + IC(s2)).
-% \end{itemize}
-
 \subsubsection{Word sense disambiguation}
@@
 The selected concepts are shown in the table below.
-We can distinguish three subsets in this selection: concepts related to practical situations like geopolitics and state management (like 'war', 'strategy', 'money'), concepts more related to the theoretical world (like 'philosophy', 'idealism', 'theory') and finally, concepts not related to Lenin's works (like 'sugar', 'car', 'television\_receiver').
-The motivation behind the selection of the two first groups is to check some easy hipotheses (such as "State and Revolution" talks a lot about "state" and "revolution", the motivation behind the third group is to check our methods looking for false positives, i.e., a high ranking in the metrics for a concept assumed not related to the works.
+We can distinguish three subsets in this selection: concepts related to practical situations like geopolitics and state management (like `war', `strategy', `money'), concepts more related to the theoretical world (like  `philosophy', `idealism', `theory') and finally, concepts not related to Lenin's works (like `sugar', `car', `television\_receiver').
+The motivation behind the selection of the two first groups is to check some easy hipotheses (such as ``State and Revolution'' talks a lot about ``state'' and ``revolution'', the motivation behind the third group is to check our methods looking for false positives, i.e., a high ranking in the metrics for a concept assumed not related to the works.
 The distinction between the two first groups and the third in pretty taxative, while the distinction between first and second group is more smooth.
@@
 \section{Results}
-This section is divided in two: first, we present the \textit{top senses} of the documents listed in "Text corpus"; second, we present the similarities between the documents and the word-senses evaluation set.
+This section is divided in two: first, we present the \textit{top senses} of the documents listed in ``Text corpus''; second, we present the similarities between the documents and the word-senses evaluation set.
 

### 2014-03-31 paper/refactor.tex
Fix quote.

@@
 The former three are analytical, this is, their calculus is based only in the semantic relations of the thesaurus, meanwhile, the last three are analytical but also use statistics from a corpus.\cite{BUDANITSKY}\cite{BUDANITSKY_2}.
-In this project, we present the results measured with path similarity because the idea is to present a proof of concept of a representation for documents (and not a 'productive' one).
+In this project, we present the results measured with path similarity because the idea is to present a proof of concept of a representation for documents (and not a `productive' one).
 This similarity represents the distance between two nodes in Wordnet based on the shortest path that connects the senses in the is-a (hypernym/hypnoym) taxonomy.

### 2014-03-31 paper/results.tex
Some aesthetical changes.

@@
-\begin{table*}[ht]
+\begin{table*}[t]
 \caption*{Top sense for all Lenin works}
@@
         marx & enterprise & physics & local\_anesthetic & rent \\
-        revolution & depository\_financial\_institution & sociable & organization  & land \\
+        revolution & depository\_financial\ldots & sociable & organization  & land \\
         plant & imperialism & space & marriage & peasant \\

### 2014-04-01 paper/refactor.tex
Some aesthetical changes.
Rewrite some formulas.

@@
 has a distribution in text that is not exactly uniform; an order of the word in the text that brings some sense to it.
+
 Ordering the words by their information value results in a list of the text's most representative words.
@@
 
-\begin{equation}
-  top\_words_{n}(T) = \{w | max(IV_T(w))\}
-\end{equation}
+That's it, if we have all the words sorted as $w_1, w_2, \ldots , w_M$ such that $ i \leq j \Rightarrow IV_{T}(w_i) >= IV_{T}(w_j)$, then, the $n$ top words are $w_1, w_2, \ldots w_n$
 
@@
 
-Given a document $T$ and an arbitrary integer $n$, the \textit{top senses} are defined as follow:
+Given $w_1, \ldots, w_M$, words of $T$ sorted by information value, and suppose that $w_{i_1}, w_{i_2}, \ldots, w_{i_n}$ are the $n$ first words  such that disambiguation for each $w_{i_j}$ is feasible.
+Then, the top senses for $T$ are
 \begin{equation}
-  top\_senses_{n}(T) = \{s | w \in top\_words_{n}(T) \wedge  s = wsd_T(w)\}
+  WSD(w_1), WSD(w_2), \ldots, WSD(w_n)
 \end{equation}
@@
 \input{results_sim_tables}
+
+\newpage
 
@@
 \appendix[All tables]
-% \input{top_senses_the_state_and_revolution}
-% \input{top_senses_lenin_imperialism_the_highest_stage_of_capitalism}
-% \input{top_senses_lenin_materialism_and_empirio-criticism}
-% \input{top_senses_lenin_the_agrarian_programme_of_social-democracy_in_the_first_russian_revolution_1905-1907}
-% \input{top_senses_lenin_what_is_to_be_done?}
 

### 2014-04-01 paper/handpicked_table.tex
Table now fits correctly.
Cut a long sentence so it fits properly.

@@
-\begin{table*}[ht]
+\begin{table*}[t]
 \caption*{Handpicked concepts to compare against top senses}
@@
             television\_receiver & an electronic device that receives television signals and displays them on a screen \\
-            hair & a covering for the body (or parts of it) consisting of a dense growth of threadlike structures (as on the human head); helps to prevent heat loss \\
+            hair & a covering for the body (or parts of it) consisting of a dense growth of threadlike structures \\
             sugar & a white crystal carbohydrate used as a sweetener and preservative \\

### 2014-04-01 paper/refactor.tex
Rewrite abstract (well, just correcting it)

@@
 \begin{abstract}
-In this project we analyzed some Lenin works in order to identify the presence of some well known topics of his biography.
-To achieve this, we defined and implemented a simple distance metric between a word-sense and a document and confronted this metric using a evaluation set of word-senses against a reduced set of  documents with well known topics.
-During this work, we generated an indexed database of Lenin's complete works from a web site\cite{LENIN} and we applied a serie of well known syntactic, semantic and lexicographic tools in order to model the similarity between a document and a word-sense.
-We applied information value\cite{DARWIN} and a simple algorithm of word sense disambiguation\cite{LESK} based on wordnet\cite{WORDNET} in order to generate the \textit{top senses} (or principal senses) of a document.
-We compare this \textit{top senses} for some documents of well known topics agains some senses of interest (for example: revolution, war, government) and observed the shape of the results.
+In this project we analyzed some Lenin works in order to identify the presence of some topics of his biography.
+To achieve this, we defined and implemented a simple metric distance between a word-sense and a document and confronted this metric using a evaluation set of word-senses against a reduced set of  documents with well known topics.
+During this work, we generated an indexed database of Lenin's complete works from a web site\cite{LENIN} and we applied a series of syntactic, semantic and lexicographic tools in order to model the similarity between a document and a word-sense.
+We applied information value\cite{DARWIN} and a simple algorithm of word sense disambiguation\cite{LESK} based on Wordnet\cite{WORDNET} in order to generate the \emph{top senses} (or principal senses) of a document.
+Finally, we compare them against some semantic senses of interest (for example: revolution, war, philosophy, etc).
 \end{abstract}

### 2014-04-01 paper/apendices.tex
Revisit apendices.

--- 2014-04-01 paper/refactor.tex
@@
-%% PNAStwoS.tex
-%% Sample file to use for PNAS articles prepared in LaTeX
-%% For two column PNAS articles
-%% Version: Apr 15, 2008
-
-%% BASIC CLASS FILE
-\documentclass{pnastwo}
-
-%% ADDITIONAL OPTIONAL STYLE FILES
-%\usepackage[dvips]{graphicx}
-%\usepackage{pnastwof}
-\usepackage{amssymb,amsfonts,amsmath}
-\usepackage[utf8]{inputenc}
-\usepackage[dvips]{graphicx}
-\usepackage{bookmark}
-\usepackage{color}
-\usepackage{array}
-\usepackage{setspace}
-\usepackage{longtable}
-\usepackage[hmargin=2cm,vmargin=2.5cm]{geometry}
-\usepackage{booktabs}
-\usepackage{colortbl}
-\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-\newcommand{\myrowcolour}{\rowcolor[gray]{0.925}}
-  \newcommand{\cheading}[2]{\textbf{#1\hfill #2}}
-
-\newcommand\dq[1]{\textquotedblleft #1\textquotedblright}
-\newcommand\sq[1]{\textquoteleft #1\textquoteright}
-\newcommand*{\allref}[1]{\ref{#1} \nameref{#1}}
-
-%% OPTIONAL MACRO DEFINITIONS
-\def\s{\sigma}
-
-%%%%%%%%%%%%
-%% For PNAS Only:
-%\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
-\copyrightyear{2008}
-\issuedate{Issue Date}
-\volume{Volume}
-\issuenumber{Issue Number}
-%\setcounter{page}{2687} %Set page number here if desired
-%%%%%%%%%%%%
-
-\begin{document}
-
-\title{A word-sense representation for documents based on information value and word sense disambiguation}
-
-\author{Leonardo Lazzaro\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
-Julián Peller\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
-Juan Manuel Pérez\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina}
-}
-
-\maketitle
-
-\begin{article}
-\begin{abstract}
-In this project we analyzed some Lenin works in order to identify the presence of some topics of his biography.
-To achieve this, we defined and implemented a simple metric distance between a word-sense and a document and confronted this metric using a evaluation set of word-senses against a reduced set of  documents with well known topics.
-During this work, we generated an indexed database of Lenin's complete works from a web site\cite{LENIN} and we applied a series of syntactic, semantic and lexicographic tools in order to model the similarity between a document and a word-sense.
-We applied information value\cite{DARWIN} and a simple algorithm of word sense disambiguation\cite{LESK} based on Wordnet\cite{WORDNET} in order to generate the \emph{top senses} (or principal senses) of a document.
-Finally, we compare them against some semantic senses of interest (for example: revolution, war, philosophy, etc).
-\end{abstract}
-
-\keywords{information value | word sense disambiguation | natural language processing | information retrieval | polysemy }
-
-%\abbreviations{NLP}
-
-\section{Introduction}
-
-\dropcap{I}n this article we propose a simple distance metric between a word-sense and a text document using different well known tools from natural language processing.
-To achieve this, we extract a hierarchy of the most representative words of a document (\textit{top words}) using the concept of \textit{information value}, a statistical linguistic model based on Shannon's information theory and proposed by Zanette et al.
-in\cite{DARWIN}.
-Briefly, information value allows us to represent a document like a ranked set of words.
-
-But this weighted set of top words has the problem of polysemy, typical in the field of nlp.
-Polysemy occurs when a term has more than one sense or meaning, for example: the term 'bank' can refer to a financial institution or to a land formation, thus, it is polysemic.
-In order to resolve this limitation, we implement a basic algorithm of word-sense disambiguation based on wordnet's synsets and we apply it over the top words, using as disambiguation context the whole document.
-We obtain, then, the \textit{top senses} of a document, this is, a ranked set of wordnet synsets that work like a representation of the given document.
-
-Finally, we utilize different wordnet predefined metrics of similarity between synsets to define our own similarities between the top-sense representation of a document and any given word-sense (wordnet synset).
-In order to evaluate the behaviour of this metrics, we test the distances of the top-senses representation of some well known documents with very specific topics against a bounded set of relevant evaluation word-senses.
-
-\section{Method}
-\subsection{Text Corpus}
-
-We selected some starred works from Lenin from the "Marxists Internet Archive"\cite{LENIN}.
-Those works are very different in topic, some of them being strictly phylosophical essays (such as ``Materialism and Empiriocriticism'') and other being more political, such as ``State and Revolution'', and finally an economic essay called ``Imperialism, the highest stage of capitalism''.
-
-\begin{itemize}
-  \item What is to be done(1901)
-  \item The Agrarian Programme of Social-Democracy in the First Russian Revolution, 1905-1907 (1907)
-  \item Materialism and Empiriocriticism (1908)
-  \item Imperialism, the highest stage of capitalism (1916)
-  \item State and Revolution (1917)
-\end{itemize}
-
-For this purpose, we developed a web crawler to fetch the works from the \cite{LENIN}, but ended up using only these works.
-
-%*Números (obras totales obtenidas, promedio tokens)
-\subsection{Semantic Analysis}
-\medskip
-\subsubsection{Information value}
-
-The information value of a word for a given text is defined and tested by Zanette \textit{et al.} in \cite{DARWIN} and \cite{ENTROPIC}.
-It is a real value that quantifies how much information a word carries according to the text. Let $T$ be a 
-text, and $T'$ a random shuffled version of $T$, and $w$ a word appearing in $T$. 
-By $S_T(w)$ we denote the Shannon Entropy of $w$ with respect to $T$ (See appendix for more info).
-
-The information value of $w$ in $T$ is
-
-\begin{equation}
-  IV_T(w) = f_w* | S_T(w) - S_{T'}(w) | 
-\end{equation}
-
-where $f_w$ is the frequency of appearance of $w$ in $T$. This value captures, in some way, whether a word
-has a distribution in text that is not exactly uniform; an order of the word in the text that brings some sense to it.
-
-Ordering the words by their information value results in a list of the text's most representative words.
-In the context of our research, we call the first $n$ words of a text -with $n$ fixed-, ordered by it's information value, the \textit{top words} of the document.
-
-That's it, if we have all the words sorted as $w_1, w_2, \ldots , w_M$ such that $ i \leq j \Rightarrow IV_{T}(w_i) >= IV_{T}(w_j)$, then, the $n$ top words are $w_1, w_2, \ldots w_n$
-
-\subsubsection{Wordnet synsets \& similarities}
-
-Having the \textit{top-words} representation of a document, we were interested in measuring the distance or similarity of that text to different words.
-In order to address this problem we used different similarity functions defined over wordnet in the python's library nltk\footnote{\url{http://www.nltk.org/}}.
-Wordnet is a lexical resource known as thesaurus, i.
-e, a data base of terms grouped as sets of synonyms (synsets), each of which have a definition and different semantic relations with others synsets (for example: hypernymy, hyponymy, meronymy, etc).
-The similarity functions are defined over this network of semantic relations.
-
-This functions aren' t defined over words but over synsets.
-A synset, briefly, is an abstract notion of sense, meaning or concept that is independent from it's linguistic formulation or spelling.
-Using synsets instead of words, the wordnet thesaurus solves two problems of ambiguity limited to the linguistic domain: polisemy and synonymy.
-Polisemy occurs when a unique term may refer to more than one concept (for example, bank may refer to a financial institution or to a land formation.
-In the other hand, synonymy occurs when different terms refer to the same concept (for example \sq{car} and \sq{automobile} refers, both, to the same concept).
-
-The similarities defined in the nltk-api are the following: Path similarity, Leacock-Chodorow similarity, Wu-Palmer similarity, Resnik similarity, Jiang-Conrath similarity and Lin similarity.
-The former three are analytical, this is, their calculus is based only in the semantic relations of the thesaurus, meanwhile, the last three are analytical but also use statistics from a corpus.\cite{BUDANITSKY}\cite{BUDANITSKY_2}.
-In this project, we present the results measured with path similarity because the idea is to present a proof of concept of a representation for documents (and not a `productive' one).
-This similarity represents the distance between two nodes in Wordnet based on the shortest path that connects the senses in the is-a (hypernym/hypnoym) taxonomy.
-
-\subsubsection{Word sense disambiguation}
-\input{wsd}
-\subsubsection{Top-sense definition}
-
-In a first approach, we pretend to measure the distance between a document (represented by it's \textit{top words}) and different words.
-To address this problem using the wordnet distances between synsets described before, we modeled the notion of \sq{word} as the sum of all its synsets.
-The results were pretty demotivating, so we refocused our energy in order to define our problem in the space of word-senses (and no more in the space of words).
-
-Using the WSD algorithm described in the previous section, we defined the notion of \textit{top senses} of a document as the word-senses resulting from the disambiguation of the \textit{top words} of the documents obtained with Zannete's information value approach.
-
-Given $w_1, \ldots, w_M$, words of $T$ sorted by information value, and suppose that $w_{i_1}, w_{i_2}, \ldots, w_{i_n}$ are the $n$ first words  such that disambiguation for each $w_{i_j}$ is feasible.
-Then, the top senses for $T$ are
-\begin{equation}
-  WSD(w_1), WSD(w_2), \ldots, WSD(w_n)
-\end{equation}
-
-\subsubsection{Word-senses evaluation set}
-
-Based on this definition, we evaluate the resultant \textit{top senses} of some texts and then check the results of the different similarities with well known concepts in the next sections.
-
-The selected concepts are shown in the table below.
-We can distinguish three subsets in this selection: concepts related to practical situations like geopolitics and state management (like `war', `strategy', `money'), concepts more related to the theoretical world (like  `philosophy', `idealism', `theory') and finally, concepts not related to Lenin's works (like `sugar', `car', `television\_receiver').
-The motivation behind the selection of the two first groups is to check some easy hipotheses (such as ``State and Revolution'' talks a lot about ``state'' and ``revolution'', the motivation behind the third group is to check our methods looking for false positives, i.e., a high ranking in the metrics for a concept assumed not related to the works.
-The distinction between the two first groups and the third in pretty taxative, while the distinction between first and second group is more smooth.
-
-Finally, we define the similarity between a document and a word-sense as follows:
-
-\begin{equation}
-  similarity(w, T) = max(path\_similarity(w, top\_senses_n(T)))
-\end{equation}
-
-\input{handpicked_table}
-\section{Results}
-This section is divided in two: first, we present the \textit{top senses} of the documents listed in ``Text corpus''; second, we present the similarities between the documents and the word-senses evaluation set.
-
-%\subsubsection{Top senses for selected works}
-\input{results}
-
-%\subsubsection{Similarities with chosen concepts}
-\input{results_sim_tables}
-
-\newpage
-
-\subsubsection{Observations}
-
-\section{Discussion}
-
-\subsection{Top senses of a text}
-The method used here, as explained before, was intended just to present the model of creating a list of top senses out of a list of top words.
-In spite of being quite elemental, the method worked fairly well with most texts, having some expected problems.
-
-The main issues concern about Lesk Algorithm's flaws.
-One of these is the sensitivity of the context, for which the appearance or not of a single word in the gloss/context can radically change the selected sense for the word.
-Moreover, we strongly depend on glosses defined by Wordnet, which tend to be short.
-
-Another issue is Wordnet itself.
-While it has overwhelming information for nouns and their relationships, the resources for verbs and adjectives are not as extensive.
-This fact was a problem not only for the construction of the glosses for Lesk, but also for measuring distances between synsets and works.
-
-\subsection{Wordnet's synset distances}
-
-As in the WSD problem, we also here just present a simple model to the problem of measuring a distance between a document and a -synset.
-The path similarity is a very simple similarity measure, which is based only in the distance between two synsets.
-Other
-
-For ``State and Revolution'', the distance worked as expected, matching with a high similarity those concepts highly related to the topics of the text, and putting down those unrelated.
-However, we must note that many synsets were extremely close of ``law.n.04'', which is a problem carried by a wrong disambiguation (the definition for it has to do with ``natural laws'', nothing to do with the text).
-
-In ``Imperialism ...
-'', we suffered the appearance of a very general sense (universe.n.01) which made a nonrelated sense as hair to appear second in the ranking.
-Also, a very characteristic concept of the  as \textbf{capitalism} appears unrelated, because it is not very close (in the hypernyms/hyponyms taxonomy) to the top senses of this work.
-``Materialism ...
-'' had the same problem but the other way around: \textbf{revolution} was just very close to \textbf{experience}, but had nothing to do with the text in general.
-
-Many of these problems come from the fact that path similarity is not a good measure of semantic similarity.
-Of course, two senses which have a high path similarity are similar (they are very close in terms of hypernyms/hyponyms), but the other way round is not valid.
-For instance, meronimy is not taken into account in this metric.
-
-Notice that, in order to use the path similarity, we had to select only noun senses for the top words.
-This is because verbs, adjectives and nouns are in different taxonomies in Wordnet, and hence are not comparable with this similarity.
-
-\section{Conclussion \& Future work}
-
-The original scope of this investigation was the definition of a measure of distance between the works of a whole year and a concept; so we could measure whether the literary production of Lenin in some year was close to ``revolution'', ``theory'', etc.
-With this purpose, we defined the \textbf{top senses} of a text, and measured the distance between them and other senses in a topological way.
-
-Although the final results were not the expected, some tools we developed in our way proved to be promising.
-The hybrid method for extracting top senses of the text based in entropy analisis plus sense disambiguation worked in an acceptable fashion, with lot of room for improvement by using better WSD algorithms.
-In the other hand, the topological representation of a text as a set of senses has yet to experimented with better semantic similarity functions than the one used here.
-
-\appendix[All tables]
-
 \appendix[Entropy of a word in a text]
@@
 The reason behind this was that it fitted the results from \cite{DARWIN} for the texts The origin of the species, Moby Dick, and  The Analysis of the mind.
-
-\appendix[Old stuff of wordnet in spanish]
-Consideremos el siguiente problema:
-\newline
-¿Cómo calcular la similaridad o distancia de un documento a un cierto concepto? 
-\newline
-El enfoque que utilizamos en este trabajo es el de realizar una representación del documento como un conjunto de palabras, y en base a esto usar una noción topológica de similaridad/distancia.
-La proyección del documento al espacio de palabras la realizamos utilizando la t\'ecnica de Information Value reci\'en descripta.
-En este espacio, utilizamos Wordnet para definir una noción de distancia entre el conjunto de palabras que representan al texto y diferentes conjuntos representando conceptos.
-\newline
-Para un documento dado, el módulo de information value genera una lista con lo $n$ términos más importantes y su iv.
-Estos valores se normalizan -dividiendo por la suma de los valores-, obteniendo así uno de los inputs del proceso siguiente.
-Recordemos, nuestro objetivo es asignar una distancia entre un documento y un concepto.
-Digamos, decidir cuán presente está o cuán importante es un concepto en un documento.
-\newline
-Wordnet es una base de datos de palabras, agrupadas en conjuntos de sinónimos (synsets), cada uno de los cuales posee una definición y diferentes relaciones semánticas con otros synsets (por ejemplo: hipernimia, hiponimia, meronimia, etc).
-Sobre estas relaciones semánticas es posible definir distintas métricas de distancia y similaridad entre synsets (Ver [1])
-\newline
-Utilizando las métricas disponibles en el módulo nltk de python para wordnet definimos la similaridad entre dos palabras como la máxima similaridad entre todos los synsets de ambas.
-(**NOTA Parametrizable: puede ser sólo el primer synset de ambos y puede no ser la máxima similaridad sino un promedio.
-También para algunas métricas quedan afuera los synsets que no son sustantivos).
-\begin{multline}
-S_w(w_1, w_2) = max \{ S_s(s_1, s_2) \}: s_1 \in synsets(w_1),\\ s_2 \in synsets(w_2)
-\end{multline}
-
-Para path similarity vale que $0 \leq S_w \leq 1$.
-
-Sobre $S_w$ (de word similarity) definimos la similaridad de un documento a un término como:
-
-\begin{equation}
-S_{dw}(d, w) = sum \{ S_w(d_i, w) \times p(d_i)  \} 
-\end{equation}
-
-donde las tuplas $(d_i , p(d_i))$ representan las palabras más importantes del documento $d$, y sus respectivos pesos normalizados. Vale que $0 \leq p(d_i) \leq 1$ pues está normalizado.
-
-Por ejemplo $S_{dw}$(“Estado y Revolución”, “guerra”) = 0.110. $S_{dw}$ es una noción de cercanía entre un documento y una palabra.
-
-Finalmente, definimos la noción de similaridad entre un año y una palabra como el promedio de las similaridades ($S_{dw}$) 
-de los distintos documentos producidos durante ese año con la palabra en cuestión:
-\begin{equation}
-  S_{yw}(y, w) = mean \{ S_dw(y_i, w) \} : y_i \in docs(y) 
-\end{equation}
-
-Los resultados que presentaremos a continuaci\'on est\'an apoyados en distintas configuraciones de estas tres m\'etricas ($S_w$, $S_dw$ y $S_{yw}$).
-
-% *SynsetAnalyzer
-%   *Synset
-%   *path, lch, wup
-% *judge_word
-% *judge_doc
-% *judge_year
-% Dado un conjunto de palabras, definimos la distancia de una palabra a este conjunto como 
-%
-
-\begin{thebibliography}{10}
-\bibitem{LENIN}
-Marxists Internet Archive (\url{http://www.marxists.org})
-\bibitem{DARWIN}
-M.A. Montemurro \& D. H. Zanette, 2009, {\em The statistics of meaning: Darwin, Gibbon and Moby Dick}, Significance, Dec. 2009, 165-169.
-\bibitem{ENTROPIC}
-M.A. Montemurro \& D. H. Zanette, 2001, {\em Entropic analysis of the role of words in literary texts}, Adv. Complex Systems Vol. 5, September 27th 2001
-\bibitem{MAS-ZANETTE}
-M.A. Montemurro \& D. H. Zanette, 2010, {\em Towards the quantification of the semantic information encoded in written language}, Adv. Complex Systems Vol. 13.
-\bibitem{WORDNET}
-George A. Miller, 1995, {\em WordNet: A Lexical Database for English }, COMMUNICATIONS OF THE ACM November 1995/Vol. 38, No. 11
-\bibitem{LESK}
-M. Lesk., 1986, {\em Automatic sense disambiguation using machine readable dictionaries: How to tell a pine cone from a ice cream cone}. In Proceedings of SIGDOC ’86.
-\bibitem{BUDANITSKY}
-Budanitsky \& Hirst, 2004, {\em Evaluating WordNet-based Measures of Lexical Semantic Relatedness}
-%\url{http://aclweb.org/anthology//J/J06/J06-1003.pdf}
-\bibitem{BUDANITSKY_2}
-Budanitsky \& Hirst, 2001, {\em Semantic distance in WordNet: An experimental, application-oriented evaluation of five measures}
-%\bibitem{SLEZAK}
-%C. Diuk, D. Slezak et al., 2013, {\em A quantitative philology of introspection}, Frontiers in Integrative Neuroscience Vol. 8
-\end{thebibliography}
-\end{article}
-\end{document}
-
-%\section{Acknowledgments}
-
-%\section{Literature cited}
-
-% \section{Analysis of almost sharp fronts}
-% We begin our analysis on almost sharp fronts for the
-% quasi-geostrophic equation recalling the notion of weak solution.
-
-% For these solutions we have the following
-
-% \appendix[Parallel calculus of information value]
-
-% \begin{table}[h]
-% \caption{Repeat length of longer allele by age of onset class.
-% This is what happens when the text continues.}
-% \begin{tabular}{@{\vrule height 10.5pt depth4pt  width0pt}lrcccc}
-% &\multicolumn5c{Repeat length}\\
-% \noalign{\vskip-11pt}
-% Age of onset,\\
-% \cline{2-6}
-% \vrule depth 6pt width 0pt years&\multicolumn1c{\it n}&Mean&SD&Range&Median\\
-% \hline
-% Juvenile, 2$-$20&40&60.15& 9.32&43$-$86&60\\
-% Typical, 21$-$50&377&45.72&2.97&40$-$58&45\\
-% Late, $>$50&26&41.85&1.56&40$-$45&42\tablenote{The no. of wells for all samples was 384. Genotypes were
-% determined by mass spectrometric assay. The $m_t$ value indicates the
-% average number of wells positive for the over represented allele.}
-% \\
-% \hline
-% \end{tabular}
-% \end{table}
-
-% \begin{table*}[ht]
-% \caption{Summary of the experimental results}
-% \begin{tabular*}{\hsize}
-% {@{\extracolsep{\fill}}rrrrrrrrrrrrr}
-% \multicolumn{3}{l}{Parameters}&
-% \multicolumn{5}{c}{Averaged Results}&
-% \multicolumn{5}{c}{Comparisons}\cr
-% \hline
-% \multicolumn1c{$n$}&\multicolumn1c{$S^*_{MAX}$}&
-% \multicolumn1c{$t_1$}&\multicolumn1c{\ $r_1$}&
-% \multicolumn1c{\ $m_1$}&\multicolumn1c{$t_2$}&
-% \multicolumn1c{$r_2$}&\multicolumn1c{$m_2$}
-% &\multicolumn1c{$t_{lb}$}&\multicolumn1c{\ \ $t_1/t_2$}&
-% $r_1/r_2$&$m_1/m_2$&
-% $t_1/t_{lb}$\cr
-% \hline
-% 10\tablenote{Stanford Synchrotron Radiation Laboratory (Stanford University,
-% Stanford, CA)}&1\quad &4&.0007&4&4&.0020&4&4&1.000&.333&1.000&1.000\cr
-% 10\tablenote{$R_{\rm FREE}=R$ factor for the $\sim 5$\% of the randomly
-% chosen unique ref\/lections not used in the ref\/inement.}&5\quad &50&.0008&8&50&.0020&12&49&.999&.417&.698&1.020\cr
-% 100\tablenote{Calculated for all observed data}&20\quad &2840975&.0423&95&2871117&.1083&521&---&
-% .990&.390&.182&---\ \ \cr
-% \hline
-% \end{tabular*}
-% \end{table*}
-
-% \appendix[Estimating the Spectral Norm of a Matrix]
-% In this appendix we describe a method for the estimation of the spectral norm
-% of matrix $A$. The method does not require access to the individual
-% entries of $A$; it requires only applications of $A$ and $A$* to vectors.
-% It is a version of the classical power method. Its probabilistic
-% analysis summarized below was introduced fairly recently in refs. 13
-% and 14. This appendix is included here for completeness.
-
-% \appendix
-% This is an example of an appendix without a title.
-
-% \begin{acknowledgments}
-% algo
-% This work was partially supported by 
-% Spanish Ministry of Science and Technology Grant BFM2002-02042 (to D.C. and
-% J.L.R.) and by National Science Foundation Grand DMS-0245242 (to C.F.).
-% \end{acknowledgments}

### 2014-04-01 paper/refactor.tex
Revisit apendices.

@@
 
-\appendix[All tables]
-
-\appendix[Entropy of a word in a text]
-\label{appendix1}
-Let's recall from \cite{DARWIN} and \cite{ENTROPIC} the concept of information value of a word.
-Let $T$ be a text, which has been split into $P$ pieces $T_1, T_2, \dots, T_P$, $w$ be a word in $T$,
-and $f_i$ the frequency of appearance of $w$ in $T_i$.
-
-For each part $1 \leq i \leq P$, we could define:
-
-\begin{equation}
-  p_i = \frac{f_i}{\Sigma_{j=1}^{P}f_i}
-\end{equation}
-
-This quantity stands for probability of finding $w$ in $T_i$, given that it is present in the text. So, 
-we define the Shannon information entropy of $w$ in $T$ as
-
-\begin{equation}
-  S = -\frac{1}{ln P}\sum_{i=1}^{P}p_i ln p_i
-\end{equation}
-
-\appendix[Optimal window size selection]
-
-As \cite{DARWIN} mentions, we should consider the window size which maximizes the information value per word, for some sense of it.
-
-Let's suppose we have a document, and a window size $W_S$ for which the information value algorithm returns a list $\{(w_1, v_1), (w_2, v_2), \dots ,(w_n, v_n) \}$ of word-information value pairs, in decreasing order of information value so that $v_1 \geq v_2 \geq \dots \geq v_n$.
-How would we assign some value to this pair of document-window size so we can choose the optimal window size?
-
-One possibility would be to take the greater information value, in this case $v_1$.
-This approach, however, gives all the value just to a single word.
-Another chance would be to take the average of all the information values, but this leads to a lot of noise added because of words without any value.
-
-The chosen approach is a tradeoff between both.
-We take the average not of all the words, but of a percentage of the most significative words.
-We call this percentage the \emph{sum threshold}.
-If $n$ is the number of words in the document, and $0 \leq ST \leq 1$ is the sum threshold, we calculate
-
-\begin{equation}
-  \frac{\sum_{i=1}^{[ST n]}v_i}{n} 
-\end{equation}
-
-The threshold value we used is $ST=0.001$, so it would consider only the $\frac{n}{1000}$ most significant words.
-The reason behind this was that it fitted the results from \cite{DARWIN} for the texts The origin of the species, Moby Dick, and  The Analysis of the mind.
-
-\appendix[Old stuff of wordnet in spanish]
-Consideremos el siguiente problema:
-\newline
-¿Cómo calcular la similaridad o distancia de un documento a un cierto concepto? 
-\newline
-El enfoque que utilizamos en este trabajo es el de realizar una representación del documento como un conjunto de palabras, y en base a esto usar una noción topológica de similaridad/distancia.
-La proyección del documento al espacio de palabras la realizamos utilizando la t\'ecnica de Information Value reci\'en descripta.
-En este espacio, utilizamos Wordnet para definir una noción de distancia entre el conjunto de palabras que representan al texto y diferentes conjuntos representando conceptos.
-\newline
-Para un documento dado, el módulo de information value genera una lista con lo $n$ términos más importantes y su iv.
-Estos valores se normalizan -dividiendo por la suma de los valores-, obteniendo así uno de los inputs del proceso siguiente.
-Recordemos, nuestro objetivo es asignar una distancia entre un documento y un concepto.
-Digamos, decidir cuán presente está o cuán importante es un concepto en un documento.
-\newline
-Wordnet es una base de datos de palabras, agrupadas en conjuntos de sinónimos (synsets), cada uno de los cuales posee una definición y diferentes relaciones semánticas con otros synsets (por ejemplo: hipernimia, hiponimia, meronimia, etc).
-Sobre estas relaciones semánticas es posible definir distintas métricas de distancia y similaridad entre synsets (Ver [1])
-\newline
-Utilizando las métricas disponibles en el módulo nltk de python para wordnet definimos la similaridad entre dos palabras como la máxima similaridad entre todos los synsets de ambas.
-(**NOTA Parametrizable: puede ser sólo el primer synset de ambos y puede no ser la máxima similaridad sino un promedio.
-También para algunas métricas quedan afuera los synsets que no son sustantivos).
-\begin{multline}
-S_w(w_1, w_2) = max \{ S_s(s_1, s_2) \}: s_1 \in synsets(w_1),\\ s_2 \in synsets(w_2)
-\end{multline}
-
-Para path similarity vale que $0 \leq S_w \leq 1$.
-
-Sobre $S_w$ (de word similarity) definimos la similaridad de un documento a un término como:
-
-\begin{equation}
-S_{dw}(d, w) = sum \{ S_w(d_i, w) \times p(d_i)  \} 
-\end{equation}
-
-donde las tuplas $(d_i , p(d_i))$ representan las palabras más importantes del documento $d$, y sus respectivos pesos normalizados. Vale que $0 \leq p(d_i) \leq 1$ pues está normalizado.
-
-Por ejemplo $S_{dw}$(“Estado y Revolución”, “guerra”) = 0.110. $S_{dw}$ es una noción de cercanía entre un documento y una palabra.
-
-Finalmente, definimos la noción de similaridad entre un año y una palabra como el promedio de las similaridades ($S_{dw}$) 
-de los distintos documentos producidos durante ese año con la palabra en cuestión:
-\begin{equation}
-  S_{yw}(y, w) = mean \{ S_dw(y_i, w) \} : y_i \in docs(y) 
-\end{equation}
-
-Los resultados que presentaremos a continuaci\'on est\'an apoyados en distintas configuraciones de estas tres m\'etricas ($S_w$, $S_dw$ y $S_{yw}$).
-
+\input{apendices}
 % *SynsetAnalyzer

### 2014-04-02 paper/refactor.tex
Add acknowledgements.

@@
 
-We selected some starred works from Lenin from the "Marxists Internet Archive"\cite{LENIN}.
+We selected some starred works from Lenin from the ``Marxists Internet Archive''\cite{LENIN}.
 Those works are very different in topic, some of them being strictly phylosophical essays (such as ``Materialism and Empiriocriticism'') and other being more political, such as ``State and Revolution'', and finally an economic essay called ``Imperialism, the highest stage of capitalism''.
@@
 
+ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT
+
 %\subsubsection{Similarities with chosen concepts}
@@
 
+\section{Acknowledgments}
+Thanks to \hyperlink{https://www.marxists.org}{Marxists Internet Archive} for helping us retrieve the Lenin's complete works.
+
 \begin{thebibliography}{10}
@@
 \end{thebibliography}
+
 \end{article}
 \end{document}
-
-%\section{Acknowledgments}
-
-%\section{Literature cited}
-
-% \section{Analysis of almost sharp fronts}
-% We begin our analysis on almost sharp fronts for the
-% quasi-geostrophic equation recalling the notion of weak solution.
-
-% For these solutions we have the following
-
-% \appendix[Parallel calculus of information value]
-
-% \begin{table}[h]
-% \caption{Repeat length of longer allele by age of onset class.
-% This is what happens when the text continues.}
-% \begin{tabular}{@{\vrule height 10.5pt depth4pt  width0pt}lrcccc}
-% &\multicolumn5c{Repeat length}\\
-% \noalign{\vskip-11pt}
-% Age of onset,\\
-% \cline{2-6}
-% \vrule depth 6pt width 0pt years&\multicolumn1c{\it n}&Mean&SD&Range&Median\\
-% \hline
-% Juvenile, 2$-$20&40&60.15& 9.32&43$-$86&60\\
-% Typical, 21$-$50&377&45.72&2.97&40$-$58&45\\
-% Late, $>$50&26&41.85&1.56&40$-$45&42\tablenote{The no. of wells for all samples was 384. Genotypes were
-% determined by mass spectrometric assay. The $m_t$ value indicates the
-% average number of wells positive for the over represented allele.}
-% \\
-% \hline
-% \end{tabular}
-% \end{table}
-
-% \begin{table*}[ht]
-% \caption{Summary of the experimental results}
-% \begin{tabular*}{\hsize}
-% {@{\extracolsep{\fill}}rrrrrrrrrrrrr}
-% \multicolumn{3}{l}{Parameters}&
-% \multicolumn{5}{c}{Averaged Results}&
-% \multicolumn{5}{c}{Comparisons}\cr
-% \hline
-% \multicolumn1c{$n$}&\multicolumn1c{$S^*_{MAX}$}&
-% \multicolumn1c{$t_1$}&\multicolumn1c{\ $r_1$}&
-% \multicolumn1c{\ $m_1$}&\multicolumn1c{$t_2$}&
-% \multicolumn1c{$r_2$}&\multicolumn1c{$m_2$}
-% &\multicolumn1c{$t_{lb}$}&\multicolumn1c{\ \ $t_1/t_2$}&
-% $r_1/r_2$&$m_1/m_2$&
-% $t_1/t_{lb}$\cr
-% \hline
-% 10\tablenote{Stanford Synchrotron Radiation Laboratory (Stanford University,
-% Stanford, CA)}&1\quad &4&.0007&4&4&.0020&4&4&1.000&.333&1.000&1.000\cr
-% 10\tablenote{$R_{\rm FREE}=R$ factor for the $\sim 5$\% of the randomly
-% chosen unique ref\/lections not used in the ref\/inement.}&5\quad &50&.0008&8&50&.0020&12&49&.999&.417&.698&1.020\cr
-% 100\tablenote{Calculated for all observed data}&20\quad &2840975&.0423&95&2871117&.1083&521&---&
-% .990&.390&.182&---\ \ \cr
-% \hline
-% \end{tabular*}
-% \end{table*}
-
-% \appendix[Estimating the Spectral Norm of a Matrix]
-% In this appendix we describe a method for the estimation of the spectral norm
-% of matrix $A$. The method does not require access to the individual
-% entries of $A$; it requires only applications of $A$ and $A$* to vectors.
-% It is a version of the classical power method. Its probabilistic
-% analysis summarized below was introduced fairly recently in refs. 13
-% and 14. This appendix is included here for completeness.
-
-% \appendix
-% This is an example of an appendix without a title.
-
-% \begin{acknowledgments}
-% algo
-% This work was partially supported by 
-% Spanish Ministry of Science and Technology Grant BFM2002-02042 (to D.C. and
-% J.L.R.) and by National Science Foundation Grand DMS-0245242 (to C.F.).
-% \end{acknowledgments}

### 2014-04-02 paper/refactor.tex
results text added

@@
 \input{handpicked_table}
+\newpage
+
 \section{Results}
@@
 
-ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT
+On $Top-senses$ table we can observe that some senses like local\_anesthetic was matched on Whats to be done? as first result. \\
+Also on State and revolution Marx was matched with a United States comedian and a similar result we got with Berstein that was matched with a composer, however in the case of Engels it was matched to a socialist who wrote the Communist Manifesto with Karl Marx.
+\\
+$Similarities$ tables shows that, in most of the works, synsets $lion$, $sugar$, $hair$, $car$ and $television\_receiver$ had a lower similarity on most of the works. \\
+One strange result was $Hair$ that matched second in similarity score in Imperialism, the Highest St....
 

### 2014-04-02 paper/refactor.tex
some fixes for tables ordering and text typos on results

--- 2014-04-02 paper/refactor.tex
@@
 
-%\subsubsection{Top senses for selected works}
 \input{results}
 
-ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT
+In Top Senses table we can observe that some senses like local\_anesthetic was matched on Whats to be done? as first result. \\
+Also in State and revolution Marx was matched with a United States comedian and a similar result we got with Berstein that was matched with a composer, however in the case of Engels it was matched to a socialist who wrote the Communist Manifesto with Karl Marx.
+\\
+$Similarities$ tables shows that, in most of the works, synsets $lion$, $sugar$, $hair$, $car$ and $television\_receiver$ had a lower similarity in most of the works. \\
+One strange result was $Hair$ that matched second in similarity score in Imperialism, the Highest St....
 
 %\subsubsection{Similarities with chosen concepts}
+\newpage
 \input{results_sim_tables}
-
-\newpage
-
-\subsubsection{Observations}
 

### 2014-04-03 paper/refactor.tex
Move acknowledgments upwards.
Fix layout.
Definitively fix layout...I hope.

@@
 \usepackage{colortbl}
+\usepackage{dblfloatfix}
 \newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
@@
 But this weighted set of top words has the problem of polysemy, typical in the field of nlp.
-Polysemy occurs when a term has more than one sense or meaning, for example: the term 'bank' can refer to a financial institution or to a land formation, thus, it is polysemic.
+Polysemy occurs when a term has more than one sense or meaning, for example: the term `bank' can refer to a financial institution or to a land formation, thus, it is polysemic.
 In order to resolve this limitation, we implement a basic algorithm of word-sense disambiguation based on wordnet's synsets and we apply it over the top words, using as disambiguation context the whole document.
@@
 \subsubsection{Word-senses evaluation set}
+\input{handpicked_table}
 
@@
 
-\input{handpicked_table}
-\newpage
-
 \section{Results}
@@
 %\subsubsection{Similarities with chosen concepts}
-\newpage
 \input{results_sim_tables}
@@
 
-\input{apendices}
-% *SynsetAnalyzer
-%   *Synset
-%   *path, lch, wup
-% *judge_word
-% *judge_doc
-% *judge_year
-% Dado un conjunto de palabras, definimos la distancia de una palabra a este conjunto como 
-%
-
 \section{Acknowledgments}
 Thanks to \hyperlink{https://www.marxists.org}{Marxists Internet Archive} for helping us retrieve the Lenin's complete works.
+
+\input{apendices}
 

### 2014-04-04 paper/refactor.tex
Rewrite formulas.
more text explaining results

@@
 \begin{equation}
-  WSD(w_1), WSD(w_2), \ldots, WSD(w_n)
+  TS(T) = \{ WSD(w_1), WSD(w_2), \ldots, WSD(w_n) \}
 \end{equation}
@@
 \begin{equation}
-  similarity(w, T) = max(path\_similarity(w, top\_senses_n(T)))
+  sim(s, T) = max \left\{ path(s,s'), s' \in TS(T) \right\}
 \end{equation}
@@
 
-In Top Senses table we can observe that some senses like local\_anesthetic was matched on Whats to be done? as first result. \\
-Also in State and revolution Marx was matched with a United States comedian and a similar result we got with Berstein that was matched with a composer, however in the case of Engels it was matched to a socialist who wrote the Communist Manifesto with Karl Marx.
+First we examined the results after applying the $WSD$ algorithm (Top Senses Table).
+We observed that most of the senses found by our algorithm were the senses related to the works, except for some of them.\\
+
+On "Whats to be done?" we observed that local\_anesthetic was matched as first result. \\
+For "State and revolution" we noticed that Marx was matched with a United States comedian and Berstein matched with a composer from the States.
+However in the case of Engels, another pronoun, it was matched to a socialist who wrote the Communist Manifesto with Karl Marx.
 \\
-$Similarities$ tables shows that, in most of the works, synsets $lion$, $sugar$, $hair$, $car$ and $television\_receiver$ had a lower similarity in most of the works. \\
-One strange result was $Hair$ that matched second in similarity score in Imperialism, the Highest St....
+
+We then calculated the similarities of our handpicked synsets for each work.
+Since our results are ordered by the similarity in general we observed that the synsets $lion$, $sugar$, $hair$, $car$ and $television\_receiver$ scored lower in most of the works, with some particular cases.
+\\
+
+Our results shows that "Imperialism, the Highest Stage of Capitalism" have some synset that scored irregular values.
+This was the case for $hair$ which matched second in similarity and that $imperialism$ scored very low.
+The result for $imperialism$ was surprising since it is a word contained in the work title.
+Also $capitalism$ wasn't at top of the list for this work.\\
+
+As for "Materialism and Empirio-Criticism" we want to point that $philosopy$ is in the top $3$.
+For the synsets $lion$, $sugar$, $hair$, $car$ and $television\_receiver$ they scored low values in  "State and Revolution", "Materialism and Empirio-Criticism", "What Is To Be Done?" and "The Agrarian Programme of Social-Democracy in the First Russian Revolution".
 

### 2014-04-04 paper/refactor.tex
fix typo

@@
 To achieve this, we defined and implemented a simple metric distance between a word-sense and a document and confronted this metric using a evaluation set of word-senses against a reduced set of  documents with well known topics.
-During this work, we generated an indexed database of Lenin's complete works from a web site\cite{LENIN} and we applied a series of syntactic, semantic and lexicographic tools in order to model the similarity between a document and a word-sense.
+During this work, we generated an indexed database of Lenin's complete works from a web site\cite{LENIN} and we applied a serie of syntactic, semantic and lexicographic tools in order to model the similarity between a document and a word-sense.
 We applied information value\cite{DARWIN} and a simple algorithm of word sense disambiguation\cite{LESK} based on Wordnet\cite{WORDNET} in order to generate the \emph{top senses} (or principal senses) of a document.

### 2014-04-04 paper/refactor.tex
some changes and references in result text

@@
 \begin{equation}
+\label{eq:sim}
   sim(s, T) = max \left\{ path(s,s'), s' \in TS(T) \right\}
@@
 \section{Results}
-This section is divided in two: first, we present the \textit{top senses} of the documents listed in ``Text corpus''; second, we present the similarities between the documents and the word-senses evaluation set.
+In this section we present and comment the results divided in two groups of observational data.
+
+In Table 2, we present the \textit{top senses} of the documents listed in ``Text corpus'', obtained using the procedure we describe in previous sections.
+Each $top-sense$ is ordered according to the information value score that we obtained previous to apply the $WSD$ algorithm.
+
+In the group of tables named Table 3, we present the similarities between the documents and the word-senses evaluation set based on the similarity function described in equation~\ref{eq:sim}, in the previous section.\\
 
@@
 First we examined the results after applying the $WSD$ algorithm (Top Senses Table).
-We observed that most of the senses found by our algorithm were the senses related to the works, except for some of them.\\
+We observed that most of the senses found by our algorithm were the senses related to the works, except for some of them.
 
-On "Whats to be done?" we observed that local\_anesthetic was matched as first result. \\
+On "Whats to be done?" we observed that local\_anesthetic was matched as first result.
+
 For "State and revolution" we noticed that Marx was matched with a United States comedian and Berstein matched with a composer from the States.
@@
 Since our results are ordered by the similarity in general we observed that the synsets $lion$, $sugar$, $hair$, $car$ and $television\_receiver$ scored lower in most of the works, with some particular cases.
-\\
 
